### 2019-06-19 thesis-draft.tex
Initial Overleaf Import

%\documentclass[12pt,twoside]{report}
\documentclass[12pt]{report}

% note that the document can be single or double sided.

\usepackage[online]{thesis-style}
%\usepackage{thesis-2e}

\begin{document}

    \title{How to Write Theses\\
            With Two Line Titles}
    \author{John Henry Candidate}
    \dept{Intelligent Design}
    \principaladviser{William Paley}
    \firstreader{Jody Green}
    \secondreader{Jan BigBooty\\(Astrology)}

    \beforepreface
    \prefacesection{Preface}
        This thesis tells you all you need to know about life, the
        universe, and everything.

\newpage

However everything should be taken with a grain of salt.

    \prefacesection{Acknowledgements}
        I would like to thank my mother and the little green men from
        Mars.

    \afterpreface

    \chapter{Introduction}

    1 In the beginning {\bfseries God} created the heaven and the earth.

    2 And the earth was without form, and void; and darkness was upon
    the face of the deep. And the Spirit of God moved upon the face of
    the waters.

    3 And God said, Let there be light: and there was light.

    4 And God saw the light, that it was good: and God divided the
    light from the darkness.

    5 And God called the light Day, and the darkness he called Night.
    And the evening and the morning were the first day.

    \chapter{Conclusions}

    18 For I testify unto every man that heareth the words of the
    prophecy of this book, If any man shall add unto these things, God
    shall add unto him the plagues that are written in this book:

    19 And if any man shall take away from the words of the book of
    this prophecy, God shall take away his part out of the book of
    life, and out of the holy city, and from the things which are
    written in this book.

    \appendix
    \chapter{A Long Proof}

\section{Qoh.1}

1 The words of the Preacher, the son of David, king in Jerusalem.

2 Vanity of vanities, saith the Preacher, vanity of vanities; all is
vanity.

3 What profit hath a man of all his labour which he taketh under the
sun?

4 One generation passeth away, and another generation cometh: but the
earth abideth for ever.

5 The sun also ariseth, and the sun goeth down, and hasteth to his
place where he arose.

6 The wind goeth toward the south, and turneth about unto the north;
it whirleth about continually, and the wind returneth again according
to his circuits.

7 All the rivers run into the sea; yet the sea is not full; unto the
place from whence the rivers come, thither they return again.

8 All things are full of labour; man cannot utter it: the eye is
   not
   satisfied with seeing, nor the ear filled with hearing.

9 The thing that hath been, it is that which shall be; and that
   which is done is that which shall be done: and there is no new
   thing
   under the sun.

10 Is there any thing whereof it may be said, See, this is new?
   it
   hath been already of old time, which was before us.

11 There is no remembrance of former things; neither shall there
   be
   any remembrance of things that are to come with those that shall
   come
   after.

12 I the Preacher was king over Israel in Jerusalem.

13 And I gave my heart to seek and search out by wisdom
   concerning
   all things that are done under heaven: this sore travail hath God
   given to the sons of man to be exercised therewith.

14 I have seen all the works that are done under the sun; and,
   behold, all is vanity and vexation of spirit.

15 That which is crooked cannot be made straight: and that which
   is
   wanting cannot be numbered.

16 I communed with mine own heart, saying, Lo, I am come to great
   estate, and have gotten more wisdom than all they that have been
   before me in Jerusalem: yea, my heart had great experience of
   wisdom
   and knowledge.

17 And I gave my heart to know wisdom, and to know madness and
   folly: I perceived that this also is vexation of spirit.

18 For in much wisdom is much grief: and he that increaseth
   knowledge increaseth sorrow.

\section{Qoh.2}

1 I said in mine heart, Go to now, I will prove thee with mirth,
   therefore enjoy pleasure: and, behold, this also is vanity.

2 I said of laughter, It is mad: and of mirth, What doeth it?

3 I sought in mine heart to give myself unto wine, yet
   acquainting
   mine heart with wisdom; and to lay hold on folly, till I might see
   what was that good for the sons of men, which they should do under
   the
   heaven all the days of their life.

4 I made me great works; I builded me houses; I planted me
   vineyards:

5 I made me gardens and orchards, and I planted trees in them of
   all
   kind of fruits:

6 I made me pools of water, to water therewith the wood that
   bringeth forth trees:

7 I got me servants and maidens, and had servants born in my
   house;
   also I had great possessions of great and small cattle above all
   that
   were in Jerusalem before me:

8 I gathered me also silver and gold, and the peculiar treasure
   of
   kings and of the provinces: I gat me men singers and women singers,

   and the delights of the sons of men, as musical instruments, and
   that
   of all sorts.

9 So I was great, and increased more than all that were before me
   in
   Jerusalem: also my wisdom remained with me.

10 And whatsoever mine eyes desired I kept not from them, I
   withheld
   not my heart from any joy; for my heart rejoiced in all my labour:
   and
   this was my portion of all my labour.

11 Then I looked on all the works that my hands had wrought, and
   on
   the labour that I had laboured to do: and, behold, all was vanity
   and
   vexation of spirit, and there was no profit under the sun.

12 And I turned myself to behold wisdom, and madness, and folly:
   for
   what can the man do that cometh after the king? even that which
   hath
   been already done.

13 Then I saw that wisdom excelleth folly, as far as light
   excelleth
   darkness.

14 The wise man's eyes are in his head; but the fool walketh in
   darkness: and I myself perceived also that one event happeneth to
   them
   all.

15 Then said I in my heart, As it happeneth to the fool, so it
   happeneth even to me; and why was I then more wise? Then I said in
   my
   heart, that this also is vanity.

16 For there is no remembrance of the wise more than of the fool
   for
   ever; seeing that which now is in the days to come shall all be
   forgotten. And how dieth the wise man? as the fool.

17 Therefore I hated life; because the work that is wrought under
   the sun is grievous unto me: for all is vanity and vexation of
   spirit.

18 Yea, I hated all my labour which I had taken under the sun:
   because I should leave it unto the man that shall be after me.

19 And who knoweth whether he shall be a wise man or a fool? yet
   shall he have rule over all my labour wherein I have laboured, and 
   wherein I have shewed myself wise under the sun. This is also
   vanity.

20 Therefore I went about to cause my heart to despair of all the
   labour which I took under the sun.

21 For there is a man whose labour is in wisdom, and in
   knowledge,  
   and in equity; yet to a man that hath not laboured therein shall he
   leave it for his portion. This also is vanity and a great evil.

22 For what hath man of all his labour, and of the vexation of
   his
   heart, wherein he hath laboured under the sun?

23 For all his days are sorrows, and his travail grief; yea, his
   heart taketh not rest in the night. This is also vanity.

24 There is nothing better for a man, than that he should eat and

   drink, and that he should make his soul enjoy good in his
   labour. This
   also I saw, that it was from the hand of God.

25 For who can eat, or who else can hasten hereunto, more than I?

26 For God giveth to a man that is good in his sight wisdom, and
   knowledge, and joy: but to the sinner he giveth travail, to gather
   and
   to heap up, that he may give to him that is good before God. This
   also
   is vanity and vexation of spirit.

%\nocite{astl2,perry1,pollardsag1}
\nocite{*}

    \bibliographystyle{plain}
%    \bibliography{suthesis}
   \bibliography{reference}

\onlinesignature

\end{document}

### 2019-06-19 chapters/introduction/introduction.tex
Updates from Overleaf

Machine learning has gained rapid popularity in the past decade and different sectors like healthcare, finance, retail, etc. are using machine learning to provide better products and services. This rising popularity has created a demand for better implementation of the state-of-the-art algorithms in order to implement more complex and sophisticated use cases. Machine learning has been around for a long time now and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.  While developing and training a machine learning model, the developers rely on the accuracy of the libraries to produce best results. The aim is to create a model that makes the best predictions.
Conventionally, oracles have been used to test the correctness of a program. Oracles provide expected values against which the output from the program can be compared and validated. Lack of reliable oracles for testing machine learning algorithms makes it very hard to test the accuracy of such programs. This problem is called the oracle problem\cite{Weyuker}. Oracle problem arises when either:
\begin{itemize}
  \item An oracle does not exist, or,
  \item An oracle can theoretically exist but it is computationally too expensive to determine the output.
\end{itemize}
Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Murphy}. Davis and Weyuker describe these set of programs as \enquote{Programs which were written in order to determine the answer in the first place. There would be no need to write such programs if the correct answer were known}\cite{Davis1981}. Most machine learning programs fall under this category as they are written in order to predict the correct answers in the first place. Several techniques can be employed to verify the correctness of such programs. One of the most popular methods being the use of pseudo-oracles. To use pseudo-oracle two or more implementations of the algorithm are independently developed to fulfill the same specification. They are run on the same input test data and the outputs from them are then compared. If the outputs match it can be asserted that the original results are according to the specification. This kind of testing is often referred to as dual coding. However, this technique introduces a significant overhead in terms of implementing two or more versions of the same algorithm and testing their outputs and is more suitable for mission-critical systems\cite{Weyuker}.\newline

Another testing methodology called Metamorphic testing introduced by Chen et. al can be used for testing ML programs instead. It addresses some of these problems while testing the \enquote{non-testable programs} without significant overhead. The idea behind Metamorphic testing is that it easier to compare and understand the relationship between outputs than to compare and understand input-output behavior. For a prototype example: To test a program which implements the $sin$ function, the output from the program for value of $sin$ at $x$ could be compare to the real value of $sin(x)$ or, the mathematical property of $sin(x) = sin(\pi-x)$ can be exploited to verify the correct implementation of $sin$ function. Such relation $(sin(x) = sin(\pi-x))$ are called Metamorphic Relations. Metamorphic testing makes use of metamorphic relations where an input relation is used to generate new input test cases from existing test data, and an output relation is used to compare the outputs produced by the test cases.\newline
In this paper, we will explore the types of guarantees one can expect a machine learning model to possess because of the properties that the underlying algorithm of the implementation.
% In particular we will look at google's tensorflow.
% Dataset coverages
% and
% We propose applying MT as a way of testing and verifying ML programs.

%ML programs importance and them following under non testable. Need for Testing ML programs.  Why current techniques are not enough and introduce MT. Use MT for testing some popular implementation of ML.

In this study we will answer the following research questions:
\begin{enumerate}
  \item How does metamorphic testing compare to other testing methodologies for testing machine learning algorithms?
  %\item Can we quantify reliability of predictions made by machine learning algorithms?
  \item How sensitive are the predictions made by ML algorithms to the change in input data?
  \item At what point does the algorithm fail to produce correct classifications on distorted inputs?
\end{enumerate}
%Point of failure. by humans& computer. (visual inpection)
%Properties of ML affect
%

### 2019-06-19 chapters/litReview/litReview.tex
Updates from Overleaf

% \section{Software testing}
% Testing is an essential activity in software engineering. In the simplest terms, it amounts to observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions. Testing is widely used in industry for quality assurance. Software testing is a broad term encompassing a wide spectrum of different activities, from the testing of a small piece of code by the developer (unit testing), to the customer validation of a large information system (acceptance testing), to the monitoring at run-time of a network-centric service-oriented application.
\section{Testing in the Presence of Uncertainty \cite{Elbaum2014}}
Uncertainty is present in most systems that are built today, whether introduced by human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, uncertainty increases the ambiguity of what constitutes the input space and what is deemed as acceptable behavior, which are two key attributes of a test. In this paper, the authors explore the potential directions for dealing with uncertainty during testing.
Two ways to deal with uncertainty are to exercise more control over the inputs provided to the unit under test and to constrain the testing environment. Some uncertainties like those present in systems that deal with the physical world are aleatoric; that is, they cannot be known precisely because of their inherent variability and noise. Epistemic uncertainties are those that could be resolved with enough effort (e.g., over-engineering a sensor-based system to minimize inference errors about the environment)— and resolving them are becoming more numerous and costly, as the systems are becoming increasingly complex. A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time. The authors provide a set of requirements for adequate handling of uncertainty in testing:
\begin{enumerate}
  \item Specifying input distributions and generating inputs with the help of the distributions instead of using discrete inputs.
  \item Probabilistic oracles that can help distinguish acceptable from unacceptable misbehaviors. These models will also provide the specification of the likelihood of results.
  \item Richer models to represent system and environment uncertainty, so that uncertainties can be connected to test requirements and outcomes. This will help with automated uncertainty quantification.
\end{enumerate}
Not all systems will impose these requirements, and not all techniques will satisfy them. In fact, they expect it will be necessary to develop a suite of techniques for dealing with uncertainty, selected according to system characteristics and the particular forms of uncertainty the system embodies and based on the use of stochastic models and quantitative analyses.

\section{On Testing Non-testable Programs \cite{Weyuker}}
The current testing research activities fall into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}
An oracle is a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts. Programs for which such oracles do not exist are called 'non-testable'. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.
Non-testable programs can be usually classified into three categories:
\begin{enumerate}
  \item Programs that were written to determine the correct answer.
  \item Programs that produce a lot of outputs such that it is hard to verify all of them.
  \item Programs where tester have a misconception (tester believes that he has the oracle even though he might not).
\end{enumerate}
In absence of oracles, the ideal way to test a program is through Pseudo Oracles/Dual Coding. But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation. A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors.
Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}
Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer. In such cases, we make use of partial oracles. It is relatively easier to test the systems on simpler inputs for which the output is known. There is rarely a single correct answer in these types of computations. Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution. The authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

### 2019-06-19 chapters/litReview/metamorphicTesting.tex
Updates from Overleaf

\section{Metamorphic Testing}
	\subsection{A Survey on Metamorphic Testing \cite{Segura2016}}
		Segura et al. did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer four important research questions:
		\begin{enumerate}
			\item RQ1: What improvements to the technique have been made?
			\item RQ2: What are its known application domains?
			\item RQ3: How are experimental evaluations performed?
			\item RQ4: What are the future research challenges?
		\end{enumerate}

		\subsubsection{Properties of good metamorphic relations}
			To answer the first question they first studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
			\begin{itemize}
				\item A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.
				\item Metamorphic relations that make execution of the follow–up test case as different as possible from the source test case.
				\item Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.
				\item Formally described metamorphic relations. In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow–up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
			\end{itemize}

		\subsubsection{Construction of metamorphic relations}
		Composition of Metamorphic Relations (CMR) can be used to construct new metamorphic relations by combining several existing relations. The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions. Two metamorphic relations are considered “compositable” if the follow-up test cases of one of the relations can always be used as source test case of the other. The composition is sensitive to the order of metamorphic relations and generalizable to any number of them. Determining whether two metamorphic relations are composable is a manual task. Chen et al. \cite{Chen2016} presented a specification–based tool called METRIC for the identification of metamorphic relations. In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames. The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.

		\subsubsection{Generation of source test cases}
		Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations. Given the source code of a program written in C and a metamorphic relation, AMT tries to find test cases that violate the relation. The underlying method is based on the translation of the code into an equivalent constraint logic program over finite domains. Other techniques like “special values” and random testing can also be used as source test cases for metamorphic testing. Genetic algorithms have also been used for the selection of source test cases, to maximize the paths traversed in the program under test.

		\subsubsection{Execution of metamorphic test cases}
		The execution of a metamorphic test case is typically performed in two steps. First, a follow–up test case is generated by applying a transformation to the inputs of a source test case. Second, source and follow–up test cases are executed, checking whether their outputs violate the metamorphic relation. \par
		Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively. In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow–up test case of each metamorphic relation as the source test case of the next metamorphic relation. \par
		Murphy et al. \cite{Murphy2009} presented a framework named Amsterdam for the automated application of metamorphic testing. The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file. Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.
		\subsubsection{Application domains}
		To answer the second question the authors selected the papers where the main objective was a case study. They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems. They also found some other domains of application like financial software, optimization programs, and encryption programs.
		Some of the research challenges identified by the authors are:
		\begin{itemize}
			\item Lack of guidelines, with step–by–step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
			\item Prioritisation and minimisation of metamorphic relations: It is worth mentioning that test case minimisation is a NP–hard problem and therefore heuristic techniques should be explored.
			\item Generation of likely metamorphic relations.
			\item Combination of metamorphic relations.
			\item Automated generation of best possible source test cases.
			\item Lack of metamorphic testing tools.
		\end{itemize}

	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
		In this paper the authors have demonstrated the usefulness of metamorphic testing in assessing the quality of applications without test oracles. Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format. The authors presented an approach called ``Automated Metamorphic System Testing'' to automate the metamorphic testing by considering the system as a blackbox and checking if the metamorphic properties holds after execution of the system. They also present another approach “Heuristic Metamorphic Testing” to reduce false positives and address some non-determinism. Unlike in the previous papers, here, the authors are focusing to improve the metamorphic testing technique itself. They list some benefits of using metamorphic testing: it can be used on broader domain of applications that display metamorphic properties, and it treats the application under test as a black box and does not require detailed understanding of the source code. They then list some of the limitations of using metamorphic testing:
		\begin{itemize}
			\item	Manual transformation of large input data can be laborious and error-prone. They need special tools to transform the input.
			\item Comparing the outputs(some of which may be very large and/or in not human-readable format) of the input data can be tedious.
			\item Floating point calculations can also lead to imprecision even though the calculations are programmatically correct.
			\item Coming up with the initial test-cases is also a challenge as some defects may only occur under certain inputs.
		\end{itemize}

		Automated Metamorphic System Testing: This technique can be used to test the application in development environment as well as in production as long as the users are only provided the output from the original execution and not the result from transformed input. In this model $i)$ Metamorphic properties are specified by the tester and applied to the input. $ii)$ The original input is fed into the application which is treated as a black-box and a transformation of the input is also generated. $iii)$ That transformed input is fed into a separate instance of the application running in a separate sandbox. $iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
		Tester need not write any code and only needs to specify the metamorphic properties. They don’t need to know the source code or other implementation details.
		Amsterdam framework: The metamorphic properties are specified using XML file. The specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.\par
		Heuristic Metamorphic testing: This method allows for small differences in outputs, in a meaningful way according to the application being used to address the problems of false positives and non-determinism. Imprecisions in floating point calculation and representation of irrational number such as may result in failure of metamorphic testing even if the implementation is correct. If two outputs are close enough they are considered the same. The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.

### 2019-06-19 chapters/litReview/mlAlgo.tex
Updates from Overleaf

\section{Overview of Machine Learning Algorithms}
\subsection{Supervised Sequence Labelling with Recurrent Neural Networks \cite{Graves}}
Artificial neural networks (ANNs) were originally developed as mathematical models of the information processing capabilities of biological brains. Although it is now clear that ANNs bear little resemblance to real biological neurons, they enjoy continuing popularity as pattern classifiers. The basic structure of an ANN is a network of small processing units, or nodes, joined to each other by weighted connections. In terms of the original biological model, the nodes represent neurons, and the connection weights represent the strength of the synapses between the neurons. The network is activated by providing an input to some or all of the nodes, and this activation then spreads throughout the network along the weighted connections. ANNs without cycles are referred to as feedforward neural networks (FNNs). Well known examples of FNNs include perceptrons, radial basis function networks, Kohonen maps and Hopfield nets. The most widely used form of FNN is the multilayer perceptron(MLP). It has been proven that an MLP with a single hidden layer containing a sufficient number of nonlinear units can approximate any continuous function on a compact input domain to arbitrary precision. For this reason MLPs are said to be universal function approximators.
At each unit in a layer the activation function $\theta_h$ is applied, yielding the final activation $b_h$ of the unit. The most common choices for neural network activation function are the hyperbolic tangent and the logistic sigmoid. An important feature of both tanh and the logistic sigmoid is their nonlinearity. Nonlinear neural networks are more powerful than linear ones since they can, for example, find nonlinear classification boundaries and model nonlinear equations. Another key property is that both functions are differentiable, which allows the network to be trained with gradient descent. Because of the way they reduce an infinite input domain to a finite output range, neural network activation functions are sometimes referred to as squashing functions. The output vector $y$ of an MLP is given by the activation of the units in the output layer. The network input $a_k$ to each output unit $k$ is calculated by summing over the units connected to it, exactly as for a hidden unit. Both the number of units in the output layer and the choice of output activation function depend on the task the network is applied to. For classification problems with $K > 2$ classes, the convention is to have $K$ output units, and normalise the output activations with the softmax function to obtain the class probabilities which is also known as a multinomial logit model.

### 2019-06-19 chapters/litReview/synthesisMatrix.tex
Updates from Overleaf

\setenumerate{leftmargin=17pt, labelindent=0pt, itemindent=0pt, topsep=0pt, noitemsep}

\begin{singlespace}
 \begin{longtable}[c]{| p{3cm} | p{5.5cm} | p{3cm} | p{3cm} |}
  \hline
  %  \multicolumn{4}{|c|}{Begin of Table}\\
  %
  %  \hline

  Paper & MRs used & Algorithms/Test Cases & Result of MT \\
  \hline
  \endfirsthead
  \hline
  \multicolumn{4}{|c|}{Continuation of Table \ref{long}}                                                                       \\
  \hline
  Paper & MRs used & Algorithms/Test Cases & Result of MT \\
  \hline
  \endhead

  Application of Metamorphic Testing to Supervised Classifiers               &
  MRs for classification algorithms:
  \begin{enumerate}
   % \begin{itemize}[leftmargin=10pt, labelindent=0pt, itemindent=0pt, itemsep=0em]
   \item Consistency with affine transformation.
   \item Permutation of class labels.
   \item Permutation of attributes.
   \item Addition of uninformative/informative attributes.
   \item Consistency with re-prediction.
   \item Addition of training samples.
   \item Addition of classes by duplicating/re-labeling samples.
   \item Removal of classes/samples.
         % \end{itemize}
  \end{enumerate}                                                                           &
  Package: Weka.\par
  \medskip
  Test Case: Randomly generated training and test data. The randomly generated data model does not encapsulate any domain knowledge.                                                             &
  Only a subset of MRs were a necessary property of the corresponding algorithm.\par\medskip
  Several MRs violated NBC algorithms.\par\medskip
  In the case of kNN algorithm, none of the necessary MRs were violated.
  \\

  \hline

  Dataset Coverage for Testing Machine Learning Computer Programs            &
  MR for Pseudo Oracles:
  \begin{enumerate}
   \item Reorder Data Points
   \item Reverse Labels
   \item Reorder Attributes
   \item Add a Constant Attribute
   \item Change Attribute Values
  \end{enumerate}
  \smallskip
  MR for Dataset Generation:
  \begin{enumerate}
   \item Reduce Margin
   \item Insert Noise
   \item Insert Separable
   \item Inconsistent Labels
  \end{enumerate}                                                  &
  Developed a Java program of an SVM classifier\par\medskip
  LIBSVM, used as a pseudo oracle.\par\medskip
  Test Case: Java pseudo random number generator.                            &
  The Java program passed the tests in terms of this criteria. \par\medskip
  When the model constructor component was tested it had some faults that the proposed method identifies.                      \\

  \hline

  Properties of Machine Learning Applications for Use in Metamorphic Testing &
  MartiRank:
  \begin{enumerate}
   \item Additive
   \item Multiplicative
   \item Permutative
   \item Invertive
   \item Inclusive
   \item Exclusive
   \item SVM-Light:
   \item Exclusive
   \item Inclusive
   \item Permutative
  \end{enumerate}
  \par\medskip
  PAYL:
  \begin{enumerate}
   \item Additive
   \item Multiplicative
   \item Permutative
   \item Invertive
   \item Inclusive
   \item Exclusive
  \end{enumerate}                                                  &
  Packages: MartiRank, SVM-Light, PAYL.                                      &
  MartiRank: the implementation produced inconsistent results when a negative label existed.\par\medskip
  SVM-Light not tested because it is inefficient to run the quadratic optimization algorithm on the full data set.\par\medskip
  PAYL exhibits the same six metamorphic properties as MartiRank.                                                              \\

  \hline

  \caption{Synthesis Matrix.\label{long}}
 \end{longtable}

 \begin{longtable}[c]{| p{3cm} | p{4cm} | p{3.5cm} | p{4cm} |}
  \hline
  %  \multicolumn{4}{|c|}{Begin of Table}\\
  %
  %  \hline

  Paper & Domain and Algo tested  & MRs investigated & New Innovative \\
  \hline
  \endfirsthead
  \hline
  \multicolumn{4}{|c|}{Continuation of Table \ref{long}}                                                                       \\
  \hline
  Paper & Domain and Algo tested  & MRs investigated & New Innovative \\
  \hline
  \endhead
  \caption{Synthesis Matrix.\label{long}}
  \endfoot

  Semi-Proving: An Integrated Method for Program Proving, Testing, and Debugging             &
  “Siemens suite of programs” specifically “replace program”: performs regular expression matching and substitutions.                                                                           &
  Given the text 'ab', replacing 'a' with 'x' is equivalent to replacing non-'b' with 'x'. \par\medskip
  'char' and '[char]' are equivalent with the exception of a few wildcards. \par\medskip
  Regular expressions that involve square brackets are equivalent. \par\medskip
  Use '?*' to match the entire input string.                                                             &
  Proof of concept. \par\medskip
  Supports automatic debugging through the identification of constraints for failure-causing inputs.
  \\

  \hline

  Metamorphic Testing Integer Overflow Faults of Mission Critical Program: A Case Study             &
  Integer Overflow Faults in TCAS: tcas.c                                                                           &
  Additive                                                            &
  Proof of concept. \par\medskip
  Formal definition of MR, original test case, follow-up test case, input relation and output relation. \par\medskip
  TCAS case study for demonstration.
  \\

  \hline
  Metamorphic Testing for Software Quality Assessment: A Study of Search Engines             &
  Search engines:
  \begin{enumerate}
    \item Google search
    \item Baidu
    \item Bing
  \end{enumerate}                                                                        &
  \begin{enumerate}
    \item MPSite
    \item MPTitle
    \item MPReverseJD
    \item SwapJD
    \item Top1Absent
  \end{enumerate}                                                         &
  Validation, verification as well as quality assessment.
  \\

  \hline

  Automatic System Testing of Programs without Test Oracles             &
  Machine learning.
  \begin{enumerate}
    \item SVM: Sequential Minimal Optimization (SMO).
    \item C4.5
    \item MartiRank: Area Under the Curve
  \end{enumerate}                                        &
  \begin{enumerate}
    \item Permute
    \item Multiply
    \item Add
    \item Negate
  \end{enumerate}                                          &
  Heuristic Metamorphic Testing.\par\medskip
  Automated Metamorphic System Testing.  \\

  \hline

  Metamorphic Testing and Beyond             &
  A laplace equation with Dirichlet boundary Conditions: “alternating direction implicit” method                                        &
  Beyond identity relations: Convergence                                          &
  Selecting useful MRs. \par\medskip
  Stronger may not necessarily be better than weaker ones. \par\medskip
  Provides guidelines.  \\

  \hline

  A Metamorphic Testing Approach for Online Testing of Service-Oriented Software Applications             &
  service-oriented calculator: arithmetic operators                                        &
  \begin{enumerate}
    \item Commutative
    \item Associative
  \end{enumerate}                                         &
  Methodological steps for online and offline testing. \par\medskip
  MT for service oriented applications.  \\

  \hline

 \end{longtable}
\end{singlespace}

### 2019-06-19 chapters/litReview/testMLprog.tex
Updates from Overleaf

\section{Testing Machine Learning Programs}
\subsection{Properties of Machine Learning Applications for Use in Metamorphic Testing \cite{Murphy}}
In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. Non-testable programs can be tested in one of the two ways:
\begin{itemize}
  \item Creating multiple implementations of the same program and testing them on same inputs and comparing the results. If the outputs are not same then either of the implementations can contain error. This approach is called pseudo-oracle.
  \item In absence of multiple oracle, metamorphic testing can be used. In metamorphic testing, the input is modified using a metamorphic relation such that the two sets of input will generate similar outputs. If similar outputs are not observed then there must be a defect.
\end{itemize}
The main challenge with metamorphic testing is to come up with the metamorphic relations to transform inputs since such coming up with such relations require domain knowledge and/or familiarity with the implementation.
In this paper the authors seek to create a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning softwares. These set of properties can be applied to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications. The problem with some of the current machine learning frameworks like: Weka and Orange is that they compare the quality of results but don’t evaluate the correctness of the results. The authors apply metamorphic testing to three ML applications: MartiRank, SVM-Light, PAYL.
MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model. The algorithm then performs similar operations from the model on the test data to produce a ranking list. SVM-Light is an open-source implementation of SVM that also has a ranking mode. The authors also investigated an intrusion detection system called PAYL. PAYL is an unsupervised machine learning system. It’s dataset simply consist of TCP/IP network payloads(stream of bytes) without any label or classification.
Based on the analysis of MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model. Thus, adding a constant value to every attribute or multiplying each attribute with a positive number, should not affect the model and generate the same ranking as before. Thus, the metamorphic properties identified were: addition and multiplication. Applying the model on two sets of data, one of which created from the other, either by multiplying a positive number or, adding a constant number, should not change the ranking. Changing the order of examples should not affect the model or ranking since the algorithm sorts the inputs thus, MartiRank also has permutative metamorphic property. Multiplying the data by a negative constant value will create a new sorting order which can easily predicted. The only change to the model will be the sorting direction i.e. the algorithm will change the sorting direction but keep the sorting order intact. Thus, MartiRank also displays an invertive metamorphic property where the output can be predicted by taking the opposite of input. MartiRank also includes inclusive and exclusive metamorphic properties. Knowing the model can help predict the position of any new elements.

\subsection{Application of Metamorphic Testing to Supervised Classifiers \cite{Xie2009}}
Building on the previous paper, the authors explore the metamorphic relations based on expected behavior of given machine learning problems. They present a case study on Weka, a popular machine learning framework, which is also the foundation for computational science tools such as BioWeka in bioinformatics. In this paper the authors explore k-Nearest Neighbors and Naive Bayes classifier algorithms. Previously, they researched on Support Vector Machines.
In this paper the authors seek to identify the metamorphic relations for the two algorithms (kNN and NBC). NBC and kNN both calculates the mean and standard deviation of the input data. Thus, the metamorphic relations identified are:
Permuting the order of input data does not affect the mean or standard deviation.
Multiplying the data with -1 does not affect the standard deviation since, the deviation from the mean will still be the same.
Multiplying the data with some other positive number will increase the standard deviation by the same amount. Thus, the output will still be predictable.
The authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
\begin{enumerate}
  \item Consistency with affine transformation.
  \item Permutation of class labels.
  \item Permutation of attributes.
  \item Addition of uninformative/informative attributes.
  \item Consistency with re-prediction.
  \item Addition of training samples.
  \item Addition of classes by duplicating/re-labeling samples.
  \item Removal of classes/samples.
\end{enumerate}
Next, the authors introduce the notion of validation and verification. Validation refers to choosing the most appropriate algorithm to solve a problem. Verification refers to whether the implemented algorithm is correct or not. Current, software testing methods have not addressed the problem of validation and only focus on verification.
The authors then performed an experiment to verify the correctness of Weka. They created a set of random input data and used the above metamorphic relationships to generate another set of inputs. Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithm. It was observed that several MRs violated NBC algorithms. Violations in the MRs that are necessary properties imply defects in implementation. In the case of kNN algorithm, none of the necessary MRs were violated which means that there are no implementation error as per the testing.

\subsection{Dataset Coverage for Testing Machine Learning Computer Programs \cite{Nakajima2016}}
Recently, computer programs for Big Data analytics or statistical machine learning have become essential components of intelligent software systems. Test oracles are rarely available for them, and this unavailability of test oracles is known as the oracle problem. Machine learning programs are a typical instance of non-testable programs and are of the known unknowns type. Metamorphic testing (MT) is a method for tackling the oracle problem. Metamorphic relations (MR) play a role as pseudo oracles to check whether executions of the same program differ for two different test inputs. The test inputs are related by translation functions derived from metamorphic properties so that the relationship between the two results is predictable. If the results coincide with each other, the program behavior is relatively correct.
This paper studies the characteristics of the supervised learning classifiers (SUT).
Identifying Quasi-testable Core: A program component, function or procedure, is quasi-testable if we have appropriate pseudo oracles or metamorphic relations. The result of the program execution embodies uncertainty because the output is accompanied by the statistical classification performance. The classifier itself is non-testable. However, pseudo oracles with a MT can be used for testing.\par
Dataset Coverage: Test coverage is essential in software testing because it is a basis to measure how much of the SUT is checked with a set of the input test data. The graph coverage is the most popular model for software testing because it captures the structural characteristics of software artifacts, such as control-flows or data-flows of a computer program. The paper introduces the notion of dataset coverage to focus on the characteristics of the population distribution in the training dataset. However, complete coverage is not possible. The number of possible populations in datasets is also infinite.\par
SVM: A support vector machine (SVM)  is a supervised machine learning classifier. The support vectors lie on the dotted hyperplanes parallel to the separating hyperplane. The margin, the minimum gap between the supporting hyperplane and the separating hyperplane, is chosen to be maximum. The pseudo code is a common, abstract description of implemented SMO computer programs. Because SMO is an algorithm for solving the SVM optimization problem, it corresponds to the model constructor and is an abstract version of the quasi-testable core.\par
Main tasks:
\begin{itemize}
  \item Obtain pseudo oracles.
  \begin{itemize}
    \item MR for Pseudo Oracles: Various combinations of the dataset is obtained by reordering the dataset.
    \item MR for Dataset Generation: Dataset is increased to increase the population of the input dataset.
  \end{itemize}
  \item Generate data points that achieve the required dataset coverage: In order that the result is predictable, the population distribution of the initial dataset is simple enough to contain linearly separable data points. Then a series of tests with pseudo oracles that are obtained based on appropriate metamorphic properties is conducted. Then dataset is extended by adding new data points to calculate a new hyperplane.
\end{itemize}
A similar metamorphic testing approach can be applied to K-nearest neighbors and naive Bayes classifiers. Since testing the whole program at once is not always possible choosing a right SUT from a non-testable program has a large impact on testing activities.

### 2019-06-19 chapters/proposedWork/environment.tex
Updates from Overleaf

\section{Setting up the Test Environment}
% \subsection{Docker}
% For replication of results. Image can be downloaded from dockerhub. Attached volume for persisting data.
\subsection{Jupyter}
The Jupyter Notebook is an open-source web application that supports data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, etc. by allowing us to create and share documents that contain live code, equations, visualizations and narrative text. Jupyter allows for displaying the result of computation inline in the form of rich media (SVG, LaTeX, etc.). The Jupyter notebook combines two components:
\begin{itemize}
  \item \textbf{A web application}: a browser-based tool for interactive authoring of documents which combine explanatory text, mathematics, computations and their rich media output.
  \item \textbf{Notebook documents}: a representation of all content visible in the web application, including inputs and outputs of the computations, explanatory text, mathematics, images, and rich media representations of objects.
\end{itemize}
Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy. In this project, the codes are written in python notebook which can be accessed from http://github.com/.

\subsection{Tensorflow}
TensorFlow\textsuperscript{TM} is an open source software library developed within Google’s AI organization by the Google Brain team with a strong support for machine learning and deep learning. Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices. It is being used at a number of well known companies like Uber, Google, AMD, etc. for high performance numerical computation and machine learning. While TensorFlow is capable of handling a wide range of tasks, it is mainly designed for deep neural network models. It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}.

\subsection{MNIST Dataset}
The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 60,000 examples, and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is a good database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1 which contain binary images of handwritten digits. The original black and white (bilevel) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.

\subsubsection{Format of Dataset}
The data is stored in a very simple file format designed for storing vectors and multidimensional matrices. All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors. There are 4 files:
\begin{itemize}
  \item train-images-idx3-ubyte: training set images
  \item train-labels-idx1-ubyte: training set labels
  \item t10k-images-idx3-ubyte:  test set images
  \item t10k-labels-idx1-ubyte:  test set labels
\end{itemize}
The format of training and test files are described in the following table.
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of items \\
\hline
0008  &   unsigned byte  & ??          &     label \\
\hline
0009  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
\hline
\end{tabular}
\caption{Training data file format.}
\label{tbl:training-file-format}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000803(2051) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of images \\
\hline
0008  &   unsigned byte  & 28          &     number of rows  \\
\hline
0012  &   unsigned byte  & 28          &     number of columns \\
\hline
0016  &   unsigned byte  & ??          &     pixel \\
\hline
0017  &   unsigned byte  & ??          &     pixel \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     pixel \\
\hline
\multicolumn{4}{|c|}{\textbf{
\shortstack{Pixels are organized row-wise. Pixel values are 0 to 255. \\ 0 means background (white), 255 means foreground (black).}}} \\
\hline
\end{tabular}
\caption{Test data file format.}
\label{tbl:test-file-format}
\end{table}

\subsection{EMNIST Dataset}
The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
and converted to a 28x28 pixel image format and dataset structure that directly matches the MNIST dataset.

\subsubsection{Dataset Summary}
There are six different splits provided in this dataset. A short summary of the dataset is provided below:
\begin{itemize}
  \item EMNIST ByClass: 814,255 characters. 62 unbalanced classes.
  \item EMNIST ByMerge: 814,255 characters. 47 unbalanced classes.
  \item EMNIST Balanced:  131,600 characters. 47 balanced classes.
  \item EMNIST Letters: 145,600 characters. 26 balanced classes.
  \item EMNIST Digits: 280,000 characters. 10 balanced classes.
  \item EMNIST MNIST: 70,000 characters. 10 balanced classes.
\end{itemize}
The full complement of the NIST Special Database 19 is available in the ByClass and ByMerge splits. The EMNIST Balanced dataset contains a set of characters with an equal number of samples per class.
The EMNIST Letters dataset merges a balanced set of the uppercase and lowercase letters into a single 26-class task. The EMNIST Digits and EMNIST MNIST dataset provide balanced handwritten digit datasets directly compatible with the original MNIST dataset.

### 2019-06-19 chapters/proposedWork/implementation.tex
Updates from Overleaf

\section{Subject Programs}
Various models from TensorFlow is being used at different organizations like Mozilla, Google, Stanford University, etc. in different domains extending from speech recognition to computer vision. To evaluate the accuracy of some of the popular algorithms used in supervised classification we decided to implement metamorphic testing of:
\begin{itemize}
\item K-Nearest Neighbors
\item Neural Networks
\end{itemize}

\section{Identification of Metamorphic Relations} \label{MRused}
Murphy et al. \cite{Murphy} identified six metamorphic properties that they believe exist in many machine learning applications: additive, multiplicative, permutative, invertive, inclusive, and exclusive. We expect the neural networks to be resistant to these transformations and produce the same classifications before and after applying tranformations.

\section{Generation of source test cases}
Source test data

\section{Generation of follow-up test cases}
Follow-up data after applying MR

\section{Evaluation metrics}
How to evaluate

### 2019-06-19 chapters/results/results.tex
Updates from Overleaf

\section{Overall Accuracy}
\begin{figure}
  \includegraphics[width=\linewidth]{images/rotation}
  \caption{MR: Rotation.}
  \label{fig:rotation 1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shade}
  \caption{MR: Shading.}
  \label{fig: Shading}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/sheer}
  \caption{MR: Sheering.}
  \label{fig: Sheer}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shift}
  \caption{MR: Shifting.}
  \label{fig: Shift}
\end{figure}

\section{Digit-by Accuracy}
\begin{figure}
  \includegraphics[width=\linewidth]{images/rotation1}
  \caption{MR: Rotation.}
  \label{fig:rotation 1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shade1}
  \caption{MR: Shading.}
  \label{fig: Shading}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/sheer1}
  \caption{MR: Sheering.}
  \label{fig: Sheer}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shift1}
  \caption{MR: Shifting.}
  \label{fig: Shift}
\end{figure}

### 2019-08-04 chapters/introduction/introduction.tex
Updates from Overleaf

@@
 \begin{enumerate}
-  \item How does metamorphic testing compare to other testing methodologies for testing machine learning algorithms?
+%   \item How does metamorphic testing compare to other testing methodologies for testing machine learning algorithms?
   %\item Can we quantify reliability of predictions made by machine learning algorithms?
-  \item How sensitive are the predictions made by ML algorithms to the change in input data?
-  \item At what point does the algorithm fail to produce correct classifications on distorted inputs?
+  \item Identifying metamorphic properties that can be used to generate new test data from image datasets.
+%   \item How does metamorphic properties affect different dataset and deep-learning algorithms?
+  \item Robustness of the deep learning algorithms to the identified metamorphic properties?
+  \item What range of Metamorphic properties identified is most useful while generating new test cases.
+%   \item How sensitive are the predictions made by ML algorithms to the change in input data?
+%   \item At what point does the algorithm fail to produce correct classifications on distorted inputs?
+
 \end{enumerate}

### 2019-08-04 chapters/litReview/finalLit.tex
Updates from Overleaf

--- 2019-06-19 chapters/litReview/litReview.tex
@@
-% \section{Software testing}
-% Testing is an essential activity in software engineering.
-In the simplest terms, it amounts to observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions.
-Testing is widely used in industry for quality assurance.
-Software testing is a broad term encompassing a wide spectrum of different activities, from the testing of a small piece of code by the developer (unit testing), to the customer validation of a large information system (acceptance testing), to the monitoring at run-time of a network-centric service-oriented application.
-\section{Testing in the Presence of Uncertainty \cite{Elbaum2014}}
-Uncertainty is present in most systems that are built today, whether introduced by human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments.
-In the context of software testing, uncertainty increases the ambiguity of what constitutes the input space and what is deemed as acceptable behavior, which are two key attributes of a test.
-In this paper, the authors explore the potential directions for dealing with uncertainty during testing.
+\section{Software testing}
+Testing is one of the most important activity in software development life cycle.
+Bertolino define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions".
+Testing is widely used in industry for quality assurance purposes.
+Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code developers, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service.
+Some studies (B.
+Beizer) have estimated that software testing can use upto fifty percent, or more, of the total development cost.
+Thus, it is program software testing is worthy of our attention for research and improvement.
+Weyuker (1982) categorizes the testing research activities into three categories:
+\begin{enumerate}
+  \item Develop a sound theoretical basis for testing.
+  \item Devise and improve testing methodologies, especially the mechanizable ones.
+  \item Define accurate measurement criteria for testing data adequately.
+\end{enumerate}
+
+However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs.
+These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments.
+In the context of software testing, the two fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle.
+(Chen, Tse, & Zhou Semi Proving: An integrated method and Elbaum2014)
+
+ One of the first problems that testers run into is that they don't have access to acceptable output to test the program output against.
+This problem is often referred to as the Oracle problem.
+Weyuker (1982) provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts.
+As per Weyuker, non-testable programs can be defined as the programs for which such oracles do not exist.
+The term non-testable is used, from the point of view of correctness testing.
+If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.
+
+ One way of elevating the oracle-problem is through the use of pseudo oracle.
+It is also referred to as dual-coding and used in higly critical software.
+(Weyuker and automatic system testing of programs without test oracles: Christian murphy, kuang shen).
+Pseudo-oracles are multiple implementation of same specification of the original program under test.
+ However dual coding comes with it's own set of problems. As [this and this ] pointed out that it 
+ multiple implementation may not exist
+ multiple implementation may be created by the same or same set of developers prone to make same mistakes.
+ pseudo-oracle requires at least two implementation and it may be a lot of overhead 
+ The authors finally make five recommendation for items to be considered as a part of documentation during testing.
+\begin{enumerate}
+  \item The criteria used to select the test data.
+  \item The degree to which the criteria were fulfilled.
+  \item The test data, the program ran on.
+  \item The output of each of each test datum.
+  \item How the results were determined to be correct or acceptable.
+\end{enumerate}
+Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.
+
+ Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used.
+While performing mathematical computations, errors from three sources can creep in:
+\begin{enumerate}
+  \item The mathematical model used to do the computations.
+  \item Programs written to implement the computation.
+  \item The features of the environment like round-off, floating point operations etc.
+\end{enumerate}
+
+Many techniques have since been developed to develop these set of non-testable programs.
+
 Two ways to deal with uncertainty are to exercise more control over the inputs provided to the unit under test and to constrain the testing environment.
@@
 \section{On Testing Non-testable Programs \cite{Weyuker}}
-The current testing research activities fall into three categories:
-\begin{enumerate}
-  \item Develop a sound theoretical basis for testing.
-  \item Devise and improve testing methodologies, especially the mechanizable ones.
-  \item Define accurate measurement criteria for testing data adequately.
-\end{enumerate}
-An oracle is a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts.
-Programs for which such oracles do not exist are called 'non-testable'.
-The term non-testable is used, from the point of view of correctness testing.
-If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.
-Non-testable programs can be usually classified into three categories:
-\begin{enumerate}
-  \item Programs that were written to determine the correct answer.
-  \item Programs that produce a lot of outputs such that it is hard to verify all of them.
-  \item Programs where tester have a misconception (tester believes that he has the oracle even though he might not).
-\end{enumerate}
-In absence of oracles, the ideal way to test a program is through Pseudo Oracles/Dual Coding.
+
  But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation. 
@@
 it is common for central cases to work perfectly whereas boundary cases to cause errors.
-Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used.
-While performing mathematical computations, errors from three sources can creep in:
-\begin{enumerate}
-  \item The mathematical model used to do the computations.
-  \item Programs written to implement the computation.
-  \item The features of the environment like round-off, floating point operations etc.
-\end{enumerate}
+
 Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer.

### 2019-08-04 chapters/litReview/metamorphicTesting.tex
Updates from Overleaf

@@
+Zhou et al. (Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H. Huang‡, T.H. Tse§,
+Zongyuan Yang ¶, Haitao Huang ¶, and T. Y. Chen ‡) argued that successful test cases
+
+Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to answer the oracle problem.
+Segura et al.
+did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing.
+% \begin{enumerate}
+% 	\item RQ1: What improvements to the technique have been made?
+% 	\item RQ2: What are its known application domains?
+% 	\item RQ3: How are experimental evaluations performed?
+% 	\item RQ4: What are the future research challenges?
+% \end{enumerate}
+
 \section{Metamorphic Testing}
 	\subsection{A Survey on Metamorphic Testing \cite{Segura2016}}
-		Segura et al. did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer four important research questions:
-		\begin{enumerate}
-			\item RQ1: What improvements to the technique have been made?
-			\item RQ2: What are its known application domains?
-			\item RQ3: How are experimental evaluations performed?
-			\item RQ4: What are the future research challenges?
-		\end{enumerate}
 

### 2019-08-04 chapters/methodology/collection.tex
Updates from Overleaf

--- 2019-06-19 chapters/proposedWork/environment.tex
@@
-\section{Setting up the Test Environment}
-% \subsection{Docker}
-% For replication of results. Image can be downloaded from dockerhub. Attached volume for persisting data.
+\section{Tools}
 \subsection{Jupyter}
@@
 
+\section{Algorithm}
+\subsection{Convolutional neural network}
+\subsection{2-layer neural network}
+
+\section{Dataset}
 \subsection{MNIST Dataset}
-The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 60,000 examples, and a test set of 10,000 examples.
+The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 55,000 examples, and a test set of 10,000 examples.
 It is a subset of a larger set available from NIST.
@@
 
-\subsubsection{Format of Dataset}
+\subsection{EMNIST Dataset}
+The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
+and converted to a 28x28 pixel image format. The EMNIST dataset structure directly matches the MNIST dataset.
+
+\subsubsection{Dataset Summary}
+There are six different splits provided in this dataset. A short summary of the dataset is provided below:
+\begin{itemize}
+  \item EMNIST ByClass: 814,255 characters. 62 unbalanced classes.
+  \item EMNIST ByMerge: 814,255 characters. 47 unbalanced classes.
+  \item EMNIST Balanced:  131,600 characters. 47 balanced classes.
+  \item EMNIST Letters: 145,600 characters. 26 balanced classes.
+  \item EMNIST Digits: 280,000 characters. 10 balanced classes.
+  \item EMNIST MNIST: 65,000 characters. 10 balanced classes.
+\end{itemize}
+The full complement of the NIST Special Database 19 is available in the ByClass and ByMerge splits. The EMNIST Balanced dataset contains a set of characters with an equal number of samples per class.
+The EMNIST Letters dataset merges a balanced set of the uppercase and lowercase letters into a single 26-class task.
+The EMNIST Digits and EMNIST MNIST dataset provide balanced handwritten digit datasets directly compatible with the original MNIST dataset.
+
+\begin{figure}[htb!]
+        \centering
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{images/digit.png}
+            \caption{Sample EMNIST-MNIST dataset}
+            \label{fig:EMNIST MNIST dataset}
+        \end{subfigure}%
+        \label{fig:Rotate-misclassifications}
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{images/letter.png}
+            \caption{Sample EMNIST-MNIST dataset}
+            \label{fig:EMNIST MNIST dataset}
+        \end{subfigure}%
+        \label{fig:Rotate-misclassifications}
+    \end{figure}
+    \FloatBarrier
+
+\subsection{Fashion MNIST Dataset}
+Fashion-MNIST is a dataset of Zalando's article images—consisting of a training set of 55,000 examples and a test set of 10,000 examples.
+Each example is a 28x28 grayscale image, associated with a label from 10 classes.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{|c|c|}
+\hline
+\textbf{Label} & \textbf{Description} \\ \hline
+0  &   T-shirt/top \\ \hline
+1  &   Trouser \\ \hline
+2   &	Pullover \\ \hline
+3   &	Dress \\ \hline
+4   &	Coat \\ \hline
+5   &	Sandal \\ \hline
+6   &	Shirt \\ \hline
+7   &	Sneaker \\ \hline
+8   &	Bag \\ \hline
+9   &	Ankle boot \\ \hline
+\end{tabular}
+\caption{Data file format.}
+\label{tbl:training-file-format}
+\end{table}
+
+\begin{figure}[htb!]
+        \centering
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=\linewidth]{images/fashion.png}
+            \caption{Sample EMNIST-MNIST dataset}
+            \label{fig:EMNIST MNIST dataset}
+        \end{subfigure}%
+        \label{fig:Rotate-misclassifications}
+    \end{figure}
+    \FloatBarrier
+
+\subsection{Format of Dataset}
 The data is stored in a very simple file format designed for storing vectors and multidimensional matrices.
@@
 
-\subsection{EMNIST Dataset}
-The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
-and converted to a 28x28 pixel image format and dataset structure that directly matches the MNIST dataset.
-
-\subsubsection{Dataset Summary}
-There are six different splits provided in this dataset. A short summary of the dataset is provided below:
-\begin{itemize}
-  \item EMNIST ByClass: 814,255 characters. 62 unbalanced classes.
-  \item EMNIST ByMerge: 814,255 characters. 47 unbalanced classes.
-  \item EMNIST Balanced:  131,600 characters. 47 balanced classes.
-  \item EMNIST Letters: 145,600 characters. 26 balanced classes.
-  \item EMNIST Digits: 280,000 characters. 10 balanced classes.
-  \item EMNIST MNIST: 70,000 characters. 10 balanced classes.
-\end{itemize}
-The full complement of the NIST Special Database 19 is available in the ByClass and ByMerge splits. The EMNIST Balanced dataset contains a set of characters with an equal number of samples per class.
-The EMNIST Letters dataset merges a balanced set of the uppercase and lowercase letters into a single 26-class task.
-The EMNIST Digits and EMNIST MNIST dataset provide balanced handwritten digit datasets directly compatible with the original MNIST dataset.
+% \subsection{Docker}
+% For replication of results. Image can be downloaded from dockerhub. Attached volume for persisting data.

### 2019-08-04 chapters/methodology/properties.tex
Updates from Overleaf

\section{Identifying Metamorphic Relations} 
We identified seven metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, shifting along-axis, zooming along x-axis, zooming along y-axis. Each image in the testing dataset (digit, letter, and, fashion) was transformed using the seven metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
\subsection{Rotate}
The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle. For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}]. 
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/rotate2.png}
            \caption{Angle: \ang{0}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate3.png}
            \caption{Angle: \ang{50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}
        \caption{Rotation property applied to Digit 3.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shear}  
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\textwidth]{images/shear2.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear3.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shear property applied to Digit 4.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shading}
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade1.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shade2.png}
            \caption{Value: 80}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade3.png}
            \caption{Value: 99}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shade property applied to Digit 9.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shifting in the X direction}
    For any value above x the image was completely out of the frame.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shiftx2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shift X property applied to Digit 7.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shifting in the Y direction}
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shifty2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shift Y property applied to Digit 5.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

### 2019-08-04 chapters/results/CNN/Rotate/rotate.tex
Updates from Overleaf

\section{Overall Accuracy}
The 
    \begin{figure}[!htb]
        \begin{center}
          \includegraphics[scale=0.6]{chapters/results/CNN/Rotate/acc.png}
          \caption{Overall accuracy for metamorphic relation rotation.}
          \label{fig:Rotate 1}
        \end{center}
    \end{figure}

\clearpage
    \begin{figure}[!htb]
    \centering
      \includegraphics[width=\linewidth]{chapters/results/CNN/Rotate/accAll.png}
      \caption{Accuracy of each digit.}
      \label{fig: Shading}
    \end{figure}

\clearpage
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc1.png}
        \caption{Misclassification of Digit 0}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc2.png}
        \caption{Misclassification of Digit 1}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc3.png}
        \caption{Misclassification of Digit 2}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc4.png}
        \caption{Misclassification of Digit 3}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{ \textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc5.png}
        \caption{Misclassification of Digit 4}
        \label{fig:Rotate-misclass1}
    \end{subfigure}
    \caption{Misclassification.}
    \label{fig:Rotate-misclassifications}
\end{figure}

\clearpage
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc6.png}
        \caption{Misclassification of Digit 5}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc7.png}
        \caption{Misclassification of Digit 6}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc8.png}
        \caption{Misclassification of Digit 7}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc9.png}
        \caption{Misclassification of Digit 8}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{ \textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc10.png}
        \caption{Misclassification of Digit 9}
        \label{fig:Rotate-misclass1}
    \end{subfigure}
    \caption{Caption for all subfigures.}
    \label{fig:Rotate-misclassifications}
\end{figure}

\clearpage

### 2019-08-04 chapters/results/CNN/Shade/shade.tex
Updates from Overleaf

\section{Shade}
        \begin{figure}[!htb]
            \begin{center}
              \includegraphics[scale=0.6]{chapters/results/CNN/Shade/acc.png}
              \caption{Overall accuracy for metamorphic relation rotation.}
              \label{fig:Shade 1}
            \end{center}
        \end{figure}

    \clearpage
        \begin{figure}[!htb]
        \centering
          \includegraphics[scale=0.4]{chapters/results/CNN/Shade/accAll.png}
          \caption{Accuracy of each digit for Shade.}
          \label{fig: Shading}
        \end{figure}

    \clearpage
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc1.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc2.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc3.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc4.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{ \textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc5.png}
            \caption{Caption for subfigure 2}
            \label{fig:Shade-misclass1}
        \end{subfigure}
        \caption{Caption for all subfigures.}
        \label{fig:Shade-misclassifications}
    \end{figure}

    \clearpage
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc6.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc7.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc8.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc9.png}
            \caption{Caption for subfigure 1}
            \label{fig:Shade-misclass0}
        \end{subfigure}
        \begin{subfigure}[b]{ \textwidth}
            \centering
            \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc10.png}
            \caption{Caption for subfigure 2}
            \label{fig:Shade-misclass1}
        \end{subfigure}
        \caption{Caption for all subfigures.}
        \label{fig:Shade-misclassifications}
    \end{figure}

\clearpage

### 2019-08-04 chapters/results/digit-by-accuracy.tex
Updates from Overleaf

\section{Digit-by Accuracy}
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/accAll.png}
        \caption{Rotate}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/accAll.png}
        \caption{Shading}
        \label{fig:Rotate-misclass1}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Shear/accAll.png}
        \caption{Shear}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/ShiftX/accAll.png}
        \caption{Shifting in X-axis}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \label{fig:Rotate-misclassifications}
\end{figure}

\begin{figure}
    \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/ShiftY/accAll.png}
        \caption{Shifting in Y-axis}
        \label{fig:Rotate-misclass0}
\end{figure}
Rotation
1.  The graph is bell shaped
2. 0 is not affected due to rotation

### 2019-08-04 chapters/results/results.tex
Updates from Overleaf

@@
+\section{Effect of transformation on model}
+From literature review we postulate that small changes to input image should not affect the prediction model.
+In this thesis we investigate the effect of the identified metamorphic properties have on the accuracy of model.
+For each machine learning algorithms generated ten models .
+For each metamorphic property identified in section X we look how it affects .
+We calculated the following metrics to evaluate the affect of metamophic relations on deep-learning algorithm.
+To tackle the non-deterministic nature of training a neural network model, we ran each of the above experiment ten times and calculated average.
+\subsection{Overall Accuracy or true positive}
+    Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made.
+\subsection{Digit-by Accuracy or true positive for each digit}
+    We analyze each digit and 
+\subsection{Misclassification of digits}
+    In order to see how each digit is affected by changes in  mp. For each digit 0-9 we calculated the number of correct predictions made by the model as compared to total number of .
+\subsection{Robustness}
+
+\clearpage
+% \input{CNN/Rotate/rotate.tex}
 \section{Overall Accuracy}
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/rotation}
-  \caption{MR: Rotation.}
-  \label{fig:rotation 1}
+\begin{figure}[htb!]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc.png}
+        \caption{Rotation}
+        \label{fig:Rotate-misclass0}
+    \end{subfigure}
+    \begin{subfigure}[b]{ 0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc.png}
+        \caption{Shading}
+        \label{fig:Rotate-misclass1}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{chapters/results/CNN/Shear/acc.png}
+        \caption{Shearing}
+        \label{fig:Rotate-misclass0}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{chapters/results/CNN/ShiftX/acc.png}
+        \caption{Shifting in X-axis}
+        \label{fig:Rotate-misclass0}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{chapters/results/CNN/ShiftY/acc.png}
+        \caption{Shifting in Y-axis}
+        \label{fig:Rotate-misclass0}
+    \end{subfigure}s
+    \caption{Accuracy graphs for convolutional neural network.}
+    \label{fig:Rotate-misclassifications}
 \end{figure}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shade}
-  \caption{MR: Shading.}
-  \label{fig: Shading}
-\end{figure}
+\clearpage
+\input{digit-by-accuracy.tex}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/sheer}
-  \caption{MR: Sheering.}
-  \label{fig: Sheer}
-\end{figure}
+\iffalse
+Number of instances of each digit: 1000000 \\
+Confusion Matrix for rotation
+Rotate
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+935597 & 1571 & 6922 & 1439 & 12189 & 14037 & 6591 & 1488 & 9736 & 10430 \\ \hline
+2156 & 681401 & 46519 & 2751 & 169826 & 27931 & 9759 & 3613 & 45566 & 10478 \\ \hline
+48251 & 14436 & 625369 & 14254 & 92329 & 14828 & 21352 & 51716 & 68410 & 49055 \\ \hline
+55511 & 924 & 27210 & 641320 & 49224 & 79421 & 24213 & 9285 & 45419 & 67473 \\ \hline
+14679 & 7786 & 82089 & 3506 & 626526 & 22201 & 29658 & 9793 & 74675 & 129087 \\ \hline
+36982 & 851 & 3881 & 20562 & 41609 & 658850 & 100751 & 8549 & 32895 & 95070 \\ \hline
+14801 & 5076 & 5850 & 2183 & 21595 & 43878 & 881633 & 61 & 24041 & 882 \\ \hline
+19761 & 41054 & 89028 & 12815 & 37202 & 7157 & 1548 & 604877 & 25560 & 160998 \\ \hline
+44287 & 3357 & 18687 & 7605 & 99678 & 27689 & 47153 & 8077 & 664412 & 79055 \\ \hline
+19214 & 3572 & 22930 & 7800 & 64705 & 32264 & 3295 & 26788 & 34992 & 784440 \\ \hline
+\end{tabular}
+\end{table}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shift}
-  \caption{MR: Shifting.}
-  \label{fig: Shift}
-\end{figure}
+Shade
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+723812 & 170554 & 42780 & 6728 & 9156 & 22649 & 14219 & 4105 & 1688 & 4309 \\ \hline
+254 & 962044 & 2730 & 390 & 2949 & 583 & 28386 & 869 & 1590 & 205 \\ \hline
+5878 & 186546 & 756806 & 7351 & 5673 & 6460 & 12743 & 9246 & 6682 & 2615 \\ \hline
+7909 & 197655 & 25332 & 704395 & 3671 & 26024 & 13630 & 7059 & 7924 & 6401 \\ \hline
+980 & 199247 & 17353 & 83 & 736257 & 5919 & 10603 & 1859 & 4639 & 23060 \\ \hline
+1759 & 185772 & 11045 & 12420 & 13794 & 736958 & 17460 & 3035 & 6985 & 10772 \\ \hline
+1724 & 187885 & 29599 & 627 & 7308 & 8158 & 762263 & 73 & 2267 & 96 \\ \hline
+1038 & 230118 & 7008 & 4753 & 6887 & 4707 & 1820 & 711488 & 7578 & 24603 \\ \hline
+6249 & 220252 & 25119 & 7814 & 19723 & 37098 & 17413 & 4407 & 644767 & 17158 \\ \hline
+3420 & 216638 & 6303 & 1732 & 48951 & 9704 & 3905 & 25036 & 11315 & 672996 \\ \hline
+\end{tabular}
+\end{table}
 
-\section{Digit-by Accuracy}
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/rotation1}
-  \caption{MR: Rotation.}
-  \label{fig:rotation 1}
-\end{figure}
+ Shear
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+843745 & 10901 & 25910 & 6041 & 22737 & 31418 & 18795 & 6279 & 25431 & 8743 \\ \hline
+489 & 827503 & 75423 & 1064 & 42026 & 5999 & 4750 & 4074 & 35602 & 3070 \\ \hline
+5078 & 18985 & 841933 & 16944 & 20220 & 8561 & 24028 & 14614 & 45286 & 4351 \\ \hline
+9944 & 9350 & 32310 & 764503 & 48583 & 73988 & 13401 & 4440 & 28001 & 15480 \\ \hline
+9834 & 5379 & 38067 & 1622 & 780726 & 4660 & 19143 & 3798 & 28973 & 107798 \\ \hline
+6990 & 7222 & 17568 & 15686 & 38861 & 840605 & 17008 & 1864 & 24632 & 29564 \\ \hline
+7975 & 4004 & 23667 & 1264 & 22961 & 18252 & 902574 & 472 & 18495 & 336 \\ \hline
+1905 & 83886 & 71323 & 13684 & 28050 & 4143 & 2944 & 699486 & 29394 & 65185 \\ \hline
+8266 & 24716 & 60365 & 5607 & 47917 & 15477 & 21918 & 8603 & 782538 & 24593 \\ \hline
+4575 & 17714 & 27060 & 5122 & 117887 & 14337 & 1801 & 34062 & 38993 & 738449 \\ \hline
+\end{tabular}
+\end{table}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shade1}
-  \caption{MR: Shading.}
-  \label{fig: Shading}
-\end{figure}
+ ShiftX
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+77949 & 614059 & 82304 & 114994 & 10084 & 27145 & 16921 & 37383 & 15310 & 3851 \\ \hline
+18598 & 762514 & 11391 & 108735 & 21327 & 19628 & 14301 & 40521 & 1593 & 1392 \\ \hline
+5413 & 596299 & 158838 & 111720 & 8599 & 65944 & 29801 & 18278 & 3585 & 1523 \\ \hline
+1960 & 613767 & 48437 & 192270 & 15577 & 60280 & 19406 & 37799 & 8608 & 1896 \\ \hline
+10748 & 606441 & 25128 & 115124 & 143172 & 26096 & 9445 & 52487 & 2675 & 8684 \\ \hline
+3280 & 576218 & 57996 & 123105 & 7793 & 122565 & 13449 & 83188 & 7653 & 4753 \\ \hline
+6802 & 629739 & 79954 & 107383 & 11197 & 39254 & 112765 & 9497 & 1752 & 1657 \\ \hline
+4431 & 612470 & 14042 & 104293 & 6656 & 54982 & 3929 & 188195 & 3754 & 7248 \\ \hline
+11402 & 604142 & 33747 & 119427 & 14964 & 36848 & 10922 & 73575 & 84225 & 10748 \\ \hline
+6458 & 610597 & 17436 & 112603 & 24052 & 23167 & 3885 & 108416 & 9620 & 83766 \\ \hline
+\end{tabular}
+\end{table}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/sheer1}
-  \caption{MR: Sheering.}
-  \label{fig: Sheer}
-\end{figure}
+ ShiftY
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+66197 & 542587 & 43176 & 106135 & 42382 & 12674 & 70021 & 78999 & 1631 & 36198 \\ \hline
+538 & 725379 & 4939 & 111517 & 12744 & 23113 & 33750 & 63499 & 898 & 23623 \\ \hline
+5931 & 549369 & 84027 & 122009 & 46036 & 29879 & 50616 & 84857 & 1755 & 25521 \\ \hline
+5459 & 536243 & 48175 & 173095 & 19257 & 21261 & 57625 & 90112 & 1912 & 46861 \\ \hline
+5912 & 587840 & 31183 & 111527 & 72612 & 18906 & 56932 & 95170 & 958 & 18960 \\ \hline
+4400 & 549322 & 56501 & 108096 & 14913 & 68901 & 55441 & 99507 & 4262 & 38657 \\ \hline
+4196 & 569875 & 38726 & 108298 & 22672 & 11800 & 106513 & 75694 & 1169 & 61057 \\ \hline
+6315 & 586659 & 32610 & 115134 & 43765 & 29717 & 47371 & 119460 & 1436 & 17533 \\ \hline
+15388 & 533073 & 30139 & 108200 & 16740 & 19676 & 83688 & 80939 & 50348 & 61809 \\ \hline
+13355 & 566917 & 27002 & 109136 & 20624 & 17805 & 81323 & 95899 & 1001 & 66938 \\ \hline
+\end{tabular}
+\end{table}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shift1}
-  \caption{MR: Shifting.}
-  \label{fig: Shift}
-\end{figure}
+\fi
+
+\clearpage
+
+To generate new data from MNIST digit dataset. While using rotation 0 should be in a prticular range. 1 should be in particular range.....

### 2019-08-07 chapters/litReview/MRMLalgo.tex
new

--- 2019-06-19 chapters/litReview/testMLprog.tex
@@
 \section{Testing Machine Learning Programs}
-\subsection{Properties of Machine Learning Applications for Use in Metamorphic Testing \cite{Murphy}}
+Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations in order to transform inputs.
+\subsection{Properties of Machine Learning Applications for Use in Metamorphic Testing \cite{Murphy2008}}
 In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test.
@@
 \end{itemize}
-The main challenge with metamorphic testing is to come up with the metamorphic relations to transform inputs since such coming up with such relations require domain knowledge and/or familiarity with the implementation.
-In this paper the authors seek to create a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning softwares.
-These set of properties can be applied to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications.
+STU
+
+Murphy, Kaiser, Hu, and, Wu (2008) created a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning software.
+These set of properties can be used to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications\cite{Murphy2008}.
+Similar work has also been done by Xie et al.(2009) where they identified metamorphic relations for k-nearest neighbors algorithm (k-NN) and naïve Bayes classifier (NBC).
+Murphy et al. investigated two supervised algorithms MartiRank and SVM-Light and an unsupervised system PAYL to identify basic metamorphic properties in machine learning algorithms.
+
 The problem with some of the current machine learning frameworks like: Weka and Orange is that they compare the quality of results but don’t evaluate the correctness of the results.
@@
 Multiplying the data with some other positive number will increase the standard deviation by the same amount. Thus, the output will still be predictable.
-The authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
+From the study of these algorithms, the authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
 \begin{enumerate}
@@
 Since testing the whole program at once is not always possible choosing a right SUT from a non-testable program has a large impact on testing activities.
+
+\cite{Segura2016}
+Composition of Metamorphic Relations (CMR) can be used to construct new metamorphic relations by combining several existing relations.
+The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions.
+Two metamorphic relations are considered “compositable” if the follow-up test cases of one of the relations can always be used as source test case of the other.
+The composition is sensitive to the order of metamorphic relations and generalizable to any number of them.
+Determining whether two metamorphic relations are composable is a manual task.
+Chen et al.
+\cite{Chen2016} presented a specification–based tool called METRIC for the identification of metamorphic relations.
+In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames.
+The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.

### 2019-08-07 chapters/litReview/finalLit.tex
new

@@
 Testing is one of the most important activity in software development life cycle.
-Bertolino define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions".
+Bertolino (2007) define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions".
 Testing is widely used in industry for quality assurance purposes.
-Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code developers, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service.
-Some studies (B.
-Beizer) have estimated that software testing can use upto fifty percent, or more, of the total development cost.
-Thus, it is program software testing is worthy of our attention for research and improvement.
+Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service, etc.\cite{Bertolino2007} A study by Beizer (2006) has estimated that software testing can use up to fifty percent, or more, of the total development cost.
+Thus, it is clear that program software testing is worthy of our attention for research and improvement.\cite{Beizer1990}
 Weyuker (1982) categorizes the testing research activities into three categories:
@@
 In the context of software testing, the two fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle.
-(Chen, Tse, & Zhou Semi Proving: An integrated method and Elbaum2014)
+\cite{Chen2002} \cite(Elbaum2014)
+Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used.
+While performing mathematical computations, errors from three sources can creep in:
+\begin{enumerate}
+  \item The mathematical model used to do the computations.
+  \item Programs written to implement the computation.
+  \item The features of the environment like round-off, floating point operations etc.
+\end{enumerate}\cite{Weyuker}
 
@@
 This problem is often referred to as the Oracle problem.
-Weyuker (1982) provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts.
+Weyuker provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts.
 As per Weyuker, non-testable programs can be defined as the programs for which such oracles do not exist.
 The term non-testable is used, from the point of view of correctness testing.
-If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.
+If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.\cite{Weyuker}
 
+ A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles.
+If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault.
+On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time.\cite(Elbaum2014)
+
+ Many techniques have since been developed to test these set of non-testable programs.
 One way of elevating the oracle-problem is through the use of pseudo oracle.
-It is also referred to as dual-coding and used in higly critical software.
-(Weyuker and automatic system testing of programs without test oracles: Christian murphy, kuang shen).
+It is also referred to as dual-coding and is used in highly critical software.\cite{Weyuker}\cite{Murphy2009}.
 Pseudo-oracles are multiple implementation of same specification of the original program under test.
- However dual coding comes with it's own set of problems. As [this and this ] pointed out that it 
- multiple implementation may not exist
- multiple implementation may be created by the same or same set of developers prone to make same mistakes.
- pseudo-oracle requires at least two implementation and it may be a lot of overhead 
- The authors finally make five recommendation for items to be considered as a part of documentation during testing.
+ However, dual coding comes with it's own set of problems.
+As the authors [this and this ] pointed out that pseudo-oracle requires at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
+ In light of shortcomings of the testing process the authors finally make five recommendation for items to be considered as a part of documentation during testing.
 \begin{enumerate}
@@
 \end{enumerate}
-Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.
-
- Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used.
-While performing mathematical computations, errors from three sources can creep in:
-\begin{enumerate}
-  \item The mathematical model used to do the computations.
-  \item Programs written to implement the computation.
-  \item The features of the environment like round-off, floating point operations etc.
-\end{enumerate}
-
-Many techniques have since been developed to develop these set of non-testable programs.
-
-Two ways to deal with uncertainty are to exercise more control over the inputs provided to the unit under test and to constrain the testing environment.
-Some uncertainties like those present in systems that deal with the physical world are aleatoric; that is, they cannot be known precisely because of their inherent variability and noise.
-Epistemic uncertainties are those that could be resolved with enough effort (e.g., over-engineering a sensor-based system to minimize inference errors about the environment)— and resolving them are becoming more numerous and costly, as the systems are becoming increasingly complex.
-A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles.
-If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault.
-On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time.
-The authors provide a set of requirements for adequate handling of uncertainty in testing:
-\begin{enumerate}
-  \item Specifying input distributions and generating inputs with the help of the distributions instead of using discrete inputs.
-  \item Probabilistic oracles that can help distinguish acceptable from unacceptable misbehaviors. These models will also provide the specification of the likelihood of results.
-  \item Richer models to represent system and environment uncertainty, so that uncertainties can be connected to test requirements and outcomes.
-This will help with automated uncertainty quantification.
-\end{enumerate}
-Not all systems will impose these requirements, and not all techniques will satisfy them.
-In fact, they expect it will be necessary to develop a suite of techniques for dealing with uncertainty, selected according to system characteristics and the particular forms of uncertainty the system embodies and based on the use of stochastic models and quantitative analyses.
-
-\section{On Testing Non-testable Programs \cite{Weyuker}}
+Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.\cite(Weyuker)
 
@@
 it is common for central cases to work perfectly whereas boundary cases to cause errors.
+\cite{Weyuker}
 
@@
 Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution.
-The authors finally make five recommendation for items to be considered as a part of documentation during testing.
-\begin{enumerate}
-  \item The criteria used to select the test data.
-  \item The degree to which the criteria were fulfilled.
-  \item The test data, the program ran on.
-  \item The output of each of each test datum.
-  \item How the results were determined to be correct or acceptable.
-\end{enumerate}
-Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

### 2019-08-07 chapters/litReview/metamorphicTesting.tex
new

@@
-Zhou et al. (Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H. Huang‡, T.H. Tse§,
-Zongyuan Yang ¶, Haitao Huang ¶, and T. Y. Chen ‡) argued that successful test cases
+\section{Metamorphic Testing}
 
-Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to answer the oracle problem.
+In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test.
+It is almost impossible to generate all the possible combinations of test cases to completely test a program which is why a lot of research is being conducted to develop more error-revealing test case selection strategies.
+A test case is called error-revealing if it is able to detect an error in the software otherwise it is labeled successful.
+Successful test case are the cases for which the program successfully computes the correct output.
+Since these test cases do not reveal any error, they are considered less important and are often not investigated further or, set aside for regression testing.
+{Zhou et al.
+(Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H.
+Huang‡, T.H.
+Tse§, Zongyuan Yang ¶, Haitao Huang ¶, and T.
+Y.
+Chen ‡)(Metamorphic testing and beyond) }
+
+Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem.
+Metamorphic testing reuses successful test cases to generate followup test cases according to metamorphic relations whose output can easily be predicted.
+A metamorphic relation(MR) is an expected relation among input and outputs of multiple executions of the target program(Metamorphic testing and beyond)(METRIC: METamorphic Relation Identification based on the Category - choice framework).
+To formally define MRs we can assume a function $f$ which produces the output $f(x)$ on input $x$.
+The MRs of the function can then be used to generate a transformation function $t$, which, when applied to input $x$ produces $t(x)$.
+This transformed input can then be run through the function $f$ and the transformation allows us to predict the value of $f(t(x))$(Automatic system testing of programs without test oracle).
+A simple example of a MR would be a program that calculates mean of a set of numbers.
+Certain transformations of the set of numbers will result in the same value for mean like: permuting the order of numbers, since, this neither changes the number of elements in the set nor the value of any element.
+Another transformation that can be used would be multiplying each number in the set with -1.
+The new mean will be the negative value of the previous mean.
+
+System under test(SUT)
+
+\subsection{Properties of a good metamorphic relation}
 Segura et al.
 did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing.
-% \begin{enumerate}
-% 	\item RQ1: What improvements to the technique have been made?
-% 	\item RQ2: What are its known application domains?
-% 	\item RQ3: How are experimental evaluations performed?
-% 	\item RQ4: What are the future research challenges?
-% \end{enumerate}
+They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems.
+They also found some other domains of application like financial software, optimization programs, and encryption programs.
 
-\section{Metamorphic Testing}
-	\subsection{A Survey on Metamorphic Testing \cite{Segura2016}}
-
-		\subsubsection{Properties of good metamorphic relations}
-			To answer the first question they first studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
+They first studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
 \begin{itemize}
 	\item A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.
-				\item Metamorphic relations that make execution of the follow–up test case as different as possible from the source test case.
+	\item Metamorphic relations that make execution of the follow-up test case as different as possible from the source test case.
 	\item Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.
 	\item Formally described metamorphic relations.
-In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow–up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
+In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow-up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
 \end{itemize}
 
-		\subsubsection{Construction of metamorphic relations}
-		Composition of Metamorphic Relations (CMR) can be used to construct new metamorphic relations by combining several existing relations.
-The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions.
-Two metamorphic relations are considered “compositable” if the follow-up test cases of one of the relations can always be used as source test case of the other.
-The composition is sensitive to the order of metamorphic relations and generalizable to any number of them.
-Determining whether two metamorphic relations are composable is a manual task.
-Chen et al.
-\cite{Chen2016} presented a specification–based tool called METRIC for the identification of metamorphic relations.
-In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames.
-The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.
-
-		\subsubsection{Generation of source test cases}
+It should be noted that MT does not check the correctness of individual outputs.
+Instead, it checks the relations among several executions.
+Since no manual output predictions and comparisons are required, MT can be efficient and fully automated.
+\cite{Segura2016} The execution of a metamorphic test case is typically performed in two steps.
+First, a follow-up test case is generated by applying a transformation to the inputs of a source test case.
+Second, source and follow-up test cases are executed, checking whether their outputs violate the metamorphic relation.
+\par
+	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
+	A number of frameworks have been developed to automate the process of metamorphic testing.
 Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations.
@@
 
-		\subsubsection{Execution of metamorphic test cases}
-		The execution of a metamorphic test case is typically performed in two steps.
-First, a follow–up test case is generated by applying a transformation to the inputs of a source test case.
-Second, source and follow–up test cases are executed, checking whether their outputs violate the metamorphic relation.
-\par
-		Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively.
-In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow–up test case of each metamorphic relation as the source test case of the next metamorphic relation.
-\par
-		Murphy et al.
-\cite{Murphy2009} presented a framework named Amsterdam for the automated application of metamorphic testing.
-The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file.
-Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.
-		\subsubsection{Application domains}
-		To answer the second question the authors selected the papers where the main objective was a case study.
-They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems.
-They also found some other domains of application like financial software, optimization programs, and encryption programs.
-		Some of the research challenges identified by the authors are:
-		\begin{itemize}
-			\item Lack of guidelines, with step–by–step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
-			\item Prioritisation and minimisation of metamorphic relations: It is worth mentioning that test case minimisation is a NP–hard problem and therefore heuristic techniques should be explored.
-			\item Generation of likely metamorphic relations.
-			\item Combination of metamorphic relations.
-			\item Automated generation of best possible source test cases.
-			\item Lack of metamorphic testing tools.
-		\end{itemize}
-
-	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
 		In this paper the authors have demonstrated the usefulness of metamorphic testing in assessing the quality of applications without test oracles.
@@
 They list some benefits of using metamorphic testing: it can be used on broader domain of applications that display metamorphic properties, and it treats the application under test as a black box and does not require detailed understanding of the source code.
-They then list some of the limitations of using metamorphic testing:
+\cite{Murphy2009}
+
+		\cite{Segura2016} Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively.
+In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow-up test case of each metamorphic relation as the source test case of the next metamorphic relation.
+\par
+		Murphy et al.
+\cite{Murphy2009} presented a framework named Amsterdam for the automated application of metamorphic testing.
+The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file.
+Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.
+
+		Automated Metamorphic System Testing: This technique can be used to test the application in development environment as well as in production as long as the users are only provided the output from the original execution and not the result from transformed input.
+In this model $i)$ Metamorphic properties are specified by the tester and applied to the input.
+$ii)$ The original input is fed into the application which is treated as a black-box and a transformation of the input is also generated.
+$iii)$ That transformed input is fed into a separate instance of the application running in a separate sandbox.
+$iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
+		Tester need not write any code and only needs to specify the metamorphic properties. They don't need to know the source code or other implementation details.
+		Amsterdam framework: The metamorphic properties are specified using XML file.
+The specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.\par
+		Heuristic Metamorphic testing: This method allows for small differences in outputs, in a meaningful way according to the application being used to address the problems of false positives and non-determinism.
+Imprecision in floating point calculation and representation of irrational number such as may result in failure of metamorphic testing even if the implementation is correct.
+If two outputs are close enough they are considered the same.
+The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.\cite{Murphy2009}
+
+Although metamorphic testing presents a lot of opportunities to expand on the existing testing processes, they also have some limitations.
+They then list some of the limitations of using metamorphic testing: \cite{Murphy2009}
 		\begin{itemize}
@@
 
-		Automated Metamorphic System Testing: This technique can be used to test the application in development environment as well as in production as long as the users are only provided the output from the original execution and not the result from transformed input.
-In this model $i)$ Metamorphic properties are specified by the tester and applied to the input.
-$ii)$ The original input is fed into the application which is treated as a black-box and a transformation of the input is also generated.
-$iii)$ That transformed input is fed into a separate instance of the application running in a separate sandbox.
-$iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
-		Tester need not write any code and only needs to specify the metamorphic properties. They don’t need to know the source code or other implementation details.
-		Amsterdam framework: The metamorphic properties are specified using XML file.
-The specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.\par
-		Heuristic Metamorphic testing: This method allows for small differences in outputs, in a meaningful way according to the application being used to address the problems of false positives and non-determinism.
-Imprecisions in floating point calculation and representation of irrational number such as may result in failure of metamorphic testing even if the implementation is correct.
-If two outputs are close enough they are considered the same.
-The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.
+		Some of the research challenges identified by the authors are:{A Survey on Metamorphic Testing \cite{Segura2016}}
+		\begin{itemize}
+			\item Lack of guidelines, with step-by-step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
+			\item Prioritisation and minimisation of metamorphic relations: It is worth mentioning that test case minimisation is a NP-hard problem and therefore heuristic techniques should be explored.
+			\item Generation of likely metamorphic relations.
+			\item Combination of metamorphic relations.
+			\item Automated generation of best possible source test cases.
+			\item Lack of metamorphic testing tools.
+		\end{itemize}

### 2019-08-07 chapters/litReview/synthesisMatrix.tex
new

@@
   Semi-Proving: An Integrated Method for Program Proving, Testing, and Debugging             &
-  “Siemens suite of programs” specifically “replace program”: performs regular expression matching and substitutions.                                                                           &
+  "Siemens suite of programs" specifically "replace program": performs regular expression matching and substitutions.                                                                           &
   Given the text 'ab', replacing 'a' with 'x' is equivalent to replacing non-'b' with 'x'. \par\medskip
@@
   Metamorphic Testing and Beyond             &
-  A laplace equation with Dirichlet boundary Conditions: “alternating direction implicit” method                                        &
+  A laplace equation with Dirichlet boundary Conditions: "alternating direction implicit" method                                        &
   Beyond identity relations: Convergence                                          &

### 2019-08-25 chapters/introduction/introduction.tex
Updates from Overleaf

@@
 \end{itemize}
-Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Murphy}.
+Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Weyuker}.
 Davis and Weyuker describe these set of programs as \enquote{Programs which were written in order to determine the answer in the first place.

### 2019-08-25 chapters/litReview/MRMLalgo.tex
Updates from Overleaf

@@
-\section{Testing Machine Learning Programs}
-Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations in order to transform inputs.
-\subsection{Properties of Machine Learning Applications for Use in Metamorphic Testing \cite{Murphy2008}}
+\section{Metamorphic Testing Machine Learning Programs}
+
 In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test.
-Non-testable programs can be tested in one of the two ways:
+Non-testable programs can be tested in the following ways:
 \begin{itemize}
-  \item Creating multiple implementations of the same program and testing them on same inputs and comparing the results.
-If the outputs are not same then either of the implementations can contain error.
+  \item Creating multiple implementations of the same program and testing them on the same inputs and comparing the results.
+If the outputs are not the same then either of the implementations may contain an error.
 This approach is called pseudo-oracle.
-  \item In absence of multiple oracle, metamorphic testing can be used.
+  \item In the absence of multiple oracles, metamorphic testing can be used.
 In metamorphic testing, the input is modified using a metamorphic relation such that the two sets of input will generate similar outputs.
@@
 \end{itemize}
-STU
 
+Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations to transform inputs.
 Murphy, Kaiser, Hu, and, Wu (2008) created a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning software.
 These set of properties can be used to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications\cite{Murphy2008}.
-Similar work has also been done by Xie et al.(2009) where they identified metamorphic relations for k-nearest neighbors algorithm (k-NN) and naïve Bayes classifier (NBC).
-Murphy et al. investigated two supervised algorithms MartiRank and SVM-Light and an unsupervised system PAYL to identify basic metamorphic properties in machine learning algorithms.
-
-The problem with some of the current machine learning frameworks like: Weka and Orange is that they compare the quality of results but don’t evaluate the correctness of the results.
-The authors apply metamorphic testing to three ML applications: MartiRank, SVM-Light, PAYL.
+They investigated two supervised algorithms MartiRank and SVM-Light and an unsupervised system PAYL to identify basic metamorphic properties in machine learning algorithms.
+Similar work has also been done by Xie et al.
+(2009) where they identified metamorphic relations for k-nearest neighbors algorithm (k-NN) and naïve Bayes classifier (NBC).
 MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model.
@@
 SVM-Light is an open-source implementation of SVM that also has a ranking mode.
-The authors also investigated an intrusion detection system called PAYL.
-PAYL is an unsupervised machine learning system.
-It’s dataset simply consist of TCP/IP network payloads(stream of bytes) without any label or classification.
-Based on the analysis of MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model.
+PAYL is an unsupervised machine learning application which is used to perform intrusion detection.
+It's dataset simply consist of TCP/IP network payloads(a stream of bytes) without any label or classification.
+
+Based on the analysis of the MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model.
 Thus, adding a constant value to every attribute or multiplying each attribute with a positive number, should not affect the model and generate the same ranking as before.
-Thus, the metamorphic properties identified were: addition and multiplication.
-Applying the model on two sets of data, one of which created from the other, either by multiplying a positive number or, adding a constant number, should not change the ranking.
-Changing the order of examples should not affect the model or ranking since the algorithm sorts the inputs thus, MartiRank also has permutative metamorphic property.
-Multiplying the data by a negative constant value will create a new sorting order which can easily predicted.
+The metamorphic properties identified were: addition and multiplication.
+Changing the order of examples should not affect the model or ranking since the algorithm sorts the inputs, thus, MartiRank also has permutative metamorphic property.
+Multiplying the data by a negative constant value will create a new sorting order which can easily be predicted.
 The only change to the model will be the sorting direction i.e.
 the algorithm will change the sorting direction but keep the sorting order intact.
-Thus, MartiRank also displays an invertive metamorphic property where the output can be predicted by taking the opposite of input.
+Therefore, MartiRank also displays an invertive metamorphic property where the new output can be predicted by taking the opposite order of the original output.
 MartiRank also includes inclusive and exclusive metamorphic properties.
 Knowing the model can help predict the position of any new elements.
+Similar properties are also exhibited by SVM-Light and PAYL.
+If the training and testing data set were transformed using an additive, multiplicative, and/or invertive relationship, then the corresponding model (hyper-plane) would be affected by being shifted, expanded, or inverted in the N dimensions.
+The resulting ranking of the new model applied to the new data set would be the same as the original model applied to the original dataset because each example (or point in N dimensions) would similarly be moved, and the relative distances would stay the same.
+SVM considers each example in the testing data independently and ranks according to the distance from the hyperplane, therefore, it has the inclusive and exclusive property.
+Similarly, PAYL also considers the existence (or absence) of payloads of certain lengths, and thus certainly has inclusive metamorphic properties.
+From more study of these applications, the authors conclude that even though this not an exhaustive list of metamorphic relations, these metamorphic properties serve as a foundation for determining the relationships and transformations that can be used for conducting metamorphic testing.
 
-\subsection{Application of Metamorphic Testing to Supervised Classifiers \cite{Xie2009}}
-Building on the previous paper, the authors explore the metamorphic relations based on expected behavior of given machine learning problems.
+Xie et al.
+(2009) were also building on the previous work and exploring the metamorphic relations based on the expected behavior of given machine learning problems.
 They present a case study on Weka, a popular machine learning framework, which is also the foundation for computational science tools such as BioWeka in bioinformatics.
-In this paper the authors explore k-Nearest Neighbors and Naive Bayes classifier algorithms.
-Previously, they researched on Support Vector Machines.
-In this paper the authors seek to identify the metamorphic relations for the two algorithms (kNN and NBC).
-NBC and kNN both calculates the mean and standard deviation of the input data.
-Thus, the metamorphic relations identified are:
+The authors explore k-Nearest Neighbors and Naive Bayes classifier algorithms.
+NBC and k-NN both calculate the mean and standard deviation of the input data.
+The authors identified the metamorphic relations for the two algorithms (k-NN and NBC).
 Permuting the order of input data does not affect the mean or standard deviation.
-Multiplying the data with -1 does not affect the standard deviation since, the deviation from the mean will still be the same.
+Multiplying the data with -1 does not affect the standard deviation since the deviation from the mean will still be the same.
 Multiplying the data with some other positive number will increase the standard deviation by the same amount. Thus, the output will still be predictable.
+
+They created a set of random input data and used the above metamorphic relationships to generate another set of inputs.
+Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithms.
+Using this set of MR the authors were able to uncover a defect in NBC implementation.
+In the case of the k-NN algorithm, none of the necessary MRs was violated
 From the study of these algorithms, the authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
@@
 Current, software testing methods have not addressed the problem of validation and only focus on verification.
-The authors then performed an experiment to verify the correctness of Weka.
-They created a set of random input data and used the above metamorphic relationships to generate another set of inputs.
-Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithm.
-It was observed that several MRs violated NBC algorithms.
-Violations in the MRs that are necessary properties imply defects in implementation.
-In the case of kNN algorithm, none of the necessary MRs were violated which means that there are no implementation error as per the testing.
 
-\subsection{Dataset Coverage for Testing Machine Learning Computer Programs \cite{Nakajima2016}}
-Recently, computer programs for Big Data analytics or statistical machine learning have become essential components of intelligent software systems.
-Test oracles are rarely available for them, and this unavailability of test oracles is known as the oracle problem.
-Machine learning programs are a typical instance of non-testable programs and are of the known unknowns type.
-Metamorphic testing (MT) is a method for tackling the oracle problem.
-Metamorphic relations (MR) play a role as pseudo oracles to check whether executions of the same program differ for two different test inputs.
-The test inputs are related by translation functions derived from metamorphic properties so that the relationship between the two results is predictable.
-If the results coincide with each other, the program behavior is relatively correct.
-This paper studies the characteristics of the supervised learning classifiers (SUT).
-Identifying Quasi-testable Core: A program component, function or procedure, is quasi-testable if we have appropriate pseudo oracles or metamorphic relations.
-The result of the program execution embodies uncertainty because the output is accompanied by the statistical classification performance.
-The classifier itself is non-testable.
-However, pseudo oracles with a MT can be used for testing.\par
-Dataset Coverage: Test coverage is essential in software testing because it is a basis to measure how much of the SUT is checked with a set of the input test data.
-The graph coverage is the most popular model for software testing because it captures the structural characteristics of software artifacts, such as control-flows or data-flows of a computer program.
-The paper introduces the notion of dataset coverage to focus on the characteristics of the population distribution in the training dataset.
-However, complete coverage is not possible.
-The number of possible populations in datasets is also infinite.\par
-SVM: A support vector machine (SVM)  is a supervised machine learning classifier.
-The support vectors lie on the dotted hyperplanes parallel to the separating hyperplane.
-The margin, the minimum gap between the supporting hyperplane and the separating hyperplane, is chosen to be maximum.
-The pseudo code is a common, abstract description of implemented SMO computer programs.
-Because SMO is an algorithm for solving the SVM optimization problem, it corresponds to the model constructor and is an abstract version of the quasi-testable core.\par
-Main tasks:
-\begin{itemize}
-  \item Obtain pseudo oracles.
-  \begin{itemize}
-    \item MR for Pseudo Oracles: Various combinations of the dataset is obtained by reordering the dataset.
-    \item MR for Dataset Generation: Dataset is increased to increase the population of the input dataset.
-  \end{itemize}
-  \item Generate data points that achieve the required dataset coverage: In order that the result is predictable, the population distribution of the initial dataset is simple enough to contain linearly separable data points.
-Then a series of tests with pseudo oracles that are obtained based on appropriate metamorphic properties is conducted.
-Then dataset is extended by adding new data points to calculate a new hyperplane.
-\end{itemize}
-A similar metamorphic testing approach can be applied to K-nearest neighbors and naive Bayes classifiers.
-Since testing the whole program at once is not always possible choosing a right SUT from a non-testable program has a large impact on testing activities.
+Chen et al.
+\cite{Chen2016} also presented a specification-based tool called METRIC for the identification of metamorphic relations.
+In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames.
+The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.
 
-\cite{Segura2016}
-Composition of Metamorphic Relations (CMR) can be used to construct new metamorphic relations by combining several existing relations.
+Sometimes a single metamorphic property is not enough to uncover defects and we have to use multiple properties.
+These multiple properties can be applied in any combination.
+Segura did an research on how to combining these properties
+\cite{Segura2016} Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively.
+In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow-up test case of each metamorphic relation as the source test case of the next metamorphic relation.
+\par
+New metamorphic relations can be constructed by combining several existing relations.
+This is called Composition of Metamorphic Relations (CMR)\cite{Segura2016}.
 The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions.
-Two metamorphic relations are considered “compositable” if the follow-up test cases of one of the relations can always be used as source test case of the other.
+Two metamorphic relations are considered "compositable" if the follow-up test cases of one of the relations can always be used as a source test case of the other.
 The composition is sensitive to the order of metamorphic relations and generalizable to any number of them.
 Determining whether two metamorphic relations are composable is a manual task.
-Chen et al.
-\cite{Chen2016} presented a specification–based tool called METRIC for the identification of metamorphic relations.
-In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames.
-The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.

### 2019-08-25 chapters/litReview/finalLit.tex
Updates from Overleaf

@@
 Testing is one of the most important activity in software development life cycle.
-Bertolino (2007) define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions".
-Testing is widely used in industry for quality assurance purposes.
-Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service, etc.\cite{Bertolino2007} A study by Beizer (2006) has estimated that software testing can use up to fifty percent, or more, of the total development cost.
-Thus, it is clear that program software testing is worthy of our attention for research and improvement.\cite{Beizer1990}
-Weyuker (1982) categorizes the testing research activities into three categories:
+Bertolino \cite{Bertolino2007} define software testing as, ``observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions.'' Testing is widely used in industry for various quality assurance purposes.
+Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc.\cite{Bertolino2007} A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost.
+Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.
+Weyuker \cite{Weyuker} categorizes the testing research activities into three categories:
 \begin{enumerate}
@@
 These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments.
-In the context of software testing, the two fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle.
-\cite{Chen2002} \cite(Elbaum2014)
+In the context of software testing, the two very obvious fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle \cite{Chen2002,Elbaum2014}.
 Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used.
-While performing mathematical computations, errors from three sources can creep in:
+While performing mathematical computations, errors from three sources can creep in \cite{Weyuker}:
 \begin{enumerate}
@@
   \item The features of the environment like round-off, floating point operations etc.
-\end{enumerate}\cite{Weyuker}
+\end{enumerate}
 
- One of the first problems that testers run into is that they don't have access to acceptable output to test the program output against.
+ One of the first problems that testers run into while testing these uncertain programs is that they don't have access to acceptable output to test the program's predictions against.
 This problem is often referred to as the Oracle problem.
-Weyuker provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts.
-As per Weyuker, non-testable programs can be defined as the programs for which such oracles do not exist.
+Weyuker \cite{Weyuker} provides founding definition of an oracle as "a system that determines the correctness of the solution by comparing the system's output to the one that it predicts".
+She also defines non-testable programs as the programs for which such oracles do not exist.
 The term non-testable is used, from the point of view of correctness testing.
-If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.\cite{Weyuker}
+If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.
 
@@
 If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault.
-On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time.\cite(Elbaum2014)
+On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.
 
@@
 One way of elevating the oracle-problem is through the use of pseudo oracle.
-It is also referred to as dual-coding and is used in highly critical software.\cite{Weyuker}\cite{Murphy2009}.
+It is also referred to as dual-coding and is used in highly critical software \cite{Weyuker,Murphy2009}.
 Pseudo-oracles are multiple implementation of same specification of the original program under test.
  However, dual coding comes with it's own set of problems.
-As the authors [this and this ] pointed out that pseudo-oracle requires at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
- In light of shortcomings of the testing process the authors finally make five recommendation for items to be considered as a part of documentation during testing.
+As the authors Weyuker \cite{Weyuker} and Murphy, Shen, and, Kaiser \cite{Murphy2009} pointed out some limitations that pseudo-oracles require at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
+ In light of these shortcomings of the testing process Weyuker \cite{Weyuker} finally make five recommendation for items to be considered as a part of documentation during testing.
 \begin{enumerate}
@@
 \end{enumerate}
-Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.\cite(Weyuker)
+Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.
 
-But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation.  
+Due to a great deal of overhead involved, pseudo-oracles may not be practical for every situation.  
 A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined.
@@
 \cite{Weyuker}
-
-Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer.
-In such cases, we make use of partial oracles.
-It is relatively easier to test the systems on simpler inputs for which the output is known.
-There is rarely a single correct answer in these types of computations.
-Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution.

### 2019-08-25 chapters/litReview/metamorphicTesting.tex
Updates from Overleaf

@@
 In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test.
-It is almost impossible to generate all the possible combinations of test cases to completely test a program which is why a lot of research is being conducted to develop more error-revealing test case selection strategies.
+It is almost impossible to generate all the possible combinations of test cases to completely test a program.
+Thus, a lot of research is being conducted to develop more error-revealing test case selection strategies.
 A test case is called error-revealing if it is able to detect an error in the software otherwise it is labeled successful.
 Successful test case are the cases for which the program successfully computes the correct output.
-Since these test cases do not reveal any error, they are considered less important and are often not investigated further or, set aside for regression testing.
-{Zhou et al.
-(Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H.
-Huang‡, T.H.
-Tse§, Zongyuan Yang ¶, Haitao Huang ¶, and T.
-Y.
-Chen ‡)(Metamorphic testing and beyond) }
+Since these test cases do not reveal any error, they are considered less important and are often not investigated further or, set aside for regression testing \cite{Zhou2004, Chen2003}.
 
-Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem.
-Metamorphic testing reuses successful test cases to generate followup test cases according to metamorphic relations whose output can easily be predicted.
-A metamorphic relation(MR) is an expected relation among input and outputs of multiple executions of the target program(Metamorphic testing and beyond)(METRIC: METamorphic Relation Identification based on the Category - choice framework).
-To formally define MRs we can assume a function $f$ which produces the output $f(x)$ on input $x$.
-The MRs of the function can then be used to generate a transformation function $t$, which, when applied to input $x$ produces $t(x)$.
-This transformed input can then be run through the function $f$ and the transformation allows us to predict the value of $f(t(x))$(Automatic system testing of programs without test oracle).
-A simple example of a MR would be a program that calculates mean of a set of numbers.
-Certain transformations of the set of numbers will result in the same value for mean like: permuting the order of numbers, since, this neither changes the number of elements in the set nor the value of any element.
-Another transformation that can be used would be multiplying each number in the set with -1.
+Chen, Cheung, and Yiu \cite{Chen1998} first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem.
+Metamorphic testing reuses successful test cases to generate followup test cases according to metamorphic relations.
+Thus, rather being a test selection strategy, metamorphic testing is used to generate new test cases whose output can easily be predicted \cite{Murphy2008}.
+A metamorphic relation(MR) is an expected relation among input and outputs of multiple executions of the target program \cite{Chen2003,Zhou2016}.
+Consider a function $f$ which produces the output $f(x)$ on input $x$.
+The metamorphic relations of the function can then be used to generate a transformation function $t$, which, when applied to input $x$ produces $t(x)$.
+The transformed input $t(x)$ can then be run through the function $f$ to generate the output $f(t(x))$.
+This $f(t(x))$ is then compared to the expected behaviour of $f$ on $t(x)$ from the metamorphic relation to find any error.
+\cite{Murphy2009}.
+To demonstrate a MR, consider a program that calculates the mean of a set of real numbers.
+Certain transformations of the input numbers will result in the same value for mean.
+An example of this transformation can be a permutation of the order of input.
+Since, this does not changes the number of elements in the input set or the value of any element, we can safely assume that the mean will remain same.
+Another transformation could be to multiply each number in the input set with -1.
 The new mean will be the negative value of the previous mean.
-
-System under test(SUT)
+In both the cases we can easily predict the output for the newly generated test cases.
+Thus, multiplication and permutation are metamorphic relations for this algorithm.
 
@@
 Segura et al.
-did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing.
+\cite{Segura2016} did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing.
 They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems.
@@
 
-They first studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
+They also studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
 \begin{itemize}
@@
 \end{itemize}
+Research from Chen et al.
+shows that metamorphic relations that makes the subsequent execution the most different from the initial execution have the best chances of revealing failure.
+Although, they did not explicitly define what is meant by "different" in terms of multiple execution \cite{Chen2003}.
 
+The execution of a metamorphic test case is typically performed in two steps.
+First, a follow-up test case is generated by applying a transformation to the inputs of a source test case.
+Second, source and follow-up test cases are executed, checking whether their outputs violate the metamorphic relation.
 It should be noted that MT does not check the correctness of individual outputs.
 Instead, it checks the relations among several executions.
-Since no manual output predictions and comparisons are required, MT can be efficient and fully automated.
-\cite{Segura2016} The execution of a metamorphic test case is typically performed in two steps.
-First, a follow-up test case is generated by applying a transformation to the inputs of a source test case.
-Second, source and follow-up test cases are executed, checking whether their outputs violate the metamorphic relation.
-\par
-	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
-	A number of frameworks have been developed to automate the process of metamorphic testing.
+Since no manual output predictions and comparisons are required, MT can be efficient and fully automated \cite{Segura2016}.
+Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format.
+% 	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
+A number of frameworks have been developed to address this issue and automate the process of metamorphic testing.
 Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations.
@@
 Genetic algorithms have also been used for the selection of source test cases, to maximize the paths traversed in the program under test.
+But, their focus was on generation of new test cases and not on verifying that the metamorphic properties hold after execution.
 
-		In this paper the authors have demonstrated the usefulness of metamorphic testing in assessing the quality of applications without test oracles.
-Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format.
-The authors presented an approach called ``Automated Metamorphic System Testing'' to automate the metamorphic testing by considering the system as a blackbox and checking if the metamorphic properties holds after execution of the system.
-They also present another approach “Heuristic Metamorphic Testing” to reduce false positives and address some non-determinism.
-Unlike in the previous papers, here, the authors are focusing to improve the metamorphic testing technique itself.
-They list some benefits of using metamorphic testing: it can be used on broader domain of applications that display metamorphic properties, and it treats the application under test as a black box and does not require detailed understanding of the source code.
-\cite{Murphy2009}
+Murphy et al.
+\cite{Murphy2009} also demonstrated how metamorphic testing can be used to assess the quality of applications without test oracles.
+They presented an approach called ``Automated Metamorphic System Testing'' to automate the metamorphic testing by considering the system as a black box and checking if the metamorphic properties holds after multiple executions of the system.
+In this model $i)$ Metamorphic properties are specified by the tester and applied to the input.
+$ii)$ A transformation of the input is also generated and the original input is fed into the application.
+$iii)$ The transformed input is fed into a separate instance of the application running in a separate sandbox.
+$iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
+All a tester has to do is provide the metamorphic properties and does not require the knowledge of implementation.
 
-		\cite{Segura2016} Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively.
-In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow-up test case of each metamorphic relation as the source test case of the next metamorphic relation.
-\par
-		Murphy et al.
-\cite{Murphy2009} presented a framework named Amsterdam for the automated application of metamorphic testing.
+In order to demonstrate Automated Metamorphic System Testing they created a framework called Amsterdam.
 The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file.
+The XML specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.
 Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.
 
-		Automated Metamorphic System Testing: This technique can be used to test the application in development environment as well as in production as long as the users are only provided the output from the original execution and not the result from transformed input.
-In this model $i)$ Metamorphic properties are specified by the tester and applied to the input.
-$ii)$ The original input is fed into the application which is treated as a black-box and a transformation of the input is also generated.
-$iii)$ That transformed input is fed into a separate instance of the application running in a separate sandbox.
-$iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
-		Tester need not write any code and only needs to specify the metamorphic properties. They don't need to know the source code or other implementation details.
-		Amsterdam framework: The metamorphic properties are specified using XML file.
-The specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.\par
-		Heuristic Metamorphic testing: This method allows for small differences in outputs, in a meaningful way according to the application being used to address the problems of false positives and non-determinism.
-Imprecision in floating point calculation and representation of irrational number such as may result in failure of metamorphic testing even if the implementation is correct.
+While implementing Amsterdam framework, it became quite clear that small deviations in results calculations (like floating point operations) could cause a problem where exact results were expected.
+Also, many applications implements non-determinism for which outputs cannot be reliably predicted, hence, rendering metamorphic testing ineffective.
+To address this, they introduce a technique called "Heuristic Metamorphic Testing", based on the concept of "heuristic test oracles".
+Heuristic Metamorphic Testing reduces false positives and addresses non-determinism by allowing for small differences in outputs, in a meaningful way according to the application being used.
 If two outputs are close enough they are considered the same.
-The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.\cite{Murphy2009}
+The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.
+This approach also treats applications under test as black boxes and do not require detailed understanding of source code.
 
 Although metamorphic testing presents a lot of opportunities to expand on the existing testing processes, they also have some limitations.
-They then list some of the limitations of using metamorphic testing: \cite{Murphy2009}
+Murphy, et al.
+\cite{Murphy2009} list some of the limitations of using metamorphic testing:
 \begin{itemize}
@@
 
-		Some of the research challenges identified by the authors are:{A Survey on Metamorphic Testing \cite{Segura2016}}
+Segura, et al. \cite{Segura2016} also identified some research challenges:
 \begin{itemize}
 	\item Lack of guidelines, with step-by-step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
-			\item Prioritisation and minimisation of metamorphic relations: It is worth mentioning that test case minimisation is a NP-hard problem and therefore heuristic techniques should be explored.
+	\item Prioritization and minimization of metamorphic relations: It is worth mentioning that test case minimization is a NP-hard problem and therefore heuristic techniques should be explored.
 	\item Generation of likely metamorphic relations.

### 2019-08-25 chapters/litReview/mlAlgo.tex
Updates from Overleaf

@@
 \section{Overview of Machine Learning Algorithms}
-\subsection{Supervised Sequence Labelling with Recurrent Neural Networks \cite{Graves}}
-Artificial neural networks (ANNs) were originally developed as mathematical models of the information processing capabilities of biological brains.
-Although it is now clear that ANNs bear little resemblance to real biological neurons, they enjoy continuing popularity as pattern classifiers.
-The basic structure of an ANN is a network of small processing units, or nodes, joined to each other by weighted connections.
-In terms of the original biological model, the nodes represent neurons, and the connection weights represent the strength of the synapses between the neurons.
-The network is activated by providing an input to some or all of the nodes, and this activation then spreads throughout the network along the weighted connections.
-ANNs without cycles are referred to as feedforward neural networks (FNNs).
-Well known examples of FNNs include perceptrons, radial basis function networks, Kohonen maps and Hopfield nets.
-The most widely used form of FNN is the multilayer perceptron(MLP).
-It has been proven that an MLP with a single hidden layer containing a sufficient number of nonlinear units can approximate any continuous function on a compact input domain to arbitrary precision.
-For this reason MLPs are said to be universal function approximators.
-At each unit in a layer the activation function $\theta_h$ is applied, yielding the final activation $b_h$ of the unit.
-The most common choices for neural network activation function are the hyperbolic tangent and the logistic sigmoid.
-An important feature of both tanh and the logistic sigmoid is their nonlinearity.
-Nonlinear neural networks are more powerful than linear ones since they can, for example, find nonlinear classification boundaries and model nonlinear equations.
-Another key property is that both functions are differentiable, which allows the network to be trained with gradient descent.
-Because of the way they reduce an infinite input domain to a finite output range, neural network activation functions are sometimes referred to as squashing functions.
-The output vector $y$ of an MLP is given by the activation of the units in the output layer.
-The network input $a_k$ to each output unit $k$ is calculated by summing over the units connected to it, exactly as for a hidden unit.
-Both the number of units in the output layer and the choice of output activation function depend on the task the network is applied to.
-For classification problems with $K > 2$ classes, the convention is to have $K$ output units, and normalise the output activations with the softmax function to obtain the class probabilities which is also known as a multinomial logit model.
+\subsection{Neural network}
+Neural networks were first introduced in 1944 by two University of Chicago researchers Warren McCullough and Walter Pitts, who later moved to MIT in 1952.
+These algorithms are modeled loosely after the human brain, that are designed to recognize patterns.
+Dr.
+Robert Hecht-Nielsen, inventor of the first neurocomputer defines a neural network as:
+"...a computing system made up of a number of simple, highly interconnected processing elements, which process information by their dynamic state response to external inputs"\cite{Caudill}.
+\begin{figure}[htb!]
+    \centering
+    \includegraphics[scale=0.15]{files/nn.png}
+    \caption{Neural network}
+    \label{Neural network}
+    \end{figure}
+    \FloatBarrier
+% cite figure: https://towardsdatascience.com/applied-deep-learning-part-1-artificial-neural-networks-d7834f67a4f6
+A typical neural network looks like a variation of Figure 2.1. \\
+Input layer: The leftmost layer in the network is made up of input neurons and the layer is called the input layer.
+There is no computation performed in the nodes at this layer.
+Input layer simply provides the information from the environment to the next layer.
+Hidden layers: The layers in the middle make up the hidden layers, as the neurons in these layers are neither inputs nor outputs.
+There can be zero or multiple hidden layers.
+Hidden layers takes the input from the input layer and passes information to the output layer after performing computation on the data.
+Output layer: The rightmost or output layer contains the output neurons, or, as in this case, a single output neuron. 
+There are no set rules to design the layers of a neural network (specially the hidden layers) and this process is often considered as an art\cite{NN}.
+We determine the number of hidden layers and nodes empirically for each particular case in order to optimize performance.
+The edges (or connections) between a layer and the layer before it are represented by a weight $\omega_{ij}$, which represents the strength of connection between i and j nodes.
+During the training phase of the neural network, we assign random values to the weights for each connection.
+The algorithm then tries to optimize the weights so that the error function is minimized.
+For each node at a layer all the output from the previous node is multiplied by the weight of connections between them and the sum of all the different connections produces the value at that node.
+This cycle is repeated for all the nodes in every layer.
+The algorithm compares the prediction from the output layer to the real value and readjusts the weights.
+Once the optimal value is reached the network can be used to make predictions\cite{hall199}.
+
+These neural networks where the output from one layer is used as input to the next layer are called feedforward neural networks\cite{NN}\cite{hall199}.
+There are no loops in the feedforward neural network and the information flows in one direction and are never fed back.
+The most well known form of a feed forward neural network is called multilayer perceptron(MLP).
+MLPs are also called universal function approximator.
+A single hidden layer MLP with a sufficient number of nonlinear units can act as a continuous function on to a narrow input domain with arbitrary precision.
+\cite{Graves}.
+There are some other models of artificial neural networks in which feedback loops are possible.
+These models are called recurrent neural networks.
+The idea in these models is to have neurons which fire for some limited duration of time, before becoming quiescent.
+That firing can stimulate other neurons, which may fire a little while later, also for a limited duration.
+That causes still more neurons to fire, and so over time we get a cascade of neurons firing.
+Loops don't cause problems in such a model, since a neuron's output only affects its input at some later time, not instantaneously.
+Recurrent neural nets have been less influential than feedforward networks, in part because the learning algorithms for recurrent nets are (at least to date) less powerful.
+But recurrent networks are still extremely interesting.
+They're much closer in spirit to how our brains work than feedforward networks.
+And it's possible that recurrent networks can solve important problems which can only be solved with great difficulty by feedforward networks.\cite{NN} % cite: http://neuralnetworksanddeeplearning.com/chap1.html
+
+\subsection{Convolutional neural network}
+Convolutional neural networks (ConvNet) are very similar to ordinary neural networks in structure.
+They work by extracting simple features at a higher resolution and then converting them into more complex features at a coarser resolution \cite{simard2003best}.
+It does so by performing dot product on the inputs received at each neuron and optionally follow it with non-linearity.
+Just like a normal neural network, convolutional neural network (from the input image to output class) can be expressed as a single differential function.
+It also has a loss function on the fully-connected output layer.
+
+Convolutional Neural Networks (ConvNet) are very similar to ordinary Neural Networks.
+they are made up of neurons that have learnable weights and biases.
+Each neuron receives some inputs, performs a dot product and optionally follows it with a non-linearity.
+The whole network still expresses a single differentiable score function: from the raw image pixels on one end to class scores at the other.
+And they still have a loss function (e.g.
+SVM/Softmax) on the last (fully-connected) layer and all the tips/tricks we developed for learning regular Neural Networks still apply.
+What makes it different is that ConvNet architectures make the explicit assumption that the inputs are images, which allows us to encode certain properties into the architecture.
+These then make the forward function more efficient to implement and vastly reduce the amount of parameters in the network.
+Convolutional Neural Networks take advantage of the fact that the input consists of images and they constrain the architecture in a more sensible way.
+In particular, unlike a regular Neural Network, the layers of a ConvNet have neurons arranged in 3 dimensions: width, height, depth.
+(Note that the word depth here refers to the third dimension of an activation volume, not to the depth of a full Neural Network, which can refer to the total number of layers in a network).
+A ConvNet architecture is made up of the following layers: \\
+Input: This layer holds the raw input image in form of it's pixel values and color channels.\\
+Convolutional layer: This layer computes the dot product between it's weight and a small region in the previous layer it is connected to.\\
+Rectified linear unit: \\
+Fully connected layer: The fully connected output layer computes the class scores for the input. The neurons in this layer are connected to every neuron in the last layer.\\
+
+A simple ConvNet is a sequence of layers, and every layer of a ConvNet transforms one volume of activations to another through a differentiable function.
+We use three main types of layers to build ConvNet architectures: Convolutional Layer, Pooling Layer, and Fully-Connected Layer (exactly as seen in regular Neural Networks).
+We will stack these layers to form a full ConvNet architecture.
+
+RELU layer will apply an elementwise activation function, such as the $max(0,x)$ thresholding at zero. This leaves the size of the volume unchanged ([32x32x12]).
+POOL layer will perform a downsampling operation along the spatial dimensions (width, height), resulting in volume such as [16x16x12].
+FC (i.e.
+fully-connected) layer will compute the class scores, resulting in volume of size [1x1x10], where each of the 10 numbers correspond to a class score, such as among the 10 categories of CIFAR-10.
+As with ordinary Neural Networks and as the name implies, each neuron in this layer will be connected to all the numbers in the previous volume.
+\begin{figure}[htb!]
+    \centering
+    \includegraphics[scale=1.25]{chapters/litReview/files/convNet.png}
+    \caption{Convolutional Neural network \cite{convNN}}
+    \label{Neural network}
+    \end{figure}
+    \FloatBarrier
+
+Note that some layers contain parameters and other don’t.
+In particular, the CONV/FC layers perform transformations that are a function of not only the activations in the input volume, but also of the parameters (the weights and biases of the neurons).
+On the other hand, the RELU/POOL layers will implement a fixed function.
+The parameters in the CONV/FC layers will be trained with gradient descent so that the class scores that the ConvNet computes are consistent with the labels in the training set for each image.
+%cite http://cs231n.github.io/convolutional-networks/
+
+\subsection{Naive Bayes}
+In it's simplest form a Naive Bayes algorithm is a type of Bayesian network where all attributes are independent given the value of the class variable.
+This property is called conditional independence.
+It is obvious that the conditional independence assumption is rarely true in most real-world applications\cite{zhang2004optimality}.
+Despite this limitation the algorithm is very popular and works quite well in many real-world situations like document classification and spam filtering.
+The classifier is a really common supervised learning algorithm because it is fast, easy to implement and relatively effective.
+They also require relatively small number of training data to estimate the necessary parameters of the network\cite{scikit-learn}.
+Given a class variable $y$ and dependent feature vector $x_{1}$...$x_{n}$, Bayes theorem states that:
+\begin{center}
+    $P(y|x_{1},...,x_{n}) = \frac{P(y)P(x_{1},...,x_{n}|y)}{P(x_{1},...,x_{n})}$
+\end{center}
+From the conditional independence of features, and, value of a class we know that: 
+\begin{center}
+$P(y \mid x_1, \dots, x_n) = \frac{P(y) \prod_{i=1}^{n} P(x_i \mid y)}
+                                 {P(x_1, \dots, x_n)}$
+\end{center}
+% Include the equations from https://scikit-learn.org/stable/modules/naive_bayes.html
+For a given input $P(x_{1},...,x_{n})$ is constant. Therefore 
+\begin{center}
+$P(y \mid x_1, \dots, x_n) \propto P(y) \prod_{i=1}^{n} P(x_i \mid y)$
+\end{center}
+And an expected classification $\hat{y}$ can be obtained by:
+\begin{center}
+$\hat{y} = \arg\max_y P(y) \prod_{i=1}^{n} P(x_i \mid y)$
+\end{center}
+The main distinction between different versions of naive Bayes classifiers are the assumptions they make about the distribution of $P(x_i \mid y)$\cite{scikit-learn}.
+The multinomial Naive Bayes suffers from a systematic problem of assigning poor weights to necessary parameters if once class has more training examples than others.
+This effect lowers the weights for classes with less training examples\cite{rennie2003tackling}.
+For this reason we have equal numbers of training and testing examples for each class in our experiment.
+
+\subsection{k-Nearest Neighbor}
+The nearest neighbor classifier is a supervised classification technique which assigns an input sample vector (whose classification is to be predicted) to the class of it's nearest neighbors.
+The similarity between the input and the neighbors is calculated based on some distance metrics.
+This process does not require any pre-processing of the labeled set of neighbors before their use \cite{cover1967}.
+This idea can be further extended to assign the class of input variable to the class represented by majority of the $k$ nearest neighbors, where $k$ is a positive number specified by the user.
+The optimal value of $k$ depends on the data.
+A larger value of $k$ makes the classification boundaries less distinct while suppressing the noise effect \cite{scikit-learn}.
+One problem with implementing $k$ nearest algorithm is that in some cases there may be a tie among classes between the $k$ neighbors.
+This problem can be solved by restricting the values of $k$.
+In a binary classification problem, the values of $k$ can be restricted to odd numbers so that ties can be avoided.
+In a multi-class classification, this can be resolved by assigning the input to the class for which the sum of distance to each neighbor is the least.
+This could further lead to a tie and in that case an arbitrary assignment can be made \cite{keller1985}.
+\begin{figure}[htb!]
+    \centering
+    \includegraphics[scale=1]{files/knn.png}
+    \caption{$k$-Nearest neighbor}
+    \label{k-Nearest neighbor}
+    \end{figure}
+    \FloatBarrier
+
+\cite{cover1967}
+A set of n pairs is given $(x1,\theta 2),...(xn,\theta n)$ s.t the x′is take value in a metric space X upon which is defined a metric d.
+The category $\theta$ i is assigned to the ith sample or individual from finite subset {1,2, ... M} and xi is the measurement made upon that ith.
+we shall say ”xi belongs to $\theta$ i” when we mean precisely that the ith sample have measurement xi with category $\theta i$ .
+Our Goal is to classify the measurement x , for a new arriving pair $(x,\theta )$, the classification is procedure to estimate the $\theta$  since x is observable .
+The estimation of $\theta$  is done by utilizing the fact that we have set of n correctly classified points.
+We shall call : nearest neighbor of x if
+'xn ∈(x1,x2,x3,....xn)'
+min d(xi,x) = d(xn,x) i = 1,2,3...,n.
+
+In this case the decision of the nearest neighbor rule is assigning the category $\theta$ n to our new measurement x .
+The 1-NN rule decide x belongs to the category of nearest neighbor and ignored the others!.
+In general k-NN rule decide x belongs to the category of majority vote of the nearest k neighbors.
+
+\subsection{Support vector machine}
+A support vector machine (SVM)  is a supervised machine learning classifier.
+The support vectors lie on the dotted hyperplanes parallel to the separating hyperplane.
+The margin, the minimum gap between the supporting hyperplane and the separating hyperplane, is chosen to be maximum.
+The pseudo-code is a common, abstract description of implemented SMO computer programs.
+Because SMO is an algorithm for solving the SVM optimization problem, it corresponds to the model constructor and is an abstract version of the quasi-testable core.\cite{Nakajima2016}
+
+support vector machines (SVMs), based on statistical learning theory, are gaining applications in the areas of machine learning, computer vision and pattern recognition because of high accuracy and good generalisation capability
+
+Based on the structural risk minimization (SRM) principal, SVM can get decision-making rules and achieve small error for independent tests set and hence can solve the learning problems efficiently \cite{svm2008}.
+Recently SVM is applied to solve the problems such as nonlinear, local minimum and high dimension.
+In many practical applications, SVM can ensure higher accuracy for a long-term prediction compared to other computational approaches.
+SVM is based on the concept of decision planes that define decision boundaries.
+SVM creates a hyperplane by using a linear model to implement nonlinear class boundaries through some nonlinear mapping input vectors into a high-dimensional feature space \cite{SAMANTA2003657}
+
+It aims to create a decision boundary between two classes that enables the prediction of labels from one or more feature vectors (6).
+This decision boundary, known as the hyperplane, is orientated in such a way that it is as far as possible from the closest data points from each of the classes.
+These closest points are called support vectors.
+The most obvious drawback to the SVM algo- rithm, as described thus far, is that it apparently only handles binary classification problems. 
+Generalizing to multiclass clas- sification is straightforward and can be accom- plished by using any of a variety of methods.
+To recognize three classes, A, B and C, we simply have to train three separate SVMs to answer the binary questions, “Is it A?,” “Is it B?” and “Is it C?”.
+More sophisti- cated approaches also exist, which generalize the SVM optimization algorithm to account for multiple classes.
+\cite{noble2006support}
+The SVM algorithm was originally proposed to construct a linear classifier in 1963 by Vapnik (7).
+An alternative use for SVM is the kernel method, which enables us to model higher dimensional, non-linear models (8).
+In a non-linear problem, a kernel function could be used to add additional dimensions to the raw data and thus make it a linear problem in the resulting higher dimensional space (Figure 2).
+Briefly, a kernel function could help do certain calculations faster which would otherwise would need computations in high dimensional space.
+It is defined as:
+
+K (x, y)=<f(x), f(y)>
+
+Here K is the kernel function, x, y are n dimensional inputs.
+f is used to map the input from n dimensional to m dimensional space.
+<x, y> denotes the dot product.
+With kernel functions, we could calculate the scalar product between two data points in a higher dimensional space without explicitly calculating the mapping from the input space to the higher dimensional space.
+In many cases, computing the kernel is easy while going to the high dimensional space to compute the inner product of two feature vectors is hard.
+The feature vector for even simple kernels can blow up in size, and for kernels like the Radial Basis Function (RBF) kernel (KRBF(x, y) = exp (-γ||x - y||2), the corresponding feature vector is infinite dimensional.
+Yet, computing the kernel is almost trivial.
+
+The choice of kernel function among other factors could greatly affect the performance of an SVM model.
+However, there is no way to figure out which kernel would do the best for a specific pattern recognition problem.
+The only way to choose the best kernel is through trials.
+We can start with a simple SVM and then experiment with a variety of ‘standard’ kernel functions.
+Depending on the nature of the problem, it is possible that one kernel is better than the other kernels.
+An optimal kernel function can be selected from a fixed set of kernels in a statistically rigorous fashion by using cross-validation.
+
+\begin{figure}[htb!]
+    \centering
+    \includegraphics[scale=0.75]{files/svm.png}
+    \caption{SVM maximizes the margin between classes}
+    \label{SVM maximizes the margin between classes}
+    \end{figure}
+    \FloatBarrier

### 2019-08-25 chapters/methodology/collection.tex
new
Updates from Overleaf

@@
 \section{Algorithm}
+\subsection{Neural network}
+ Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections.
+If the image is a 64 by 64 greyscale image, then we'd have 4,096=64x64 input neurons, with the intensities scaled appropriately between 0 and 1.
+The output layer will contain just a single neuron, with output values of less than 0.5 indicating "input image is not a 9", and values greater than 0.5 indicating "input image is a 9 ".
+The input pixels are greyscale, with a value of 0.0 representing white, a value of 1.0 representing black, and in between values representing gradually darkening shades of grey.
+The second layer of the network is a hidden layer.
+
+2 layer
 \subsection{Convolutional neural network}
-\subsection{2-layer neural network}
+In EMNIST dataset, each image is single-channel of size 28 x 28 x 1.
+
+\subsection{Naive Bayes}
+What the function is 
+Input and output
+
+\subsection{k-Nearest Neighbor}
+The 1-NN rule decide x belongs to the category of nearest neighbor and ignored the others!.
+In general k-NN rule decide x belongs to the category of majority vote of the nearest k neighbors.
 
@@
             \includegraphics[width=\linewidth]{images/letter.png}
-            \caption{Sample EMNIST-MNIST dataset}
+            \caption{Sample EMNIST-Letter dataset}
             \label{fig:EMNIST MNIST dataset}

### 2019-08-25 chapters/methodology/properties.tex
Updates from Overleaf

@@
 \section{Identifying Metamorphic Relations} 
-We identified seven metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, shifting along-axis, zooming along x-axis, zooming along y-axis.
-Each image in the testing dataset (digit, letter, and, fashion) was transformed using the seven metamorphic properties.
+We identified five metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, and, shifting along y-axis.
+Each image in the testing dataset (digit, letter, and, fashion) was transformed using the five metamorphic properties.
 We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
@@
 \subsection{Shear}  
+The images were transformed between angle [-50, 50]
     \begin{figure}[!htbp]

### 2019-08-25 chapters/results/results.tex
Updates from Overleaf

@@
 \subsection{Robustness}
+We difined robustness in relative terms and we will be comparing the robustness of these algorithms with respect to each other for different datasets and different metamorphic relations.
+We also attempt to quantify robustness by measuring how tolerant the algorithm is to changes to original input.
 
@@
 To generate new data from MNIST digit dataset. While using rotation 0 should be in a prticular range. 1 should be in particular range.....
+
+We make following recommendations for transforming digits in MNIST dataset.
+\import{chapters/results/}{tables.tex}
+
+\newpage
+\section{Discussion}
+In this paper we identified five metamorphic properties that can be used with image datasets MNIST and MNIST-Fashion.
+We also provided recommendations for creating follow up test cases from this dataset by providing the most effective values to use for these metamorphic properties.
+We also evaluated the robustness of five machine learning algorithms on these metamorphic properties.

### 2019-08-25 chapters/results/tables.tex
Updates from Overleaf

\subsection{Rotate}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
\hline
Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
\hline
0  &   -37&46 & -44&31 & -50&17 & -45&45 & -50&49 \\
\hline
1 &   -15&18 & -11&15 & -9&12 & -21&22 & -28&43  \\
\hline
2  &   -19&15 & -14&11 & -12&10 & -14&12 & -19&16  \\
\hline
3  &   -20&15 & -17&15 & -9&19 & -17&13 & -25&26  \\
\hline
4  &   -15&15 & -12&15 & -13&14 & -15&22 & -14&15 \\
\hline
5  &   -16&17 & -9&8 & -14&5 & -11&10 & -25&18  \\
\hline
6  &   -26&32 & -20&43 & -11&36 & -16&43 & -19&37 \\
\hline
7  &   -18&11 & -19&8 & -13&7 & -20&11 & -19&13 \\
\hline
8  &   -16&18 & -13&15 & -13&12 & -14&21 & -17&15 \\
\hline
9  &   -21&24 & -10&18 & -6&22 & -12&16 & -11&18 \\ 
\hline
\end{tabular}
\caption{Rotate.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 41.4  & 17.45  & 0  \\
    NN    & 34.8 & 24.75  & 0  \\
    NB    & 30.4 & 42.0 & 0 \\
    SVM   & 40.0 & 29.1 & 0 \\
    KNN   & 47.7  & 20.81 & 0.0 \\
    }\rotate

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=75,
            ylabel={\%},
        ]
        \addplot table[x=interval,y=Digit]{\rotate};
        \addplot table[x=interval,y=Fashion]{\rotate};
        \addplot table[x=interval,y=Letter]{\rotate};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}

\subsection{ShiftX}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
     & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
    \hline
    Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
    \hline
    0  &   -5&4 & -3&3 & -4&3 & -4&3 & -4&4 \\
    \hline
        \multirow{3}{*}{1}
            &-50&-29 & -50&-38 &  \multirow{3}{*}{-2}&\multirow{3}{*}{2} & -50&-28 & -50&-25\\
            &-5&5 & -2&1 & & & -6&4 & -9&11\\
            &32&49 & 40&49  & & & 28&49 & 27&49\\
    \hline
    \multirow{2}{*}{2}  
        &   \multirow{2}{*}{-7}&\multirow{2}{*}{7}  &  \multirow{2}{*}{-5}&\multirow{2}{*}{6}  &  -41&-25   &  \multirow{2}{*}{-5}&\multirow{2}{*}{8} & \multirow{2}{*}{-5}&\multirow{2}{*}{11}\\
        & & &   & & -12&6   & & & &\\          
    \hline
    3  &   -6&3 & -7&1 & -7&0 & -7&2 & -8&4  \\
    \hline
    4  &   -7&6 & -4&4 & -5&5 & -4&5 & -5&4 \\
    \hline
    5  &   -5&8 & -2&7 & -2&21 & -3&9 & -5&13 \\
    \hline
    6  &   -5&8 & -4&4 & -3&3 & -5&5 & -5&5 \\
    \hline
    7  &   -5&6 & -6&2 & -4&2 & -7&4 & -11&4 \\
    \hline
    8  &   -4&5 & -2&4 & -1&5 & -3&4 & -3&6 \\
    \hline
    9  &   -5&5 & -4&2 & -2&2 & -4&3 & -3&3 \\ 
    \hline
\end{tabular}
\caption{ShiftX.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 12.42  & 10.75  & 0  \\
    NN    & 7.83 & 14.71  & 0  \\
    NB    & 9.73 & 22.27 & 0 \\
    SVM   & 11.5 & 11.18 & 0 \\
    KNN   & 14.17  & 9.27 & 0.0 \\
    }\shiftX

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=50,
            ylabel={\Angle},
        ]
        \addplot table[x=interval,y=Digit]{\shiftX};
        \addplot table[x=interval,y=Fashion]{\shiftX};
        \addplot table[x=interval,y=Letter]{\shiftX};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}
MNIST: KNN is the most robust.

\subsection{Shade}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
\hline
Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
\hline
0  &   0.0&0.6 & 0.0&0.74 & 0.0&0.96 & 0.0&0.5 & 0.0&0.51 \\
\hline
1  &   0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 \\
\hline
2  &   0.0&0.64 & 0.0&0.78 & 0.0&0.93 & 0.0&0.5 & 0.0&0.49 \\
\hline
3  &   0.0&0.62 & 0.0&0.76 & 0.0&0.97 & 0.0&0.49 & 0.0&0.5  \\
\hline
4  &   0.0&0.63 & 0.0&0.87 & 0.0&0.99 & 0.0&0.51 & 0.0&0.5 \\
\hline
5  &   0.0&0.62 & 0.0&0.91 & 0.0&0.92 & 0.0&0.53 & 0.0&0.5  \\
\hline
6  &   0.0&0.62 & 0.0&0.81 & 0.0&0.97 & 0.0&0.5 & 0.0&0.5 \\
\hline
7  &   0.0&0.6 & 0.0&0.89 & 0.0&0.98 & 0.0&0.51 & 0.0&0.52\\
\hline
8  &   0.0&0.57 & 0.0&0.61 & 0.0&0.9 & 0.0&0.49 & 0.0&0.49\\
\hline
9  &   0.0&0.57 & 0.0&0.7 & 0.0&0.94 & 0.0&0.5 & 0.0&0.5\\ 
\hline
\end{tabular}
\caption{Shade.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 64.6  & 55.6  & 0  \\
    NN    & 80.6 & 56.1  & 0  \\
    NB    & 95.5 & 68.63 & 0 \\
    SVM   & 55.2 & 55.8 & 0 \\
    KNN   & 55.0  & 51.9 & 0.0 \\
    }\shade

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={\%},
        ]
        \addplot table[x=interval,y=Digit]{\shade};
        \addplot table[x=interval,y=Fashion]{\shade};
        \addplot table[x=interval,y=Letter]{\shade};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}

\subsection{Shear}
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
\hline
Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
\hline
0  &   -24&28 & -19&16 & -17&10 & -36&25 & -50&39 \\
\hline
1  &   -50&18 & -24&14 & -14&10 & -50&24 & -50&49 \\
\hline
2  &   -22&33 & -25&25 & -17&49 & -25&26 & -32&29 \\
\hline
3  &   -25&23 & -31&21 & -12&33 & -32&22 & -35&35  \\
\hline
4  &   -25&20 & -17&17 & -25&13 & -21&31 & -24&18 \\
\hline
5  &   -32&26 & -24&18 & -45&4 & -25&23 & -31&27  \\
\hline
6  &   -39&29 & -23&30 & -9&21 & -31&30 & -40&34 \\
\hline
7  &   -21&20 & -23&18 & -26&40 & -24&23 & -26&16 \\
\hline
8  &   -26&25 & -22&23 & -16&17 & -36&27 & -36&22 \\
\hline
9  &   -17&21 & -13&15 & -6&15 & -20&16 & -23&15\\ 
\hline
\end{tabular}
\caption{Shear.}
\label{tbl:test-file-format}
\end{table}

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & Digit & Fashion & Letter \\
    CNN   & 52.4  & 38.82  & 0  \\
    NN    & 41.8 & 41.18  & 0  \\
    NB    & 39.9 & 53.6 & 0 \\
    SVM   & 54.7 & 53.8 & 0 \\
    KNN   & 63.1  & 45.1 & 0.0 \\
    }\shade

\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            width=\textwidth,
            height=.5\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,SVM,KNN},
            xtick=data,
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={\%},
        ]
        \addplot table[x=interval,y=Digit]{\shade};
        \addplot table[x=interval,y=Fashion]{\shade};
        \addplot table[x=interval,y=Letter]{\shade};
        \legend{Digit, Fashion, Letter}
    \end{axis}
\end{tikzpicture}

### 2020-04-13 chapters/introduction/introduction.tex
final draft

@@
+Machine learning algorithms are gaining rapid popularity 
+Testing 
+Oracle problem
+In this paper we first introduce metamorphic testing. Then identify new metamorphic properties for image datasets.
+
 Machine learning has gained rapid popularity in the past decade and different sectors like healthcare, finance, retail, etc.
-are using machine learning to provide better products and services.
+are using machine learning techniques to provide better products and services.
 This rising popularity has created a demand for better implementation of the state-of-the-art algorithms in order to implement more complex and sophisticated use cases.
-Machine learning has been around for a long time now and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.
-While developing and training a machine learning model, the developers rely on the accuracy of the libraries to produce best results.
-The aim is to create a model that makes the best predictions.
+Machine learning algorithms has been around for a long time now and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.
+While developing and training a machine learning model, the developers rely on the accuracy of these libraries to produce best results where the aim is to create a model that makes the best predictions.
 Conventionally, oracles have been used to test the correctness of a program.
@@
 Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Weyuker}.
-Davis and Weyuker describe these set of programs as \enquote{Programs which were written in order to determine the answer in the first place.
+Davis and Weyuker describe these programs as \enquote{Programs which were written in order to determine the answer in the first place.
 There would be no need to write such programs if the correct answer were known}\cite{Davis1981}.
@@
   %\item Can we quantify reliability of predictions made by machine learning algorithms?
-  \item Identifying metamorphic properties that can be used to generate new test data from image datasets.
+    \item Identify metamorphic properties that can be used to generate new test data from image datasets.
 %   \item How does metamorphic properties affect different dataset and deep-learning algorithms?
-  \item Robustness of the deep learning algorithms to the identified metamorphic properties?
-  \item What range of Metamorphic properties identified is most useful while generating new test cases.
+    \item Does metamorphic properties have similar affect on the individual classes in a dataset.
+    \item What range of metamorphic transformation produce similar accuracy as the original dataset?
+    % \item Are some machine-learning algorithms more robust than others?
+
 %   \item How sensitive are the predictions made by ML algorithms to the change in input data?

### 2020-04-13 chapters/litReview/mlAlgo.tex
final draft

@@
 % cite figure: https://towardsdatascience.com/applied-deep-learning-part-1-artificial-neural-networks-d7834f67a4f6
-A typical neural network looks like a variation of Figure 2.1. \\
+A typical neural network looks like a variation of Figure \ref{Neural network}. \\
 Input layer: The leftmost layer in the network is made up of input neurons and the layer is called the input layer.
@@
 Just like a normal neural network, convolutional neural network (from the input image to output class) can be expressed as a single differential function.
-It also has a loss function on the fully-connected output layer.
+It also has a loss function on the fully-connected output layer and the neurons have learnable weights and biases which are optimized during the learning phase.
 
-Convolutional Neural Networks (ConvNet) are very similar to ordinary Neural Networks.
-they are made up of neurons that have learnable weights and biases.
-Each neuron receives some inputs, performs a dot product and optionally follows it with a non-linearity.
-The whole network still expresses a single differentiable score function: from the raw image pixels on one end to class scores at the other.
-And they still have a loss function (e.g.
-SVM/Softmax) on the last (fully-connected) layer and all the tips/tricks we developed for learning regular Neural Networks still apply.
-What makes it different is that ConvNet architectures make the explicit assumption that the inputs are images, which allows us to encode certain properties into the architecture.
-These then make the forward function more efficient to implement and vastly reduce the amount of parameters in the network.
-Convolutional Neural Networks take advantage of the fact that the input consists of images and they constrain the architecture in a more sensible way.
+What makes it different from an ordinary neural network is the architecture of a ConvNet.
+It makes explicit assumption that the inputs are images, which allows us to encode certain properties into the architecture.
 In particular, unlike a regular Neural Network, the layers of a ConvNet have neurons arranged in 3 dimensions: width, height, depth.
-(Note that the word depth here refers to the third dimension of an activation volume, not to the depth of a full Neural Network, which can refer to the total number of layers in a network).
-A ConvNet architecture is made up of the following layers: \\
-Input: This layer holds the raw input image in form of it's pixel values and color channels.\\
-Convolutional layer: This layer computes the dot product between it's weight and a small region in the previous layer it is connected to.\\
-Rectified linear unit: \\
-Fully connected layer: The fully connected output layer computes the class scores for the input. The neurons in this layer are connected to every neuron in the last layer.\\
+A simple ConvNet is a sequence of layers and every layer transforms one volume of activation to another through a differentiable function.
 
-A simple ConvNet is a sequence of layers, and every layer of a ConvNet transforms one volume of activations to another through a differentiable function.
-We use three main types of layers to build ConvNet architectures: Convolutional Layer, Pooling Layer, and Fully-Connected Layer (exactly as seen in regular Neural Networks).
-We will stack these layers to form a full ConvNet architecture.
-
-RELU layer will apply an elementwise activation function, such as the $max(0,x)$ thresholding at zero. This leaves the size of the volume unchanged ([32x32x12]).
-POOL layer will perform a downsampling operation along the spatial dimensions (width, height), resulting in volume such as [16x16x12].
-FC (i.e.
-fully-connected) layer will compute the class scores, resulting in volume of size [1x1x10], where each of the 10 numbers correspond to a class score, such as among the 10 categories of CIFAR-10.
-As with ordinary Neural Networks and as the name implies, each neuron in this layer will be connected to all the numbers in the previous volume.
 \begin{figure}[htb!]
@@
     \caption{Convolutional Neural network \cite{convNN}}
-    \label{Neural network}
+    \label{Convolutional Neural network}
     \end{figure}
@@
 
-Note that some layers contain parameters and other don’t.
-In particular, the CONV/FC layers perform transformations that are a function of not only the activations in the input volume, but also of the parameters (the weights and biases of the neurons).
-On the other hand, the RELU/POOL layers will implement a fixed function.
-The parameters in the CONV/FC layers will be trained with gradient descent so that the class scores that the ConvNet computes are consistent with the labels in the training set for each image.
+A ConvNet architecture is made up of the following layers and these layers are stacked to form the full network \cite{krizhevsky2012imagenet}: \\
+Input layer: This layer holds the raw input image in form of it's pixel values and color channels.\\
+Convolutional layer (Conv): This layer computes the dot product between it's weight and a small region in the previous layer it is connected to.
+It is a linear operation which multiplies the input from the previous layer to a two-dimensional array of weights called filter or kernel.
+\\
+Rectified linear unit (ReLu): This layer applies an element-wise activation function, like $max(0,x)$ with the threshold at zero.
+It introduces non-linearity to the system which has just been doing linear computations (element wise multiplication and sum) in previous Conv layers.
+\\
+Pooling layer (POOL): This layer performs a downsampling operation along the spatial dimensions.
+This helps in two major ways: $i)$ The amount of parameters or weights is reduced by 75\%.
+$ii)$ It also reduces the problem of overfitting.\\
+Fully connected layer (FC): The fully connected output layer computes the class scores for the input.
+The neurons in this layer are connected to every neuron in the previous layer.
+The only difference between this layer and the Conv layer is that the neurons in Conv layer are only connected to a local region in the input layer and the neurons in Conv layer share parameters.
+The neurons in both the layer compute dot product and their function form is identical.
+Thus, it is easily possible to convert between the fully connected and Conv layer.\\
+
+It should be noted that some layers contain parameters while others may not.
+The ReLu/Pool layer implements a fixed function whereas, the Conv/FC layers transformation functions work on the activations in the input volume and the weights and biases of the neurons.
+The parameters in Conv/FC layer is trained using gradient descent such that the scores computed by ConvNet is consistent with the expected output of each image in the training set \cite{convNNStan}.
 %cite http://cs231n.github.io/convolutional-networks/
@@
 In a multi-class classification, this can be resolved by assigning the input to the class for which the sum of distance to each neighbor is the least.
-This could further lead to a tie and in that case an arbitrary assignment can be made \cite{keller1985}.
+This could further lead to a tie and in that case an arbitrary assignment has to be made \cite{keller1985}.
 \begin{figure}[htb!]
@@
 
-\cite{cover1967}
-A set of n pairs is given $(x1,\theta 2),...(xn,\theta n)$ s.t the x′is take value in a metric space X upon which is defined a metric d.
-The category $\theta$ i is assigned to the ith sample or individual from finite subset {1,2, ... M} and xi is the measurement made upon that ith.
-we shall say ”xi belongs to $\theta$ i” when we mean precisely that the ith sample have measurement xi with category $\theta i$ .
-Our Goal is to classify the measurement x , for a new arriving pair $(x,\theta )$, the classification is procedure to estimate the $\theta$  since x is observable .
-The estimation of $\theta$  is done by utilizing the fact that we have set of n correctly classified points.
-We shall call : nearest neighbor of x if
-'xn ∈(x1,x2,x3,....xn)'
-min d(xi,x) = d(xn,x) i = 1,2,3...,n.
-
-In this case the decision of the nearest neighbor rule is assigning the category $\theta$ n to our new measurement x .
-The 1-NN rule decide x belongs to the category of nearest neighbor and ignored the others!.
-In general k-NN rule decide x belongs to the category of majority vote of the nearest k neighbors.
+Given a set of n test data $(x_i, y_i),\dots(x_n, y_n)$ where $x_i$ is the feature vector and $y_i$ is the class label.
+$x_i$ is defined in a feature space $X$ with distance metric $d$.
+For a new incoming input $(x, y)$ the goal is to estimate the value of $y$ using the set of already classified data points.
+A data point $\acute{x_n} \in (x_1, x_2, \dots x_n)$ is said to be the nearest neighbor of $x$ if:
+\begin{center}
+$min\ d(x_i,x) = d(\acute{x_n},x) i = 1,2,3...,n.$ 
+\end{center}
+$x$ is then assigned to the category of $\acute{y_n}$.
+If $k = 1$, the algorithm assigns $x$ to the category of it's nearest neighbor, ignoring the others.
+In general, $k$-NN assigns $x$ to the majority class of nearest $k$ neighbors \cite{cover1967}.
 
 \subsection{Support vector machine}
-A support vector machine (SVM)  is a supervised machine learning classifier.
-The support vectors lie on the dotted hyperplanes parallel to the separating hyperplane.
-The margin, the minimum gap between the supporting hyperplane and the separating hyperplane, is chosen to be maximum.
-The pseudo-code is a common, abstract description of implemented SMO computer programs.
-Because SMO is an algorithm for solving the SVM optimization problem, it corresponds to the model constructor and is an abstract version of the quasi-testable core.\cite{Nakajima2016}
-
-support vector machines (SVMs), based on statistical learning theory, are gaining applications in the areas of machine learning, computer vision and pattern recognition because of high accuracy and good generalisation capability
-
-Based on the structural risk minimization (SRM) principal, SVM can get decision-making rules and achieve small error for independent tests set and hence can solve the learning problems efficiently \cite{svm2008}.
-Recently SVM is applied to solve the problems such as nonlinear, local minimum and high dimension.
-In many practical applications, SVM can ensure higher accuracy for a long-term prediction compared to other computational approaches.
-SVM is based on the concept of decision planes that define decision boundaries.
-SVM creates a hyperplane by using a linear model to implement nonlinear class boundaries through some nonlinear mapping input vectors into a high-dimensional feature space \cite{SAMANTA2003657}
-
-It aims to create a decision boundary between two classes that enables the prediction of labels from one or more feature vectors (6).
-This decision boundary, known as the hyperplane, is orientated in such a way that it is as far as possible from the closest data points from each of the classes.
+A support vector machine (SVM) is a supervised machine learning classifier based on the structural risk minimization (SRM) principal.
+It solves learning problems by making decision-based rules and minimizing error for independent samples \cite{svm2008}.
+It has gained rapid popularity in the fields of machine learning, pattern recognition and computer vision because of high accuracy and good generalization capability.
+SVM creates a decision boundary, also known as hyperplanes, between elements of two classes that allows it to make predictions from one or more feature vectors.
+The hyperplanes are oriented such that it maximizes the distance between the closest data points in the two classes.
 These closest points are called support vectors.
-The most obvious drawback to the SVM algo- rithm, as described thus far, is that it apparently only handles binary classification problems. 
-Generalizing to multiclass clas- sification is straightforward and can be accom- plished by using any of a variety of methods.
-To recognize three classes, A, B and C, we simply have to train three separate SVMs to answer the binary questions, “Is it A?,” “Is it B?” and “Is it C?”.
-More sophisti- cated approaches also exist, which generalize the SVM optimization algorithm to account for multiple classes.
-\cite{noble2006support}
-The SVM algorithm was originally proposed to construct a linear classifier in 1963 by Vapnik (7).
-An alternative use for SVM is the kernel method, which enables us to model higher dimensional, non-linear models (8).
-In a non-linear problem, a kernel function could be used to add additional dimensions to the raw data and thus make it a linear problem in the resulting higher dimensional space (Figure 2).
-Briefly, a kernel function could help do certain calculations faster which would otherwise would need computations in high dimensional space.
-It is defined as:
-
-K (x, y)=<f(x), f(y)>
-
-Here K is the kernel function, x, y are n dimensional inputs.
-f is used to map the input from n dimensional to m dimensional space.
-<x, y> denotes the dot product.
-With kernel functions, we could calculate the scalar product between two data points in a higher dimensional space without explicitly calculating the mapping from the input space to the higher dimensional space.
-In many cases, computing the kernel is easy while going to the high dimensional space to compute the inner product of two feature vectors is hard.
-The feature vector for even simple kernels can blow up in size, and for kernels like the Radial Basis Function (RBF) kernel (KRBF(x, y) = exp (-γ||x - y||2), the corresponding feature vector is infinite dimensional.
-Yet, computing the kernel is almost trivial.
-
-The choice of kernel function among other factors could greatly affect the performance of an SVM model.
-However, there is no way to figure out which kernel would do the best for a specific pattern recognition problem.
-The only way to choose the best kernel is through trials.
-We can start with a simple SVM and then experiment with a variety of ‘standard’ kernel functions.
-Depending on the nature of the problem, it is possible that one kernel is better than the other kernels.
-An optimal kernel function can be selected from a fixed set of kernels in a statistically rigorous fashion by using cross-validation.
-
+Support vectors are the input data $x_i$ for which $|y_i|(wx_i^T + b)=1$.
+It creates these nonlinear boundaries by mapping input vectors to a higher dimensional feature space \cite{SAMANTA2003657,Nakajima2016}.
 \begin{figure}[htb!]
@@
     \FloatBarrier
+
+Given a set of training feature vector $x_i \in R_d$ with label $y_i \in (−1, +1)$: $(x_1, y_1), ..., (x_n, y_n)$ \\
+A hyperplane is defined as:
+\begin{center}
+    $wx^T + b=0$
+\end{center}
+where $w$ is the weight vector, and $b$ is the bias.
+$w$ and $b$ are selected such that the following condition holds for all the elements in the training set.
+\begin{center}
+    $wx_i^T + b \geq +1$ if $y_i=1$\\
+    $wx_i^T + b \leq −1$ if $y_i=–1$
+\end{center}
+During the training step, the model tries to place the hyperplace such that it maximizes the distance between the support vectors.
+This is done by finding the optimal values for $w$ and $b$ such the value of $1/(\parallel w\parallel)^2$ is maximum.
+
+The obvious problem with SVM described above is that it works only in binary classification problems.
+A number of methods can be employed to enable SVM for multiclass classification.
+To classify an input data to three classes, x, y, and, z, three SVMs are needed to answer: $i)$ Is it x?
+$ii)$ Is it y?
+$iii)$ Is it z?\cite{noble2006support}
+An alternative way is to make use of kernel methods which enables us to model higher dimensional, non-linear models.
+A kernel function helps us to do faster calculations which would otherwise require higher dimensional computation.
+It adds additional dimension to the input data and makes it a linear problem in a higher dimensional feature space.
+A kernel function is defined as:
+\begin{center}
+  $K (x, y)=<f(x), f(y)>$ where,  
+\end{center}
+$K$ is the kernel function.\\
+$x, y$ are $m$ dimensional inputs.\\
+$f$ maps the inputs from $m$ dimensional feature space to $n$ dimensional feature space.\\
+$<x, y>$ denotes a dot product.\\
+Kernels can heavily affect the performance of a SVM but unfortunately there is no set way of choosing a kernel.
+We can start with a simpler kernel and then experiment with a number of standard kernels to produce best predictions by using cross-validation \cite{huang2018applications}.

### 2020-04-13 chapters/methodology/collection.tex
final draft

--- 2019-08-04 chapters/methodology/collection.tex
@@
  \section{Tools}
-\subsection{Jupyter}
-The Jupyter Notebook is an open-source web application that supports data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, etc.
-by allowing us to create and share documents that contain live code, equations, visualizations and narrative text.
-Jupyter allows for displaying the result of computation inline in the form of rich media (SVG, LaTeX, etc.).
-The Jupyter notebook combines two components:
+We used Python as the programming language to implement our code.
+We chose Python because of it's popularity and easy syntax.
+There are also a plenty of Pythonn libraries like Tensorflow, Keras and scikit-learn available to easily implement machine learning, deep-learning, natural language processing algorithms.
+Along with Python as a programming language we also used following programs, tools, and datasets to perform our experiment.
+\subsection{HCC}
+Due to the high computation requirements for some dataset we needed a faster and reliable hardware.
+The Holland Computing Center (HCC) claim to be the fastest resource in the state of Nebraska.
+HCC provides these services to researcher and students associated with any campus of the University of Nebraska system.
+Some shared services are available for free and dedicated services can be obtained for a modest price.
+We used their servers to run our Jupyter notebooks.
+
+\subsection{Jupyter Notebook}
+Jupyter notebook is part of project Jupyter which aims to provide interactive interface for development across multiple platforms and programming languages.
+Jupyter's web interface supports data cleaning, data transformation and visualization, numerical operations etc.
+It allows us to create live code snippets and equations and shows results of inline computation right next to the code in the form of rich media (SVG, LaTeX etc).
+It combines two components:
 \begin{itemize}
-  \item \textbf{A web application}: a browser-based tool for interactive authoring of documents which combine explanatory text, mathematics, computations and their rich media output.
-  \item \textbf{Notebook documents}: a representation of all content visible in the web application, including inputs and outputs of the computations, explanatory text, mathematics, images, and rich media representations of objects.
+  \item \textbf{A web application}: a web-based interactive tool to write code, markdown, etc. It also displays the rich media output.
+  \item \textbf{Notebook documents}: a representation of all the content written and displayed using the web application.
 \end{itemize}
 Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy.
-In this project, the codes are written in python notebook which can be accessed from http://github.com/.
+In this project, the codes are written in python notebook which can be accessed from our github repository.
 
 \subsection{Tensorflow}
+TensorFlow is an end-to-end open source platform for machine learning.
+It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications
 TensorFlow\textsuperscript{TM} is an open source software library developed within Google’s AI organization by the Google Brain team with a strong support for machine learning and deep learning.
@@
 It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}.
+Tensorflow provides api for loading the MNIST dataset identified in section \ref{dataset}.
+We also used tensorflow to implement neural network and convolutional neural network defined in section \ref{Algorithms}
 
-\section{Algorithm}
+\subsection{Scikit-learn}
+Scikit-learn is a Python module for machine learning built on top of SciPy and is distributed under the 3-Clause BSD license.
+It provides a range of supervised and unsupervised learning algorithms via a consistent interface in Python.
+
+\section{Algorithms}\label{Algorithms}
+We implemented some popular machine learning algorithms to test our hypothesis that "small changes to input data will not affect the accuracy of the model drastically".
+We used TensorFlow and scikit-learn to implement the machine learning algorithms.
 \subsection{Convolutional neural network}
-\subsection{2-layer neural network}
+The images in the MNIST dataset is a one dimensional vector of 784 features (28x28 pixels).
+We first reshape the images to match the picture format height x width x channel.
+Each image in the MNIST dataset is now a single-channel of 28x28x1 size.
+The images are now fed into the network as input.
+The first convolution layer has 32 filters with a kernel size of five.
+The activation function we used is the ReLU function and the output from this layer is fed into a pooling layer.
+The data goes through another iteration of convolution and pooling before being flattened and sent to the fully connected layer.
+The output layer gives us a number which corresponds to the class of the image it is assigned to.
 
-\section{Dataset}
+\subsection{Neural network}
+
+ Hidden fully connected layer with 256 neurons.
+Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections.
+If the image is a 64 by 64 greyscale image, then we'd have 64x64=4,096 input neurons, with the intensities scaled appropriately between 0 and 1.
+The output layer will contain just a single neuron, with output values of less than 0.5 indicating "input image is not a 9", and values greater than 0.5 indicating "input image is a 9 ".
+The input pixels are greyscale, with a value of 0.0 representing white, a value of 1.0 representing black, and in between values representing gradually darkening shades of grey.
+The second layer of the network is a hidden layer.
+
+2 layer
+
+\subsection{Naive Bayes}
+We used scikit-learn to implement Naive Bayes algorithm. The images were first transformed to a one dimensional vector of 784 features. 
+A naive bayes classifier is then created using the $sklearn.naive\_bayes.MultinomialNB()$ function.
+This classifier is then fitted using the $fit()$ function, which takes the images and labels as input and fits the classifier according to the images and labels.
+The resulting classifier is then used to predict the labels of test data.
+
+\subsection{$k$-Nearest Neighbor}
+ We used scikit-learn to implement our $k$-nearest neighbor algorithm. Scikit's $sklearn.neighbors$ module provides functionality for unsupervised and supervised neighbors-based learning methods. 
+ The $KNeighborsClassifier$ function from the $sklearn.neighbors$ module implements learning based on the $k$ nearest neighbors of each query point, where $k$ is an integer value specified by the user.
+The $k$-neighbors classification in KNeighborsClassifier is the most commonly used technique.
+Since the optimal value $k$ is dependent on data we ran the experiment with multiple values of $k$ and found that the $k$=3 produces the best accuracy.
+In general a larger $k$ suppresses the effects of noise, but makes the classification boundaries less distinct.
+ We used Euclidean distance as the distance metric and assigned equal weights to all the query points.
+In some cases it might be better to assign weights based on the distance.
+The close query point contribute more to the fit and the ones far contribute less.
+For our case the uniform weight with simple majority vote of the nearest neighbors worked just fine.
+
+\subsection{SVM}
+Our support vector machine algorithm was also implemented using scikit-learn.
+The $sklearn.svm.SVC$ class is based on libsvm and is capable of performing multi-class classification.
+Internally, they use libsvm and liblinear to handle all computations.
+These libraries are wrapped using C and Cython.
+It supports multi-class classification on a one-vs-one scheme.
+In this scheme a classifier is created for each pair of classes and during prediction, the class which receives most votes is assigned to the data point.
+In an event of a tie, the class with highest total confidence calculated by summing over the pair-wise classification confidence is selected.
+As the other classifiers, $skleran.SVM$ also takes as input two arrays: an array of training samples and another array of class labels.
+The training samples and labels are first sent to $fit$ function which fits the SVM model according to the data.
+The resulting model is then used to predict the labels of test data.
+
+\section{Dataset}\label{dataset}
+To have a variety of dataset we selected the following three datasets for our experiment.
+Many experiments are data dependent. To see if our technique is not data dependent we used three different datasets.
 \subsection{MNIST Dataset}
@@
 \subsection{Fashion MNIST Dataset}
-Fashion-MNIST is a dataset of Zalando's article images—consisting of a training set of 55,000 examples and a test set of 10,000 examples.
+Fashion-MNIST is a dataset of Zalando's article images-consisting of a training set of 55,000 examples and a test set of 10,000 examples.
 Each example is a 28x28 grayscale image, associated with a label from 10 classes.

### 2020-04-13 chapters/methodology/properties.tex
final draft

@@
-\section{Identifying Metamorphic Relations} 
-We identified five metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, and, shifting along y-axis.
+\section{Identifying Metamorphic Relations} \label{identifyingMR}
+We identified five metamorphic properties for each dataset: rotation, shearing, shading, shifting the image along x-axis, and, shifting the image along y-axis.
 Each image in the testing dataset (digit, letter, and, fashion) was transformed using the five metamorphic properties.
 We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
+
+There are 10000 test images in the in the MNIST digit dataset.
+There are 10 class labels from 0 to 9, and each class label has 1000 instances.
+We applied the following metamorphic properties to each test image.
 \subsection{Rotate}
+Since we are dealing with image datasets, we hypothesize that small changes to the images by rotating them clock-wise or counter clock wise would not have drastic effect on the accuracy of model.
+To test our hypothesis we rotated the test data at each angle between [\ang{-50}, \ang{50}].
+We also expect certain digits with symmetry (like 0) will be less afftected by these metamorphic properties.
+ Each image in the test dataset was transformed using keras ImageDataGenerator method. 
 The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle.
@@
 \subsection{Shear} 
-The images were transformed between angle [-50, 50]
+To shear the images we used image pre-processing library offered by Keras.
+The ImageDataGenerator class generates batches of tensor image data with real-time data augmentation.
+We used the ImageDataGenerator's $apply\_transform()$ method to apply a transformation to an image according to given parameters.
+The $apply\_transform()$ method takes in the image, transformation type, and, the amount of transformation to be applied as parameter.
+It then applies the transformation and returns a transformed version of the input in the same shape.
+The transformation parameter we used here was $shear$ and the images were transformed between angle $[-50, 50]$.
+
     \begin{figure}[!htbp]
@@
 \subsection{Shading}
+We represent the pixels of the MNIST images as floats between 0 and 1 where, 0 is white and 1 represents black.
+To apply the shading transformation we added values to the white pixels of the test data until they become black.
     \begin{figure}[htb!]
@@
 \subsection{Shifting in the X direction}
-    For any value above x the image was completely out of the frame.
+Since the images were 28 pixels wide, shifting the images by more than 28 pixels in either direction moved the images out of the frame completely.
+Thus, we transformed the test datasets by moving each image by pixels between 0 and 28 in both the X directions.
+We used ImageDataGenerator's $apply\_transform()$ function with $tx$ parameter to perform this transformation.
     \begin{figure}[htb!]
@@
             \includegraphics[width=\linewidth]{images/shiftx1.png}
-            \caption{Value: -10}
+            \caption{Value: 10}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\linewidth]{images/shiftx3.png}
-            \caption{Value: 10}
+            \caption{Value: -10}
             \label{fig:Rotate-misclass0}
@@
 
-\subsection{Shifting in the Y direction}
+\subsection{Shifting in the Y direction(ShiftY)}
+The last metamorphic property we identified was shifting the images on Y axis.
+We used ImageDataGenerator's $apply\_transform()$ function with $ty$ parameter to transform the test data.
+Since the images are 28x28 pixels we shifted the images by each pixel between 0 and 28 pixels in both direction.
     \begin{figure}[htb!]
@@
     \FloatBarrier
+
+After generating all the transformed versions of the datasets they were saved to be used as follow-up test cases for our machine-learning algorithms.

### 2020-04-13 chapters/results/figures.tex
final draft

\subsection{Overall Accuracy or true positive}\label{4.1.1}
In this section we tested the algorithms using the transformed test dataset. The test datatsets were applied with increasing value of transformations identified in \ref{identifyingMR}. A copy of these new datasets generated from the original dataset by applying the transformations were saved to serve as follow-up test cases. For example, the MNIST dataset was transformed by applying the shading metamorphic relation for every pixel between [-28,28]. The models were then tested with transformed test data and their accuracy were calculated for every follow-up test data. The following graphs shows the change in accuracy of the whole dataset as the degree of transformation is changed. The X-axis shows the value of metamorphic transformation applied to the original test data and the Y-axis shows the accuracy corresponding to that value of transformation.
    \begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Rotate.png}
        \caption{Rotation}
    \end{subfigure}
    \begin{subfigure}[b]{ 0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Shade.png}
        \caption{Shading}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Shear.png}
        \caption{Shearing}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShiftX.png}
        \caption{Shifting along X-axis}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShiftY.png}
        \caption{Shifting along Y-axis}
    \end{subfigure}
    \caption{Accuracy of the algorithms.}
    \label{fig:Accuracy}
    \end{figure}

 From the graphs in \ref{fig:Accuracy} we can see that different algorithms respond differently to the follow-up datasets. To quantify this difference, we calculated the area under curve for all the curves in \ref{fig:Accuracy}. The following table shows the area under each curve in \ref{fig:Accuracy}.
    \begin{table}[ht]
    \centering
        \begin{tabular}{|c|c|c|c|c|c|}
        \hline
         & CNN & NN & NB & KNN & SVM \\
         \hline
        Rotation & 91.01 & 81.70 & 70.31 & 72.71 & 66.60  \\
        \hline
        Shading & 64.40 & 75.51 & 79.52 & 50.26 & 52.23 \\
        \hline
        Shearing & 94.07 & 87.95 & 74.23 & 84.26 & 81.08 \\
        \hline
        Shift-X & 48.51 & 32.06 & 27.36 & 42.33 & 36.88 \\
        \hline
        Shift-Y & 30.32 & 26.19 & 26.55 & 34.04 & 29.90 \\
        \hline
        \end{tabular}
        \caption{Area under curve.}
        \label{tbl:test-file-format}
    \end{table}
    Figure 4.1(a) through (c) shows the variation in accuracy of . A higher area under curve means 
    KNN has a higher accuracy but, the area under curve is much lower than the convolutional neural network and the 2-layer neural network. Suggests that if you want to use metamorphic transformation to reveal flaw in an algorithm some transformations may be preferable over others.

\subsection{Class Accuracy}\label{Digit-by Accuracy}
    We discussed several papers in Section \ref{2.4MetamorphicTestingMachineLearning} on how the metamorphic relations affect datasets but none of them have investigated how the transformations affect the individual classes in those dataset. It is trivially easy to imagine that not all the data points in a dataset will be affected in the same way with all the transformations. For example, the digit $0$ will still be easily recognizable as $0$ even if it is rotated by 180\textdegree  due to it's symmetry. On the other hand, the digit $9$ can easily be confused with digit $6$ if rotated clockwise by 180\textdegree and vice-versa. Due to this non-uniform affect of transformations on the different data points we decided to investigate how each class of data points affects the accuracy of the model. Thus, besides studying the overall effect of the metamorphic transformations on the whole dataset, we will also study how they affect individual data classes in the MNIST dataset.

    Figure 4.2 to 4.7 shows the accuracy of MNIST dataset class labels $[0-9]$ for our metamorphic relations. Every figure in Figure 4.2-4.7 has ten sub-graphs, each, representing the correct classification of a class label. We want to see if there was a major difference in how each class is affected by a metamorphic relation to get a sense for robustness of the whole dataset. To quantify this we calculated the area under curve for each of the sub-graphs in tables \ref{tbl:test-file-formatRotate}-\ref{tbl:test-file-formatShiftY}. A higher area under curve means that the class was less influenced by the transformation with respect to other classes and it's accuracy on the transformed testing input will be closer to training data.

    Figure \ref{fig:Digit by misclassification for Rotation MR} shows the graphs for the accuracy of the classes in the MNIST dataset after applying the rotation transformation. There are five subplots in each sub-graph in Figure \ref{fig:Digit by misclassification for Rotation MR}. Each subplot represents the accuracy of that digit for the five machine learning algorithms we implemented. The X-axis represents the angle with which the test data points were rotated and the Y-axis represents the accuracy of all the test data points in that class.\\
    \begin{figure}[H]
    \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/RotateAll.png}
        \caption{Class accuracy for MT:Rotate}
        \label{fig:Digit by misclassification for Rotation MR}
    \end{figure}

    We did similar analysis for all the metamorphic property we identified in section \ref{identifyingMR}. For every class in the MNIST test dataset we applied the transformations with increasing value and calculated the accuracy of the algorithms at each value.\\
    Figure \ref{fig:Digit by misclassification for Shading MR} shows the graphs for the accuracy of each class in MNIST dataset for the shading transformation. The five subplots in each sub-graph in Figure \ref{fig:Digit by misclassification for Shading MR} represents the accuracy of that digit for the five machine learning algorithms we implemented. The X-axis represents the value with which the test data points were shaded and the Y-axis represent the accuracy of all the test data points in that class. We also observed that all the algorithms started to predict the test data points as $1$ once the foreground became dark which is reflected in higher values of accuracy for digit $1$. \\

    \begin{figure}[ht!]
    \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShadeAll.png}
        \caption{Class accuracy for MT:Shading}
        \label{fig:Digit by misclassification for Shading MR}
    \end{figure}

    The following graphs shows similar graphs for the metamorphic properties shear, shifting the images on X axis, shifting the images on Y axis.

    \begin{figure}[H]
    \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShearAll.png}
        \caption{Class accuracy for MT:Shear}
        \label{fig:Digit by misclassification for Shear MR}
    \end{figure}

    \begin{figure}[ht!]
    \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShiftXAll.png}
        \caption{Class accuracy for MT: ShiftX}
        \label{fig:Rotate-misclass0}
    \end{figure}

    \begin{figure}[H]
    \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShiftYAll.png}
        \caption{Class accuracy for MT: ShiftY}
        \label{fig:Rotate-misclass0}
    \end{figure}

    To further compare the accuracy of the different classes we calculated the area under each curve. The following tables shows the area under curve for each class $[0,9]$ in the above graphs. The cells with \textcolor{green}{green} background has the highest value among all the cells in that row and the ones in \textcolor{red}{red} has the lowest.
    \begin{table}[H]
    \centering
        \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
        \hline
         & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
        \hline
        CNN & \cellcolor{green!25} 97.01 & 87.69 & 92.87 & 90.29 & 87.77 & 91.86 & 96.54 & 90.47 & 88.99 & \cellcolor{red!25}86.62 \\ 
        \hline
        NN &   94.34 & 84.75 & 75.98 & 79.87 & 80.47 & \cellcolor{red!25}68.33 & \cellcolor{green!25}95.66 & 78.64 & 76.16 & 82.76 \\
        \hline
        NB & \cellcolor{green!25}88.80 & 76.64 & 64.08 & 75.23 & 66.16 & \cellcolor{red!25}56.60 & 84.09 & 57.65 & 65.20 & 68.69 \\
        \hline
        KNN & \cellcolor{green!25}98.31 & 90.80 & 65.39 & 81.12 & \cellcolor{red!25}56.70 & 73.24 & 80.56 & 60.03 & 62.05 & 58.92 \\
        \hline
        SVM & \cellcolor{green!25}93.97 & 76.54 & \cellcolor{red!25}50.38 & 60.45 & 76.49 & 51.74 & 79.87 & 61.49 & 61.58 & 53.49 \\
        \hline
        \end{tabular}
        \caption{Area under curve for each class for MR: Rotation.}
        \label{tbl:test-file-formatRotate}
    \end{table}

     From the table \ref{tbl:test-file-formatRotate} we can see that the digit $0$ has the highest area under curve in the convolutional neural network implementation and the digit $9$ has the lowest area. From this we can say that the accuracy of the sub-set of MNIST dataset with class label $0$ is not affected as much as the other classes when the rotation property is applied. Thus, when creating follow-up test cases for a convolutional neural network, the tester can apply the rotation property to the digit $0$ to a larger angle than any other classes. We will make these recommendations more concrete in \ref{tbl:indexrecommendations}.\\
     We generated the following tables to perform the same analysis on all the metamorphic properties. The digits with red background have the lowest area under curve for that algorithm thus, the lowest average accuracy for all the degree of transformation. The cells with green background have the highest area under curve and thus the highest average accuracy for all the degree of transformation.

    \begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
     & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
    \hline
    CNN & 63.02 & \cellcolor{green!25}99.38 & 59.26 & 60.58 & 69.07 & 58.96 & 60.93 & 63.65 & \cellcolor{red!25}53.64 & 55.51 \\ 
    \hline
    NN & 72.64 & \cellcolor{green!25}96.66 & 72.61 & 69.35 & 80.50 & 80.77 & 81.16 & 82.36 & \cellcolor{red!25}50.98 & 68.08 \\
    \hline
    NB & 89.85 & \cellcolor{green!25}93.71 & 75.36 & 85.34 & 73.75 & \cellcolor{red!25}67.04 & 88.28 & 71.61 & 70.71 & 79.58 \\
    \hline
    KNN & 52.81 & \cellcolor{green!25}99.87 & 39.91 & 46.68 & 42.49 & 48.36 & 47.00 & 52.17 & \cellcolor{red!25}32.81 & 40.52 \\
    \hline
    SVM & 47.12 & \cellcolor{green!25}99.61 & 47.91 & 44.62 & 53.40 & 56.73 & 47.62 & 52.26 & \cellcolor{red!25}31.80 & 41.23 \\
    \hline
    \end{tabular}
    \caption{Area under curve for each class for MR: Shading.}
    \label{tbl:test-file-formatShade}
    \end{table}
    From the table \ref{tbl:test-file-formatShade} we can see that the digit $1$ had the highest accuracy as compared to other classes in the dataset for every algorithm we implemented. On the other hand, the digit $8$ had the lowest accuracy in four out of the five algorithms we implemented.
    Digit $6$ has the highest area under curve in the CNN and NN algorithms. The digits $3$, $1$, and, $0$ have the highest area under curve in the NB, KNN, and, SVM implementations respectively.

    \begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
    & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
    \hline
    CNN & 94.75 & 95.80 & 96.42 & 91.66 & 94.39 & 96.26 &\cellcolor{green!25}98.05 & 94.18 & \cellcolor{red!25}88.89 & 90.28  \\ 
    \hline
    NN & 90.99 & 90.21 & 88.38 & 87.06 & 85.43 & \cellcolor{red!25}82.57 & \cellcolor{green!25}95.77 & 88.55 & 86.13 & 84.41 \\
    \hline
    NB & 79.97 & 79.09 & 78.67 & \cellcolor{green!25}81.60 & 70.81 & 68.39 & 79.37 & 72.12 & 69.02 & \cellcolor{red!25}63.31 \\
    \hline
    KNN & 96.32 & \cellcolor{green!25}99.54 & 85.20 & 88.43 & 78.91 & 83.46 & 93.39 & \cellcolor{red!25}69.79 & 76.79 & 70.73 \\
    \hline
    SVM & \cellcolor{green!25}90.17 & 90.03 & 79.92 & 78.93 & 85.78 & 76.11 & 88.71 & 75.08 & 82.16 & \cellcolor{red!25}63.90 \\
    \hline
    \end{tabular}
    \caption{Area under curve for each class for MR: Shear.}
    \label{tbl:test-file-formatShear}
    \end{table}
    The digit $6$ has the highest area under curve for CNN and NN while the digits $8$ and $5$ have the lowest area under curve.

    \begin{table}[htb!]
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
    & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
    \hline
    CNN & \cellcolor{red!25}25.17 & \cellcolor{green!25}92.04 & 65.01 & 31.49 & 64.78 & 42.84 & 46.12 & 61.14 & 27.62 & 28.84 \\
    \hline
    NN & 21.30 & \cellcolor{red!25}15.45 & 48.59 & 30.03 & 31.99 & 33.89 & 40.76 & \cellcolor{green!25}49.62 & 21.58 & 27.42 \\
    \hline
    NB & 19.03 & 14.50 & \cellcolor{green!25}60.03 & 27.11 & 30.67 & 45.91 & 20.14 & 25.42 & 16.63 & \cellcolor{red!25}14.14 \\
    \hline
    KNN & 27.56 & \cellcolor{green!25}67.33 & 56.41 & 39.62 & 32.09 & 58.53 & 34.05 & 50.71 & 32.65 & \cellcolor{red!25}24.31 \\
    \hline
    SVM & \cellcolor{red!25}22.05 & 40.13 & \cellcolor{green!25}57.64 & 33.38 & 39.98 & 49.06 & 35.29 & 43.62 & 24.94 & 22.74 \\
    \hline
    \end{tabular}
    \caption{Area under curve for each class for MR: ShiftX.}
    \label{tbl:test-file-formatShiftX}
    \end{table}

    \begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
    & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
    \hline
    CNN & 26.80 & \cellcolor{green!25}52.91 & 25.32 & 22.45 & 30.47 & 26.39 & 38.99 & 29.25 & \cellcolor{red!25}21.09 & 29.53 \\ 
    \hline
    NN &  20.99 & 35.29 & 22.58 & 14.69 & 20.49 & \cellcolor{red!25}14.18 & \cellcolor{green!25}52.86 & 30.59 & 15.52 & 34.77 \\
    \hline
    NB & 19.95 & \cellcolor{green!25}56.37 & 23.13 & 19.51 & 20.90 & \cellcolor{red!25}16.07 & 36.29 & 23.58 & 24.89 & 24.81 \\
    \hline
    KNN & 28.72 & \cellcolor{green!25}95.26 & 26.83 & 23.77 & 36.41 & 25.06 & 34.64 & 29.50 & \cellcolor{red!25}19.31 & 20.93 \\
    \hline
    SVM & 25.09 & \cellcolor{green!25}61.47 & 26.25 & \cellcolor{red!25}17.09 & 30.53 & 25.75 & 43.48 & 31.59 & 17.84 & 19.90  \\
    \hline
    \end{tabular}
    \caption{Area under curve for each class for MR: ShiftY.}
    \label{tbl:test-file-formatShiftY}
    \end{table}

A similar analysis was also done for the Fashion-MNIST, and, EMNIST dataset but due to space limitation they are not reported here, instead, they are reported on the project's github page.

\clearpage
\newpage
In the tables 4.2 to 4.6 we have seen that the different classes are affected differently depending upon the algorithm and the metamorphic transformation applied to them. In this section, we want to make recommendations to pick the best values for the metamorphic properties such that the the accuracy of the transformed dataset will be close to the original dataset. For our purpose we define accuracy being close as within $90\%$ of the origin dataset. To do this we first calculated the accuracy of each class in the original dataset without applying any transformation. We then calculated the degrees of transformation for which the accuracy of the transformed dataset was greater than or equal to $90\%$ of the accuracy of the original dataset for the five algorithms. Based on this exercise we make the recommendation to testers who want to use these properties to generate follow-up test cases. The following table shows the minimum and maximum values of transformations where the accuracy was found to be within $90\%$ of the accuracy without any transformation.

% \pgfplotstableread[row sep=\\,col sep=&]{
%   Class & RotateX & RotateY & ShadeX & ShadeY & ShearX & ShearY & ShiftXx & ShiftXy    & ShiftYx & ShiftYy\\
%     0 &     0 &     35 &         0.1 &     51      & 0.2 & 22    & 0.3        & 3         & 0.4       & 2  \\
%     1 &     200 &     22 &        200.1 &     99      & 200.2 & 20    & 200.3        & -25       & 200.4       & 3  \\
%     2 &     400 &     12 &        400.1 &     50      & 400.2 & 26    & 400.3        & -24       & 400.4      & 2  \\
%     3 &     600 &     13 &        600.1 &     51      & 600.2 & 22    & 600.3        & 1         & 600.4       & 2  \\
%     4 &     800 &     15 &        800.1 &     51      & 800.2 & 19    & 800.3        & 4         & 800.4       & 1  \\
%     5 &     1000 &     10 &        1000.1 &     50      & 1000.2 & 11    & 1000.3        & 6         & 1000.4       & 2  \\
%     6 &     1200 &     37 &        1200.1 &     50      & 1200.2 & 30    & 1200.3        & 3         & 1200.4       & -27  \\
%     7 &     1400 &     11 &        1400.1 &     51      & 1400.2 & 16    & 1400.3        & 2         & 1400.4        & 2  \\
%     8 &     1600 &     15 &        1600.1 &     50      & 1600.2 & 21    & 1600.3        & 3         & 1600.4       & 2  \\
%     9 &     1800 &     16 &        1800.1 &     50      & 1800.2 & 15    & 1800.3        & 2         & 1800.4       & 2  \\
% }\recomx

% \pgfplotstableread[row sep=\\,col sep=&]{
%   Class & RotateY & RotateX & ShadeY & ShadeX & ShearY & ShearX & ShiftXy & ShiftXx    & ShiftYy & ShiftYx\\
%     0   & -45       & 0     & 0         & 0.1    & -35  & 0.2    & -3       & 0.3       & -2    &  0.4  \\
%     1   & -19       & 200     & 0         & 200.1    & -28  & 200.2    & 16       & 200.3         & -5  & 200.4  \\
%     2   & -14       & 400    & 0        & 400.1   & -25  & 400.2    & -4      & 400.3       & -2    & 400.4  \\
%     3   & -17       & 600    & 0         & 600.1    & -25  & 600.2    & -4     & 600.3         & -2  & 600.4  \\
%     4   & -14       & 800     & 0         & 800.1    & -21  & 800.2    & -3       & 800.3         & -3  & 800.4  \\
%     5   & -11       & 1000     & 0         & 1000.1    & -25  & 1000.2    & -1       & 1000.3         & -1  & 1000.4  \\
%     6   & -16       & 1200     & 0         & 1200.1    & -18  & 1200.2    & -3       & 1200.3         & -3  & 1200.4  \\
%     7   & -19       & 1400     & 0         & 1400.1    & -24  & 1400.2    & -4       & 1400.3         & -1  & 1400.4  \\
%     8   & -14       & 1600     & 0         & 1600 .1    & -32  & 1600 .2    & -1       & 1600 .3         & -2  & 1600 .4  \\
%     9   & -11       & 1800     & 0         & 1800.1    & -12  & 1800.2    & -2       & 1800.3         & -1  & 1800.4 \\
% }\recomy

% \begin{tikzpicture}

% \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
% \nextgroupplot[ybar, bar width=.1cm,xtick=\empty,yshift=1cm, ymin=0,ymax=60,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=\textwidth,height=.5\textwidth,]%ytick=\empty]
% \addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\recomx};
% \addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\recomx};
% \addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\recomx};
% \addplot[fill=yellow,draw=black] table[x=ShiftXx,y=ShiftXy]{\recomx};
% \addplot[fill=brown,draw=black] table[x=ShiftYx,y=ShiftYy]{\recomx};

% \addlegendentry{CNN}
% \addlegendentry{NN}
% \addlegendentry{NB}
% \addlegendentry{SVM}
% \addlegendentry{KNN}

% \nextgroupplot[ybar, width=\textwidth,height=.5\textwidth, bar width=.1cm,yshift=1cm,ymin=-60,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\recomy}{Class}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
% \addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\recomy};
% \addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\recomy};
% \addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\recomy};
% \addplot[fill=yellow,draw=black] table[x=ShiftXx,y=ShiftXy]{\recomy};
% \addplot[fill=brown,draw=black] table[x=ShiftYx,y=ShiftYy]{\recomy};

% \end{groupplot}
% \end{tikzpicture}

\begin{center}
 \begin{table}[ht]
  \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
     \multirow{2}{*}{Class} & \multicolumn{2}{c|}{Rotation} & \multicolumn{2}{c|}{Shade} & \multicolumn{2}{c|}{Shear} & \multicolumn{2}{c|}{ShiftX} & \multicolumn{2}{c|}{ShiftY} \\\cline{2-11} 
     & Min & Max & Min & Max & Min & Max & Min & Max & Min & Max \\
     \hline
    $0$ & $-45$ & $35$ & $0$ & $51$ & $-35$ & $22$ & $-3$ & $3$ & $-2$ & $2$  \\
    $1$ & $-19$ & $22$ & $0$ & $99$ & $-28$ & $20$ & $-2$ & $2$ & $-5$ & $3$  \\
    $2$ & $-14$ & $12$ & $0$ & $50$ & $-25$ & $26$ & $-4$ & $7$ & $-2$ & $2$  \\
    $3$ & $-17$ & $13$ & $0$ & $51$ & $-25$ & $22$ & $-4$ & $1$ & $-2$ & $2$  \\
    $4$ & $-14$ & $15$ & $0$ & $51$ & $-21$ & $19$ & $-3$ & $4$ & $-3$ & $1$  \\
    $5$ & $-11$ & $10$ & $0$ & $50$ & $-25$ & $11$ & $-1$ & $6$ & $-1$ & $2$  \\
    $6$ & $-16$ & $37$ & $0$ & $50$ & $-18$ & $30$ & $-3$ & $3$ & $-3$ & $2$  \\
    $7$ & $-19$ & $11$ & $0$ & $51$ & $-24$ & $16$ & $-4$ & $2$ & $-1$ & $2$  \\
    $8$ & $-14$ & $15$ & $0$ & $50$ & $-32$ & $21$ & $-1$ & $3$ & $-2$ & $2$  \\
    $9$ & $-11$ & $16$ & $0$ & $50$ & $-12$ & $15$ & $-2$ & $2$ & $-1$ & $2$  \\
    \hline
    \end{tabular}
    \caption{Recommendations for using the transformed MNIST dataset.}
    \label{tbl:indexrecommendations}
   \end{table}   
\end{center}

We have also provided these recommendations for the Fashion-MNIST and EMNIST datasets on the project's github page.
% \subsection{Misclassification of digits}
%     In order to see how each digit is affected by changes in  mp. For each digit 0-9 we calculated the number of correct predictions made by the model as compared to total number of .

### 2020-04-13 chapters/results/results.tex
final draft

--- 2019-06-19 chapters/results/results.tex
@@
-\section{Overall Accuracy}
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/rotation}
-  \caption{MR: Rotation.}
-  \label{fig:rotation 1}
+In this section we will discuss our findings after implementing the machine learning algorithms and the metamorphic properties.
+
+Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made.
+To evaluate the accuracy of our machine learning models, we first trained the models on the training data.
+The MNIST, Fashion-MNIST, and, EMNIST training datasets have 55000, 55000, and, 119800 training data respectively.
+The training data consists of the images and their corresponding labels which are used as input to the algorithm in order to generate a model.
+Once we generated the trained models, we used the test data to calculate the accuracy of the models.
+The MNIST, Fashion-MNIST, and, EMNIST testing dataset have 10000, 10000, and, 20800 testing data respectively.
+The following graphs show the accuracy of the various models on the test dataset.
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+    interval & MNIST & Fashion & EMNIST \\
+    CNN     & 97.01 & 83.56 & 78.20 \\
+    NN     & 91.41 & 79.89 & 64.96 \\
+    NB    & 80.85 & 65.6 & 57.81 \\
+    KNN   & 97.28 & 85.24 & 86.25 \\
+    SVM   & 95.47 & 84.56 & 81.25\\
+    }\accuracy
+
+\begin{center}
+\begin{tikzpicture}
+    \begin{axis}[
+            ybar,
+            bar width=.75cm,
+            height=.5\textwidth,
+            width=\textwidth,
+            legend style={at={(0.5,1)},
+                anchor=north,legend columns=-1},
+            symbolic x coords={CNN,NN,NB,KNN, SVM},
+            xtick=data,
+            ytick={0,20,40,60,80,100},
+            nodes near coords,
+            nodes near coords align={vertical},
+            ymin=0,ymax=120,
+            ylabel={Accuracy},
+            xlabel={Algorithms}
+        ]
+        \addplot table[x=interval,y=MNIST]{\accuracy};
+        \addplot table[x=interval,y=Fashion]{\accuracy};
+        \addplot table[x=interval,y=EMNIST]{\accuracy};
+        \legend{MNIST, Fashion, EMNIST}
+    \end{axis}
+\end{tikzpicture}      
+\end{center}{}
+An interesting observation from the table above is that, deep learning algorithms are not necessarily always a good choice when we are trying to maximize accuracy.
+Depending on the type of dataset, regular machine learning algorithms like KNN can also yield high accuracy and outperform deep learning algorithms.
+In the following sections we will discuss how the metamorphic transformations affected the accuracy of the models and what conclusions we can draw from it.
+\section{Effect of metamorphic transformation on the accuracy of the model}
+From literature review we saw that metamorphic testing can be a very useful technique to test the correctness of an algorithm.
+In this thesis, we will investigate the effect of the identified metamorphic properties on the accuracy of the machine learning algorithms.
+For each metamorphic property identified in \ref{identifyingMR} we want to see how the accuracy of the models change with the varying degree of transformation.
+Our hypothesis is that small changes to the input image should not affect the prediction of the model drastically.
+After creating a trained model with the training dataset, we applied the metamorphic properties on the training data to generate transformed versions of the test data.
+We calculated the following metrics to evaluate the effect of the metamorphic relations on machine learning algorithm.
+To tackle the stochastic nature of training a neural network model, we ran each of the above experiment ten times and calculated average for accuracy.
+
+\input{figures.tex}
+
+\clearpage
+\subsection{Robustness}
+
+In the section \ref{Digit-by Accuracy} we saw that that the accuracy of the algorithms varied depending upon the transformation applied to the test data as well as the degree of the transformation.
+Robustness is the property of an algorithm whereby if the test data is "similar" to the training data then the testing error is also close to the training error \cite{Xu2012}.
+Thus, a robust algorithm should produce similar errors while predicting similar test data.
+In this section, we will be comparing the robustness of the five algorithms with respect to each other for different metamorphic relations and verify the accuracy of the recommendations we made in the table \ref{tbl:indexrecommendations}.
+For this we generated a new dataset with those recommendations and compared it's accuracy with the accuracy of the original dataset.
+To generate a balanced dataset of 5000 samples we randomly picked 100 transformed images from each transformation for every class label.
+This new test dataset was then tested for accuracy on the five algorithms we implemented.
+The bar graph below shows the accuracy of the new test dataset as compared to the original MNIST dataset.
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+    Algorithm & MNIST & Transformed  \\
+    CNN     & 97.01 & 95.2 \\
+    NN     & 91.41 & 89.02 \\
+    NB    & 80.85 & 78.76 \\
+    SVM   & 95.47 & 90.98\\
+    KNN   & 97.28 & 93.06\\
+    }\Robustness
+
+\begin{figure}[H]
+\begin{tikzpicture}
+    \begin{axis}[
+            ybar,
+            bar width=.75cm,
+            height=.5\textwidth,
+            width=\textwidth,
+            legend style={at={(0.5,1)},
+                anchor=north,legend columns=-1},
+            symbolic x coords={CNN,NN,NB,KNN, SVM},
+            xtick=data,
+            ytick={0,20,40,60,80,100},
+            nodes near coords,
+            nodes near coords align={vertical},
+            ymin=0,ymax=120,
+            ylabel={Accuracy},
+            xlabel={Algorithms}
+        ]
+        \addplot table[x=Algorithm,y=MNIST]{\Robustness};
+        \addplot table[x=Algorithm,y=Transformed]{\Robustness};
+        \legend{MNIST, Transformed Images}
+    \end{axis}
+\end{tikzpicture}      
+\caption{Accuracy of tranformed dataset vs original dataset}
+\label{img:transformedaccuracy}
 \end{figure}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shade}
-  \caption{MR: Shading.}
-  \label{fig: Shading}
-\end{figure}
+The more robust algorithm will have the accuracy of the transformed images closer to the accuracy of the original MNIST data.
+From the graph above we see that the convolutional neural network has a $1.81\%$ decrease in accuracy while the accuracy of the neural-network, NB, KNN, and, SVM decreased by $2.39\%$, $2.09\%$, $4.22\%$, and, $4.49\%$ respectively.
+Thus, among the algorithms we implemented the convolutional neural network is proven to be the most robust followed by Naive Bayes implementation.
+While the KNN and SVM implementations are the least robust.
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/sheer}
-  \caption{MR: Sheering.}
-  \label{fig: Sheer}
-\end{figure}
+In Section \ref{4.1.1} we discovered that the accuracy of the test data decreased as the degree of the transformation was increased.
+So a second way of looking at robustness is to look at transformations which can be applied to the dataset without lowering the accuracy of the model below 90 percent of the original value.
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shift}
-  \caption{MR: Shifting.}
-  \label{fig: Shift}
-\end{figure}
+\import{chapters/results/}{tables.tex}
 
-\section{Digit-by Accuracy}
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/rotation1}
-  \caption{MR: Rotation.}
-  \label{fig:rotation 1}
-\end{figure}
+\newpage
+\section{Discussion}
+In this paper we identified five metamorphic properties "Rotation", "Shading", "Shearing", "Shifting the image along $x$ axis", and, "Shifting the image along $y$ axis" that can be used with image datasets.
+We then applied these metamorphic transformations to three datasets: MNIST, Fashion-MNIST, and, EMNIST.
+We also looked at how the accuracy of the datasets are affected by the transformations we identified.
+We also investigated the accuracy of transformations on individual classes in the MNIST dataset.
+We then provide recommendations for creating follow up test cases from the MNIST dataset by using the minimum and maximum values of transformations to use for these metamorphic properties.
+We also implemented five common machine learning algorithms and evaluated their robustness on these metamorphic properties.
+We make following recommendations for transforming digits in MNIST dataset.
+This paper also make the following contributions: 
+We made a methodological contribution where we have provided a set of functions to easily manipulate, and, transform image datasets for future research.
+Future researchers can utilize these functions to plugin more algorithms and metamorphic properties.
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shade1}
-  \caption{MR: Shading.}
-  \label{fig: Shading}
-\end{figure}
+Contributions:
+Methodological contribution where others can plugin more algors or MT.
+Experimental contribution:Which algo does better.
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/sheer1}
-  \caption{MR: Sheering.}
-  \label{fig: Sheer}
-\end{figure}
+Conclusions:
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/shift1}
-  \caption{MR: Shifting.}
-  \label{fig: Shift}
-\end{figure}
+Framework to apply MT in midst of distortions.
+CNN not so much better than others based on learning just from the dataset.

### 2020-04-13 chapters/results/tables.tex
final draft

@@
-\subsection{Rotate}
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
- & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-\hline
-Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-\hline
-0  &   -37&46 & -44&31 & -50&17 & -45&45 & -50&49 \\
-\hline
-1 &   -15&18 & -11&15 & -9&12 & -21&22 & -28&43  \\
-\hline
-2  &   -19&15 & -14&11 & -12&10 & -14&12 & -19&16  \\
-\hline
-3  &   -20&15 & -17&15 & -9&19 & -17&13 & -25&26  \\
-\hline
-4  &   -15&15 & -12&15 & -13&14 & -15&22 & -14&15 \\
-\hline
-5  &   -16&17 & -9&8 & -14&5 & -11&10 & -25&18  \\
-\hline
-6  &   -26&32 & -20&43 & -11&36 & -16&43 & -19&37 \\
-\hline
-7  &   -18&11 & -19&8 & -13&7 & -20&11 & -19&13 \\
-\hline
-8  &   -16&18 & -13&15 & -13&12 & -14&21 & -17&15 \\
-\hline
-9  &   -21&24 & -10&18 & -6&22 & -12&16 & -11&18 \\ 
-\hline
-\end{tabular}
-\caption{Rotate.}
-\label{tbl:test-file-format}
-\end{table}
+% \subsection{Rotate}
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
+% \hline
+%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
+% \hline
+% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
+% \hline
+% 0  &   -37&46 & -44&31 & -50&17 & -45&45 & -50&49 \\
+% \hline
+% 1 &   -15&18 & -11&15 & -9&12 & -21&22 & -28&43  \\
+% \hline
+% 2  &   -19&15 & -14&11 & -12&10 & -14&12 & -19&16  \\
+% \hline
+% 3  &   -20&15 & -17&15 & -9&19 & -17&13 & -25&26  \\
+% \hline
+% 4  &   -15&15 & -12&15 & -13&14 & -15&22 & -14&15 \\
+% \hline
+% 5  &   -16&17 & -9&8 & -14&5 & -11&10 & -25&18  \\
+% \hline
+% 6  &   -26&32 & -20&43 & -11&36 & -16&43 & -19&37 \\
+% \hline
+% 7  &   -18&11 & -19&8 & -13&7 & -20&11 & -19&13 \\
+% \hline
+% 8  &   -16&18 & -13&15 & -13&12 & -14&21 & -17&15 \\
+% \hline
+% 9  &   -21&24 & -10&18 & -6&22 & -12&16 & -11&18 \\ 
+% \hline
+% \end{tabular}
+% \caption{Rotate.}
+% \label{tbl:test-file-format}
+% \end{table}
+
+% \subsubsection{MT: Rotate}
+% \pgfplotstableread[row sep=\\,col sep=&]{
+%     interval & Digit & Fashion & Letter \\
+%     CNN & 75.4 & 39.8 & 43.72 \\
+%     NN & 61.6 & 43.36 & 40.59 \\
+%     NB & 54.5 & 57.9 & 37.29 \\
+%     SVM & 40.0 & 51.5 & 23.153 \\ 
+%     KNN & 47.7 & 35.08 & 26.31 \\
+%     }\rotate
+
+% \begin{tikzpicture}
+%     \begin{axis}[
+%             ybar,
+%             bar width=.75cm,
+%             width=\textwidth,
+%             height=.5\textwidth,
+%             legend style={at={(0.5,1)},
+%                 anchor=north,legend columns=-1},
+%             symbolic x coords={CNN,NN,NB,SVM,KNN},
+%             xtick=data,
+%             nodes near coords,
+%             nodes near coords align={vertical},
+%             ymin=0,ymax=120,
+%             ylabel={Value},
+%         ]
+%         \addplot table[x=interval,y=Digit]{\rotate};
+%         \addplot table[x=interval,y=Fashion]{\rotate};
+%         \addplot table[x=interval,y=Letter]{\rotate};
+%         \legend{Digit, Fashion, Letter}
+%     \end{axis}
+% \end{tikzpicture}
+\clearpage
+When the rotation metamorphic transformation is applied to the MNIST dataset, the convolutional neural-network algorithm has the largest bar.
+This means that that a larger angle of rotation can be applied to the MNIST dataset before it's accuracy drops below $90\%$ of the original MNIST dataset.
+Similarly, Naive Bayes is the most robust for Fashion-MNIST datset and KNN is the most robust for EMNIST dataset.
 
 \pgfplotstableread[row sep=\\,col sep=&]{
-    interval & Digit & Fashion & Letter \\
-    CNN   & 41.4  & 17.45  & 0  \\
-    NN    & 34.8 & 24.75  & 0  \\
-    NB    & 30.4 & 42.0 & 0 \\
-    SVM   & 40.0 & 29.1 & 0 \\
-    KNN   & 47.7  & 20.81 & 0.0 \\
-    }\rotate
+    Mx & My & Fx & Fy & Ex & Ey \\
+    0 & 39 & 0.1 & 13 & 0.2 & 24 \\
+    4 & 27 & 4.1 & 19 & 4.2 & 19 \\
+    8 & 25 & 8.1 & 19 & 8.2 & 20 \\
+    12 & 16 & 12.1 & 18 & 12.2 & 21 \\
+    16 & 19 & 16.1 & 15 & 16.2 & 24 \\
+    }\mnistx
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+   Algo & Mx & My & Fx & Fy & Ex & Ey \\
+   CNN & 0 & -34 & 0.1 & -14 & 0.2 & -20 \\
+    NN & 4 & -28 & 4.1 & -17 & 4.2 & -18 \\
+    NB & 8 & -24 & 8.1 & -19 & 8.2 & -17 \\
+    SVM & 12 & -16 & 12.1 & -17 & 12.2 & -20 \\
+     KNN & 16 & -18 & 16.1 & -16 & 16.2 & -25 \\
+    }\mnisty
+
+\begin{figure}[H]
 
 \begin{tikzpicture}
-    \begin{axis}[
-            ybar,
-            bar width=.75cm,
-            width=\textwidth,
-            height=.5\textwidth,
-            legend style={at={(0.5,1)},
-                anchor=north,legend columns=-1},
-            symbolic x coords={CNN,NN,NB,SVM,KNN},
-            xtick=data,
-            nodes near coords,
-            nodes near coords align={vertical},
-            ymin=0,ymax=75,
-            ylabel={\%},
-        ]
-        \addplot table[x=interval,y=Digit]{\rotate};
-        \addplot table[x=interval,y=Fashion]{\rotate};
-        \addplot table[x=interval,y=Letter]{\rotate};
-        \legend{Digit, Fashion, Letter}
-    \end{axis}
+
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=60,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnistx};
+\addlegendentry{MNIST}
+
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\mnistx};
+\addlegendentry{Fashion}
+
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\mnistx};
+\addlegendentry{EMNIST}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-60,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnisty};
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\mnisty};
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\mnisty};
+\end{groupplot}
 \end{tikzpicture}
+\caption{Robustness graph for rotation property}
+\end{figure}
 
-\subsection{ShiftX}
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-    \hline
-     & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-    \hline
-    Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-    \hline
-    0  &   -5&4 & -3&3 & -4&3 & -4&3 & -4&4 \\
-    \hline
-        \multirow{3}{*}{1}
-            &-50&-29 & -50&-38 &  \multirow{3}{*}{-2}&\multirow{3}{*}{2} & -50&-28 & -50&-25\\
-            &-5&5 & -2&1 & & & -6&4 & -9&11\\
-            &32&49 & 40&49  & & & 28&49 & 27&49\\
-    \hline
-    \multirow{2}{*}{2}  
-        &   \multirow{2}{*}{-7}&\multirow{2}{*}{7}  &  \multirow{2}{*}{-5}&\multirow{2}{*}{6}  &  -41&-25   &  \multirow{2}{*}{-5}&\multirow{2}{*}{8} & \multirow{2}{*}{-5}&\multirow{2}{*}{11}\\
-        & & &   & & -12&6   & & & &\\          
-    \hline
-    3  &   -6&3 & -7&1 & -7&0 & -7&2 & -8&4  \\
-    \hline
-    4  &   -7&6 & -4&4 & -5&5 & -4&5 & -5&4 \\
-    \hline
-    5  &   -5&8 & -2&7 & -2&21 & -3&9 & -5&13 \\
-    \hline
-    6  &   -5&8 & -4&4 & -3&3 & -5&5 & -5&5 \\
-    \hline
-    7  &   -5&6 & -6&2 & -4&2 & -7&4 & -11&4 \\
-    \hline
-    8  &   -4&5 & -2&4 & -1&5 & -3&4 & -3&6 \\
-    \hline
-    9  &   -5&5 & -4&2 & -2&2 & -4&3 & -3&3 \\ 
-    \hline
-\end{tabular}
-\caption{ShiftX.}
-\label{tbl:test-file-format}
-\end{table}
+% \subsection{Shade}
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
+% \hline
+%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
+% \hline
+% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
+% \hline
+% 0  &   0.0&0.6 & 0.0&0.74 & 0.0&0.96 & 0.0&0.5 & 0.0&0.51 \\
+% \hline
+% 1  &   0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 \\
+% \hline
+% 2  &   0.0&0.64 & 0.0&0.78 & 0.0&0.93 & 0.0&0.5 & 0.0&0.49 \\
+% \hline
+% 3  &   0.0&0.62 & 0.0&0.76 & 0.0&0.97 & 0.0&0.49 & 0.0&0.5  \\
+% \hline
+% 4  &   0.0&0.63 & 0.0&0.87 & 0.0&0.99 & 0.0&0.51 & 0.0&0.5 \\
+% \hline
+% 5  &   0.0&0.62 & 0.0&0.91 & 0.0&0.92 & 0.0&0.53 & 0.0&0.5  \\
+% \hline
+% 6  &   0.0&0.62 & 0.0&0.81 & 0.0&0.97 & 0.0&0.5 & 0.0&0.5 \\
+% \hline
+% 7  &   0.0&0.6 & 0.0&0.89 & 0.0&0.98 & 0.0&0.51 & 0.0&0.52\\
+% \hline
+% 8  &   0.0&0.57 & 0.0&0.61 & 0.0&0.9 & 0.0&0.49 & 0.0&0.49\\
+% \hline
+% 9  &   0.0&0.57 & 0.0&0.7 & 0.0&0.94 & 0.0&0.5 & 0.0&0.5\\ 
+% \hline
+% \end{tabular}
+% \caption{Shade.}
+% \label{tbl:test-file-format}
+% \end{table}
+
+% \subsubsection{MT: Shade}
+% \pgfplotstableread[row sep=\\,col sep=&]{
+%     interval & Digit & Fashion & Letter \\
+%     CNN   & 64.6  & 55.6  & 36.76  \\
+%     NN    & 80.6 & 56.1  & 74.69  \\
+%     NB    & 95.5 & 68.63 & 62.30 \\
+%     SVM   & 55.2 & 55.8 & 40.81 \\
+%     KNN   & 55.0  & 51.9 & 56.29 \\
+%     }\shade
+
+% \begin{tikzpicture}
+%     \begin{axis}[
+%             ybar,
+%             bar width=.75cm,
+%             width=\textwidth,
+%             height=.5\textwidth,
+%             legend style={at={(0.5,1)},
+%                 anchor=north,legend columns=-1},
+%             symbolic x coords={CNN,NN,NB,SVM,KNN},
+%             xtick=data,
+%             nodes near coords,
+%             nodes near coords align={vertical},
+%             ymin=0,ymax=120,
+%             ylabel={Value},
+%         ]
+%         \addplot table[x=interval,y=Digit]{\shade};
+%         \addplot table[x=interval,y=Fashion]{\shade};
+%         \addplot table[x=interval,y=Letter]{\shade};
+%         \legend{Digit, Fashion, Letter}
+%     \end{axis}
+% \end{tikzpicture}
 
 \pgfplotstableread[row sep=\\,col sep=&]{
-    interval & Digit & Fashion & Letter \\
-    CNN   & 12.42  & 10.75  & 0  \\
-    NN    & 7.83 & 14.71  & 0  \\
-    NB    & 9.73 & 22.27 & 0 \\
-    SVM   & 11.5 & 11.18 & 0 \\
-    KNN   & 14.17  & 9.27 & 0.0 \\
-    }\shiftX
-
-\begin{tikzpicture}
-    \begin{axis}[
-            ybar,
-            bar width=.75cm,
-            width=\textwidth,
-            height=.5\textwidth,
-            legend style={at={(0.5,1)},
-                anchor=north,legend columns=-1},
-            symbolic x coords={CNN,NN,NB,SVM,KNN},
-            xtick=data,
-            nodes near coords,
-            nodes near coords align={vertical},
-            ymin=0,ymax=50,
-            ylabel={\Angle},
-        ]
-        \addplot table[x=interval,y=Digit]{\shiftX};
-        \addplot table[x=interval,y=Fashion]{\shiftX};
-        \addplot table[x=interval,y=Letter]{\shiftX};
-        \legend{Digit, Fashion, Letter}
-    \end{axis}
-\end{tikzpicture}
-MNIST: KNN is the most robust.
-
-\subsection{Shade}
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
- & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-\hline
-Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-\hline
-0  &   0.0&0.6 & 0.0&0.74 & 0.0&0.96 & 0.0&0.5 & 0.0&0.51 \\
-\hline
-1  &   0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 \\
-\hline
-2  &   0.0&0.64 & 0.0&0.78 & 0.0&0.93 & 0.0&0.5 & 0.0&0.49 \\
-\hline
-3  &   0.0&0.62 & 0.0&0.76 & 0.0&0.97 & 0.0&0.49 & 0.0&0.5  \\
-\hline
-4  &   0.0&0.63 & 0.0&0.87 & 0.0&0.99 & 0.0&0.51 & 0.0&0.5 \\
-\hline
-5  &   0.0&0.62 & 0.0&0.91 & 0.0&0.92 & 0.0&0.53 & 0.0&0.5  \\
-\hline
-6  &   0.0&0.62 & 0.0&0.81 & 0.0&0.97 & 0.0&0.5 & 0.0&0.5 \\
-\hline
-7  &   0.0&0.6 & 0.0&0.89 & 0.0&0.98 & 0.0&0.51 & 0.0&0.52\\
-\hline
-8  &   0.0&0.57 & 0.0&0.61 & 0.0&0.9 & 0.0&0.49 & 0.0&0.49\\
-\hline
-9  &   0.0&0.57 & 0.0&0.7 & 0.0&0.94 & 0.0&0.5 & 0.0&0.5\\ 
-\hline
-\end{tabular}
-\caption{Shade.}
-\label{tbl:test-file-format}
-\end{table}
+    Mx & My & Fx & Fy & Ex & Ey \\
+    0 & 55 & 0.1 & 55 & 0.2 & 53 \\
+    4 & 69 & 4.1 & 53 & 4.2 & 61 \\
+    8 & 96 & 8.1 & 76 & 8.2 & 92 \\
+    12 & 52 & 12.1 & 52 & 12.2 & 51 \\
+    16 & 51 & 16.1 & 52 & 16.2 & 51 \\
+    }\shadex
 
 \pgfplotstableread[row sep=\\,col sep=&]{
-    interval & Digit & Fashion & Letter \\
-    CNN   & 64.6  & 55.6  & 0  \\
-    NN    & 80.6 & 56.1  & 0  \\
-    NB    & 95.5 & 68.63 & 0 \\
-    SVM   & 55.2 & 55.8 & 0 \\
-    KNN   & 55.0  & 51.9 & 0.0 \\
-    }\shade
+   Algo & Mx & My & Fx & Fy & Ex & Ey \\
+    CNN & 0 & 0 & 0.1 & 0 & 0.2 & 0 \\
+    NN & 4 & 0 & 4.1 & 0 & 4.2 & 0 \\
+    NB & 8 & 0 & 8.1 & 0 & 8.2 & 0 \\
+    SVM & 12 & 0 & 12.1 & 0 & 12.2 & 0 \\
+    KNN & 16 & 0 & 16.1 & 0 & 16.2 & 0 \\
+    }\shadey
 
+\begin{figure}[H]
 \begin{tikzpicture}
-    \begin{axis}[
-            ybar,
-            bar width=.75cm,
-            width=\textwidth,
-            height=.5\textwidth,
-            legend style={at={(0.5,1)},
-                anchor=north,legend columns=-1},
-            symbolic x coords={CNN,NN,NB,SVM,KNN},
-            xtick=data,
-            nodes near coords,
-            nodes near coords align={vertical},
-            ymin=0,ymax=120,
-            ylabel={\%},
-        ]
-        \addplot table[x=interval,y=Digit]{\shade};
-        \addplot table[x=interval,y=Fashion]{\shade};
-        \addplot table[x=interval,y=Letter]{\shade};
-        \legend{Digit, Fashion, Letter}
-    \end{axis}
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.6\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shadex};
+\addlegendentry{MNIST}
+
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shadex};
+\addlegendentry{Fashion}
+
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shadex};
+\addlegendentry{EMNIST}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=0, bar width=.2cm,yshift=1cm,ymin=0,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shadey}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},ytick=\empty,]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shadey};
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shadey};
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shadey};
+
+\end{groupplot}
 \end{tikzpicture}
+\caption{Robustness graph for shading property}
+\end{figure}
+For the shading metamorphic property we find that Naive Bayes is the most robust algorithm for all the three datasets.
 
-\subsection{Shear}
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
- & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-\hline
-Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-\hline
-0  &   -24&28 & -19&16 & -17&10 & -36&25 & -50&39 \\
-\hline
-1  &   -50&18 & -24&14 & -14&10 & -50&24 & -50&49 \\
-\hline
-2  &   -22&33 & -25&25 & -17&49 & -25&26 & -32&29 \\
-\hline
-3  &   -25&23 & -31&21 & -12&33 & -32&22 & -35&35  \\
-\hline
-4  &   -25&20 & -17&17 & -25&13 & -21&31 & -24&18 \\
-\hline
-5  &   -32&26 & -24&18 & -45&4 & -25&23 & -31&27  \\
-\hline
-6  &   -39&29 & -23&30 & -9&21 & -31&30 & -40&34 \\
-\hline
-7  &   -21&20 & -23&18 & -26&40 & -24&23 & -26&16 \\
-\hline
-8  &   -26&25 & -22&23 & -16&17 & -36&27 & -36&22 \\
-\hline
-9  &   -17&21 & -13&15 & -6&15 & -20&16 & -23&15\\ 
-\hline
-\end{tabular}
-\caption{Shear.}
-\label{tbl:test-file-format}
-\end{table}
+% \subsection{Shear}
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
+% \hline
+%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
+% \hline
+% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
+% \hline
+% 0  &   -24&28 & -19&16 & -17&10 & -36&25 & -50&39 \\
+% \hline
+% 1  &   -50&18 & -24&14 & -14&10 & -50&24 & -50&49 \\
+% \hline
+% 2  &   -22&33 & -25&25 & -17&49 & -25&26 & -32&29 \\
+% \hline
+% 3  &   -25&23 & -31&21 & -12&33 & -32&22 & -35&35  \\
+% \hline
+% 4  &   -25&20 & -17&17 & -25&13 & -21&31 & -24&18 \\
+% \hline
+% 5  &   -32&26 & -24&18 & -45&4 & -25&23 & -31&27  \\
+% \hline
+% 6  &   -39&29 & -23&30 & -9&21 & -31&30 & -40&34 \\
+% \hline
+% 7  &   -21&20 & -23&18 & -26&40 & -24&23 & -26&16 \\
+% \hline
+% 8  &   -26&25 & -22&23 & -16&17 & -36&27 & -36&22 \\
+% \hline
+% 9  &   -17&21 & -13&15 & -6&15 & -20&16 & -23&15\\ 
+% \hline
+% \end{tabular}
+% \caption{Shear.}
+% \label{tbl:test-file-format}
+% \end{table}
+\newline
+
+% \subsubsection{MT: Shear}
+% \pgfplotstableread[row sep=\\,col sep=&]{
+%     interval & Digit & Fashion & Letter \\
+%     CNN & 52.4 & 38.81 & 28.84 \\
+%     NN  & 41.8 & 41.18 & 28.11 \\
+%     NB  & 39.9 & 53.6 & 31.5 \\
+%     SVM & 54.7 & 53.8 & 34.84 \\
+%     KNN & 63.1 & 45.1 & 38.23 \\
+%     }\shear
+
+% \begin{tikzpicture}
+%     \begin{axis}[
+%             ybar,
+%             bar width=.75cm,
+%             width=\textwidth,
+%             height=.5\textwidth,
+%             legend style={at={(0.5,1)},
+%                 anchor=north,legend columns=-1},
+%             symbolic x coords={CNN,NN,NB,SVM,KNN},
+%             xtick=data,
+%             nodes near coords,
+%             nodes near coords align={vertical},
+%             ymin=0,ymax=120,
+%             ylabel={Angle},
+%         ]
+%         \addplot table[x=interval,y=Digit]{\shear};
+%         \addplot table[x=interval,y=Fashion]{\shear};
+%         \addplot table[x=interval,y=Letter]{\shear};
+%         \legend{Digit, Fashion, Letter}
+%     \end{axis}
+% \end{tikzpicture}
+\pgfplotstableread[row sep=\\,col sep=&]{
+    Mx & My & Fx & Fy & Ex & Ey \\
+    0 & 47 & 0.1 & 24 & 0.2 & 30 \\
+    4 & 43 & 4.1 & 29 & 4.2 & 24 \\
+    8 & 34 & 8.1 & 33 & 8.2 & 26 \\
+    12 & 23 & 12.1 & 31 & 12.2 & 29 \\
+    16 & 23 & 16.1 & 29 & 16.2 & 35 \\
+    }\shearx
 
 \pgfplotstableread[row sep=\\,col sep=&]{
-    interval & Digit & Fashion & Letter \\
-    CNN   & 52.4  & 38.82  & 0  \\
-    NN    & 41.8 & 41.18  & 0  \\
-    NB    & 39.9 & 53.6 & 0 \\
-    SVM   & 54.7 & 53.8 & 0 \\
-    KNN   & 63.1  & 45.1 & 0.0 \\
-    }\shade
+   Algo & Mx & My & Fx & Fy & Ex & Ey \\
+    CNN & 0 & -48 & 0.1 & -25 & 0.2 & -30 \\
+    NN & 4 & -46 & 4.1 & -30 & 4.2 & -26 \\
+    NB & 8 & -31 & 8.1 & -43 & 8.2 & -23 \\
+    SVM & 12 & -28 & 12.1 & -40 & 12.2 & -33 \\
+    KNN & 16 & -31 & 16.1 & -32 & 16.2 & -45 \\
+    }\sheary
 
+\begin{figure}[H]
 \begin{tikzpicture}
-    \begin{axis}[
-            ybar,
-            bar width=.75cm,
-            width=\textwidth,
-            height=.5\textwidth,
-            legend style={at={(0.5,1)},
-                anchor=north,legend columns=-1},
-            symbolic x coords={CNN,NN,NB,SVM,KNN},
-            xtick=data,
-            nodes near coords,
-            nodes near coords align={vertical},
-            ymin=0,ymax=120,
-            ylabel={\%},
-        ]
-        \addplot table[x=interval,y=Digit]{\shade};
-        \addplot table[x=interval,y=Fashion]{\shade};
-        \addplot table[x=interval,y=Letter]{\shade};
-        \legend{Digit, Fashion, Letter}
-    \end{axis}
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=60,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearx};
+\addlegendentry{MNIST}
+
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shearx};
+\addlegendentry{Fashion}
+
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shearx};
+\addlegendentry{EMNIST}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-60,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\sheary}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\sheary};
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\sheary};
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\sheary};
+
+\end{groupplot}
 \end{tikzpicture}
+\caption{Robustness graph for Shear property}
+\end{figure}
+For the Shearing property, the convolutional neural-network is the most robust. The Fashion-MNIST and EMNIST datasets have Naive Bayes and KNN as the most robust algorithm respectively.
+% \subsection{ShiftX}
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
+%     \hline
+%      & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
+%     \hline
+%     Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
+%     \hline
+%     0  &   -5&4 & -3&3 & -4&3 & -4&3 & -4&4 \\
+%     \hline
+%         \multirow{3}{*}{1}
+%             &-50&-29 & -50&-38 &  \multirow{3}{*}{-2}&\multirow{3}{*}{2} & -50&-28 & -50&-25\\
+%             &-5&5 & -2&1 & & & -6&4 & -9&11\\
+%             &32&49 & 40&49  & & & 28&49 & 27&49\\
+%     \hline
+%     \multirow{2}{*}{2}  
+%         &   \multirow{2}{*}{-7}&\multirow{2}{*}{7}  &  \multirow{2}{*}{-5}&\multirow{2}{*}{6}  &  -41&-25   &  \multirow{2}{*}{-5}&\multirow{2}{*}{8} & \multirow{2}{*}{-5}&\multirow{2}{*}{11}\\
+%         & & &   & & -12&6   & & & &\\          
+%     \hline
+%     3  &   -6&3 & -7&1 & -7&0 & -7&2 & -8&4  \\
+%     \hline
+%     4  &   -7&6 & -4&4 & -5&5 & -4&5 & -5&4 \\
+%     \hline
+%     5  &   -5&8 & -2&7 & -2&21 & -3&9 & -5&13 \\
+%     \hline
+%     6  &   -5&8 & -4&4 & -3&3 & -5&5 & -5&5 \\
+%     \hline
+%     7  &   -5&6 & -6&2 & -4&2 & -7&4 & -11&4 \\
+%     \hline
+%     8  &   -4&5 & -2&4 & -1&5 & -3&4 & -3&6 \\
+%     \hline
+%     9  &   -5&5 & -4&2 & -2&2 & -4&3 & -3&3 \\ 
+%     \hline
+% \end{tabular}
+% \caption{ShiftX.}
+% \label{tbl:test-file-format}
+% \end{table}
+\newline
+
+% \subsubsection{MT: ShiftX}
+% \pgfplotstableread[row sep=\\,col sep=&]{
+%     interval & Digit & Fashion & Letter \\
+%     CNN & 11.2 & 5.166666666666667 & 2.892857142857143 \\ 
+%     NN & 6.9 & 8.615384615384615 & 2.3214285714285716 \\
+%     NB & 8.727272727272727 & 18.0 & 2.5454545454545454 \\
+%     SVM & 8.545454545454545 & 7.3076923076923075 & 3.0 \\
+%     KNN & 10.416666666666666 & 6.6 & 3.75 \\
+%     }\shiftX
+
+% \begin{tikzpicture}
+%     \begin{axis}[
+%             ybar,
+%             bar width=.75cm,
+%             width=\textwidth,
+%             height=.5\textwidth,
+%             legend style={at={(0.5,1)},
+%                 anchor=north,legend columns=-1},
+%             symbolic x coords={CNN,NN,NB,SVM,KNN},
+%             xtick=data,
+%             nodes near coords,
+%             nodes near coords align={vertical},
+%             ymin=0,ymax=50,
+%             ylabel={Pixels},
+%         ]
+%         \addplot table[x=interval,y=Digit]{\shiftX};
+%         \addplot table[x=interval,y=Fashion]{\shiftX};
+%         \addplot table[x=interval,y=Letter]{\shiftX};
+%         \legend{Digit, Fashion, Letter}
+%     \end{axis}
+% \end{tikzpicture}
+\pgfplotstableread[row sep=\\,col sep=&]{
+    Mx & My & Fx & Fy & Ex & Ey \\
+    0 & 5 & 0.1 & 1 & 0.2 & 1 \\
+    4 & 3 & 4.1 & 1 & 4.2 & 1 \\
+    8 & 3 & 8.1 & 2 & 8.2 & 1 \\
+    12 & 4 & 12.1 & 1 & 12.2 & 1 \\
+    16 & 4 & 16.1 & 1 & 16.2 & 1 \\
+    }\shearxX
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+   Algo & Mx & My & Fx & Fy & Ex & Ey \\
+    CNN & 0 & -5 & 0.1 & -1 & 0.2 & -1 \\
+    NN & 4 & -3 & 4.1 & -1 & 4.2 & -1 \\
+    NB & 8 & -3 & 8.1 & -2 & 8.2 & -1 \\
+    SVM & 12 & -4 & 12.1 & -1 & 12.2 & -1 \\
+    KNN & 16 & -5 & 16.1 & -1 & 16.2 & -1 \\
+    }\shearxY
+
+\begin{figure}[H]
+\begin{tikzpicture}
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=10,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.3\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearxX};
+\addlegendentry{MNIST}
+
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shearxX};
+\addlegendentry{Fashion}
+
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shearxX};
+\addlegendentry{EMNIST}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=.3\textwidth, bar width=.2cm,yshift=1cm,ymin=-10,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shearxY}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west}]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearxY};
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shearxY};
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shearxY};
+\end{groupplot}
+\end{tikzpicture}
+\caption{Robustness graph for ShiftX property}
+\end{figure}
+
+On average the length of the bars for ShiftX metamorphic property is much lower than rotation, shearing, or, shading.
+This means that the algorithms are much less robust when the images are shifted in the direction of X axis.
+Among the algorithms we implemented, CNN is the most robust on MNIST-digit dataset, Naive Bayes on MNIST-Fashion, and, all the algorithms perform equally on the EMNIST dataset.
+
+% \subsubsection{MT: ShiftY}
+% \pgfplotstableread[row sep=\\,col sep=&]{
+%     interval & Digit & Fashion & Letter \\
+%     CNN & 6.6 & 1.4 & 2.0714285714285716 \\
+%     NN & 4.7272727272727275 & 4.076923076923077 & 2.357142857142857 \\
+%     NB & 6.0 & 8.285714285714286 & 2.5161290322580645 \\
+%     SVM & 6.8 & 4.428571428571429 & 2.357142857142857 \\
+%     KNN & 11.3 & 5.333333333333333 & 3.1379310344827585 \\
+%     }\shiftY
+
+% \newline
+% \begin{tikzpicture}
+%     \begin{axis}[
+%             ybar,
+%             bar width=.75cm,
+%             width=\textwidth,
+%             height=.5\textwidth,
+%             legend style={at={(0.5,1)},
+%                 anchor=north,legend columns=-1},
+%             symbolic x coords={CNN,NN,NB,SVM,KNN},
+%             xtick=data,
+%             nodes near coords,
+%             nodes near coords align={vertical},
+%             ymin=0,ymax=50,
+%             ylabel={Pixels},
+%         ]
+%         \addplot table[x=interval,y=Digit]{\shiftY};
+%         \addplot table[x=interval,y=Fashion]{\shiftY};
+%         \addplot table[x=interval,y=Letter]{\shiftY};
+%         \legend{Digit, Fashion, Letter}
+%     \end{axis}
+% \end{tikzpicture}
+\pgfplotstableread[row sep=\\,col sep=&]{
+    Mx & My & Fx & Fy & Ex & Ey \\
+    0 & 3 & 0.1 & 1 & 0.2 & 1 \\
+    4 & 2 & 4.1 & 1 & 4.2 & 0 \\
+    8 & 2 & 8.1 & 1 & 8.2 & 1 \\
+    12 & 3 & 12.1 & 1 & 12.2 & 1 \\
+    16 & 3 & 16.1 & 1 & 16.2 & 1 \\
+    }\shearyX
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+   Algo & Mx & My & Fx & Fy & Ex & Ey \\
+    CNN & 0 & -4 & 0.1 & -1 & 0.2 & -1 \\
+    NN & 4 & -2 & 4.1 & 0 & 4.2 & -1 \\
+    NB & 8 & -3 & 8.1 & -1 & 8.2 & -1 \\
+    SVM & 12 & -3 & 12.1 & -1 & 12.2 & -1 \\
+    KNN & 16 & -4 & 16.1 & -1 & 16.2 & -1 \\
+    }\shearyY
+
+\begin{figure}[H]
+\begin{tikzpicture}
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=10,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.3\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearyX};
+\addlegendentry{MNIST}
+
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shearyX};
+\addlegendentry{Fashion}
+
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shearyX};
+\addlegendentry{EMNIST}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=.3\textwidth, bar width=.2cm,yshift=1cm,ymin=-10,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shearyY}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
+\addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearyY};
+\addplot[fill=red,draw=black] table[x=Fx,y=Fy]{\shearyY};
+\addplot[fill=brown,draw=black] table[x=Ex,y=Ey]{\shearyY};
+
+\end{groupplot}
+\end{tikzpicture}
+\caption{Robustness graph for ShiftY property}
+\end{figure}
+Just like the ShiftX property, the length of bars here are much smaller than others.
+Thus al here we find that k-NN is also more robust than the rest of the algorithms we tested when applied to MNIST-digit and EMNIST-letter dataset.
+While, Naive Bayes is more robust when applied to MNIST-Fashion dataset.

### 2020-04-15 chapters/introduction/introduction.tex
New

@@
-Machine learning algorithms are gaining rapid popularity 
-Testing 
-Oracle problem
-In this paper we first introduce metamorphic testing. Then identify new metamorphic properties for image datasets.
+% Machine learning algorithms are gaining rapid popularity 
+% Testing 
+% Oracle problem.
+% In this paper we first introduce metamorphic testing. Then identify new metamorphic properties for image datasets.
 
-Machine learning has gained rapid popularity in the past decade and different sectors like healthcare, finance, retail, etc.
+Machine learning has gained rapid popularity in the past decade, and different sectors like healthcare, finance, retail, etc.
 are using machine learning techniques to provide better products and services.
 This rising popularity has created a demand for better implementation of the state-of-the-art algorithms in order to implement more complex and sophisticated use cases.
-Machine learning algorithms has been around for a long time now and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.
-While developing and training a machine learning model, the developers rely on the accuracy of these libraries to produce best results where the aim is to create a model that makes the best predictions.
+Machine learning algorithms have been around for a long time now, and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.
+While developing and training a machine learning model, the developers rely on the accuracy of these libraries to produce the best results where the aim is to create a model that makes the best predictions.
 Conventionally, oracles have been used to test the correctness of a program.
 Oracles provide expected values against which the output from the program can be compared and validated.
-Lack of reliable oracles for testing machine learning algorithms makes it very hard to test the accuracy of such programs.
+Lack of reliable oracles for testing machine learning algorithms makes it very difficult to test the accuracy of such programs.
 This problem is called the oracle problem\cite{Weyuker}.
@@
   \item An oracle does not exist, or,
-  \item An oracle can theoretically exist but it is computationally too expensive to determine the output.
+  \item An oracle can theoretically exist, but it is computationally too expensive to generate/use it.
 \end{itemize}
-Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Weyuker}.
-Davis and Weyuker describe these programs as \enquote{Programs which were written in order to determine the answer in the first place.
+Such a set of programs that do not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Weyuker}.
+Davis and Weyuker describe these programs as \enquote{Programs, which were written in order to determine the answer in the first place.
 There would be no need to write such programs if the correct answer were known}\cite{Davis1981}.
-Most machine learning programs fall under this category as they are written in order to predict the correct answers in the first place.
-Several techniques can be employed to verify the correctness of such programs.
-One of the most popular methods being the use of pseudo-oracles.
-To use pseudo-oracle two or more implementations of the algorithm are independently developed to fulfill the same specification.
-They are run on the same input test data and the outputs from them are then compared.
+Since most machine learning programs are developed to determine the correct answers in the first place, most of them fall under this category.
+Nevertheless, several techniques can be employed to verify the correctness of such programs.
+One of the most popular methods is the use of pseudo-oracles.
+In order to use pseudo-oracle, two or more implementations of the algorithm are independently developed, which fulfill the same specification.
+They are run on the same input test data, and their outputs are compared.
 If the outputs match it can be asserted that the original results are according to the specification.
 This kind of testing is often referred to as dual coding.
-However, this technique introduces a significant overhead in terms of implementing two or more versions of the same algorithm and testing their outputs and is more suitable for mission-critical systems\cite{Weyuker}.\newline
+Nevertheless, this technique introduces significant overhead in terms of implementing two or more versions of the same algorithm and testing their outputs.
+This can lead to significant computation and financial costs.
+However, dual coding is more suitable for mission-critical systems\cite{Weyuker}.
+\newline
 
-Another testing methodology called Metamorphic testing introduced by Chen et.
-al can be used for testing ML programs instead.
-It addresses some of these problems while testing the \enquote{non-testable programs} without significant overhead.
-The idea behind Metamorphic testing is that it easier to compare and understand the relationship between outputs than to compare and understand input-output behavior.
-For a prototype example: To test a program which implements the $sin$ function, the output from the program for value of $sin$ at $x$ could be compare to the real value of $sin(x)$ or, the mathematical property of $sin(x) = sin(\pi-x)$ can be exploited to verify the correct implementation of $sin$ function.
-Such relation $(sin(x) = sin(\pi-x))$ are called Metamorphic Relations.
-Metamorphic testing makes use of metamorphic relations where an input relation is used to generate new input test cases from existing test data, and an output relation is used to compare the outputs produced by the test cases.\newline
-In this paper, we will explore the types of guarantees one can expect a machine learning model to possess because of the properties that the underlying algorithm of the implementation.
+Chen et al.
+introduced another method of testing these machine learning programs with no oracle called Metamorphic testing.
+It addresses some of those problems while testing the \enquote{non-testable programs} without significant overhead.
+The idea behind Metamorphic testing is that it is easier to compare and understand the relationship between outputs than to compare and understand input-output behavior.
+For example: To test a program which implements the $sin$ function, the output from the program for value of $sin$ at $x$ could be compare to the real value of $sin(x)$ or, we can exploit the the mathematical property of $sin(x) = sin(\pi-x)$ to verify the correct implementation of $sin$ function.
+Mathematical properties like $(sin(x) = sin(\pi-x))$ are called "Metamorphic Relations" and, metamorphic testing makes use of metamorphic relations where an input relation is used to generate new input test cases from existing test data.
+An output relation is also used to compare the outputs produced by the new test cases.
+\newline
+In this paper, we will explore some new properties which can be used with image datasets in particular, and we will also test them on some standard machine learning algorithms.
 % In particular we will look at google's tensorflow.
@@
 %   \item How does metamorphic properties affect different dataset and deep-learning algorithms?
-    \item Does metamorphic properties have similar affect on the individual classes in a dataset.
-    \item What range of metamorphic transformation produce similar accuracy as the original dataset?
+    \item Do metamorphic transformations have a similar effect on all the classes in a dataset?
+    \item What range of metamorphic transformation produces similar accuracy as the original dataset?
     % \item Are some machine-learning algorithms more robust than others?
@@
 %   \item At what point does the algorithm fail to produce correct classifications on distorted inputs?
-
 \end{enumerate}
+We will also investigate the robustness of some machine learning algorithms that we implement to test our transformed datasets.
 %Point of failure. by humans& computer. (visual inpection)

### 2020-04-15 chapters/litReview/finalLit.tex
New

@@
 \section{Software testing}
-Testing is one of the most important activity in software development life cycle.
-Bertolino \cite{Bertolino2007} define software testing as, ``observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions.'' Testing is widely used in industry for various quality assurance purposes.
+Testing is one of the most crucial activities in the software development life cycle.
+Bertolino \cite{Bertolino2007} define software testing as, \enquote{observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions}.
+Software testing is a very common practice in the software industry and is used to ensure the quality of the product.
 Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc.\cite{Bertolino2007} A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost.
-Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.
+Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.\\
 Weyuker \cite{Weyuker} categorizes the testing research activities into three categories:
 \begin{enumerate}
-  \item Develop a sound theoretical basis for testing.
-  \item Devise and improve testing methodologies, especially the mechanizable ones.
-  \item Define accurate measurement criteria for testing data adequately.
+  \item \enquote{Develop a sound theoretical basis for testing}.
+  \item \enquote{Devise and improve testing methodologies, especially the mechanizable ones}.
+  \item \enquote{Define accurate measurement criteria for testing data adequately}.
 \end{enumerate}
 
-However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs.
-These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments.
-In the context of software testing, the two very obvious fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle \cite{Chen2002,Elbaum2014}.
-Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used.
+However,  there are a lot of uncertainties in program testing, and it is often not so straightforward to test programs.
+These uncertainties in most systems are introduced by either human biases, non-deterministic machine learning algorithms, external libraries, or sensing variability.
+This complexity emerges due to the need to support deep interactions between interconnected software systems, execution environments, and their users.
+In the context of software testing, the two very fundamental problems are increased uncertainty of what makes up the input space and what is considered as acceptable behavior in the absence of an oracle \cite{Chen2002,Elbaum2014}.
+
+Although non-testable programs occur in all areas of software engineering, the problem is undoubtedly most acute in areas where mathematical computations are performed, particularly where floating-point computation is involved.
 While performing mathematical computations, errors from three sources can creep in \cite{Weyuker}:
+
 \begin{enumerate}
@@
 
- One of the first problems that testers run into while testing these uncertain programs is that they don't have access to acceptable output to test the program's predictions against.
-This problem is often referred to as the Oracle problem.
-Weyuker \cite{Weyuker} provides founding definition of an oracle as "a system that determines the correctness of the solution by comparing the system's output to the one that it predicts".
+ One of the first problems that testers run into while testing these uncertain programs is that they do not have access to acceptable outputs against which the program's predictions can be compared.
+The lack of access to correct output is often referred to as the Oracle problem.
+Weyuker \cite{Weyuker} provides the founding definition of an oracle as \enquote{a system that determines the correctness of the solution by comparing the system's output to the one that it predicts}.
 She also defines non-testable programs as the programs for which such oracles do not exist.
-The term non-testable is used, from the point of view of correctness testing.
-If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.
+If a tester cannot agree on the output of a program or has to spend a tremendous amount of resources to find the correctness of the results, testing those systems may not be worth it.
+Thus the term non-testable is used from the point of view of correctness testing.
 
- A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles.
-If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault.
-On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.
-
- Many techniques have since been developed to test these set of non-testable programs.
-One way of elevating the oracle-problem is through the use of pseudo oracle.
+ Many techniques have since been developed to test these sets of non-testable programs.
+One way of elevating the oracle-problem is by using pseudo oracles.
 It is also referred to as dual-coding and is used in highly critical software \cite{Weyuker,Murphy2009}.
-Pseudo-oracles are multiple implementation of same specification of the original program under test.
- However, dual coding comes with it's own set of problems.
-As the authors Weyuker \cite{Weyuker} and Murphy, Shen, and, Kaiser \cite{Murphy2009} pointed out some limitations that pseudo-oracles require at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
+Pseudo-oracles are multiple implementations of the same specification of the original program under test.
+ However, dual coding comes with its own set of problems.
+As the authors Weyuker \cite{Weyuker} and Murphy, Shen, and, Kaiser \cite{Murphy2009} pointed out some limitations of pseudo-oracles include the use of least two implementations, which may come out to be a lot of overhead or, multiple implementations may not exist or, the multiple implementations may be created by the same or same set of developers prone to make same mistakes.
  In light of these shortcomings of the testing process Weyuker \cite{Weyuker} finally make five recommendation for items to be considered as a part of documentation during testing.
 \begin{enumerate}
-  \item The criteria used to select the test data.
-  \item The degree to which the criteria were fulfilled.
-  \item The test data, the program ran on.
-  \item The output of each of each test datum.
-  \item How the results were determined to be correct or acceptable.
+  \item \enquote{The criteria used to select the test data.}
+  \item \enquote{The degree to which the criteria were fulfilled.}
+  \item \enquote{The test data, the program ran on.}
+  \item \enquote{The output of each of each test datum.}
+  \item \enquote{How the results were determined to be correct or acceptable.}
 \end{enumerate}
-Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.
+Although these recommendations do not solve the problem of lack of oracle, however, they do provide information on whether the program should be considered adequately tested or not.
 
 Due to a great deal of overhead involved, pseudo-oracles may not be practical for every situation.  
-A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined.
+% A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined.
 The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases.
@@
 \cite{Weyuker}
+
+Another course of action that is used often in these situations is to test the program on "simplified" test data for which the correct output can be easily determined.
+Testers can then extrapolate the results for more complex cases from the output of the "simplified" test data.
+However, not all test cases can be generated with this technique.
+This deliberate omission of even the important test cases is because they might be too difficult, if not, impossible to check and not because they are not expected to yield useful information.
+The second problem with using simple test cases is very obvious i.e.
+it is normal for central and simple cases to work perfectly, whereas edge cases that may be ignored tend to cause errors.
+\cite{Weyuker}
+
+ Developing sophisticated oracles is another way of encountering the oracle problem.
+If the oracles are very relaxed such that they tolerate the effects of uncertainties, then there is a chance that a fault may be masked.
+On the other hand, f the oracles are too narrow, it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.

### 2020-04-15 chapters/litReview/mlAlgo.tex
New

@@
 \subsection{Neural network}
-Neural networks were first introduced in 1944 by two University of Chicago researchers Warren McCullough and Walter Pitts, who later moved to MIT in 1952.
-These algorithms are modeled loosely after the human brain, that are designed to recognize patterns.
+Neural networks were first introduced in 1944 by two University of Chicago researchers Warren McCullough and Walter Pitts.
+The neural network algorithms are modeled loosely after the human brain, which is very efficient in pattern recognition.
 Dr.
-Robert Hecht-Nielsen, inventor of the first neurocomputer defines a neural network as:
+Robert Hecht-Nielsen, who also invented the first neurocomputer, defines a neural network as:
 "...a computing system made up of a number of simple, highly interconnected processing elements, which process information by their dynamic state response to external inputs"\cite{Caudill}.
@@
 % cite figure: https://towardsdatascience.com/applied-deep-learning-part-1-artificial-neural-networks-d7834f67a4f6
-A typical neural network looks like a variation of Figure \ref{Neural network}. \\
-Input layer: The leftmost layer in the network is made up of input neurons and the layer is called the input layer.
+A typical neural network looks like a variation of Figure \ref{Neural network} and is composed of the following layers. \\
+Input layer: This is the leftmost layer in the network.
+It is made up of input neurons, and the layer is called the input layer.
 There is no computation performed in the nodes at this layer.
-Input layer simply provides the information from the environment to the next layer.
-Hidden layers: The layers in the middle make up the hidden layers, as the neurons in these layers are neither inputs nor outputs.
+The input layer simply provides information from the environment to the next layer.
+\\
+Hidden layers: The layers in the middle make up the hidden layers.
+As the name suggests, these layers are neither inputs nor outputs.
 There can be zero or multiple hidden layers.
-Hidden layers takes the input from the input layer and passes information to the output layer after performing computation on the data.
-Output layer: The rightmost or output layer contains the output neurons, or, as in this case, a single output neuron. 
-There are no set rules to design the layers of a neural network (specially the hidden layers) and this process is often considered as an art\cite{NN}.
-We determine the number of hidden layers and nodes empirically for each particular case in order to optimize performance.
+Hidden layers take the input from the input layer and pass the information to the output or other hidden layer after performing computation on the data.
+\\
+Output layer: The last layer in the neural network is called the output layer.
+This layer contains the output neurons, which tells the final class of the input.
+In the example above, we have a single output neuron.
+\\
+
+% There are no set rules to design the layers of a neural network (specially the hidden layers) and this process is often considered as an art\cite{NN}.
+The number of hidden layers and nodes are often determined empirically for each particular case in order to optimize performance.
 The edges (or connections) between a layer and the layer before it are represented by a weight $\omega_{ij}$, which represents the strength of connection between i and j nodes.
@@
 Once the optimal value is reached the network can be used to make predictions\cite{hall199}.
+There are no set rules to design the layers of a neural network (especially the hidden layers), and this process is often considered as an art\cite{NN}.
+The number of hidden layers and nodes is often determined empirically for each particular case in order to optimize performance.
+The edges (or connections) between two layers($i$ and $j$) are represented by weight $\omega_{ij}$, which represents the strength of the connection between $i$ and $j$ nodes.
+When the neural network is being trained, we assign random values to the weights for each connection.
+The weights are then optimized such that the error function is minimized.
+For each node at a layer, all the outputs from the previous nodes are multiplied by the weight of connections between them.
+The weighted outputs are then summed and used as the value at that node.
+This cycle is repeated for all the nodes in every layer.
+The algorithm compares the prediction from the output layer to the real value and readjusts the weights.
+Once the optimal value is reached, the network can be used to make predictions\cite{hall199}.
 
-These neural networks where the output from one layer is used as input to the next layer are called feedforward neural networks\cite{NN}\cite{hall199}.
-There are no loops in the feedforward neural network and the information flows in one direction and are never fed back.
-The most well known form of a feed forward neural network is called multilayer perceptron(MLP).
+These neural networks where the input of a layer is received from the output of the previous layer are called feedforward neural networks\cite{NN}\cite{hall199}.
+The feedforward neural network has no loops, and the information flows in one direction and is never fed back.
+The most well-known form of a feedforward neural network is called a multilayer perceptron(MLP).
 MLPs are also called universal function approximator.
-A single hidden layer MLP with a sufficient number of nonlinear units can act as a continuous function on to a narrow input domain with arbitrary precision.
-\cite{Graves}.
-There are some other models of artificial neural networks in which feedback loops are possible.
-These models are called recurrent neural networks.
-The idea in these models is to have neurons which fire for some limited duration of time, before becoming quiescent.
-That firing can stimulate other neurons, which may fire a little while later, also for a limited duration.
-That causes still more neurons to fire, and so over time we get a cascade of neurons firing.
-Loops don't cause problems in such a model, since a neuron's output only affects its input at some later time, not instantaneously.
-Recurrent neural nets have been less influential than feedforward networks, in part because the learning algorithms for recurrent nets are (at least to date) less powerful.
-But recurrent networks are still extremely interesting.
-They're much closer in spirit to how our brains work than feedforward networks.
-And it's possible that recurrent networks can solve important problems which can only be solved with great difficulty by feedforward networks.\cite{NN} % cite: http://neuralnetworksanddeeplearning.com/chap1.html
+An MLP with one hidden layer and a sufficient number of nonlinear units can act as a continuous function on a narrow input domain with arbitrary precision \cite{Graves}.
+Other models of artificial neural networks where a feedback loop is possible are called recurrent neural networks.
+The neurons in these networks fire for a limited duration of time before becoming dormant.
+However, the firing stimulates other neurons in the network, which may fire after some time for a limited duration of time.
+This can have a cascading effect causing yet other neurons to fire later.
+Having loops in these models does not create problems since the neurons firing does not affect their input instantly but at a later time.
+Even though the recurrent neural networks are much similar to our brains than feedforward networks, they have not been as influential as the feedforward networks.
+This is mostly because the learning algorithms for recurrent nets are (at least to date) less powerful than feedforward networks.
+In the future, it will be possible that the recurrent networks will be able to solve significant problems which feedforward networks solve with great difficulty.\cite{NN}
+% cite: http://neuralnetworksanddeeplearning.com/chap1.html
 
 \subsection{Convolutional neural network}
-Convolutional neural networks (ConvNet) are very similar to ordinary neural networks in structure.
+% Convolutional neural networks (ConvNet) are very similar to ordinary neural networks in structure.
 They work by extracting simple features at a higher resolution and then converting them into more complex features at a coarser resolution \cite{simard2003best}.
@@
 
-What makes it different from an ordinary neural network is the architecture of a ConvNet.
+% What makes it different from an ordinary neural network is the architecture of a ConvNet.
 It makes explicit assumption that the inputs are images, which allows us to encode certain properties into the architecture.
@@
 A simple ConvNet is a sequence of layers and every layer transforms one volume of activation to another through a differentiable function.
+Convolutional neural networks (ConvNet) are very similar to the conventional neural networks in terms of structure.
+They work by extracting simple features at a higher resolution and transforming them into more complex features at a more granular resolution \cite{simard2003best}.
+It does so by performing dot product on the inputs received at each neuron and optionally follow it with non-linearity.
+Just like a typical neural network, ConvNets (from the input image to output class) can be represented with a single differential function.
+The neurons in ConvNets have learnable weights and biases, which are optimized during the learning phase.
+It also has a loss function on the fully-connected output layer, which is minimized.
+
+What makes it different from an ordinary neural network is the architecture of a ConvNet.
+It makes very specific assumptions that the inputs are images, which allows us to encode specific properties into the architecture.
+In particular, unlike a regular Neural Network, the neurons in the layers of a ConvNet are arranged in 3 dimensions: width, height, depth.
+A simple ConvNet is a sequence of layers, and every layer transforms one volume of activation to another through a differentiable function.
 
@@
 
-A ConvNet architecture is made up of the following layers and these layers are stacked to form the full network \cite{krizhevsky2012imagenet}: \\
-Input layer: This layer holds the raw input image in form of it's pixel values and color channels.\\
-Convolutional layer (Conv): This layer computes the dot product between it's weight and a small region in the previous layer it is connected to.
+% A ConvNet architecture is made up of the following layers and these layers are stacked to form the full network \cite{krizhevsky2012imagenet}: \\
+% Input layer: This layer holds the raw input image in form of it's pixel values and color channels.\\
+% Convolutional layer (Conv): This layer computes the dot product between it's weight and a small region in the previous layer it is connected to.
 It is a linear operation which multiplies the input from the previous layer to a two-dimensional array of weights called filter or kernel.
 \\
+% Rectified linear unit (ReLu): This layer applies an element-wise activation function, like $max(0,x)$ with the threshold at zero.
+It introduces non-linearity to the system which has just been doing linear computations (element wise multiplication and sum) in previous Conv layers.
+\\
+% Pooling layer (POOL): This layer performs a downsampling operation along the spatial dimensions.
+This helps in two major ways: $i)$ The amount of parameters or weights is reduced by 75\%.
+$ii)$ It also reduces the problem of overfitting.\\
+% Fully connected layer (FC): The fully connected output layer computes the class scores for the input.
+The neurons in this layer are connected to every neuron in the previous layer.
+The only difference between this layer and the Conv layer is that the neurons in Conv layer are only connected to a local region in the input layer and the neurons in Conv layer share parameters.
+The neurons in both the layer compute dot product and their function form is identical.
+Thus, it is easily possible to convert between the fully connected and Conv layer.\\
+A ConvNet architecture is made up of the following layers. The full network is made of multiple instances of these layers stacked one after other \cite{krizhevsky2012imagenet}: \\
+Input layer: This layer contains the raw input image in the form of its pixel values and color channels.\\
+Convolutional layer (Conv): This layer calculates a dot product between its assigned weights and a small region in the previous layer it is connected to.
+It is a linear operation that multiplies the input from the previous layer to a two-dimensional array of weights called filter or kernel.
+\\
 Rectified linear unit (ReLu): This layer applies an element-wise activation function, like $max(0,x)$ with the threshold at zero.
-It introduces non-linearity to the system which has just been doing linear computations (element wise multiplication and sum) in previous Conv layers.
+The purpose of this layer is to introduce non-linearity to a system, which has just been doing linear computations (element-wise multiplication and sum) so far.
 \\
@@
 $ii)$ It also reduces the problem of overfitting.\\
-Fully connected layer (FC): The fully connected output layer computes the class scores for the input.
-The neurons in this layer are connected to every neuron in the previous layer.
-The only difference between this layer and the Conv layer is that the neurons in Conv layer are only connected to a local region in the input layer and the neurons in Conv layer share parameters.
-The neurons in both the layer compute dot product and their function form is identical.
+Fully connected layer (FC): The fully connected output layer is used to compute the class scores for an input.
+The only difference between this layer and the Conv layer is that the neurons in the Conv layer are only connected to a local region in the input layer while the neurons in the FC layer are connected to every neuron in the previous layer.
+The neurons in both the layer compute dot product, and their function form is identical.
 Thus, it is easily possible to convert between the fully connected and Conv layer.\\
 
-It should be noted that some layers contain parameters while others may not.
+It should be noted that some layers have parameters, while others may not.
+The ReLu/Pool layer implements a fixed function, whereas the Conv/FC layers transformation functions work on the activations in the input volume and the parameters (weights and biases) of the neurons.
+During the training period, the weights and biases of the Conv/FC layer are trained using gradient descent.
+The parameters are trained such that the scores computed by ConvNet generate outputs that match the expected output of each image in the training set \cite{convNNStan}.
+% It should be noted that some layers contain parameters while others may not.
 The ReLu/Pool layer implements a fixed function whereas, the Conv/FC layers transformation functions work on the activations in the input volume and the weights and biases of the neurons.

### 2020-04-15 chapters/methodology/collection.tex
New

--- 2019-08-04 chapters/methodology/collection.tex
@@
+In this chapter, we will discuss the tools we used to perform our experiment. 
+We used Python as the programming language to implement our code.
+We chose Python because of its popularity and easy syntax.
+There are also plenty of Python libraries like Tensorflow, Keras, and scikit-learn available to easily implement machine learning, deep-learning, natural language processing algorithms.
+Along with Python as the programming language, we also used the following programs, tools, and datasets to perform our experiment.
  \section{Tools}
-\subsection{Jupyter}
-The Jupyter Notebook is an open-source web application that supports data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, etc.
-by allowing us to create and share documents that contain live code, equations, visualizations and narrative text.
-Jupyter allows for displaying the result of computation inline in the form of rich media (SVG, LaTeX, etc.).
-The Jupyter notebook combines two components:
+\subsection{HCC}
+Due to the high computation requirements for some dataset we needed a faster and reliable hardware.
+The Holland Computing Center (HCC) claim to be the fastest resource in the state of Nebraska.
+HCC provides these services to researcher and students associated with any campus of the University of Nebraska system.
+Some shared services are available for free and dedicated services can be obtained for a modest price.
+We used their servers to run our Jupyter notebooks.
+
+\subsection{Jupyter Notebook}
+Jupyter notebook is part of project Jupyter, which aims at providing an interactive interface for development across multiple platforms and programming languages.
+Jupyter's web interface supports data cleaning, data transformation, and visualization, numerical operations, etc.
+It allows us to create live code snippets and equations and shows results of inline computation right next to the code in the form of rich media (SVG, LaTeX, etc.).
+It combines two components:
 \begin{itemize}
-  \item \textbf{A web application}: a browser-based tool for interactive authoring of documents which combine explanatory text, mathematics, computations and their rich media output.
-  \item \textbf{Notebook documents}: a representation of all content visible in the web application, including inputs and outputs of the computations, explanatory text, mathematics, images, and rich media representations of objects.
+  \item \textbf{A web application}: a web-based interactive tool to write code, markdown, etc. It also displays the rich media output.
+  \item \textbf{Notebook documents}: a representation of all the content written and displayed using the web application.
 \end{itemize}
 Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy.
-In this project, the codes are written in python notebook which can be accessed from http://github.com/.
+In this project, we wrote the codes in python notebook, which can be accessed from our GitHub repository.
 
 \subsection{Tensorflow}
-TensorFlow\textsuperscript{TM} is an open source software library developed within Google’s AI organization by the Google Brain team with a strong support for machine learning and deep learning.
+% TensorFlow is an end-to-end open source platform for machine learning.
+It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications
+TensorFlow\textsuperscript{TM} is an open-source software library developed within Google’s AI organization by the Google Brain team with strong support for machine learning and deep learning.
+Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices.
+Several well-known companies like Uber, Google, AMD, etc.
+use Tensorflow for high-performance numerical computation and machine learning tasks.
+While TensorFlow is capable of handling a wide range of tasks, it is designed mainly for deep neural network models.
+Tensorflow provides API for loading, manipulating, and using the MNIST dataset identified in section \ref{dataset}.
+We also used TensorFlow to implement neural network and convolutional neural network defined insection \ref{Algorithms}
+
+% TensorFlow\textsuperscript{TM} is an open source software library developed within Google's AI organization by the Google Brain team with a strong support for machine learning and deep learning.
 Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices.
@@
 It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}.
+Tensorflow provides api for loading the MNIST dataset identified in section \ref{dataset}.
+We also used tensorflow to implement neural network and convolutional neural network defined in section \ref{Algorithms}
 
-\section{Algorithm}
+\subsection{Scikit-learn}
+Scikit-learn is a Python module for machine learning built on top of SciPy and is distributed under the 3-Clause BSD license.
+It provides APIs to a range of supervised and unsupervised learning algorithms via a consistent interface in Python.
+
+\section{Algorithms}\label{Algorithms}
+In order to answer research questions two and three, we implemented some popular machine learning algorithms to provide quantitative data on the effect of metamorphic relations on the accuracy of datasets and their classes.
+We used TensorFlow and scikit-learn to implement the following machine learning algorithms.
+
 \subsection{Convolutional neural network}
-\subsection{2-layer neural network}
+The images in the MNIST dataset is a one-dimensional vector of 784 features (28x28 pixels).
+We first reshape the images to match the picture format height x width x channel.
+Each image in the MNIST dataset is now a single-channel of 28x28x1 size.
+The images are then fed into the network as input.
+The first convolution layer has 32 filters with a kernel size of five.
+The activation function we used is the ReLU function, and the output from this layer is fed into a pooling layer.
+The data goes through another iteration of convolution and pooling before being flattened and sent to the fully connected layer.
+The output layer gives us a number that corresponds to the class of the image it is assigned.
 
-\section{Dataset}
+\subsection{Neural network}
+
+ Hidden fully connected layer with 256 neurons.
+Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections.
+If the image is a 64 by 64 greyscale image, then we'd have 64x64=4,096 input neurons, with the intensities scaled appropriately between 0 and 1.
+The output layer will contain just a single neuron, with output values of less than 0.5 indicating "input image is not a 9", and values greater than 0.5 indicating "input image is a 9 ".
+The input pixels are greyscale, with a value of 0.0 representing white, a value of 1.0 representing black, and in between values representing gradually darkening shades of grey.
+The second layer of the network is a hidden layer.
+
+\subsection{Naive Bayes}
+We used scikit-learn to implement the Naive Bayes algorithm. We transformed the images into a one-dimensional vector of 784 features. 
+Using the $sklearn.naive\_bayes.MultinomialNB()$ function we created a Naive Bayes classifier, which is then fitted using the $fit()$ function, which takes the images and labels as input and fits the classifier according to the images and labels.
+The resulting classifier is then used to predict the labels of test data.
+
+\subsection{$k$-Nearest Neighbor}
+ We used scikit-learn to implement our $k$-nearest neighbor algorithm.
+Scikit's $sklearn.neighbors$ module provides the functionality to implement unsupervised and supervised neighbors-based learning methods.
+ The KNeighborsClassifier function from the $sklearn.neighbors$ module implements learning based on the $k$ nearest neighbors of each query point, where $k$ is an integer value specified by the user.
+The k-neighbors classification in KNeighborsClassifier is the most commonly used technique.
+Since the optimal value $k$ is dependent on data, we ran the experiment with multiple values of $k$ and found that the $k$=3 produces the best accuracy.
+In general, a larger $k$ suppresses the effects of noise but makes the classification boundaries less distinct.
+ We used Euclidean distance as the distance metric and assigned equal weights to all the query points.
+In some cases, it might be better to assign weights based on the distance.
+The close query point contributes more to the fit, and the ones far contribute less.
+For our case, the uniform weight with a simple majority vote of the nearest neighbors worked just fine.
+
+\subsection{SVM}
+We also implemented the support vector machine algorithm using scikit-learn.
+The $sklearn.svm.SVC$ class is based on libsvm and is capable of performing multi-class classification.
+Internally, they use libsvm and liblinear to handle all computations.
+These libraries are wrapped using C and Cython.
+It supports multi-class classification on a one-vs-one scheme.
+In this scheme, a classifier is created for each pair of classes and during prediction, the class which receives most votes is assigned to the data point.
+In the event of a tie, we selected the class with the highest total confidence calculated by summing over the pair-wise classification confidence.
+As the other classifiers, $skleran.SVM$ also takes as input two arrays: an array of training samples and another array of class labels.
+The training samples and labels are passed to $fit$ function, which fits the SVM model according to the data.
+The resulting model is then used to predict the labels of test data.
+
+\section{Datasets}\label{dataset}
+In order to create metamorphic properties that can be used by multiple image datasets and are not data-dependent, we tested our metamorphic properties on three different datasets.
+We choose the following three datasets, but the experiment can be easily replicated on other datasets.
+
 \subsection{MNIST Dataset}
-The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 55,000 examples, and a test set of 10,000 examples.
+The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST} has a training set of 55,000 examples and a test set of 10,000 examples.
 It is a subset of a larger set available from NIST.
 The digits have been size-normalized and centered in a fixed-size image.
-It is a good database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting.
-The MNIST database was constructed from NIST's Special Database 3 and Special Database 1 which contain binary images of handwritten digits.
-The original black and white (bilevel) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio.
+It is an excellent database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting.
+The MNIST database was constructed from NIST's Special Database 3 and Special Database 1, which contain binary images of handwritten digits.
+The original black and white (bi-level) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio.
 The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.
@@
 All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors.
-There are 4 files:
+There are four files:
 \begin{itemize}

### 2020-04-15 chapters/methodology/properties.tex
New

--- 2019-08-04 chapters/methodology/properties.tex
@@
-\section{Identifying Metamorphic Relations} 
-We identified seven metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, shifting along-axis, zooming along x-axis, zooming along y-axis.
-Each image in the testing dataset (digit, letter, and, fashion) was transformed using the seven metamorphic properties.
+\section{Identifying Metamorphic Relations} \label{identifyingMR}
+To answer our first research question, we implemented some affine transformations on the datasets as possible candidates for metamorphic properties.
+We observed that applying these affine transformations on the dataset to a very small degree produced similar accuracy as that of the original dataset.
+Thus we selected these five transformations as metamorphic properties for each dataset: rotate, shear, shade, shift the image along $x$-axis, and shift the image along $y$-axis.
+Each image in the testing dataset (MNIST, Fashion-MNIST, and EMNIST-Letter) was transformed using these five metamorphic properties.
 We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
+
+There are $10000$ test images in the MNIST dataset.
+There are $10$ class labels from $0$ to $9$, and each class label has $1000$ samples.
+We applied the following metamorphic properties to each test image.
 \subsection{Rotate}
-The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle.
-For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}].
+% Since we are dealing with image datasets, we hypothesize that small changes to the images by rotating them clock-wise or counter clock wise would not have drastic effect on the accuracy of model.
+To test our hypothesis we rotated the test data at each angle between [\ang{-50}, \ang{50}].
+The first metamorphic property we identified was rotating the images on the $z$ axis.
+To implement the rotate property, we used the Keras ImageDataGenerator class.
+ImageDataGenerator implements $apply\_transform()$ method, which can be used to rotate images by passing the argument $'theta'$ along with the angle to rotate the image.
+Every image in the three datasets was rotated for every angle in [$-50$, $50$].
+This generated 100 versions of the follow-up test dataset of the original data, where each version differs from the last by $1$ degree of rotation.
+We expect that certain digits with symmetry (like $0$) will not be affected that much by the rotate property.
+% The test images from each dataset is transformed For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}].
+The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle.
     \begin{figure}[!htbp]
@@
         \end{subfigure}
-        \caption{Rotation property applied to Digit 3.}
-        \label{fig:Rotate-misclassifications}
+        \caption{Rotate property applied to Digit 3.}
+        \label{fig:Rotate-property}
     \end{figure}
@@
 
-\subsection{Shear}  
-    \begin{figure}[!htbp]
-        \centering
-        \begin{subfigure}[b]{.3\textwidth}
-            \includegraphics[width=\linewidth]{images/shear1.png}
-            \caption{Angle: \ang{-50}}
-            \label{fig:Rotate-misclass0}
-        \end{subfigure}%
-        \begin{subfigure}[b]{.3\textwidth}
-            \includegraphics[width=\textwidth]{images/shear2.png}
-            \caption{Angle: \ang{-50}}
-            \label{fig:Rotate-misclass0}
-        \end{subfigure}%
-        \begin{subfigure}[b]{.3\textwidth}
-            \includegraphics[width=\linewidth]{images/shear3.png}
-            \caption{Angle: \ang{-50}}
-            \label{fig:Rotate-misclass0}
-        \end{subfigure}
-
-        \caption{Shear property applied to Digit 4.}
-        \label{fig:Rotate-misclassifications}
-    \end{figure}
-    \FloatBarrier
-
-\subsection{Shading}
+\subsection{Shade}
+We represent the pixels of the MNIST images as floating point numbers between 0 and 1 where 0 is white, and 1 represents black.
+To apply the shade transformation, we increased the non-black pixels by $0.01$ for every image until they became black.
     \begin{figure}[htb!]
@@
         \caption{Shade property applied to Digit 9.}
-        \label{fig:Rotate-misclassifications}
+        \label{fig:Shade-property}
     \end{figure}
@@
 
-\subsection{Shifting in the X direction}
-    For any value above x the image was completely out of the frame.
+\subsection{Shear} 
+To shear the images, we used the image pre-processing library offered by Keras.
+The ImageDataGenerator class generates batches of tensor image data with real-time data augmentation.
+We used the ImageDataGenerator's $apply\_transform()$ method to apply a transformation to an image according to given parameters.
+The $apply\_transform()$ method takes in the image, transformation type, and, the amount of transformation to be applied as a parameter.
+It then applies the transformation and returns a transformed version of the input in the same shape.
+The transformation parameter we used here was $shear$, and the images were transformed for every angle in $[-50, 50]$.
+
+    \begin{figure}[!htbp]
+        \centering
+        \begin{subfigure}[b]{.3\textwidth}
+            \includegraphics[width=\linewidth]{images/shear1.png}
+            \caption{Angle: \ang{-50}}
+            \label{fig:Rotate-misclass0}
+        \end{subfigure}%
+        \begin{subfigure}[b]{.3\textwidth}
+            \includegraphics[width=\textwidth]{images/shear2.png}
+            \caption{Angle: \ang{-50}}
+            \label{fig:Rotate-misclass0}
+        \end{subfigure}%
+        \begin{subfigure}[b]{.3\textwidth}
+            \includegraphics[width=\linewidth]{images/shear3.png}
+            \caption{Angle: \ang{-50}}
+            \label{fig:Rotate-misclass0}
+        \end{subfigure}
+
+        \caption{Shear property applied to Digit 4.}
+        \label{fig:Shear-property}
+    \end{figure}
+    \FloatBarrier
+
+\subsection{Shift the image along the X axis(ShiftX)}
+Since the images are $28$ pixels wide, shifting the images by more than 28 pixels in either direction moved the images out of the frame completely.
+Thus, we transformed the test datasets by moving each image by pixels between 0 and 28 in both the X directions.
+We used ImageDataGenerator's $apply\_transform()$ function with $tx$ parameter and a pixel value in order to perform this transformation.
+This generated 56 follow-up test dataset of the original data where each version differs from the last by $1$ pixel shift along the $x$ axis.
     \begin{figure}[htb!]
@@
 
-        \caption{Shift X property applied to Digit 7.}
-        \label{fig:Rotate-misclassifications}
+        \caption{ShiftX property applied to Digit 7.}
+        \label{fig:ShiftX-property}
     \end{figure}
@@
 
-\subsection{Shifting in the Y direction}
+\subsection{Shift the image along the Y axis(ShiftY)}
+The last metamorphic property we identified was shifting the images on the Y-axis.
+We used ImageDataGenerator's $apply\_transform()$ function with $ty$ parameter to transform the test data.
+Since the images are 28x28 pixels, we shifted the images by each pixel between 0 and 28 pixels in both Y directions.
     \begin{figure}[htb!]
@@
 
-        \caption{Shift Y property applied to Digit 5.}
-        \label{fig:Rotate-misclassifications}
+        \caption{ShiftY property applied to Digit 5.}
+        \label{fig:ShiftY-property}
     \end{figure}
     \FloatBarrier
+
+The follow-up test images have the same structure and labels as the original image.
+After generating all the transformed versions of the datasets, they were saved to be used as follow-up test cases for our machine-learning algorithms.
+The section \ref{identifyingMR} also answers our first research question.
+
+After generating the follow-up test cases and implementing the machine-learning algorithms, we tested the trained model on the five follow-up test cases.
+The rotate, shade, and shear properties have 100 versions of the transformed original dataset each.
+The shiftX and shiftY properties have 56 versions of original test data as follow-up test data.
+Each of the 412 follow-up test datasets was then tested on the trained models, and their accuracy was calculated.
+We will discuss our findings in the next section.

### 2020-04-15 chapters/results/figures.tex
New

@@
 \subsection{Overall Accuracy or true positive}\label{4.1.1}
-In this section we tested the algorithms using the transformed test dataset.
-The test datatsets were applied with increasing value of transformations identified in \ref{identifyingMR}.
-A copy of these new datasets generated from the original dataset by applying the transformations were saved to serve as follow-up test cases.
-For example, the MNIST dataset was transformed by applying the shading metamorphic relation for every pixel between [-28,28].
-The models were then tested with transformed test data and their accuracy were calculated for every follow-up test data.
-The following graphs shows the change in accuracy of the whole dataset as the degree of transformation is changed.
-The X-axis shows the value of metamorphic transformation applied to the original test data and the Y-axis shows the accuracy corresponding to that value of transformation.
+In this section, we compare the accuracy of the original MNIST test data to the accuracy of the follow-up test cases.
+After generating the model and testing the original test data, we used the same model to test the follow-up transformed test dataset.
+The test datasets were applied to the models with the increasing value of transformations.
+As we discussed in section \ref{identifyingMR}, the follow-up test cases were generated by transforming the original dataset with an increasing value of metamorphic properties.
+A copy of these new datasets was saved to serve as follow-up test cases.
+The follow-up test images have the same structure and labels as the original image.
+For example, the MNIST dataset was transformed by applying the shiftX metamorphic property for every pixel between [-28,28].
+The models were then tested with transformed test data, and their accuracy was calculated for every follow-up test data.
+The following graphs show the change in accuracy of the whole dataset with the change in the degree of transformation.
+The X-axis shows the value of metamorphic transformation applied to the original test data, and the Y-axis shows the corresponding accuracy to that value of transformation.
     \begin{figure}[htb!]
@@
         \includegraphics[width=\textwidth]{chapters/results/MT/ShiftX.png}
-        \caption{Shifting along X-axis}
+        \caption{Shifting image along X-axis}
     \end{subfigure}
@@
          \includegraphics[width=\textwidth]{chapters/results/MT/ShiftY.png}
-        \caption{Shifting along Y-axis}
+        \caption{Shifting image along Y-axis}
     \end{subfigure}
@@
 
- From the graphs in \ref{fig:Accuracy} we can see that different algorithms respond differently to the follow-up datasets.
-To quantify this difference, we calculated the area under curve for all the curves in \ref{fig:Accuracy}.
-The following table shows the area under each curve in \ref{fig:Accuracy}.
-    \begin{table}[ht]
+ From the graphs in \ref{fig:Accuracy}, we can see that different algorithm respond differently to the follow-up datasets.
+To quantify this difference, we calculated the area under the curve for all the graphs in \ref{fig:Accuracy}.
+The following table shows the area under each curve in \ref{fig:Accuracy}.\\
+    \begin{table}[H]
     \centering
@@
          \hline
-        Rotation & 91.01 & 81.70 & 70.31 & 72.71 & 66.60  \\
+        Rotate & 91.01 & 81.70 & 70.31 & 72.71 & 66.60  \\
         \hline
-        Shading & 64.40 & 75.51 & 79.52 & 50.26 & 52.23 \\
+        Shade & 64.40 & 75.51 & 79.52 & 50.26 & 52.23 \\
         \hline
-        Shearing & 94.07 & 87.95 & 74.23 & 84.26 & 81.08 \\
+        Shear & 94.07 & 87.95 & 74.23 & 84.26 & 81.08 \\
         \hline
-        Shift-X & 48.51 & 32.06 & 27.36 & 42.33 & 36.88 \\
+        ShiftX & 48.51 & 32.06 & 27.36 & 42.33 & 36.88 \\
         \hline
-        Shift-Y & 30.32 & 26.19 & 26.55 & 34.04 & 29.90 \\
+        ShiftY & 30.32 & 26.19 & 26.55 & 34.04 & 29.90 \\
         \hline
@@
         \caption{Area under curve.}
-        \label{tbl:test-file-format}
+        \label{tbl:rot-file-format}
     \end{table}
-    Figure 4.1(a) through (c) shows the variation in accuracy of . A higher area under curve means 
-    KNN has a higher accuracy but, the area under curve is much lower than the convolutional neural network and the 2-layer neural network.
+
+    In table \ref{tbl:rot-file-format}, the convolutional neural network has the highest area under the curve for the rotate, shear, and shiftX property.
+This means that, on average, the accuracy of the convolutional neural network does not decrease as much as the other algorithms when tested with the various degree of transformed follow-up test cases.
+    On the other hand, KNN has the lowest area under the curve for the shade metamorphic property.
+Thus, the accuracy of the KNN program drops rapidly as the value of shade property in the test dataset increases.
+    % Figure 4.1(a) through (c) shows the variation in accuracy of . A higher area under curve means 
+    % KNN has a higher accuracy but, the area under curve is much lower than the convolutional neural network and the 2-layer neural network.
 Suggests that if you want to use metamorphic transformation to reveal flaw in an algorithm some transformations may be preferable over others.

### 2020-04-15 chapters/results/results.tex
New

@@
-In this section we will discuss our findings after implementing the machine learning algorithms and the metamorphic properties.
+In this section, we will discuss our findings after implementing the machine learning algorithms and metamorphic properties.
 
@@
 To evaluate the accuracy of our machine learning models, we first trained the models on the training data.
-The MNIST, Fashion-MNIST, and, EMNIST training datasets have 55000, 55000, and, 119800 training data respectively.
-The training data consists of the images and their corresponding labels which are used as input to the algorithm in order to generate a model.
+The MNIST, Fashion-MNIST, and EMNIST-Letter training datasets have 55000, 55000, and 119800 training data, respectively.
+The training data consists of images and their corresponding labels, which are used as input to the algorithm to generate a model.
 Once we generated the trained models, we used the test data to calculate the accuracy of the models.
-The MNIST, Fashion-MNIST, and, EMNIST testing dataset have 10000, 10000, and, 20800 testing data respectively.
-The following graphs show the accuracy of the various models on the test dataset.
+The following graphs show the accuracy of the various models on the original test dataset.
 
 \pgfplotstableread[row sep=\\,col sep=&]{
-    interval & MNIST & Fashion & EMNIST \\
+    interval & MNIST & Fashion & EMNIST-Letter \\
     CNN     & 97.01 & 83.56 & 78.20 \\
@@
 \end{center}{}
-An interesting observation from the table above is that, deep learning algorithms are not necessarily always a good choice when we are trying to maximize accuracy.
-Depending on the type of dataset, regular machine learning algorithms like KNN can also yield high accuracy and outperform deep learning algorithms.
-In the following sections we will discuss how the metamorphic transformations affected the accuracy of the models and what conclusions we can draw from it.
-\section{Effect of metamorphic transformation on the accuracy of the model}
-From literature review we saw that metamorphic testing can be a very useful technique to test the correctness of an algorithm.
+An interesting observation from the table above is that deep learning algorithms are not necessarily always the right choice when we are trying to maximize accuracy.
+Depending on the dataset, regular machine learning algorithms like KNN can also yield high accuracy and outperform deep learning algorithms in terms of accuracy.
+In the following sections, we will discuss how the metamorphic transformations affected the accuracy of the models and what conclusions we can draw from it.
+\section{Affect of metamorphic transformation on the accuracy of the models}
+From the literature review, we saw that metamorphic testing could be an instrumental technique to test the correctness of a program.
 In this thesis, we will investigate the effect of the identified metamorphic properties on the accuracy of the machine learning algorithms.
-For each metamorphic property identified in \ref{identifyingMR} we want to see how the accuracy of the models change with the varying degree of transformation.
-Our hypothesis is that small changes to the input image should not affect the prediction of the model drastically.
+For each metamorphic property identified in \ref{identifyingMR}, we want to see how the accuracy of the models changes with the varying degree of transformation.
+We hypothesize that small changes to the input image should not affect the prediction of the model drastically.
 After creating a trained model with the training dataset, we applied the metamorphic properties on the training data to generate transformed versions of the test data.
-We calculated the following metrics to evaluate the effect of the metamorphic relations on machine learning algorithm.
-To tackle the stochastic nature of training a neural network model, we ran each of the above experiment ten times and calculated average for accuracy.
-
+We calculated the following metrics to evaluate the effect of metamorphic relations on the machine learning algorithm we implemented.
+To tackle the stochastic nature of training a neural network model, we ran each of the above experiments ten times and calculated the average accuracy of the models on the transformed datasets.
 \input{figures.tex}
@@
 We then applied these metamorphic transformations to three datasets: MNIST, Fashion-MNIST, and, EMNIST.
-We also looked at how the accuracy of the datasets are affected by the transformations we identified.
-We also investigated the accuracy of transformations on individual classes in the MNIST dataset.
-We then provide recommendations for creating follow up test cases from the MNIST dataset by using the minimum and maximum values of transformations to use for these metamorphic properties.
-We also implemented five common machine learning algorithms and evaluated their robustness on these metamorphic properties.
-We make following recommendations for transforming digits in MNIST dataset.
-This paper also make the following contributions: 
-We made a methodological contribution where we have provided a set of functions to easily manipulate, and, transform image datasets for future research.
+We then implemented five machine learning algorithms and measured the accuracy of the three datasets as well as the accuracy on the transformed dataset.
+We also investigated the accuracy of transformations on individual classes in the MNIST dataset and provided recommendations for creating follow up test cases from the MNIST dataset.
+These recommendations include the minimum and maximum values of transformations that can be used for the metamorphic properties.
+We also evaluated the robustness of the machine learning algorithms on these metamorphic properties.
+From this evaluation we found that convolutional neural-networks are more robust than the other machine learning algorithms we implemented.
+\\
+This paper also makes the a methodological contribution where we have provided a set of functions on the project's github page to easily manipulate, and, transform image datasets for future research. 
+% These functions can be used as frameworks to . 
 Future researchers can utilize these functions to plugin more algorithms and metamorphic properties.
 
-Contributions:
-Methodological contribution where others can plugin more algors or MT.
-Experimental contribution:Which algo does better.
+% Contributions:
+% Methodological contribution where others can plugin more algors or MT.
+% Experimental contribution:Which algo does better.
 
-Conclusions:
+% Conclusions:
 
-Framework to apply MT in midst of distortions.
-CNN not so much better than others based on learning just from the dataset.
+% Framework to apply MT in midst of distortions.
+% CNN not so much better than others based on learning just from the dataset.

### 2020-04-17 ApplyTransformations.py
Add files via upload

@@ -1,0 +1,50 @@
+# Base code include
+from include import *
+from base import *
+
+datasetLocation = "data/Original" # Directory containing the dataset
+MT = Rotate       # Metamorphic property
+startValue = -50  # starting value of transformation
+endValue = 50     # last value of transformation
+step = 1          # step
+num_classes = 10  # Number of classes
+num_images = 1000 # Number of images to pick from each class
+outputDir = "data/+str(MT)/"   # output directory
+
+
+# Read dataset
+mnist = input_data.read_data_sets(datasetLocation, one_hot=False)
+
+# Load data to be tansformed
+xTest = mnist.test.images
+yTest = mnist.test.labels
+
+# Reshape it as image
+xTest = xTest.reshape(xTest.shape[0], 1, 28, 28)
+
+# Temporary variables
+yT = []
+xT = []
+
+# Create a set of num_images images from each class
+for n in range(num_classes):
+    train_filter = np.isin(yTest, [n])
+    x, y = xTest[train_filter], yTest[train_filter]
+    yT.append(list(y[:num_images]))
+    xT.append(x[:num_images])
+yTest = [i for l in yT for i in l]
+xT = np.array(xT)
+xTest = np.concatenate(xT)
+
+# Start the transformation
+for x in range(startValue,endValue,step):
+    print("MR: "+str(MT)+", Step: "+str(x))
+    fout = "outputDir"+str(x)
+    # Remove output directory if exists
+    if (os.path.exists(fout)):
+        os.remove(fout)
+    # Transform the data
+    x_test = Transform (xTest, yTest, MT, x)
+    # Save the data
+    with open(fout, 'wb') as f:
+        pickle.dump([x_test, yTest], f)

### 2020-04-17 base.py

@@ -1,0 +1,507 @@
+from include import *
+
+xTestBackup = []
+yTestBackup = []
+xTrainBackup = []
+yTrainBackup = []
+
+def conv_net(x_dict, n_classes, dropout, reuse, is_training):
+    
+    # Define a scope for reusing the variables
+    with tf.variable_scope('ConvNet', reuse=reuse):
+        # TF Estimator input is a dict, in case of multiple inputs
+        x = x_dict['images']
+
+        # MNIST data input is a 1-D vector of 784 features (28*28 pixels)
+        # Reshape to match picture format [Height x Width x Channel]
+        # Tensor input become 4-D: [Batch Size, Height, Width, Channel]
+        x = tf.reshape(x, shape=[-1, 28, 28, 1])
+
+        # Convolution Layer with 32 filters 
+        conv1 = tf.layers.conv2d(x, 32, 5, activation=tf.nn.relu)
+
+        # Convolution Layer with 64 filters 
+        conv2 = tf.layers.conv2d(conv1, 64, 3, activation=tf.nn.relu)
+
+        # Flatten the data to a 1-D vector for the fully connected layer
+        fc1 = tf.contrib.layers.flatten(conv2)
+
+        # Fully connected layer (in tf contrib folder for now)
+        fc1 = tf.layers.dense(fc1, 1024)
+        # Apply Dropout (if is_training is False, dropout is not applied)
+        fc1 = tf.layers.dropout(fc1, rate=dropout, training=is_training)
+
+        # Output layer, class prediction
+        out = tf.layers.dense(fc1, n_classes)
+
+    return out
+
+# Define the model function (following TF Estimator Template)
+def model_fn(features, labels, mode):
+    
+    # Build the neural network
+    # Because Dropout have different behavior at training and prediction time, we
+    # need to create 2 distinct computation graphs that still share the same weights.
+    logits_train = conv_net(features, num_classes, dropout, reuse=False, is_training=True)
+    logits_test = conv_net(features, num_classes, dropout, reuse=True, is_training=False)
+    
+    # Predictions
+    pred_classes = tf.argmax(logits_test, axis=1)
+    pred_probas = tf.nn.softmax(logits_test)
+    
+    # If prediction mode, early return
+    if mode == tf.estimator.ModeKeys.PREDICT:
[…]

### 2020-04-17 include.py

@@ -1,0 +1,82 @@
+# Import common modules
+
+from __future__ import division, print_function, absolute_import
+
+import os
+import enum
+import pickle
+import logging
+import datetime
+import shutil, sys                                                                                                     
+import numpy as np
+from sklearn import svm
+from sklearn.svm import SVC
+import tensorflow as tf
+from random import randrange                                  
+from matplotlib import pyplot
+from itertools import groupby
+from operator import itemgetter
+from keras import backend as K
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import figure
+from sklearn.metrics import accuracy_score
+from sklearn.preprocessing import StandardScaler
+from sklearn.metrics import accuracy_score
+from sklearn.naive_bayes import MultinomialNB
+from sklearn.pipeline import Pipeline
+from sklearn.model_selection import GridSearchCV
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.metrics import confusion_matrix
+from sklearn.metrics import classification_report
+from keras.preprocessing.image import ImageDataGenerator
+from tensorflow.examples.tutorials.mnist import input_data
+
+K.set_image_dim_ordering('th')
+
+# Set logging info
+logging.getLogger("tensorflow").setLevel(logging.INFO)
+
+# Metamorphic transformations name
+Shade = "Shade"
+Rotate = "Rotate"
+Shear = "Shear"
+ShiftX = "ShiftX"
+ShiftY = "ShiftY"
+ZoomX = "ZoomX"
+ZoomY = "ZoomY"
+
+# Model mode
+Test = "Test"
+Train = "Train"
+
+# Training Parameters
+learning_rate = 0.01
+num_steps = 500
+batch_size = 128
+
+# Network Parameters
+n_hidden_1 = 256 # 1st layer number of neurons
+n_hidden_2 = 256 # 2nd layer number of neurons
+num_input = 784 # MNIST data input (img shape: 28*28)
+dropout = 0.25 # Dropout, probability to drop a unit
+
+# Number of and classes
+num_classes = 10
+# Number of images to be sampled
+num_images = 1000
+
+# Machine learning algorithms
+NN = "NN"
+CNN = "CNN"
+KNN = "KNN"
+NB = "NB"
+SVM = "SVM"
+
+# Datasets
+Digit = "digit"
+Letter = "letter"
+Fashion = "fashion"
+
+# Set default algo
+Algo = CNN
+

### 2020-04-18 base.py
base

@@ -74,9 +74,6 @@ def model_fn(features, labels, mode):
     return estim_specs
 
 
-# In[ ]:
-
-
 # Define the neural network
 def neural_net(x_dict):
     # TF Estimator input is a dict, in case of multiple inputs
@@ -129,9 +126,6 @@ def nn_model_fn(features, labels, mode):
     return estim_specs
 
 
-# In[ ]:
-
-
 def reloadData(dataType):
     global xTestBackup
     global yTestBackup
@@ -148,20 +142,21 @@ def reloadData(dataType):
         xTrain[:] = xTrainBackup
         yTrain[:] = yTrainBackup
         
-
-
-# In[ ]:
+'''
+Parameters:
+    model:  The model to be trained
+    xData: (List) List of test images
+    yData: (List) List of test corresponding labels
+    shuffle:(bool) Shuffle the data before testing
+Returns a list of predictions for each data and the accuracy
+'''
 def TestModel(model, xData, yData, shuffle):
-    #input_fn = tf.estimator.inputs.numpy_input_fn(
-    #        x={'images': xData}, y= np.array(yData),
-    #        batch_size=batch_size, shuffle=shuffle)
-    #accuracy = model.evaluate(input_fn)
-
     # Prepare the input data
     input_fn = tf.estimator.inputs.numpy_input_fn(
         x={'images': xData}, shuffle=shuffle)
     # Use the model to predict the images class
     preds = list(model.predict(input_fn))
+    # calculate accuracy
     acc = 0.0
     for x in range(len(yData)):
         if (yData[x]==preds[x]):
@@ -170,10 +165,13 @@ def TestModel(model, xData, yData, shuffle):
     #return preds, accuracy['accuracy']
     return preds, acc
 
-
-# In[ ]:
-
-
+'''
+Parameters:
+    model:  The model to be trained
+    xTrain: (List) List of images
+    yTrain: (List) List of corresponding labels
+    shuffle:(bool) Shuffle the data before training
+'''
 def TrainModel(model, xTrain, yTrain, shuffle):
     input_fn = tf.estimator.inputs.numpy_input_fn(
             x={'images': xTrain}, y= np.array(yTrain),
@@ -181,160 +179,146 @@ def TrainModel(model, xTrain, yTrain, shuffle):
     # Train the Model
     model.train(input_fn, steps=num_steps)
 
+'''
+Parameters:
+    xData:  (List) List of images
+    yData:  (List) List of corresponding labels
[…]

### 2020-04-20 chapters/litReview/MRMLalgo.tex
final draft
Final

@@
-\section{Metamorphic Testing Machine Learning Programs}
+\section{Metamorphic Testing of Machine Learning Programs}\label{2.4MetamorphicTestingMachineLearning}
 
-In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test.
+In the absence of a reliable oracle to predict the correct output for arbitrary inputs, machine learning programs are often very hard to test.
 Non-testable programs can be tested in the following ways:
 \begin{itemize}
-  \item Creating multiple implementations of the same program and testing them on the same inputs and comparing the results.
-If the outputs are not the same then either of the implementations may contain an error.
+  \item Creating multiple implementations of the same program and testing them on the same inputs and if the outputs on those inputs are not the same, then an error on either of the implementations may have occurred.
 This approach is called pseudo-oracle.
-  \item In the absence of multiple oracles, metamorphic testing can be used.
+  \item If multiple implementations do not exist, metamorphic testing can be used.
 In metamorphic testing, the input is modified using a metamorphic relation such that the two sets of input will generate similar outputs.
-If similar outputs are not observed then there must be a defect.
+If similar outputs are not observed, then there must be a defect in the program.
 \end{itemize}
 
-Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations to transform inputs.
+% Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations to transform inputs.
 Murphy, Kaiser, Hu, and, Wu (2008) created a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning software.
@@
 (2009) where they identified metamorphic relations for k-nearest neighbors algorithm (k-NN) and naïve Bayes classifier (NBC).
+Performing metamorphic testing requires domain understanding and familiarity with the program to be able to come up with the metamorphic relations to transform inputs.
+Murphy, Kaiser, Hu, and Wu \cite{Murphy2008} created a taxonomy of metamorphic relations that can be used for machine learning software.
+To use metamorphic testing as a general testing method, one can apply these properties to define metamorphic relations\cite{Murphy2008}.
+They investigated two supervised algorithms MartiRank and SVM-Light, and an unsupervised system PAYL to identify basic metamorphic properties in machine learning algorithms.
+Similar work has also been done by Xie et al.
+\cite{Xie2009}, where they identified metamorphic relations for $k$-nearest neighbor algorithm ($k$-NN) and Naive Bayes classifier (NB).
+
+% MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model.
+The algorithm then performs similar operations from the model on the test data to produce a ranking list.
+% SVM-Light is an open-source implementation of SVM that also has a ranking mode.
+% PAYL is an unsupervised machine learning application which is used to perform intrusion detection.
+It's dataset simply consist of TCP/IP network payloads(a stream of bytes) without any label or classification.
 MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model.
-The algorithm then performs similar operations from the model on the test data to produce a ranking list.
-SVM-Light is an open-source implementation of SVM that also has a ranking mode.
-PAYL is an unsupervised machine learning application which is used to perform intrusion detection.
-It's dataset simply consist of TCP/IP network payloads(a stream of bytes) without any label or classification.
+The algorithm then produces a ranked list of test data by performing similar operations from the model.
+SVM-Light is an alternative implementation of SVM, which is open-source. It has a ranking mode too.
+PAYL  is used to perform intrusion detection. It is an unsupervised machine learning application. It's dataset consist of TCP/IP network payloads(a stream of bytes) with no label or classification.
 
-Based on the analysis of the MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model.
+% Based on the analysis of the MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model.
 Thus, adding a constant value to every attribute or multiplying each attribute with a positive number, should not affect the model and generate the same ranking as before.
@@
 From more study of these applications, the authors conclude that even though this not an exhaustive list of metamorphic relations, these metamorphic properties serve as a foundation for determining the relationships and transformations that can be used for conducting metamorphic testing.
+After analyzing the MartiRank algorithm, the authors realized that the relative value of the attributes is what matters, and the absolute values did not determine the model.
+Thus, arithmetic operations, like adding each element with a constant value or multiplying them with a positive number, did not affect the ranking.
+The ranking also does not change if the test data is rearranged in order.
+Thus, the metamorphic properties identified here were: addition, multiplication, and permutation.
+Multiplying the data with a negative number produces the same ranking in reverse order i.e., the algorithm will change the sorting direction but keep the order intact.
+Therefore, MartiRank also displays an invertive metamorphic property where the new output can be predicted by taking the opposite order of the original output.
+MartiRank also includes inclusive and exclusive metamorphic properties since, removing a data point or adding new data does not change the order of the original data, and the new order can be predicted very easily.
+If the datasets are transformed using the above properties, then the model would be shifted (for additive), expanded (for multiplicative), or inverted (for inverse).
+The ranking of the new dataset on the new model would still be the same because the new data points are moved similarly, and there is no change in their relative distance.
+Every test data point in an SVM algorithm is considered independently and ranked according to its distance from the hyperplane.
+Thus, it exhibits the inclusive and exclusive metamorphic properties as well.
+The authors conclude that even though this list of properties is not exhaustive, they still serve as a foundation for identifying transformations and relations that can be used for metamorphic testing.
 
@@
 
-They created a set of random input data and used the above metamorphic relationships to generate another set of inputs.
+They created a set of random input data and used the above metamorphic relations to generate another set of inputs.
 Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithms.
@@
 Chen et al.
-\cite{Chen2016} also presented a specification-based tool called METRIC for the identification of metamorphic relations.
-In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames.
-The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.
+\cite{Chen2016} presented a tool called METRIC.
+It is a specification-based tool for identifying metamorphic relations.
+In this framework, the input domain is partitioned using program specifications.
+The partitioning is done in terms of categories, choices, and complete test frames.
+He then conducted an empirical study with 19 participants suggest that METRIC is capable and effective at identifying metamorphic relations.
+Using affine transformations as metamorphic relation to test machine learning algorithms
 
@@
 Segura did an research on how to combining these properties
-\cite{Segura2016} Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively.
-In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow-up test case of each metamorphic relation as the source test case of the next metamorphic relation.
+\cite{Segura2016} The metamorphic relations can be combined such that the output from one metamorphic transformation is used as input for the next.
+This process is called Iterative Metamorphic Testing (IMT).
+IMT can be used to iteratively apply a sequence of metamorphic relations by reusing the follow-up test cases as a source for the next MR.
  \par
-New metamorphic relations can be constructed by combining several existing relations.
+% New metamorphic relations can be constructed by combining several existing relations.
 This is called Composition of Metamorphic Relations (CMR)\cite{Segura2016}.
@@
 Determining whether two metamorphic relations are composable is a manual task.
+New metamorphic relations can be created by combining multiple existing relations.
+This is called the Composition of Metamorphic Relations (CMR)\cite{Segura2016}.
+If the follow-up test data of one metamorphic relation can be used as an input source for the other, then the two metamorphic relations are considered "compositable".
+It is expected that the final relation will encapsulate the properties of the original metamorphic relations and provide the same effectiveness with fewer test executions.
+The composition can be generalized to two or more metamorphic relations and is also sensitive to the order in which they are applied.
+Deciding whether the metamorphic relations are composable is a manual task.

### 2020-04-20 chapters/litReview/finalLit.tex
Final

@@
-\section{Software testing}
+% Testing without oracles
+% - Overview (Weyuker 1982), (Barr, et al. 2015), (Elbaum and Rosenblum 2014) 
+% - Differential testing (McKeeman 1998)
+% - Dual coding/N-version programming, ... 
+% - Metamorphic testing (Chen, et al. 1998, 2018, ...), (Liu, et al. 2014), (Segura, et al. 2016)
+%   - Applications of metamorphic testing: scientific software, ...
+
+% Machine learning
+% - Overview
+% - Common algorithms
+% - Robustness of machine learning (Carlini and Wagner 2017), (Moosavi-Dezfooli, et al. 2016), (Zheng, et al. 2016)
+
+% Metamorphic testing of ML programs (Gail Kaiser lab papers)
+
+\section{Testing without oracle}
 Testing is one of the most crucial activities in the software development life cycle.
@@
 Although these recommendations do not solve the problem of lack of oracle, however, they do provide information on whether the program should be considered adequately tested or not.
-
 Due to a great deal of overhead involved, pseudo-oracles may not be practical for every situation.
@@
 
+ A third and more effective method of addressing some of the concerns about the oracle problem is the use of differential testing.
+McKeeman \cite{McKeeman98differentialtesting} first introduced the idea of differential testing, which works by testing a dataset on two or more comparable systems.
+The systems are run with mechanically generated test cases, and their output is observed.
+If one of the systems crashes or goes into an infinite loop, we have detected a potential bug in the implementation.
+Differential testing is widely used as a method to discover semantic bugs.
+It has successfully uncovered bugs in various domains like C compilers, JVM, SSL/TLS implementations, etc.
+However, since it requires two or more similar systems, it inherits some of the same problems of pseudo-oracle testing.
 Developing sophisticated oracles is another way of encountering the oracle problem.

### 2020-04-20 chapters/litReview/metamorphicTesting.tex
final draft
New
Final

@@
-\section{Metamorphic Testing}
+\section{Metamorphic testing}\label{2.2MetamorphicTesting}
 
-In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test.
+% In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test.
 It is almost impossible to generate all the possible combinations of test cases to completely test a program.
@@
 Since these test cases do not reveal any error, they are considered less important and are often not investigated further or, set aside for regression testing \cite{Zhou2004, Chen2003}.
+In the absence of a reliable oracle to indicate the correct output for random inputs, machine learning programs are often challenging to test.
+It is almost impossible to generate all the possible combinations of test cases to test a program completely.
+Thus, a lot of research is being conducted to develop test case selection strategies, which are more error-revealing.
+A test case is called error-revealing if it can detect an error in the software; otherwise, it is labeled successful.
+A successful test case is the cases for which the program successfully computes the correct output.
+These test cases are often considered less important since they do not reveal any error.
+They are often not investigated further or are set aside for regression testing \cite{Zhou2004, Chen2003}.
 
-Chen, Cheung, and Yiu \cite{Chen1998} first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem.
+% Chen, Cheung, and Yiu \cite{Chen1998} first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem.
 Metamorphic testing reuses successful test cases to generate followup test cases according to metamorphic relations.
@@
 \cite{Murphy2009}.
-To demonstrate a MR, consider a program that calculates the mean of a set of real numbers.
+Chen, Cheung, and Yiu \cite{Chen1998} first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem.
+Metamorphic testing reuses successful test cases to generate followup test cases by applying metamorphic relations to them.
+Thus, metamorphic testing is used to generate new test cases whose output can easily be predicted rather than being a test selection strategy \cite{Murphy2008}.
+Chen, Kuo, Tse, and Zhou define metamorphic relations as \enquote{A metamorphic relation(MR) is an expected relation among input and outputs of multiple executions of the target program} \cite{Chen2003,Zhou2016}.
+Consider a function $f$ which produces the output $f(x)$ on input $x$.
+A transformation function $t$ generated from the metamorphic relation of the function $f$ can be used on the input $x$ to produce the transformed input $t(x)$.
+The transformed input $t(x)$ can then be run through the function $f$ to generate the output $f(t(x))$.
+This $f(t(x))$ is then compared to the expected behaviour of $f$ on $t(x)$ from the metamorphic relation to find any error.
+\cite{Murphy2009}.
+
+% To demonstrate a MR, consider a program that calculates the mean of a set of real numbers.
 Certain transformations of the input numbers will result in the same value for mean.
@@
 Thus, multiplication and permutation are metamorphic relations for this algorithm.
+To demonstrate a metamorphic relation, consider a program that determines the mean of a set of real numbers.
+Certain transformations of the input numbers will result in the same value for the mean.
+An example of this transformation can be a permutation of the order of input.
+Since this does not change the number of elements in the input set or the value of any element, we can safely assume that the mean will remain the same.
+Another transformation could be to multiply each number in the input set with -1.
+The new mean will be the negative value of the previous mean.
+In both cases, we can easily predict the output of the newly generated test cases.
+Thus, multiplication and permutation are metamorphic relations for this algorithm.
 
@@
 Segura et al.
-\cite{Segura2016} did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing.
-They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems.
-They also found some other domains of application like financial software, optimization programs, and encryption programs.
+\cite{Segura2016} did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and the future of metamorphic testing.
+They identified the most popular use of metamorphic testing in web services, followed by computer graphics, simulation and modeling, and embedded systems.
+They also found some other domains of application like financial software, optimization programs, and encryption programs where metamorphic testing can be used.
 
-They also studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
+They also studied the properties which make metamorphic relations more effective. To select the most effective metamorphic relations to detect faults, one must have\cite{Segura2016}:
 \begin{itemize}
-	\item A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.
-	\item Metamorphic relations that make execution of the follow-up test case as different as possible from the source test case.
-	\item Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.
-	\item Formally described metamorphic relations.
-In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow-up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
+	\item \enquote{A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.}
+	\item \enquote{Metamorphic relations that make execution of the follow-up test case as different as possible from the source test case.}
+	\item \enquote{Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.}
+	\item \enquote{Formally described metamorphic relations.
+In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow-up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.}
 \end{itemize}
-Research from Chen et al.
+% Research from Chen et al.
 shows that metamorphic relations that makes the subsequent execution the most different from the initial execution have the best chances of revealing failure.
 Although, they did not explicitly define what is meant by "different" in terms of multiple execution \cite{Chen2003}.
+Research from Chen et al.
+shows that the metamorphic relations which create a very different follow-up test cases from the initial one have the best chances of revealing a failure.
+Although, they did not explicitly define what is meant by "different" in terms of multiple execution \cite{Chen2003}.
 
-The execution of a metamorphic test case is typically performed in two steps.
+% The execution of a metamorphic test case is typically performed in two steps.
 First, a follow-up test case is generated by applying a transformation to the inputs of a source test case.
@@
 Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format.
+Metamorphic testing is typically performed in two steps.
+The first step is to generate follow-up test cases by applying transformations to the source test data.
+Next, the source and follow-up test cases are tested one by one, verifying whether their outputs violate the metamorphic relation.
+It should be noted that metamorphic testing checks for the relations among several executions and not the correctness of a particular output.
+Since no manual interventions are required to predict or compare the outputs, metamorphic testing can easily be automated \cite{Segura2016}.
+Comparing the outputs of the morphed data still remains a challenge, especially if the dataset is large or not in a human-readable format.
+
 % 	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
-A number of frameworks have been developed to address this issue and automate the process of metamorphic testing.
+% A number of frameworks have been developed to address this issue and automate the process of metamorphic testing.
 Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations.
@@
 The underlying method is based on the translation of the code into an equivalent constraint logic program over finite domains.
-Other techniques like “special values” and random testing can also be used as source test cases for metamorphic testing.
+Other techniques like "special values"  and random testing can also be used as source test cases for metamorphic testing.
 Genetic algorithms have also been used for the selection of source test cases, to maximize the paths traversed in the program under test.
 But, their focus was on generation of new test cases and not on verifying that the metamorphic properties hold after execution.
+A number of frameworks have been developed to address this issue and automate the process of metamorphic testing.
+Gotlieb and Botella \cite{Gotlieb2003} introduced a framework called Automated Metamorphic Testing (AMT), which automatically generates test data after specifying metamorphic relations.
+For programs written in C language, AMT takes its source code and metamorphic relations.
+It then tries to find the test cases which will violate the metamorphic relations.
+It does so by translating the code into a finite domain constraint logic program.
+Other sources of test cases like random testing and "special values" can also be used.
+In order to maximize the program under test, genetic algorithms can be used as test case selection strategies.
+However, their focus was primarily on the generation of new test cases and not on verifying that the metamorphic properties hold after execution.
 
-Murphy et al.
+% Murphy et al.
 \cite{Murphy2009} also demonstrated how metamorphic testing can be used to assess the quality of applications without test oracles.
@@
 All a tester has to do is provide the metamorphic properties and does not require the knowledge of implementation.
+Murphy et al.
+\cite{Murphy2009} also demonstrated how metamorphic testing could be used to assess the quality of applications without test oracles.
+They proposed a system ``Automated Metamorphic System Testing'' in order to automate the metamorphic testing by considering the test program as a black box instead of a white box and checking if the metamorphic properties hold after multiple executions of the system.
+In this model, $i)$ \enquote{Metamorphic properties are specified by the tester and applied to the input}.
+$ii)$ \enquote{A transformation of the input is also generated, and the original input is fed into the application.} $iii)$ \enquote{The transformed input is fed into a separate instance of the application running in a separate sandbox.} $iv)$ \enquote{When the invocations are finished, the results are compared, and if they do not match according to the metamorphic properties, there is an error}.
+All a tester has to do is provide the metamorphic properties and does not require the knowledge of the implementation.
 
-In order to demonstrate Automated Metamorphic System Testing they created a framework called Amsterdam.
+% In order to demonstrate Automated Metamorphic System Testing they created a framework called Amsterdam.
 The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file.
@@
 Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.
+In order to demonstrate Automated Metamorphic System Testing, they created a framework called Amsterdam.
+The input to Amsterdam is the metamorphic properties defined in XML and the program under test.
+The XML contains instructions on how to: $i)$ transform the input, $ii)$ execute the program, and $iii)$ compare the outputs.
+Amsterdam then automatically performs the instructions specified in the XML file.
 
-While implementing Amsterdam framework, it became quite clear that small deviations in results calculations (like floating point operations) could cause a problem where exact results were expected.
+% While implementing Amsterdam framework, it became quite clear that small deviations in results calculations (like floating point operations) could cause a problem where exact results were expected.
 Also, many applications implements non-determinism for which outputs cannot be reliably predicted, hence, rendering metamorphic testing ineffective.
@@
 This approach also treats applications under test as black boxes and do not require detailed understanding of source code.
+While implementing Amsterdam framework, it became quite clear that small deviations in results calculations (like floating-point operations) could cause a problem where exact results were expected.
+Also, many applications implement non-determinism for which outputs cannot be reliably predicted, thus, rendering metamorphic testing ineffective.
+To address this, they proposed a technique called "Heuristic Metamorphic Testing," which is based upon the concept of "heuristic test oracles".
+Heuristic Metamorphic Testing takes the context of the program into consideration and allows for small variations of outputs in a meaningful way.
+If two outputs are close enough, they are treated as same.
+The definition of close enough depends on the context and program being tested.
+This reduces false positives and address non-determinism.
+Heuristic metamorphic testing treats the program under test as a black box, and the testers do not need the understanding of source code.
 
-Although metamorphic testing presents a lot of opportunities to expand on the existing testing processes, they also have some limitations.
+Although metamorphic testing presents many opportunities to expand on the existing testing processes, they also have some limitations.
 Murphy, et al.
@@
 \begin{itemize}
-	\item Manual transformation of large input data can be laborious and error-prone. They need special tools to transform the input.
-	\item Comparing the outputs(some of which may be very large and/or in not human-readable format) of the input data can be tedious.
-	\item Floating point calculations can also lead to imprecision even though the calculations are programmatically correct.
-	\item Coming up with the initial test-cases is also a challenge as some defects may only occur under certain inputs.
+	\item \enquote{Manual transformation of large input data can be laborious and error-prone. They need special tools to transform the input.}
+	\item \enquote{Comparing the outputs(some of which may be very large and/or in not human-readable format) of the input data can be tedious.}
+	\item \enquote{Floating point calculations can also lead to imprecision even though the calculations are programmatically correct.}
+	\item \enquote{Coming up with the initial test-cases is also a challenge as some defects may only occur under certain inputs.}
 \end{itemize}
@@
 \begin{itemize}
-	\item Lack of guidelines, with step-by-step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
-	\item Prioritization and minimization of metamorphic relations: It is worth mentioning that test case minimization is a NP-hard problem and therefore heuristic techniques should be explored.
-	\item Generation of likely metamorphic relations.
-	\item Combination of metamorphic relations.
-	\item Automated generation of best possible source test cases.
-	\item Lack of metamorphic testing tools.
+	\item \enquote{Lack of guidelines, with step-by-step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.}
+	\item \enquote{Prioritization and minimization of metamorphic relations: It is worth mentioning that test case minimization is a NP-hard problem and therefore heuristic techniques should be explored.}
+	\item \enquote{Generation of likely metamorphic relations.}
+	\item \enquote{Combination of metamorphic relations.}
+	\item \enquote{Automated generation of best possible source test cases.}
+	\item \enquote{Lack of metamorphic testing tools.}
 \end{itemize}

### 2020-04-20 chapters/litReview/mlAlgo.tex
Final

@@
-\section{Overview of Machine Learning Algorithms}
+\section{Machine learning algorithms}
+In this thesis, we will test our metamorphic relations by using them to generate follow-up test data for machine learning algorithms and checking if the metamorphic properties hold after multiple executions of the system.
+Thus, we investigated the following common machine learning algorithms.
+Just like in "Automated Metamorphic System Testing" proposed by Murphy et al.
+\cite{Murphy2009}, the algorithms we implement are also considered as a black box instead of a white box.
 \subsection{Neural network}
@@
 The neurons in both the layer compute dot product, and their function form is identical.
-Thus, it is easily possible to convert between the fully connected and Conv layer.\\
+Thus, it is easily possible to convert between the fully connected and Conv layer.
 
@@
 \subsection{Naive Bayes}
-In it's simplest form a Naive Bayes algorithm is a type of Bayesian network where all attributes are independent given the value of the class variable.
+% In it's simplest form a Naive Bayes algorithm is a type of Bayesian network where all attributes are independent given the value of the class variable.
 This property is called conditional independence.
@@
 Given a class variable $y$ and dependent feature vector $x_{1}$...$x_{n}$, Bayes theorem states that:
+In its purest form, a Naive Bayes algorithm is a type of Bayesian network.
+Naive Bayes algorithm is conditionally independent, i.e., the attributes of the data are independent, given the value of classes.
+However, the data is rarely conditionally independent in most real-world problems\cite{zhang2004optimality}.
+Even with these limitations, the Naive Bayes algorithms fare well in most real-world problems like spam filtering and document classification.
+Due to its speed, effectiveness, and simplicity, Naive Bayes is a very common learning algorithm.
+The number of training data required to train the parameters of the network is also relatively small \cite{scikit-learn}.
+\\
+Bayes theorem states that:
 \begin{center}
-    $P(y|x_{1},...,x_{n}) = \frac{P(y)P(x_{1},...,x_{n}|y)}{P(x_{1},...,x_{n})}$
+    $P(y|x_{1},...,x_{n}) = \frac{P(y)P(x_{1},...,x_{n}|y)}{P(x_{1},...,x_{n})}$\\
+    where $y$ is the class variable and $x_1,\dots,x_n$, are the dependent feature vectors.
 \end{center}
-From the conditional independence of features, and, value of a class we know that: 
 \begin{center}
+Since the features in Naive Bayes are independent: 
 $P(y \mid x_1, \dots, x_n) = \frac{P(y) \prod_{i=1}^{n} P(x_i \mid y)}
@@
 % Include the equations from https://scikit-learn.org/stable/modules/naive_bayes.html
-For a given input $P(x_{1},...,x_{n})$ is constant. Therefore 
+For a given input we know that $P(x_{1},...,x_{n})$ is constant. Therefore: 
 \begin{center}
@@
 \end{center}
-And an expected classification $\hat{y}$ can be obtained by:
+And an expected classification $\hat{y}$ can be obtained by finding the value of $y$ such that $P(y \mid x_1, \dots, x_n)$ is maximized:
 \begin{center}
@@
 \end{center}
-The main distinction between different versions of naive Bayes classifiers are the assumptions they make about the distribution of $P(x_i \mid y)$\cite{scikit-learn}.
+% The main distinction between different versions of naive Bayes classifiers are the assumptions they make about the distribution of $P(x_i \mid y)$\cite{scikit-learn}.
 The multinomial Naive Bayes suffers from a systematic problem of assigning poor weights to necessary parameters if once class has more training examples than others.
@@
 For this reason we have equal numbers of training and testing examples for each class in our experiment.
+There are multiple versions of Naive Bayes classifier, but the main distinction between them is the assumptions they make about the distribution of $P(x_i \mid y)$\cite{scikit-learn}.
+The multinomial Naive Bayes suffers from a systematic problem of assigning poor weights to necessary parameters in an unbalanced training dataset.
+If one class has fewer training examples than others, the algorithm lowers the weights for thoseclasses\cite{rennie2003tackling}.
+For this reason, we have equal numbers of training and testing examples for each class in our experiment.
 
-\subsection{k-Nearest Neighbor}
-The nearest neighbor classifier is a supervised classification technique which assigns an input sample vector (whose classification is to be predicted) to the class of it's nearest neighbors.
+\subsection{$k$-Nearest Neighbor}
+% The nearest neighbor classifier is a supervised classification technique which assigns an input sample vector (whose classification is to be predicted) to the class of it's nearest neighbors.
 The similarity between the input and the neighbors is calculated based on some distance metrics.
@@
 This could further lead to a tie and in that case an arbitrary assignment has to be made \cite{keller1985}.
+The nearest neighbor classifier is a supervised classification technique that assigns the class of an input vector (whose classification needs to be predicted) to the class of its nearest neighbors.
+The similarity between the input and the neighbors is calculated based on some distance metrics.
+This process does not require any pre-processing of the labeled set of neighbors before their use \cite{cover1967}.
+This idea can be further extended to assign the class of an input variable to the class represented by the majority of its $k$ of the nearest neighbors, where $k$ is a positive number specified by the user.
+The optimal value of $k$ depends upon the data.
+A larger value of $k$ will make the classification boundaries less distinct but suppress the effect of noise \cite{scikit-learn}.
+One problem with implementing the $k$ nearest algorithm is that in some cases, there may be a tie among classes between the $k$ neighbors.
+This problem can be solved by restricting the values of $k$.
+In binary classification problems, the values of $k$ can be restricted to odd numbers so that ties can be avoided.
+In multi-class classifications, this can be resolved by assigning the input to the class for which the sum of the distance to each neighbor is the least.
+However, even this could lead to a tie, and in that case, an arbitrary assignment has to be made \cite{keller1985}.
+
 \begin{figure}[htb!]
@@
     \includegraphics[scale=1]{files/knn.png}
-    \caption{$k$-Nearest neighbor}
+    \caption{$k$-Nearest neighbor: the black dot is assigned to triangle}
     \label{k-Nearest neighbor}
@@
 
-Given a set of n test data $(x_i, y_i),\dots(x_n, y_n)$ where $x_i$ is the feature vector and $y_i$ is the class label.
+% Given a set of n test data $(x_i, y_i),\dots(x_n, y_n)$ where $x_i$ is the feature vector and $y_i$ is the class label.
 $x_i$ is defined in a feature space $X$ with distance metric $d$.
@@
 A data point $\acute{x_n} \in (x_1, x_2, \dots x_n)$ is said to be the nearest neighbor of $x$ if:
+% \begin{center}
+% $min\ d(x_i,x) = d(\acute{x_n},x) i = 1,2,3...,n.$ 
+% \end{center}
+% $x$ is then assigned to the category of $\acute{y_n}$.
+If $k = 1$, the algorithm assigns $x$ to the category of it's nearest neighbor, ignoring the others.
+In general, $k$-NN assigns $x$ to the majority class of nearest $k$ neighbors \cite{cover1967}.
+Given a set of n classified data $(x_i, y_i),\dots(x_n, y_n)$ where $x_i$ is the feature vector and $y_i$ is their class label.
+$x_i$ is defined in a feature space $X$ with distance metric $d$.
+For a new incoming input $(x, y)$ to be classified, the goal is to assign the value of $y$ using the set of already classified data points.
+A data point $\acute{x_n} \in (x_1, x_2, \dots x_n)$ is said to be the nearest neighbor of $x$ if:
 \begin{center}
-$min\ d(x_i,x) = d(\acute{x_n},x) i = 1,2,3...,n.$ 
+$min\ d(x_i,x) = d(\acute{x_n},x); for i = 1,\dots,n.$ 
 \end{center}
@@
 If $k = 1$, the algorithm assigns $x$ to the category of it's nearest neighbor, ignoring the others.
-In general, $k$-NN assigns $x$ to the majority class of nearest $k$ neighbors \cite{cover1967}.
+If the value of $k$ is more than one then $k$-NN will assign $x$ to the majority class $k$ of its nearest neighbors \cite{cover1967}.
 
 \subsection{Support vector machine}
-A support vector machine (SVM) is a supervised machine learning classifier based on the structural risk minimization (SRM) principal.
+% A support vector machine (SVM) is a supervised machine learning classifier based on the structural risk minimization (SRM) principal.
 It solves learning problems by making decision-based rules and minimizing error for independent samples \cite{svm2008}.
@@
 It creates these nonlinear boundaries by mapping input vectors to a higher dimensional feature space \cite{SAMANTA2003657,Nakajima2016}.
+A support vector machine (SVM) is another type of supervised machine learning classifier, which is based on the principle of structural risk minimization (SRM). 
+It works by making decision-based rules and minimizing error for independent samples \cite{svm2008}.
+It has gained rapid popularity in the fields of machine learning, pattern recognition, and computer vision because of high accuracy and good generalization capability.
+SVM solves the learning problem by fitting a hyperplane, also known as decision boundary, between elements of two classes that allows it to make predictions from one or more feature vectors.
+The hyperplanes are oriented such that the distance between the closest data points (also called support vectors) in the two classes is maximum.
+Support vectors are the input data $x_i$ for which $|y_i|(wx_i^T + b)=1$.
+It creates these nonlinear boundaries by mapping input vectors to a higher dimensional feature space \cite{SAMANTA2003657,Nakajima2016}.
+
 \begin{figure}[htb!]
@@
 \end{center}
-where $w$ is the weight vector, and $b$ is the bias.
-$w$ and $b$ are selected such that the following condition holds for all the elements in the training set.
+Where $b$ is the bias, and $w$ is the weight vector. The following conditions should hold for all the elements in the training set:
 \begin{center}
@@
 \end{center}
-During the training step, the model tries to place the hyperplace such that it maximizes the distance between the support vectors.
+During the training step, the model tries to place the hyperplane such that it maximizes the distance between the support vectors.
 This is done by finding the optimal values for $w$ and $b$ such the value of $1/(\parallel w\parallel)^2$ is maximum.
@@
 $ii)$ Is it y?
-$iii)$ Is it z?\cite{noble2006support}
-An alternative way is to make use of kernel methods which enables us to model higher dimensional, non-linear models.
+$iii)$ Is it z?\cite{noble2006support}.
+An alternative way is to make use of kernel methods, which can represent and transform higher dimensional, non-linear models easily. 
+% A kernel function helps us to do faster calculations which would otherwise require higher dimensional computation.
+It adds additional dimension to the input data and makes it a linear problem in a higher dimensional feature space.
 A kernel function helps us to do faster calculations which would otherwise require higher dimensional computation. 
-It adds additional dimension to the input data and makes it a linear problem in a higher dimensional feature space.
+It transforms the input data into a higher dimensional linear problem by adding additional dimensions, which can be easily solved in higher dimensional feature space.
 A kernel function is defined as:
 \begin{center}
-  $K (x, y)=<f(x), f(y)>$ where,  
+  $K (x, y)=<f(x), f(y)>$   
 \end{center}
-$K$ is the kernel function.\\
-$x, y$ are $m$ dimensional inputs.\\
-$f$ maps the inputs from $m$ dimensional feature space to $n$ dimensional feature space.\\
+where $K$ is the kernel function, $x, y$ are $m$ dimensional inputs. The function $f$ maps the inputs from $m$ dimensional feature space to $n$ dimensional feature space and
 $<x, y>$ denotes a dot product.\\
-Kernels can heavily affect the performance of a SVM but unfortunately there is no set way of choosing a kernel.
+% Kernels can heavily affect the performance of a SVM but unfortunately there is no set way of choosing a kernel.
 We can start with a simpler kernel and then experiment with a number of standard kernels to produce best predictions by using cross-validation \cite{huang2018applications}.
+Kernels can profoundly affect the performance of an SVM.
+Unfortunately, there is no fixed strategy to pick a kernel.
+The best strategy to select a kernel is by starting with a simpler kernel and then experiment with standard kernels, and select the one which produces the best predictions \cite{huang2018applications}.

### 2020-04-20 chapters/methodology/algorithms.tex
Final

--- 2020-04-15 chapters/methodology/collection.tex
@@
-In this chapter, we will discuss the tools we used to perform our experiment. 
-We used Python as the programming language to implement our code.
-We chose Python because of its popularity and easy syntax.
-There are also plenty of Python libraries like Tensorflow, Keras, and scikit-learn available to easily implement machine learning, deep-learning, natural language processing algorithms.
-Along with Python as the programming language, we also used the following programs, tools, and datasets to perform our experiment.
- \section{Tools}
-\subsection{HCC}
-Due to the high computation requirements for some dataset we needed a faster and reliable hardware.
-The Holland Computing Center (HCC) claim to be the fastest resource in the state of Nebraska.
-HCC provides these services to researcher and students associated with any campus of the University of Nebraska system.
-Some shared services are available for free and dedicated services can be obtained for a modest price.
-We used their servers to run our Jupyter notebooks.
-
-\subsection{Jupyter Notebook}
-Jupyter notebook is part of project Jupyter, which aims at providing an interactive interface for development across multiple platforms and programming languages.
-Jupyter's web interface supports data cleaning, data transformation, and visualization, numerical operations, etc.
-It allows us to create live code snippets and equations and shows results of inline computation right next to the code in the form of rich media (SVG, LaTeX, etc.).
-It combines two components:
-\begin{itemize}
-  \item \textbf{A web application}: a web-based interactive tool to write code, markdown, etc. It also displays the rich media output.
-  \item \textbf{Notebook documents}: a representation of all the content written and displayed using the web application.
-\end{itemize}
-Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy.
-In this project, we wrote the codes in python notebook, which can be accessed from our GitHub repository.
-
-\subsection{Tensorflow}
-% TensorFlow is an end-to-end open source platform for machine learning.
-It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications
-TensorFlow\textsuperscript{TM} is an open-source software library developed within Google’s AI organization by the Google Brain team with strong support for machine learning and deep learning.
-Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices.
-Several well-known companies like Uber, Google, AMD, etc.
-use Tensorflow for high-performance numerical computation and machine learning tasks.
-While TensorFlow is capable of handling a wide range of tasks, it is designed mainly for deep neural network models.
-Tensorflow provides API for loading, manipulating, and using the MNIST dataset identified in section \ref{dataset}.
-We also used TensorFlow to implement neural network and convolutional neural network defined insection \ref{Algorithms}
-
-% TensorFlow\textsuperscript{TM} is an open source software library developed within Google's AI organization by the Google Brain team with a strong support for machine learning and deep learning.
-Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices.
-It is being used at a number of well known companies like Uber, Google, AMD, etc.
-for high performance numerical computation and machine learning.
-While TensorFlow is capable of handling a wide range of tasks, it is mainly designed for deep neural network models.
-It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}.
-Tensorflow provides api for loading the MNIST dataset identified in section \ref{dataset}.
-We also used tensorflow to implement neural network and convolutional neural network defined in section \ref{Algorithms}
-
-\subsection{Scikit-learn}
-Scikit-learn is a Python module for machine learning built on top of SciPy and is distributed under the 3-Clause BSD license.
-It provides APIs to a range of supervised and unsupervised learning algorithms via a consistent interface in Python.
-
-\section{Algorithms}\label{Algorithms}
+\section{Implementation of machine learning algorithms}\label{Algorithms}
 In order to answer research questions two and three, we implemented some popular machine learning algorithms to provide quantitative data on the effect of metamorphic relations on the accuracy of datasets and their classes.
@@
 The images are then fed into the network as input.
+We used tensorflow to implement the convolutional network.
 The first convolution layer has 32 filters with a kernel size of five.
@@
 \subsection{Neural network}
+We implemented a neural network with seven hidden layers using TensorFlow.
+The input image is a one-dimensional vector of 784 features (28x28 pixels), where each pixel value lies between $0.0$ and $1.0$.
+The pixel value represents $0.0$ white, and the value $1.0$ represents black, and all the values in between represent varying degrees of grey.
+Each hidden layer is made up of 256 neurons and is fully connected to its previous layer.
+All the neurons in a layer are independent, and none of them share a connection with each other.
+The structure of the network was determined empirically by testing multiple numbers of layers and picking a network that produced the best accuracy.
+The output layer is a fully-connected layer with one neuron for each class.
+The output layer produces a value between 0 and 1 for each class.
+A value of less than 0.5 indicates that the input image does not belong to that class, and a value greater than 0.5 indicates that the image belongs to that class.
+The image is assigned to the class of the neuron with maximum value.
 
- Hidden fully connected layer with 256 neurons.
+%  Hidden fully connected layer with 256 neurons.
 Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections.
@@
 Scikit's $sklearn.neighbors$ module provides the functionality to implement unsupervised and supervised neighbors-based learning methods.
- The KNeighborsClassifier function from the $sklearn.neighbors$ module implements learning based on the $k$ nearest neighbors of each query point, where $k$ is an integer value specified by the user.
+$k$ is an integer provided by the user.
+ The KNeighborsClassifier function from the $sklearn.neighbors$ module implements learning based on the $k$ nearest neighbors of each query point.
 The k-neighbors classification in KNeighborsClassifier is the most commonly used technique.
 Since the optimal value $k$ is dependent on data, we ran the experiment with multiple values of $k$ and found that the $k$=3 produces the best accuracy.
-In general, a larger $k$ suppresses the effects of noise but makes the classification boundaries less distinct.
+In general, a larger $k$ makes the classification boundaries less distinct but suppresses the effects of noise.
  We used Euclidean distance as the distance metric and assigned equal weights to all the query points.
@@
 
-\section{Datasets}\label{dataset}
-In order to create metamorphic properties that can be used by multiple image datasets and are not data-dependent, we tested our metamorphic properties on three different datasets.
-We choose the following three datasets, but the experiment can be easily replicated on other datasets.
-
-\subsection{MNIST Dataset}
-The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST} has a training set of 55,000 examples and a test set of 10,000 examples.
-It is a subset of a larger set available from NIST.
-The digits have been size-normalized and centered in a fixed-size image.
-It is an excellent database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting.
-The MNIST database was constructed from NIST's Special Database 3 and Special Database 1, which contain binary images of handwritten digits.
-The original black and white (bi-level) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio.
-The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.
-
-\subsection{EMNIST Dataset}
-The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
-and converted to a 28x28 pixel image format. The EMNIST dataset structure directly matches the MNIST dataset.
-
-\subsubsection{Dataset Summary}
-There are six different splits provided in this dataset. A short summary of the dataset is provided below:
-\begin{itemize}
-  \item EMNIST ByClass: 814,255 characters. 62 unbalanced classes.
-  \item EMNIST ByMerge: 814,255 characters. 47 unbalanced classes.
-  \item EMNIST Balanced:  131,600 characters. 47 balanced classes.
-  \item EMNIST Letters: 145,600 characters. 26 balanced classes.
-  \item EMNIST Digits: 280,000 characters. 10 balanced classes.
-  \item EMNIST MNIST: 65,000 characters. 10 balanced classes.
-\end{itemize}
-The full complement of the NIST Special Database 19 is available in the ByClass and ByMerge splits. The EMNIST Balanced dataset contains a set of characters with an equal number of samples per class.
-The EMNIST Letters dataset merges a balanced set of the uppercase and lowercase letters into a single 26-class task.
-The EMNIST Digits and EMNIST MNIST dataset provide balanced handwritten digit datasets directly compatible with the original MNIST dataset.
-
-\begin{figure}[htb!]
-        \centering
-        \begin{subfigure}[b]{\textwidth}
-            \centering
-            \includegraphics[width=\linewidth]{images/digit.png}
-            \caption{Sample EMNIST-MNIST dataset}
-            \label{fig:EMNIST MNIST dataset}
-        \end{subfigure}%
-        \label{fig:Rotate-misclassifications}
-        \begin{subfigure}[b]{\textwidth}
-            \centering
-            \includegraphics[width=\linewidth]{images/letter.png}
-            \caption{Sample EMNIST-Letter dataset}
-            \label{fig:EMNIST MNIST dataset}
-        \end{subfigure}%
-        \label{fig:Rotate-misclassifications}
-    \end{figure}
-    \FloatBarrier
-
-\subsection{Fashion MNIST Dataset}
-Fashion-MNIST is a dataset of Zalando's article images-consisting of a training set of 55,000 examples and a test set of 10,000 examples.
-Each example is a 28x28 grayscale image, associated with a label from 10 classes.
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|}
-\hline
-\textbf{Label} & \textbf{Description} \\ \hline
-0  &   T-shirt/top \\ \hline
-1  &   Trouser \\ \hline
-2   &	Pullover \\ \hline
-3   &	Dress \\ \hline
-4   &	Coat \\ \hline
-5   &	Sandal \\ \hline
-6   &	Shirt \\ \hline
-7   &	Sneaker \\ \hline
-8   &	Bag \\ \hline
-9   &	Ankle boot \\ \hline
-\end{tabular}
-\caption{Data file format.}
-\label{tbl:training-file-format}
-\end{table}
-
-\begin{figure}[htb!]
-        \centering
-        \begin{subfigure}[b]{\textwidth}
-            \centering
-            \includegraphics[width=\linewidth]{images/fashion.png}
-            \caption{Sample EMNIST-MNIST dataset}
-            \label{fig:EMNIST MNIST dataset}
-        \end{subfigure}%
-        \label{fig:Rotate-misclassifications}
-    \end{figure}
-    \FloatBarrier
-
-\subsection{Format of Dataset}
-The data is stored in a very simple file format designed for storing vectors and multidimensional matrices.
-All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors.
-There are four files:
-\begin{itemize}
-  \item train-images-idx3-ubyte: training set images
-  \item train-labels-idx1-ubyte: training set labels
-  \item t10k-images-idx3-ubyte:  test set images
-  \item t10k-labels-idx1-ubyte:  test set labels
-\end{itemize}
-The format of training and test files are described in the following table.
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
-\hline
-0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
-\hline
-0004  &   32 bit integer & 60000       &     number of items \\
-\hline
-0008  &   unsigned byte  & ??          &     label \\
-\hline
-0009  &   unsigned byte  & ??          &     label \\
-\hline
-\multicolumn{4}{|c|}{\textbf{........}} \\
-\hline
-xxxx  &   unsigned byte  & ??          &     label \\
-\hline
-\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
-\hline
-\end{tabular}
-\caption{Training data file format.}
-\label{tbl:training-file-format}
-\end{table}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
-\hline
-0000  &   32 bit integer & 0x00000803(2051) & magic number (MSB first) \\
-\hline
-0004  &   32 bit integer & 60000       &     number of images \\
-\hline
-0008  &   unsigned byte  & 28          &     number of rows  \\
-\hline
-0012  &   unsigned byte  & 28          &     number of columns \\
-\hline
-0016  &   unsigned byte  & ??          &     pixel \\
-\hline
-0017  &   unsigned byte  & ??          &     pixel \\
-\hline
-\multicolumn{4}{|c|}{\textbf{........}} \\
-\hline
-xxxx  &   unsigned byte  & ??          &     pixel \\
-\hline
-\multicolumn{4}{|c|}{\textbf{
-\shortstack{Pixels are organized row-wise. Pixel values are 0 to 255. \\ 0 means background (white), 255 means foreground (black).}}} \\
-\hline
-\end{tabular}
-\caption{Test data file format.}
-\label{tbl:test-file-format}
-\end{table}
-
-% \subsection{Docker}
-% For replication of results. Image can be downloaded from dockerhub. Attached volume for persisting data.
+After generating the follow-up test cases and implementing the machine-learning algorithms, we tested the trained model on the five follow-up test cases.
+The rotate, shade, and shear transformations each have 100 versions of the transformed original dataset.
+The shiftX and shiftY transformations each have 56 versions of original test data as follow-up test data.
+Each of the 412 follow-up test datasets was then tested on the trained models, and their accuracy was calculated.
+We will discuss our findings in the next section.

### 2020-04-20 chapters/methodology/dataset.tex
Final

\section{Datasets}\label{dataset}
In order to create metamorphic properties that can be used by multiple image datasets and are not data-dependent, we tested our metamorphic properties on three different datasets. We choose the following three datasets, but the experiment can be easily replicated on other image datasets.

\subsection{MNIST Dataset}
% The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST} has a training set of 55,000 examples and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is an excellent database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1, which contain binary images of handwritten digits. The original black and white (bi-level) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.
Yann LeCun maintains one of the most popular databases for machine learning algorithms. The MNIST database is a collection of $55,000$ training images and $10,000$ test images \cite{MNIST}.  The MNIST dataset is a subset of a larger NIST dataset - Special Database 3 and Special Database 1. The images in the dataset are handwritten digits samples between $[0,9]$, which are size-normalized and centered in a 28x28 pixel image. The original images were size normalized into a 20x20 pixel box while preserving their aspect ratio. The images were converted to 28x28 pixel by first calculating their center of mass and then translating the images such that the center of mass is on the center of the 28x28 field. The following figuire shows a sample set of MNIST data.
\begin{figure}[htb!]
\centering
    \centering
    \includegraphics[width=\linewidth]{images/digit.png}
    \caption{Sample MNIST dataset}
    \label{fig:EMNIST MNIST dataset}
\end{figure}

\subsection{EMNIST Dataset}
% The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
% and converted to a 28x28 pixel image format. 
The EMNIST dataset has the same shape as MNIST dataset. They are 28x28 pixels of handwritten characters that are derived from the "NIST Special Database 19". There are six different splits provided in this dataset. The splits are organized by class, by balance, by type, etc. Some splits are unbalanced and contain an uneven number of examples for classes. The EMNIST-Digit and EMNIST-MNIST datasets are directly compatible with the original MNIST dataset. For this study, we choose "EMNIST Letters" split, which has $145,600$ characters in 26 balanced classes where each class has the same number of samples. The characters are in uppercase and lowercase, which have have been merged into one 26-class set.
The figure \ref{fig:emnist-letter} shows a sample image of the EMNIST-Letter dataset.

\begin{figure}[htb!]
        \centering

            \centering
            \includegraphics[width=\linewidth]{images/letter.png}
            \caption{Sample EMNIST-Letter dataset}
            \label{fig:EMNIST MNIST dataset}
        \label{fig:emnist-letter}
    \end{figure}
    \FloatBarrier

\subsection{Fashion MNIST Dataset}
Zalando's article images consist of a set of $55,000$ training examples and $10,000$ test examples. The dataset is commonly referred to as the Fashion-MNIST dataset. Every data point in the dataset is a grayscale image of size 28x28. The labels in the dataset have a value between $[0, 9]$. Table \ref{tbl:MNIST-Fashion} shows a sample of the dataset.

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Label} & \textbf{Description} \\ \hline
0  &   T-shirt/top \\ \hline
1  &   Trouser \\ \hline
2   &	Pullover \\ \hline
3   &	Dress \\ \hline
4   &	Coat \\ \hline
5   &	Sandal \\ \hline
6   &	Shirt \\ \hline
7   &	Sneaker \\ \hline
8   &	Bag \\ \hline
9   &	Ankle boot \\ \hline
\end{tabular}
\caption{Data file format.}
\label{tbl:MNIST-Fashion}
\end{table}

\begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/fashion.png}
            \caption{Sample Fashion-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Format of Dataset}
Each dataset we selected has the same file structure. The data is stored across four files. The "train-images-idx3-ubyte" and "train-labels-idx1-ubyte" files contain the training images and labels, respectively. The "t10k-images-idx3-ubyte" and "t10k-labels-idx1-ubyte" files contain the test images and labels. The labels for the MNIST and Fashion-MNIST are between $[0, 9]$, while the labels for EMNIST-LETTER are between $[1, 26]$. The integers in the files are stored in MSB first format (high endian).

The format of training and test files are described in the following table.
\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of items \\
\hline
0008  &   unsigned byte  & ??          &     label \\
\hline
0009  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
\hline
\end{tabular}
\caption{Training data file format.}
\label{tbl:training-file-format}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000803(2051) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of images \\
\hline
0008  &   unsigned byte  & 28          &     number of rows  \\
\hline
0012  &   unsigned byte  & 28          &     number of columns \\
\hline
0016  &   unsigned byte  & ??          &     pixel \\
\hline
0017  &   unsigned byte  & ??          &     pixel \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     pixel \\
\hline
\multicolumn{4}{|c|}{\textbf{
\shortstack{Pixels are organized row-wise. Pixel values are 0 to 255. \\ 0 means background (white), 255 means foreground (black).}}} \\
\hline
\end{tabular}
\caption{Test data file format.}
\label{tbl:test-file-format}
\end{table}

### 2020-04-20 chapters/methodology/properties.tex
Final

@@
 The section \ref{identifyingMR} also answers our first research question.
-
-After generating the follow-up test cases and implementing the machine-learning algorithms, we tested the trained model on the five follow-up test cases.
-The rotate, shade, and shear properties have 100 versions of the transformed original dataset each.
-The shiftX and shiftY properties have 56 versions of original test data as follow-up test data.
-Each of the 412 follow-up test datasets was then tested on the trained models, and their accuracy was calculated.
-We will discuss our findings in the next section.

### 2020-04-20 chapters/methodology/tools.tex
Final

--- 2020-04-15 chapters/methodology/collection.tex
@@
 It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications
-TensorFlow\textsuperscript{TM} is an open-source software library developed within Google’s AI organization by the Google Brain team with strong support for machine learning and deep learning.
-Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices.
-Several well-known companies like Uber, Google, AMD, etc.
-use Tensorflow for high-performance numerical computation and machine learning tasks.
-While TensorFlow is capable of handling a wide range of tasks, it is designed mainly for deep neural network models.
-Tensorflow provides API for loading, manipulating, and using the MNIST dataset identified in section \ref{dataset}.
-We also used TensorFlow to implement neural network and convolutional neural network defined insection \ref{Algorithms}
+TensorFlow was developed as an open-source library at Google by their Brain team.
+It is used by many well-known companies like AMD, Uber, etc to develop machine learning models and perform complex numerical computations.
+Although TensorFlow can do complex numerical computations, it was designed mainly for developing deep learning models.
+It provides APIs for loading, manipulating, and using the datasets along with generating and using machine learning models.
+We used TensorFlow to implement the seven-layer neural network and convolutional neural network defined in section \ref{Algorithms}.
 
@@
 
-\section{Algorithms}\label{Algorithms}
-In order to answer research questions two and three, we implemented some popular machine learning algorithms to provide quantitative data on the effect of metamorphic relations on the accuracy of datasets and their classes.
-We used TensorFlow and scikit-learn to implement the following machine learning algorithms.
-
-\subsection{Convolutional neural network}
-The images in the MNIST dataset is a one-dimensional vector of 784 features (28x28 pixels).
-We first reshape the images to match the picture format height x width x channel.
-Each image in the MNIST dataset is now a single-channel of 28x28x1 size.
-The images are then fed into the network as input.
-The first convolution layer has 32 filters with a kernel size of five.
-The activation function we used is the ReLU function, and the output from this layer is fed into a pooling layer.
-The data goes through another iteration of convolution and pooling before being flattened and sent to the fully connected layer.
-The output layer gives us a number that corresponds to the class of the image it is assigned.
-
-\subsection{Neural network}
-
- Hidden fully connected layer with 256 neurons.
-Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections.
-If the image is a 64 by 64 greyscale image, then we'd have 64x64=4,096 input neurons, with the intensities scaled appropriately between 0 and 1.
-The output layer will contain just a single neuron, with output values of less than 0.5 indicating "input image is not a 9", and values greater than 0.5 indicating "input image is a 9 ".
-The input pixels are greyscale, with a value of 0.0 representing white, a value of 1.0 representing black, and in between values representing gradually darkening shades of grey.
-The second layer of the network is a hidden layer.
-
-\subsection{Naive Bayes}
-We used scikit-learn to implement the Naive Bayes algorithm. We transformed the images into a one-dimensional vector of 784 features. 
-Using the $sklearn.naive\_bayes.MultinomialNB()$ function we created a Naive Bayes classifier, which is then fitted using the $fit()$ function, which takes the images and labels as input and fits the classifier according to the images and labels.
-The resulting classifier is then used to predict the labels of test data.
-
-\subsection{$k$-Nearest Neighbor}
- We used scikit-learn to implement our $k$-nearest neighbor algorithm.
-Scikit's $sklearn.neighbors$ module provides the functionality to implement unsupervised and supervised neighbors-based learning methods.
- The KNeighborsClassifier function from the $sklearn.neighbors$ module implements learning based on the $k$ nearest neighbors of each query point, where $k$ is an integer value specified by the user.
-The k-neighbors classification in KNeighborsClassifier is the most commonly used technique.
-Since the optimal value $k$ is dependent on data, we ran the experiment with multiple values of $k$ and found that the $k$=3 produces the best accuracy.
-In general, a larger $k$ suppresses the effects of noise but makes the classification boundaries less distinct.
- We used Euclidean distance as the distance metric and assigned equal weights to all the query points.
-In some cases, it might be better to assign weights based on the distance.
-The close query point contributes more to the fit, and the ones far contribute less.
-For our case, the uniform weight with a simple majority vote of the nearest neighbors worked just fine.
-
-\subsection{SVM}
-We also implemented the support vector machine algorithm using scikit-learn.
-The $sklearn.svm.SVC$ class is based on libsvm and is capable of performing multi-class classification.
-Internally, they use libsvm and liblinear to handle all computations.
-These libraries are wrapped using C and Cython.
-It supports multi-class classification on a one-vs-one scheme.
-In this scheme, a classifier is created for each pair of classes and during prediction, the class which receives most votes is assigned to the data point.
-In the event of a tie, we selected the class with the highest total confidence calculated by summing over the pair-wise classification confidence.
-As the other classifiers, $skleran.SVM$ also takes as input two arrays: an array of training samples and another array of class labels.
-The training samples and labels are passed to $fit$ function, which fits the SVM model according to the data.
-The resulting model is then used to predict the labels of test data.
-
-\section{Datasets}\label{dataset}
-In order to create metamorphic properties that can be used by multiple image datasets and are not data-dependent, we tested our metamorphic properties on three different datasets.
-We choose the following three datasets, but the experiment can be easily replicated on other datasets.
-
-\subsection{MNIST Dataset}
-The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST} has a training set of 55,000 examples and a test set of 10,000 examples.
-It is a subset of a larger set available from NIST.
-The digits have been size-normalized and centered in a fixed-size image.
-It is an excellent database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting.
-The MNIST database was constructed from NIST's Special Database 3 and Special Database 1, which contain binary images of handwritten digits.
-The original black and white (bi-level) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio.
-The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.
-
-\subsection{EMNIST Dataset}
-The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
-and converted to a 28x28 pixel image format. The EMNIST dataset structure directly matches the MNIST dataset.
-
-\subsubsection{Dataset Summary}
-There are six different splits provided in this dataset. A short summary of the dataset is provided below:
-\begin{itemize}
-  \item EMNIST ByClass: 814,255 characters. 62 unbalanced classes.
-  \item EMNIST ByMerge: 814,255 characters. 47 unbalanced classes.
-  \item EMNIST Balanced:  131,600 characters. 47 balanced classes.
-  \item EMNIST Letters: 145,600 characters. 26 balanced classes.
-  \item EMNIST Digits: 280,000 characters. 10 balanced classes.
-  \item EMNIST MNIST: 65,000 characters. 10 balanced classes.
-\end{itemize}
-The full complement of the NIST Special Database 19 is available in the ByClass and ByMerge splits. The EMNIST Balanced dataset contains a set of characters with an equal number of samples per class.
-The EMNIST Letters dataset merges a balanced set of the uppercase and lowercase letters into a single 26-class task.
-The EMNIST Digits and EMNIST MNIST dataset provide balanced handwritten digit datasets directly compatible with the original MNIST dataset.
-
-\begin{figure}[htb!]
-        \centering
-        \begin{subfigure}[b]{\textwidth}
-            \centering
-            \includegraphics[width=\linewidth]{images/digit.png}
-            \caption{Sample EMNIST-MNIST dataset}
-            \label{fig:EMNIST MNIST dataset}
-        \end{subfigure}%
-        \label{fig:Rotate-misclassifications}
-        \begin{subfigure}[b]{\textwidth}
-            \centering
-            \includegraphics[width=\linewidth]{images/letter.png}
-            \caption{Sample EMNIST-Letter dataset}
-            \label{fig:EMNIST MNIST dataset}
-        \end{subfigure}%
-        \label{fig:Rotate-misclassifications}
-    \end{figure}
-    \FloatBarrier
-
-\subsection{Fashion MNIST Dataset}
-Fashion-MNIST is a dataset of Zalando's article images-consisting of a training set of 55,000 examples and a test set of 10,000 examples.
-Each example is a 28x28 grayscale image, associated with a label from 10 classes.
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|}
-\hline
-\textbf{Label} & \textbf{Description} \\ \hline
-0  &   T-shirt/top \\ \hline
-1  &   Trouser \\ \hline
-2   &	Pullover \\ \hline
-3   &	Dress \\ \hline
-4   &	Coat \\ \hline
-5   &	Sandal \\ \hline
-6   &	Shirt \\ \hline
-7   &	Sneaker \\ \hline
-8   &	Bag \\ \hline
-9   &	Ankle boot \\ \hline
-\end{tabular}
-\caption{Data file format.}
-\label{tbl:training-file-format}
-\end{table}
-
-\begin{figure}[htb!]
-        \centering
-        \begin{subfigure}[b]{\textwidth}
-            \centering
-            \includegraphics[width=\linewidth]{images/fashion.png}
-            \caption{Sample EMNIST-MNIST dataset}
-            \label{fig:EMNIST MNIST dataset}
-        \end{subfigure}%
-        \label{fig:Rotate-misclassifications}
-    \end{figure}
-    \FloatBarrier
-
-\subsection{Format of Dataset}
-The data is stored in a very simple file format designed for storing vectors and multidimensional matrices.
-All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors.
-There are four files:
-\begin{itemize}
-  \item train-images-idx3-ubyte: training set images
-  \item train-labels-idx1-ubyte: training set labels
-  \item t10k-images-idx3-ubyte:  test set images
-  \item t10k-labels-idx1-ubyte:  test set labels
-\end{itemize}
-The format of training and test files are described in the following table.
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
-\hline
-0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
-\hline
-0004  &   32 bit integer & 60000       &     number of items \\
-\hline
-0008  &   unsigned byte  & ??          &     label \\
-\hline
-0009  &   unsigned byte  & ??          &     label \\
-\hline
-\multicolumn{4}{|c|}{\textbf{........}} \\
-\hline
-xxxx  &   unsigned byte  & ??          &     label \\
-\hline
-\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
-\hline
-\end{tabular}
-\caption{Training data file format.}
-\label{tbl:training-file-format}
-\end{table}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
-\hline
-0000  &   32 bit integer & 0x00000803(2051) & magic number (MSB first) \\
-\hline
-0004  &   32 bit integer & 60000       &     number of images \\
-\hline
-0008  &   unsigned byte  & 28          &     number of rows  \\
-\hline
-0012  &   unsigned byte  & 28          &     number of columns \\
-\hline
-0016  &   unsigned byte  & ??          &     pixel \\
-\hline
-0017  &   unsigned byte  & ??          &     pixel \\
-\hline
-\multicolumn{4}{|c|}{\textbf{........}} \\
-\hline
-xxxx  &   unsigned byte  & ??          &     pixel \\
-\hline
-\multicolumn{4}{|c|}{\textbf{
-\shortstack{Pixels are organized row-wise. Pixel values are 0 to 255. \\ 0 means background (white), 255 means foreground (black).}}} \\
-\hline
-\end{tabular}
-\caption{Test data file format.}
-\label{tbl:test-file-format}
-\end{table}
-
 % \subsection{Docker}

### 2020-04-20 chapters/results/discussion.tex
Final

\section{Summary of Contributions}
In this paper we identified five metamorphic properties "Rotation", "Shading", "Shearing", "Shifting the image along $X$-axis", and, "Shifting the image along $Y$-axis" that can be used to transform image datasets to create follow-up test cases.  We applied these transformations on three datasets and calculated their accuracy on five common machine learning algorithms. We found that the individual classes are affected differently depending on the transformation. Hence, we provided recommendations to select the parameters of our properties such that the follow-up test cases are similar to the original dataset. 
We also evaluated the robustness of the machine learning algorithms on the follow-up test data. From this evaluation, we found convolutional neural-networks to be more robust on the MNIST dataset than the other machine learning algorithms we implemented. However, this trend does not carry over to the other datasets. For both the Fashion-MNIST and EMNIST-Letter datasets, the Naive Bayes algorithm showed more robustness. We also found that the first three properties: rotate, shade, and shear, are not as sensitive as the shiftX and shiftY properties.
% These functions can be used as frameworks to . 
% Future researchers can utilize these functions to plugin more algorithms and metamorphic properties.
During the study, we faced the challenge of defining the concept of "similarity" of test cases. There is no universally agreed-upon definition of similarity, and its definition depends upon the context of use. For this study, the follow-up datasets that produced accuracy within $90\%$ of the original dataset are considered similar to the original dataset. Future researchers can change the definition of "similarity" to produce different results.

% We also investigated the robustness of the five machine learning algorithms on metamorphic transformations.

This research also provides a methodological contribution where we have generated a framework, which can be easily extended to add more metamorphic properties, datasets, and algorithms for future research. All the functions, datasets, and algorithms used in this project are hosted on the project's Github page \cite{abhishek2020}. Further researches can be done to combine these transformations to create even more complex transformations by using the output of one transformation as input to others.
% Contributions:
% Methodological contribution where others can plugin more algors or MT.
% Experimental contribution:Which algo does better.

\section{Conclusion}
In this study, we set to investigate three main questions: can we identify new metamorphic properties to be used with image datasets? Do these properties affect all the classes equally? And what range of transformation can be applied, such that the follow-up test data remains similar to original data? We answered the first question by naming five affine transformations, which can be used as metamorphic properties. We also implemented them on three datasets to generate new test cases. To answer the second research question, we implemented five machine learning algorithms and tested the accuracy of the new test cases for each class. We found that the classes had different areas under curve for metamorphic transformations; thus, they are affected differently by the different metamorphic transformations. 
We also made recommendations to select parameters for our metamorphic transformations such that the resulting follow-up test cases are similar to the original dataset. These recommendations can be used as a test case generation strategy to generate additional transformed test data for MNIST, Fashion-MNIST, and EMNIST-Letter dataset. Future researches should consider using our metamorphic transformations and recommendations to generate new test cases for machine learning algorithms.

### 2020-04-20 chapters/results/figures.tex
Final

@@
-\subsection{Overall Accuracy or true positive}\label{4.1.1}
+\subsection{Comparison of Accuracy by Transformation}\label{4.1.1}
 In this section, we compare the accuracy of the original MNIST test data to the accuracy of the follow-up test cases.
@@
 The follow-up test images have the same structure and labels as the original image.
-For example, the MNIST dataset was transformed by applying the shiftX metamorphic property for every pixel between [-28,28].
+For example, the MNIST dataset was transformed by applying the shiftX metamorphic property for every pixel between $[-28,28]$.
 The models were then tested with transformed test data, and their accuracy was calculated for every follow-up test data.
@@
         \includegraphics[width=\textwidth]{chapters/results/MT/ShiftX.png}
-        \caption{Shifting image along X-axis}
+        \caption{ShiftX}
     \end{subfigure}
@@
          \includegraphics[width=\textwidth]{chapters/results/MT/ShiftY.png}
-        \caption{Shifting image along Y-axis}
+        \caption{ShiftY}
     \end{subfigure}
@@
 This means that, on average, the accuracy of the convolutional neural network does not decrease as much as the other algorithms when tested with the various degree of transformed follow-up test cases.
-    On the other hand, KNN has the lowest area under the curve for the shade metamorphic property.
-Thus, the accuracy of the KNN program drops rapidly as the value of shade property in the test dataset increases.
+    On the other hand, $k$NN has the lowest area under the curve for the shade metamorphic property.
+Thus, the accuracy of the $k$NN program drops rapidly as the value of shade property in the test dataset increases.
     % Figure 4.1(a) through (c) shows the variation in accuracy of . A higher area under curve means 
@@
 
-\subsection{Class Accuracy}\label{Digit-by Accuracy}
-    We discussed several papers in Section \ref{2.4MetamorphicTestingMachineLearning} on how the metamorphic relations affect datasets but none of them have investigated how the transformations affect the individual classes in those dataset.
+\subsection{Comparison of Accurracy by Class}\label{Digit-by Accuracy}
+    % We discussed several papers in Section \ref{2.4MetamorphicTestingMachineLearning} on how the metamorphic relations affect datasets but none of them have investigated how the transformations affect the individual classes in those dataset.
 It is trivially easy to imagine that not all the data points in a dataset will be affected in the same way with all the transformations.
@@
 Thus, besides studying the overall effect of the metamorphic transformations on the whole dataset, we will also study how they affect individual data classes in the MNIST dataset.
+    We discussed several papers in Section \ref{2.4MetamorphicTestingMachineLearning} on the effect of metamorphic transformations on datasets, but no prior research was conducted on their impact on individual class in a dataset.
+It is trivially easy to imagine some classes not being affected in the same way in certain transformations.
+For example, the digit $0$ will still be easily recognizable as $0$, even if it is rotated by 180\textdegree  due to its symmetry.
+On the other hand, the digit $9$ has a higher chance of being mistaken for digit $6$ if rotated clockwise by 180\textdegree and vice-versa.
+Thus, in this section, we investigate the effect of metamorphic transformations on individual classes.
 
-    Figure 4.2 to 4.7 shows the accuracy of MNIST dataset class labels $[0-9]$ for our metamorphic relations.
+    % Figure \ref{fig:Digit by misclassification for Rotation MR} to \ref{fig:Digit by misclassification for ShiftY MR} shows the accuracy of MNIST dataset class labels $[0-9]$ for our metamorphic relations.
 Every figure in Figure 4.2-4.7 has ten sub-graphs, each, representing the correct classification of a class label.
@@
 A higher area under curve means that the class was less influenced by the transformation with respect to other classes and it's accuracy on the transformed testing input will be closer to training data.
+    Figure \ref{fig:Digit by misclassification for Rotation MR}-\ref{fig:Digit by misclassification for ShiftY MR} shows the accuracy of MNIST dataset class labels $[0-9]$ for our metamorphic relations.
+Every figure in \ref{fig:Digit by misclassification for Rotation MR}-\ref{fig:Digit by misclassification for ShiftY MR} has ten sub-graphs, each representing the correct classification of a class label with respect to the degree of transformation.
+We want to find clear outliers in the dataset which influence the accuracy of the model in a major way.
+To quantify this we calculated the area under curve for each of the sub-graphs in tables \ref{tbl:test-file-formatRotate}-\ref{tbl:test-file-formatShiftY}.
+A higher area under curve means that the transformation less influenced the class with respect to other classes, and its accuracy on the transformed testing input will be closer to training data.
 
-    Figure \ref{fig:Digit by misclassification for Rotation MR} shows the graphs for the accuracy of the classes in the MNIST dataset after applying the rotation transformation.
+    % Figure \ref{fig:Digit by misclassification for Rotation MR} shows the graphs for the accuracy of the classes in the MNIST dataset after applying the rotation transformation.
 There are five subplots in each sub-graph in Figure \ref{fig:Digit by misclassification for Rotation MR}.
@@
 The X-axis represents the angle with which the test data points were rotated and the Y-axis represents the accuracy of all the test data points in that class.\\
+    Figure \ref{fig:Digit by misclassification for Rotation MR} shows the graphs for the accuracy of the classes in the MNIST dataset after applying the rotation transformation.
+There are ten subgraphs, one for each class in $[0,9]$.
+Each sub-graph has five sub-plots, one for each machine learning algorithm that was implemented.
+The X-axis represents the degree of transformation (in this case, the angle of rotated), and the Y-axis represents the accuracy of all the test data points in that class.\\
     \begin{figure}[H]
@@
 
-    We did similar analysis for all the metamorphic property we identified in section \ref{identifyingMR}.
-For every class in the MNIST test dataset we applied the transformations with increasing value and calculated the accuracy of the algorithms at each value.\\
-    Figure \ref{fig:Digit by misclassification for Shading MR} shows the graphs for the accuracy of each class in MNIST dataset for the shading transformation.
-The five subplots in each sub-graph in Figure \ref{fig:Digit by misclassification for Shading MR} represents the accuracy of that digit for the five machine learning algorithms we implemented.
-The X-axis represents the value with which the test data points were shaded and the Y-axis represent the accuracy of all the test data points in that class.
+    % We did a similar analysis for all the metamorphic property identified in section \ref{identifyingMR}.
+For every class in the MNIST test dataset, we applied the transformations with increasing value and calculated the accuracy of the algorithms at each value.
 We also observed that all the algorithms started to predict the test data points as $1$ once the foreground became dark which is reflected in higher values of accuracy for digit $1$.
 \\
+     We did a similar analysis for all the metamorphic property identified in section \ref{identifyingMR}.
+For every class in the MNIST test dataset, we applied the transformations with increasing value and calculated the accuracy of the algorithms at each value.
+We observe that all the test data is predicted as $1$ once the foreground becomes dark.
+This is also reflected in the higher values of accuracy in the graph for digit $1$.
 
-    \begin{figure}[ht!]
+    \begin{figure}[H]
     \centering
@@
 
-    The following graphs shows similar graphs for the metamorphic properties shear, shifting the images on X axis, shifting the images on Y axis.
+    The following figures show similar graphs for the metamorphic properties shear, shifting the images on X axis, shifting the images on Y axis.
 
@@
         \caption{Class accuracy for MT: ShiftX}
-        \label{fig:Rotate-misclass0}
+        \label{fig:Digit by misclassification for ShiftX MR}
     \end{figure}
@@
         \caption{Class accuracy for MT: ShiftY}
-        \label{fig:Rotate-misclass0}
+        \label{fig:Digit by misclassification for ShiftY MR}
     \end{figure}
 
-    To further compare the accuracy of the different classes we calculated the area under each curve.
-The following tables shows the area under curve for each class $[0,9]$ in the above graphs.
-The cells with \textcolor{green}{green} background has the highest value among all the cells in that row and the ones in \textcolor{red}{red} has the lowest.
+  To further compare the accuracy of the different classes, we calculated the area under each curve for each plot.
+The following tables show the area under the curve for each class $[0,9]$ in the above graphs.
+The cells with \textcolor{green}{green} background has the highest value among all the cells in that row, and the ones in \textcolor{red}{red} has the lowest.
     \begin{table}[H]
@@
 
-     From the table \ref{tbl:test-file-formatRotate} we can see that the digit $0$ has the highest area under curve in the convolutional neural network implementation and the digit $9$ has the lowest area.
-From this we can say that the accuracy of the sub-set of MNIST dataset with class label $0$ is not affected as much as the other classes when the rotation property is applied.
+     In table \ref{tbl:test-file-formatRotate} we can see that the digit $0$ has the highest area under the curve in the convolutional neural network implementation and the digit $9$ has the lowest area.
+From this, we can say that the accuracy of the sub-set of the MNIST dataset with class label $0$ is not affected as much as the other classes when the rotation property is applied.
 Thus, when creating follow-up test cases for a convolutional neural network, the tester can apply the rotation property to the digit $0$ to a larger angle than any other classes.
-We will make these recommendations more concrete in \ref{tbl:indexrecommendations}.\\
+We will make these recommendations more concrete in \ref{tbl:indexrecommendations}.
      We generated the following tables to perform the same analysis on all the metamorphic properties.
-The digits with red background have the lowest area under curve for that algorithm thus, the lowest average accuracy for all the degree of transformation.
-The cells with green background have the highest area under curve and thus the highest average accuracy for all the degree of transformation.
 
@@
     \end{table}
-    From the table \ref{tbl:test-file-formatShade} we can see that the digit $1$ had the highest accuracy as compared to other classes in the dataset for every algorithm we implemented.
+    In table \ref{tbl:test-file-formatShade}, we see that the digit $1$ had the highest accuracy as compared to every other class in the dataset for every algorithm we implemented.
 On the other hand, the digit $8$ had the lowest accuracy in four out of the five algorithms we implemented.
-    Digit $6$ has the highest area under curve in the CNN and NN algorithms. The digits $3$, $1$, and, $0$ have the highest area under curve in the NB, KNN, and, SVM implementations respectively.
-
     \begin{table}[H]
@@
     \end{table}
-    The digit $6$ has the highest area under curve for CNN and NN while the digits $8$ and $5$ have the lowest area under curve.
-
+    In table \ref{tbl:test-file-formatShear}, we find that the digit $6$ had the highest area under curve while the digits $8$ and $5$ have the lowest area under curve for the convolutional neural network and the seven-layer neural network.
+The digits $3$, $1$, and $0$ have the highest area under curve in the Naive Bayes, KNN, and, SVM implementations respectively.
     \begin{table}[htb!]
@@
     \end{table}
+    For the metamorphic transformation shiftY, we find that the digit $1$ has the highest area under the curve for all but the seven-layer neural network implementation.
+Thus, images with class $1$ can be shifted to a larger value before they get confused with other classes.
 
-A similar analysis was also done for the Fashion-MNIST, and, EMNIST dataset but due to space limitation they are not reported here, instead, they are reported on the project's github page.
+A similar analysis was also done for the Fashion-MNIST, and, EMNIST dataset but due to space limitation they are not reported here, instead, they are reported on the project's github page \cite{abhishek2020}.
 
-\clearpage
-\newpage
-In the tables 4.2 to 4.6 we have seen that the different classes are affected differently depending upon the algorithm and the metamorphic transformation applied to them.
+\section{Recommendations}
+% In the tables 4.2 to 4.6 we have seen that the different classes are affected differently depending upon the algorithm and the metamorphic transformation applied to them.
 In this section, we want to make recommendations to pick the best values for the metamorphic properties such that the the accuracy of the transformed dataset will be close to the original dataset.
-For our purpose we define accuracy being close as within $90\%$ of the origin dataset.
+For our purpose we define accuracy being close as it being within $90\%$ of the origin dataset.
 To do this we first calculated the accuracy of each class in the original dataset without applying any transformation.
@@
 Based on this exercise we make the recommendation to testers who want to use these properties to generate follow-up test cases.
-The following table shows the minimum and maximum values of transformations where the accuracy was found to be within $90\%$ of the accuracy without any transformation.
+The following table shows the minimum and maximum values of transformations:
+In tables \ref{tbl:test-file-formatRotate} to \ref{tbl:test-file-formatShiftY}, we have seen that the different classes are affected differently depending upon the algorithm, and the metamorphic transformation applied to them.
+In this section, we want to make recommendations to pick the best values for transforming metamorphic properties such that the accuracy of the transformed dataset will be close to the original dataset.
+For this framework, we define accuracy being close as it is within $90\%$ of the original dataset.
+A tester will be able to use these recommendations to generate new data that are similar to the original dataset.
+To make the recommendations, we first calculated the accuracy of each class in the original dataset without applying any transformation.
+We then calculated the degrees of transformation for which the transformed dataset was similar to the original dataset by testing them on five algorithms.
+Since different algorithms had different values for the range of transformations, we took the minimum range from all the algorithms.
+Based on this exercise, we make the recommendation to testers who want to use these properties to generate follow-up test cases.
+The table \ref{tbl:indexrecommendations} shows the minimum and maximum values of transformations for each class of data in the MNIST dataset which will produce a dataset similar to the origin dataset:
+% where the accuracy was found to be within $90\%$ of the accuracy without any transformation.
 
@@
 \begin{center}
- \begin{table}[ht]
+ \begin{table}[H]
   \centering
@@
 \end{center}
-
-We have also provided these recommendations for the Fashion-MNIST and EMNIST datasets on the project's github page.
+We have also provided these recommendations for the Fashion-MNIST and EMNIST datasets on the project's github page \cite{abhishek2020}.
 % \subsection{Misclassification of digits}

### 2020-04-20 chapters/results/results.tex
Final

@@
+% 4.1 Overall Accurracy
+% 4.2 Comparison of Accuracy by Transformation
+% 4.3 Comparison of Accurracy by Image Class
+% 4.4 Recommendations
+% 4.5 Testing for Robustness
+
 In this section, we will discuss our findings after implementing the machine learning algorithms and metamorphic properties.
@@
         \addplot table[x=interval,y=Fashion]{\accuracy};
-        \addplot table[x=interval,y=EMNIST]{\accuracy};
-        \legend{MNIST, Fashion, EMNIST}
+        \addplot table[x=interval,y=EMNIST-Letter]{\accuracy};
+        \legend{MNIST, Fashion, EMNIST-Letter}
     \end{axis}
@@
 An interesting observation from the table above is that deep learning algorithms are not necessarily always the right choice when we are trying to maximize accuracy.
-Depending on the dataset, regular machine learning algorithms like KNN can also yield high accuracy and outperform deep learning algorithms in terms of accuracy.
+Depending on the data, regular machine learning algorithms like $k$NN can also yield high accuracy and outperform deep learning algorithms in terms of accuracy.
 In the following sections, we will discuss how the metamorphic transformations affected the accuracy of the models and what conclusions we can draw from it.
-\section{Affect of metamorphic transformation on the accuracy of the models}
+\section{Effect of metamorphic transformation on the accuracy of the models}
 From the literature review, we saw that metamorphic testing could be an instrumental technique to test the correctness of a program.
@@
 
-\clearpage
-\subsection{Robustness}
-
-In the section \ref{Digit-by Accuracy} we saw that that the accuracy of the algorithms varied depending upon the transformation applied to the test data as well as the degree of the transformation.
-Robustness is the property of an algorithm whereby if the test data is "similar" to the training data then the testing error is also close to the training error \cite{Xu2012}.
+\section{Testing for Robustness}
+To verify the effectiveness of the recommendations we made in section 1, we tested them by generating a new dataset with it and testing the algorithms for robustness.
+Robustness is the property of an algorithm whereby if the test data is "similar" to the training data, then the testing error is also close to the training error \cite{Xu2012}.
+Thus, a robust algorithm should produce similar errors while predicting similar test data.
+In this section, we will compare the robustness of the five algorithms with respect to each other for different metamorphic relations and verify the accuracy of the recommendations we made in the table \ref{tbl:indexrecommendations}.
+We generated a balanced dataset of $5000$ samples by randomly picking $100$ transformed images from each transformation for every class label using the table \ref{tbl:indexrecommendations}.
+This new test dataset was then tested for accuracy on the five algorithms we implemented.
+The bar graph below shows the accuracy of the new test dataset as compared to the original MNIST dataset.
+%  Robustness is the property of an algorithm whereby if the test data is "similar" to the training data then the testing error is also close to the training error \cite{Xu2012}.
 Thus, a robust algorithm should produce similar errors while predicting similar test data.
@@
 \end{tikzpicture}      
-\caption{Accuracy of tranformed dataset vs original dataset}
+\caption{Accuracy of original vs tranformed MNIST dataset}
 \label{img:transformedaccuracy}
@@
 
-The more robust algorithm will have the accuracy of the transformed images closer to the accuracy of the original MNIST data.
+% A more robust algorithm will have the accuracy of the transformed images closer to the accuracy of the original MNIST data.
 From the graph above we see that the convolutional neural network has a $1.81\%$ decrease in accuracy while the accuracy of the neural-network, NB, KNN, and, SVM decreased by $2.39\%$, $2.09\%$, $4.22\%$, and, $4.49\%$ respectively.
@@
 While the KNN and SVM implementations are the least robust.
+The more robust algorithm has the accuracy of the transformed images closer to the accuracy of the original MNIST data.
+From the graph above we see that the convolutional neural network has a $1.81\%$ decrease in accuracy while the accuracy of the neural-network, NB, $k$NN, and, SVM decreased by $2.39\%$, $2.09\%$, $4.22\%$, and, $4.49\%$ respectively.
+Thus, among the algorithms we implemented, the convolutional neural network is shown to be the most robust on MNIST dataset, followed by Naive Bayes implementation while the $k$NN and the SVM implementations are the least robust.
+However after doing a similar analysis on the Fashion and EMNIST-Letter datasets we found that the trend does not carry over.
+The Naive Bayes algorithm showed a higher accuracy on the 5000 transformed test data than on the original test data.
+Thus showing more robustness than others.
 
-In Section \ref{4.1.1} we discovered that the accuracy of the test data decreased as the degree of the transformation was increased.
+% In Section \ref{4.1.1} we discovered that the accuracy of the test data decreased as the degree of the transformation was increased.
 So a second way of looking at robustness is to look at transformations which can be applied to the dataset without lowering the accuracy of the model below 90 percent of the original value.
 
-\import{chapters/results/}{tables.tex}
+\section{Testing for Robustness by transformation}
+In this section, we investigate the robustness of the algorithms for each transformation.
+The following graph plots the transformations for which the accuracy of the dataset is close to the original dataset.
+The $X$-axis represent the algorithms, and the $Y$-axis represents the degree of transformation applied to the MNIST dataset.
+\pgfplotstableread[row sep=\\,col sep=&]{
+    RotateX & RotateY & ShadeX & ShadeY & ShearX & ShearY & ShiftXX & ShiftXY & ShiftYX & ShiftYY \\
+    0 & 39 & 0.1 & 55 & 0.2 & 47 & 0.3 & 5 & 0.4 & 3 \\
+    4 & 27 & 4.1 & 69 & 4.2 & 43 & 4.3 & 3 & 4.4 & 2 \\
+    8 & 25 & 8.1 & 96 & 8.2 & 34 & 8.3 & 3 & 8.4 & 2 \\
+    12 & 16 & 12.1 & 52 & 12.2 & 23 & 12.3 & 4 & 12.4 & 3 \\
+    16 & 19 & 16.1 & 51 & 16.2 & 23 & 16.3 & 4 & 16.4 & 3 \\
+    }\mnistx
 
-\newpage
-\section{Discussion}
-In this paper we identified five metamorphic properties "Rotation", "Shading", "Shearing", "Shifting the image along $x$ axis", and, "Shifting the image along $y$ axis" that can be used with image datasets.
-We then applied these metamorphic transformations to three datasets: MNIST, Fashion-MNIST, and, EMNIST.
-We then implemented five machine learning algorithms and measured the accuracy of the three datasets as well as the accuracy on the transformed dataset.
-We also investigated the accuracy of transformations on individual classes in the MNIST dataset and provided recommendations for creating follow up test cases from the MNIST dataset.
-These recommendations include the minimum and maximum values of transformations that can be used for the metamorphic properties.
-We also evaluated the robustness of the machine learning algorithms on these metamorphic properties.
-From this evaluation we found that convolutional neural-networks are more robust than the other machine learning algorithms we implemented.
-\\
-This paper also makes the a methodological contribution where we have provided a set of functions on the project's github page to easily manipulate, and, transform image datasets for future research. 
-% These functions can be used as frameworks to . 
-Future researchers can utilize these functions to plugin more algorithms and metamorphic properties.
+\pgfplotstableread[row sep=\\,col sep=&]{
+   Algo & RotateX & RotateY & ShadeX & ShadeY & ShearX & ShearY & ShiftXX & ShiftXY & ShiftYX & ShiftYY \\
+  CNN & 0 & -34 & 0.1 & 0 & 0.2 & -48 & 0.3 & -5 & 0.4 & -4 \\
+  NN &  4 & -28 & 4.1 & 0 & 4.2 & -46 & 4.3 & -3 & 4.4 & -2 \\
+  NB & 8 & -24 & 8.1 & 0 & 8.2 & -31 & 8.3 & -3 & 8.4 & -3 \\
+  SVM & 12 & -16 & 12.1 & 0 & 12.2 & -28 & 12.3 & -4 & 12.4 & -3 \\
+  KNN & 16 & -18 & 16.1 & 0 & 16.2 & -31 & 16.3 & -5 & 16.4 & -4 \\
+    }\mnisty
 
-% Contributions:
-% Methodological contribution where others can plugin more algors or MT.
-% Experimental contribution:Which algo does better.
+\begin{figure}[H]
 
-% Conclusions:
+\begin{tikzpicture}
 
-% Framework to apply MT in midst of distortions.
-% CNN not so much better than others based on learning just from the dataset.
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ylabel={Degree of transfromation},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnistx};
+\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\mnistx};
+\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\mnistx};
+\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\mnistx};
+\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\mnistx};
+
+\addlegendentry{Rotate}
+\addlegendentry{Shade}
+\addlegendentry{Shear}
+\addlegendentry{ShiftX}
+\addlegendentry{ShiftY}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=.5\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms}]
+\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnisty};
+\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\mnisty};
+\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\mnisty};
+\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\mnisty};
+\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\mnisty};
+
+\end{groupplot}
+\end{tikzpicture}
+
+\caption{Robustness graph for MNIST}
+\label{fig:RobGraphforMNIST}
+\end{figure}
+% In Figure \ref{fig:RobGraphforMNIST}, we plotted the degree of transformation for which the algorithms produce a similar accuracy to the original MNIST dataset.
+The X-axis lists the algorithms, and the Y-axis lists the degrees of transformation for which the accuracy of the algorithm was similar to the accuracy of the original dataset.
+When the rotation metamorphic transformation is applied to the MNIST dataset, the convolutional neural-network algorithm has the largest bar.
+This means that that a larger angle of rotation can be applied to the MNIST dataset before it's accuracy drops below $90\%$ of the original MNIST dataset.
+Similarly, Naive Bayes is the most robust for Fashion-MNIST datset and KNN is the most robust for EMNIST dataset.
+% For the shading metamorphic property we find that Naive Bayes is the most robust algorithm for all the three datasets.
+% For the Shearing property, the convolutional neural-network is the most robust. The Fashion-MNIST and EMNIST datasets have Naive Bayes and KNN as the most robust algorithm respectively.
+% On average the length of the bars for ShiftX metamorphic property is much lower than rotation, shearing, or, shading.
+This means that the algorithms are much less robust when the images are shifted in the direction of X axis.
+Among the algorithms we implemented, CNN is the most robust on MNIST-digit dataset, Naive Bayes on MNIST-Fashion, and, all the algorithms perform equally on the EMNIST dataset.
+
+% Just like the ShiftX property, the length of bars here are much smaller than others.
+Thus al here we find that k-NN is also more robust than the rest of the algorithms we tested when applied to MNIST-digit and EMNIST-letter dataset.
+While, Naive Bayes is more robust when applied to MNIST-Fashion dataset.
+For the rotation metamorphic transformation, the convolutional neural network has the biggest bar.
+Thus, the degree of rotation that can be applied to the MNIST dataset is higher for the convolutional neural network before the accuracy of the algorithm drops below $90\%$ of the original dataset.
+The same is also valid for shear, shiftX, and shiftY properties.
+However, for the shading property, we find that Naive Bayes implementation is most robust because of the amount of shading that can be applied to the dataset before its accuracy is dissimilar to the original MNIST dataset.
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+    RotateX & RotateY & ShadeX & ShadeY & ShearX & ShearY & ShiftXX & ShiftXY & ShiftYX & ShiftYY \\
+    0 & 13 & 0.1 & 55 & 0.2 & 24&0.3 & 1&0.4 & 1 \\
+4 & 19 & 4.1 & 53 & 4.2 & 29&4.3 & 1&4.4 & 1 \\
+8 & 19 & 8.1 & 76 & 8.2 & 33&8.3 & 2&8.4 & 1 \\
+12 & 18 & 12.1 & 52 & 12.2 & 31&12.3 & 1&12.4 & 1 \\
+16 & 15 & 16.1 & 52 & 16.2 & 29&16.3 & 1&16.4 & 1 \\
+    }\fashionx
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+   Algo & RotateX & RotateY & ShadeX & ShadeY & ShearX & ShearY & ShiftXX & ShiftXY & ShiftYX & ShiftYY \\
+  CNN & 0 & -14 & 0.1 & 0 & 0.2 & -25 & 0.3 & -1 & 0.4 & -1 \\
+   NN& 4 & -17 & 4.1 & 0 & 4.2 & -30 & 4.3 & -1 & 4.4 & 0 \\
+   NB& 8 & -19 & 8.1 & 0 & 8.2 & -43 & 8.3 & -2 & 8.4 & -1 \\
+    SVM&12 & -17 & 12.1 & 0 & 12.2 & -40 & 12.3 & -1 & 12.4 & -1 \\
+    KNN&16 & -16 & 16.1 & 0 & 16.2 & -32 & 16.3 & -1 & 16.4 & -1 \\
+    }\fashiony
+
+\begin{figure}[H]
+
+\begin{tikzpicture}
+
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ylabel={Degree of transfromation},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\fashionx};
+\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\fashionx};
+\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\fashionx};
+\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\fashionx};
+\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\fashionx};
+
+\addlegendentry{Rotate}
+\addlegendentry{Shade}
+\addlegendentry{Shear}
+\addlegendentry{ShiftX}
+\addlegendentry{ShiftY}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=.5\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\fashiony}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms}]
+\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\fashiony};
+\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\fashiony};
+\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\fashiony};
+\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\fashiony};
+\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\fashiony};
+
+\end{groupplot}
+\end{tikzpicture}
+
+\caption{Robustness graph for Fashion-MNIST}
+\label{fig:RobGraphforFashion}
+\end{figure}
+
+The figure \ref{fig:RobGraphforFashion} shows the same graph for the Fahion-MNIST dataset.
+Here the Naive Bayes algorithm shows the most robustness for all the five transformations since the dataset can be transformed for larger values before the accuracy is dissimilar to the original dataset.
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+    RotateX & RotateY & ShadeX & ShadeY & ShearX & ShearY & ShiftXX & ShiftXY & ShiftYX & ShiftYY \\
+    0 & 24 & 0.1 & 53 & 0.2 & 30 & 0.3 & 1 & 0.4 & 1 \\
+    4 & 19 & 4.1 & 61 & 4.2 & 24 & 4.3 & 1 & 4.4 & 0 \\
+    8 & 20 & 8.1 & 92 & 8.2 & 26 & 8.3 & 1 & 8.4 & 1 \\
+    12 & 21 & 12.1 & 51 & 12.2 & 29 & 12.3 & 1 & 12.4 & 1 \\
+    16 & 24 & 16.1 & 51 & 16.2 & 35 & 16.3 & 1 & 16.4 & 1 \\
+    }\letterx
+
+\pgfplotstableread[row sep=\\,col sep=&]{
+   Algo & RotateX & RotateY & ShadeX & ShadeY & ShearX & ShearY & ShiftXX & ShiftXY & ShiftYX & ShiftYY \\
+  CNN & 0 & -20 & 0.1 & 0 & 0.2 & -30 & 0.3 & -1 & 0.4 & -1 \\
+  NN & 4 & -18 & 4.1 & 0 & 4.2 & -26 & 4.3 & -1 & 4.4 & -1 \\
+ NB& 8 & -17 & 8.1 & 0 & 8.2 & -23 & 8.3 & -1 & 8.4 & -1 \\
+ SVM& 12 & -20 & 12.1 & 0 & 12.2 & -33 & 12.3 & -1 & 12.4 & -1 \\
+    KNN&    16 & -25 & 16.1 & 0 & 16.2 & -45 & 16.3 & -1 & 16.4 & -1 \\
+    }\lettery
+
+\begin{figure}[H]
+
+\begin{tikzpicture}
+
+\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
+\nextgroupplot[ylabel={Degree of transfromation},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth,]%ytick=\empty]
+\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\letterx};
+\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\letterx};
+\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\letterx};
+\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\letterx};
+\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\letterx};
+
+\addlegendentry{Rotate}
+\addlegendentry{Shade}
+\addlegendentry{Shear}
+\addlegendentry{ShiftX}
+\addlegendentry{ShiftY}
+
+\nextgroupplot[ybar, width=0.85\textwidth,height=.5\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\lettery}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms}]
+\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\lettery};
+\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\lettery};
+\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\lettery};
+\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\lettery};
+\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\lettery};
+
+\end{groupplot}
+\end{tikzpicture}
+
+\caption{Robustness graph for EMNIST-Letter}
+\label{fig:RobGraphforMNIST}
+\end{figure}
+
+Similarly, for the MNIST-Letter dataset, we find that the $k$NN algorithm is the most robust for all the transformation except shading.
+For the shading algorithm, the Naive Bayes algorithm shows the most robustness.

### 2020-04-20 chapters/results/robustness.tex
Final

--- 2020-04-13 chapters/results/tables.tex
@@
-% \subsection{Rotate}
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-% \hline
-%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-% \hline
-% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-% \hline
-% 0  &   -37&46 & -44&31 & -50&17 & -45&45 & -50&49 \\
-% \hline
-% 1 &   -15&18 & -11&15 & -9&12 & -21&22 & -28&43  \\
-% \hline
-% 2  &   -19&15 & -14&11 & -12&10 & -14&12 & -19&16  \\
-% \hline
-% 3  &   -20&15 & -17&15 & -9&19 & -17&13 & -25&26  \\
-% \hline
-% 4  &   -15&15 & -12&15 & -13&14 & -15&22 & -14&15 \\
-% \hline
-% 5  &   -16&17 & -9&8 & -14&5 & -11&10 & -25&18  \\
-% \hline
-% 6  &   -26&32 & -20&43 & -11&36 & -16&43 & -19&37 \\
-% \hline
-% 7  &   -18&11 & -19&8 & -13&7 & -20&11 & -19&13 \\
-% \hline
-% 8  &   -16&18 & -13&15 & -13&12 & -14&21 & -17&15 \\
-% \hline
-% 9  &   -21&24 & -10&18 & -6&22 & -12&16 & -11&18 \\ 
-% \hline
-% \end{tabular}
-% \caption{Rotate.}
-% \label{tbl:test-file-format}
-% \end{table}
-
-% \subsubsection{MT: Rotate}
-% \pgfplotstableread[row sep=\\,col sep=&]{
-%     interval & Digit & Fashion & Letter \\
-%     CNN & 75.4 & 39.8 & 43.72 \\
-%     NN & 61.6 & 43.36 & 40.59 \\
-%     NB & 54.5 & 57.9 & 37.29 \\
-%     SVM & 40.0 & 51.5 & 23.153 \\ 
-%     KNN & 47.7 & 35.08 & 26.31 \\
-%     }\rotate
-
-% \begin{tikzpicture}
-%     \begin{axis}[
-%             ybar,
-%             bar width=.75cm,
-%             width=\textwidth,
-%             height=.5\textwidth,
-%             legend style={at={(0.5,1)},
-%                 anchor=north,legend columns=-1},
-%             symbolic x coords={CNN,NN,NB,SVM,KNN},
-%             xtick=data,
-%             nodes near coords,
-%             nodes near coords align={vertical},
-%             ymin=0,ymax=120,
-%             ylabel={Value},
-%         ]
-%         \addplot table[x=interval,y=Digit]{\rotate};
-%         \addplot table[x=interval,y=Fashion]{\rotate};
-%         \addplot table[x=interval,y=Letter]{\rotate};
-%         \legend{Digit, Fashion, Letter}
-%     \end{axis}
-% \end{tikzpicture}
-\clearpage
+\section{Testing for Robustness by transformation}
 When the rotation metamorphic transformation is applied to the MNIST dataset, the convolutional neural-network algorithm has the largest bar.
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=60,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
+\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=40,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.35\textwidth,]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnistx};
@@
 
-\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-60,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
+\nextgroupplot[ybar, width=0.85\textwidth,height=.35\textwidth, bar width=.2cm,yshift=1cm,ymin=-40,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnisty};
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.6\textwidth,]%ytick=\empty]
+\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth,]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shadex};

### 2020-04-21 Fashion/ApplyTransformations.py
Fashion

@@ -1,0 +1,83 @@
+# Training Parameters
+from include import *
+from base import *
+
+
+# Training Parameters
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+xTest = mnist.test.images
+yTest = mnist.test.labels
+
+xTest = xTest.reshape(xTest.shape[0], 1, 28, 28)
+
+#reloadData(Test)
+yT = []
+xT = []
+for n in range(num_classes):
+    train_filter = np.isin(yTest, [n])
+    x, y = xTest[train_filter], yTest[train_filter]
+    yT.append(list(y[:num_images]))
+    xT.append(x[:num_images])
+yTest = [i for l in yT for i in l]
+xT = np.array(xT)
+xTest = np.concatenate(xT)
+
+MT = sys.argv[1]
+
+for step in range(-50,50):
+    print("MR: "+str(MT)+", Step: "+str(step+50))
+    fout = "data/"+str(MT)+"/"+str(step+50)
+    if (os.path.exists(fout)):
+        os.remove(fout)
+    value = step*0.5
+    x_test = Transform (xTest, yTest, MT, value)
+    with open(fout, 'wb') as f:
+        pickle.dump([x_test, yTest], f)
+# for step in range(-50,50):
+#     print("MR: Rotate, Step: "+str(step+50))
+#     fout = "variables/Transformations/Rotate/"+str(step+50)
+#     if (os.path.exists(fout)):
+#         os.remove(fout)
+#     x_test = Transform (xTest, yTest, Rotate, step)
+#     with open(fout, 'wb') as f:
+#         pickle.dump([x_test, yTest], f)
+
+
+# for step in range(-50,50):
+#     print("MR: Shear, Step: "+str(step+50))
+#     fout = "variables/Transformations/Shear/"+str(step+50)
+#     if (os.path.exists(fout)):
+#         os.remove(fout)
+#     x_test = Transform (xTest, yTest, Shear, step)
+#     with open(fout, 'wb') as f:
+#         pickle.dump([x_test, yTest], f)
+        
+# for step in range(-50,50):
+#     print("MR: ShiftX, Step: "+str(step+50))
+#     fout = "variables/Transformations/ShiftX/"+str(step+50)
+#     if (os.path.exists(fout)):
+#         os.remove(fout)
+#     x_test = Transform (xTest, yTest, ShiftX, step)
+#     with open(fout, 'wb') as f:
[…]

### 2020-04-21 Fashion/TrainNeuralNetworks.py

@@ -1,0 +1,52 @@
+# Training Parameters
+from base import *
+
+# Training Parameters
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+# Load the Mnist test data
+xTmp = mnist.test.images
+yTmp = list(mnist.test.labels)
+xTmp = xTmp.reshape(xTmp.shape[0], 1, 28, 28)
+# # convert from int to float
+xTmp = xTmp.astype('float32')
+xTest = []
+for x in xTmp:
+    xTest.append(np.transpose(x))
+xTest = np.array(xTest)
+xTest = xTest.reshape(xTest.shape[0],  784)
+yTest = yTmp
+xTestBackup = xTest.copy()
+yTestBackup = yTmp.copy()
+
+# Load the Mnist test data
+xTmp = mnist.train.images
+yTmp = list(mnist.train.labels)
+xTmp = xTmp.reshape(xTmp.shape[0], 1, 28, 28)
+# # convert from int to float
+xTmp = xTmp.astype('float32')
+xTrain = []
+for x in xTmp:
+    xTrain.append(np.transpose(x))
+xTrain = np.array(xTrain)
+xTrain = xTrain.reshape(xTrain.shape[0],  784)
+yTrain = yTmp
+xTrainBackup = xTrain.copy()
+yTrainBackup = yTmp.copy()
+
+Algo = CNN
+
+for i in range(10):
+   
+    model_dir = "models/"+Algo+"/TrainedModel"+str(i)
+    #model_dir = "models/Test"+str(i)
+    if (os.path.exists(model_dir)):
+        shutil.rmtree(model_dir)
+    if Algo == "CNN":
+        model = tf.estimator.Estimator(model_fn, model_dir=model_dir)
+    elif Algo == "NN":
+        model = tf.estimator.Estimator(nn_model_fn, model_dir=model_dir)
+
+    TrainModel (model, xTrain, yTrain, False)
+    p,a = TestModel (model, xTest, yTest, False)
+    print ("Step: "+str(i)+" Accuracy: "+str(a))    

### 2020-04-21 Fashion/base.py

@@ -1,0 +1,591 @@
+from include import *
+
+xTestBackup = []
+yTestBackup = []
+xTrainBackup = []
+yTrainBackup = []
+
+def conv_net(x_dict, n_classes, dropout, reuse, is_training):
+    
+    # Define a scope for reusing the variables
+    with tf.variable_scope('ConvNet', reuse=reuse):
+        # TF Estimator input is a dict, in case of multiple inputs
+        x = x_dict['images']
+
+        # MNIST data input is a 1-D vector of 784 features (28*28 pixels)
+        # Reshape to match picture format [Height x Width x Channel]
+        # Tensor input become 4-D: [Batch Size, Height, Width, Channel]
+        x = tf.reshape(x, shape=[-1, 28, 28, 1])
+
+        # Convolution Layer with 32 filters 
+        conv1 = tf.layers.conv2d(x, 32, 5, activation=tf.nn.relu)
+
+        # Convolution Layer with 64 filters 
+        conv2 = tf.layers.conv2d(conv1, 64, 3, activation=tf.nn.relu)
+
+        # Flatten the data to a 1-D vector for the fully connected layer
+        fc1 = tf.contrib.layers.flatten(conv2)
+
+        # Fully connected layer (in tf contrib folder for now)
+        fc1 = tf.layers.dense(fc1, 1024)
+        # Apply Dropout (if is_training is False, dropout is not applied)
+        fc1 = tf.layers.dropout(fc1, rate=dropout, training=is_training)
+
+        # Output layer, class prediction
+        out = tf.layers.dense(fc1, n_classes)
+
+    return out
+
+# Define the model function (following TF Estimator Template)
+def model_fn(features, labels, mode):
+    
+    # Build the neural network
+    # Because Dropout have different behavior at training and prediction time, we
+    # need to create 2 distinct computation graphs that still share the same weights.
+    logits_train = conv_net(features, num_classes, dropout, reuse=False, is_training=True)
+    logits_test = conv_net(features, num_classes, dropout, reuse=True, is_training=False)
+    
+    # Predictions
+    pred_classes = tf.argmax(logits_test, axis=1)
+    pred_probas = tf.nn.softmax(logits_test)
+    
+    # If prediction mode, early return
+    if mode == tf.estimator.ModeKeys.PREDICT:
[…]

### 2020-04-21 Fashion/implementKnn.py

@@ -1,0 +1,68 @@
+from base import *
+from include import *
+
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+xTrain = mnist.train.images
+yTrain = mnist.train.labels
+
+xTrain = xTrain.reshape(xTrain.shape[0], 1, 28, 28)
+xTrain = Transform (xTrain, yTrain, Rotate, 0)
+xTrain = xTrain.reshape(xTrain.shape[0],  784)
+ 
+
+def processResults2 (predMatrix, yMatrix):
+    totalData = [0]*num_classes
+    for y in yMatrix:
+        totalData[y] = totalData[y]+1
+    aMatrix = []
+    accMatrix = [[0]*num_classes for x in range(num_classes)]
+    for j in range(len(predMatrix)):
+        accMatrix[yMatrix[j]][predMatrix[j]] += 1
+            
+    for x in range(len(accMatrix)):
+        for y in range(len(accMatrix[x])):
+            accMatrix[x][y] = round(accMatrix[x][y]/totalData[x], 3)
+                
+    aMatrix.append(accMatrix)
+    return aMatrix
+
+start = datetime.datetime.now()
+neigh = KNeighborsClassifier(n_neighbors=3)
+neigh.fit(xTrain, yTrain)
+end = datetime.datetime.now()
+print(end-start)
+
+accuracyMatrix = []
+yMatrix = []
+pMatrix = []
+accMatrix = []
+
+Algo = "KNN"
+MT = Rotate
+
+for step in range(-50,-49):
+    accuracy = 0
+    with open("data/"+str(MT)+"/"+str(step+50), 'rb') as f:
+        [xTest, yTest] = pickle.load(f)
+
+    xTest = xTest.reshape(xTest.shape[0],  784)
+    
+    start = datetime.datetime.now()
+    pTemp = neigh.predict( xTest )
+    end = datetime.datetime.now()
+    print(end-start)
+    accuracy = accuracy_score(yTest, pTemp)
+    
+    accMatrixTemp = processResults2(pTemp, yTest)
+    accuracyMatrix.append(accuracy)
+    yMatrix.append(yTest)
+    pMatrix.append(pTemp)
+    accMatrix.append(accMatrixTemp)
+    print("Done!")
+    print("Accuracy:", accuracy)       
+fname = "data/Output/"+Algo+"_"+str(MT)
+if (os.path.exists(fname)):
+        os.remove(fname)
[…]

### 2020-04-21 Fashion/include.py

@@ -1,0 +1,82 @@
+
+# coding: utf-8
+
+# In[ ]:
+
+
+from __future__ import division, print_function, absolute_import
+
+# Import MNIST data
+import os
+import enum
+import pickle
+import logging
+import datetime
+import shutil, sys                                                                                                     
+from random import randrange
+                                   
+import numpy as np
+import tensorflow as tf
+from matplotlib import pyplot
+from itertools import groupby
+from operator import itemgetter
+from keras import backend as K
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import figure
+#from keras.datasets import mnist
+#from keras.datasets import fashion_mnist
+from sklearn.metrics import accuracy_score
+from sklearn.preprocessing import StandardScaler
+from sklearn.metrics import accuracy_score
+from sklearn.naive_bayes import MultinomialNB
+from sklearn.svm import SVC
+from sklearn import svm
+from sklearn.pipeline import Pipeline
+from sklearn.model_selection import GridSearchCV
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.metrics import confusion_matrix
+from sklearn.metrics import classification_report
+#from sklearn.metrics import multilabel_confusion_matrix
+from keras.preprocessing.image import ImageDataGenerator
+from tensorflow.examples.tutorials.mnist import input_data
+
+K.set_image_dim_ordering('th')
+logging.getLogger("tensorflow").setLevel(logging.INFO)
+
+# In[ ]:
+Shade = "Shade"
+Rotate = "Rotate"
+Shear = "Shear"
+ShiftX = "ShiftX"
+ShiftY = "ShiftY"
+ZoomX = "ZoomX"
+ZoomY = "ZoomY"
+
+Test = "Test"
+Train = "Train"
+
+# Training Parameters
+learning_rate = 0.01
+num_steps = 500
+batch_size = 128
+
+# Network Parameters
+n_hidden_1 = 256 # 1st layer number of neurons
+n_hidden_2 = 256 # 2nd layer number of neurons
+num_input = 784 # MNIST data input (img shape: 28*28)
+dropout = 0.25 # Dropout, probability to drop a unit
+
+num_classes = 10
+num_images = 1000
+
+NN = "NN"
+CNN = "CNN"
+KNN = "KNN"
+NB = "NB"
+SVM = "SVM"
+
+Algo = CNN
+
+Digit = "digit"
+Letter = "letter"
+Fashion = "fashion"

### 2020-04-21 MNIST/base.py
digit

@@ -6,7 +6,7 @@ xTrainBackup = []
 yTrainBackup = []
 
 def conv_net(x_dict, n_classes, dropout, reuse, is_training):
-    
+
     # Define a scope for reusing the variables
     with tf.variable_scope('ConvNet', reuse=reuse):
         # TF Estimator input is a dict, in case of multiple inputs
@@ -17,10 +17,10 @@ def conv_net(x_dict, n_classes, dropout, reuse, is_training):
         # Tensor input become 4-D: [Batch Size, Height, Width, Channel]
         x = tf.reshape(x, shape=[-1, 28, 28, 1])
 
-        # Convolution Layer with 32 filters 
+        # Convolution Layer with 32 filters
         conv1 = tf.layers.conv2d(x, 32, 5, activation=tf.nn.relu)
 
-        # Convolution Layer with 64 filters 
+        # Convolution Layer with 64 filters
         conv2 = tf.layers.conv2d(conv1, 64, 3, activation=tf.nn.relu)
 
         # Flatten the data to a 1-D vector for the fully connected layer
@@ -38,30 +38,30 @@ def conv_net(x_dict, n_classes, dropout, reuse, is_training):
 
 # Define the model function (following TF Estimator Template)
 def model_fn(features, labels, mode):
-    
+
     # Build the neural network
     # Because Dropout have different behavior at training and prediction time, we
     # need to create 2 distinct computation graphs that still share the same weights.
     logits_train = conv_net(features, num_classes, dropout, reuse=False, is_training=True)
     logits_test = conv_net(features, num_classes, dropout, reuse=True, is_training=False)
-    
+
     # Predictions
     pred_classes = tf.argmax(logits_test, axis=1)
     pred_probas = tf.nn.softmax(logits_test)
-    
+
     # If prediction mode, early return
     if mode == tf.estimator.ModeKeys.PREDICT:
-        return tf.estimator.EstimatorSpec(mode, predictions=pred_classes) 
-        
+        return tf.estimator.EstimatorSpec(mode, predictions=pred_classes)
+
     # Define loss and optimizer
     loss_op = tf.reduce_mean(tf.nn.sparse_softmax_cross_entropy_with_logits(
         logits=logits_train, labels=tf.cast(labels, dtype=tf.int32)))
     optimizer = tf.train.AdamOptimizer(learning_rate=learning_rate)
[…]

### 2020-04-21 MNIST/implementKnn.py

@@ -1,0 +1,68 @@
+from base import *
+from include import *
+
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+xTrain = mnist.train.images
+yTrain = mnist.train.labels
+
+xTrain = xTrain.reshape(xTrain.shape[0], 1, 28, 28)
+xTrain = Transform (xTrain, yTrain, Rotate, 0)
+xTrain = xTrain.reshape(xTrain.shape[0],  784)
+ 
+
+def processResults2 (predMatrix, yMatrix):
+    totalData = [0]*num_classes
+    for y in yMatrix:
+        totalData[y] = totalData[y]+1
+    aMatrix = []
+    accMatrix = [[0]*num_classes for x in range(num_classes)]
+    for j in range(len(predMatrix)):
+        accMatrix[yMatrix[j]][predMatrix[j]] += 1
+            
+    for x in range(len(accMatrix)):
+        for y in range(len(accMatrix[x])):
+            accMatrix[x][y] = round(accMatrix[x][y]/totalData[x], 3)
+                
+    aMatrix.append(accMatrix)
+    return aMatrix
+
+start = datetime.datetime.now()
+neigh = KNeighborsClassifier(n_neighbors=3)
+neigh.fit(xTrain, yTrain)
+end = datetime.datetime.now()
+print(end-start)
+
+accuracyMatrix = []
+yMatrix = []
+pMatrix = []
+accMatrix = []
+
+Algo = "KNN"
+MT = Rotate
+
+for step in range(-50,50):
+    accuracy = 0
+    with open("data/"+str(MT)+"/"+str(step+50), 'rb') as f:
+        [xTest, yTest] = pickle.load(f)
+
+    xTest = xTest.reshape(xTest.shape[0],  784)
+    
+    start = datetime.datetime.now()
+    pTemp = neigh.predict( xTest )
+    end = datetime.datetime.now()
+    print(end-start)
+    accuracy = accuracy_score(yTest, pTemp)
+    
+    accMatrixTemp = processResults2(pTemp, yTest)
+    accuracyMatrix.append(accuracy)
+    yMatrix.append(yTest)
+    pMatrix.append(pTemp)
+    accMatrix.append(accMatrixTemp)
+    print("Done!")
+    print("Accuracy:", accuracy)       
+fname = "data/Output/"+Algo+"_"+str(MT)
+if (os.path.exists(fname)):
+        os.remove(fname)
[…]

### 2020-04-21 MNIST/implementSVM.py

@@ -1,0 +1,64 @@
+from base import *
+from include import *
+
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+xTrain = mnist.train.images
+yTrain = mnist.train.labels
+
+xTrain = xTrain.reshape(xTrain.shape[0], 1, 28, 28)
+xTrain = Transform (xTrain, yTrain, Rotate, 0)
+xTrain = xTrain.reshape(xTrain.shape[0],  784)
+
+def processResults2 (predMatrix, yMatrix):
+    totalData = [0]*num_classes
+    for y in yMatrix:
+        totalData[y] = totalData[y]+1
+    aMatrix = []
+    accMatrix = [[0]*num_classes for x in range(num_classes)]
+    for j in range(len(predMatrix)):
+        accMatrix[yMatrix[j]][predMatrix[j]] += 1
+            
+    for x in range(len(accMatrix)):
+        for y in range(len(accMatrix[x])):
+            accMatrix[x][y] = round(accMatrix[x][y]/totalData[x], 3)
+                
+    aMatrix.append(accMatrix)
+    return aMatrix
+
+start = datetime.datetime.now()
+clf = svm.SVC()
+clf.fit(xTrain, yTrain)
+end = datetime.datetime.now()
+print(end-start)
+
+accuracyMatrix = []
+yMatrix = []
+pMatrix = []
+accMatrix = []
+
+Algo = "SVM"
+MT = ShiftY
+
+for step in range(-50,50):
+    accuracy = 0
+    with open("data/"+str(MT)+"/"+str(step+50), 'rb') as f:
+        [xTest, yTest] = pickle.load(f)
+
+    xTest = xTest.reshape(xTest.shape[0],  784)
+    
+    pTemp = clf.predict(xTest)
+    accuracy = accuracy_score(yTest, pTemp)
+    
+    accMatrixTemp = processResults2(pTemp, yTest)
+    accuracyMatrix.append(accuracy)
+    yMatrix.append(yTest)
+    pMatrix.append(pTemp)
+    accMatrix.append(accMatrixTemp)
+    print("Done!")
+    print("Accuracy:", accuracy)       
+fname = "data/Output/"+Algo+"_"+str(MT)
+if (os.path.exists(fname)):
+        os.remove(fname)
+with open(fname, 'wb') as f:
+    pickle.dump([yMatrix, pMatrix, accuracyMatrix, accMatrix], f)

### 2020-04-21 MNIST/testNeuralNetworks.py

@@ -1,0 +1,44 @@
+# Network Parameters
+from base import *
+
+yMatrix = []
+predMatrix = []
+accuracyMatrix = []
+accMatrix = []
+
+Algo = sys.argv[1]
+MT = sys.argv[2]
+
+model_dir = "models/"+Algo
+#model_dir = "models/Test"+str(i)
+if Algo == "CNN":
+    model = tf.estimator.Estimator(model_fn, model_dir=model_dir)
+elif Algo == "NN":
+    model = tf.estimator.Estimator(nn_model_fn, model_dir=model_dir)
+yMatrixTemp = []
+predMatrixTemp = []
+accuracyMatrixTemp = []
+
+for step in range(-50,50):
+    with open("data/"+str(MT)+"/"+str(step+50), 'rb') as f:
+        [xTest, yTest] = pickle.load(f)
+    yTest = np.array(yTest)
+    if Algo == NN:
+        xTest = xTest.reshape(xTest.shape[0],  784)
+    p,a = TestModel (model, xTest, yTest, False)
+    yMatrixTemp.append(yTest)
+    predMatrixTemp.append(p)
+    accuracyMatrixTemp.append(a)
+    print ("Step: "+str(step)+" Accuracy: "+str(a))
+accMatrixTemp = processResults(predMatrixTemp, yMatrixTemp)
+yMatrix.append(yMatrixTemp)
+predMatrix.append(predMatrixTemp)
+accuracyMatrix.append(accuracyMatrixTemp)
+accMatrix.append(accMatrixTemp)
+ 
+fname = "data/Output/"+Algo+"_"+str(MT)
+
+if (os.path.exists(fname)):
+        os.remove(fname)
+with open(fname, 'wb') as f:
+    pickle.dump([yMatrix, predMatrix, accuracyMatrix, accMatrix], f)

### 2020-04-21 EMNIST-Letter/ApplyTransformations.py
EMNIST

@@ -1,0 +1,83 @@
+# Training Parameters
+from include import *
+from base import *
+
+
+# Training Parameters
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+xTest = mnist.test.images
+yTest = mnist.test.labels
+
+xTest = xTest.reshape(xTest.shape[0], 1, 28, 28)
+
+#reloadData(Test)
+yT = []
+xT = []
+for n in range(num_classes):
+    train_filter = np.isin(yTest, [n+1])
+    x, y = xTest[train_filter], yTest[train_filter]
+    yT.append(list(y[:num_images]))
+    xT.append(x[:num_images])
+yTest = [i-1 for l in yT for i in l]
+xT = np.array(xT)
+xTest = np.concatenate(xT)
+
+MT = sys.argv[1]
+
+# for step in range(-50,50):
+#     print("MR: "+str(MT)+", Step: "+str(step+50))
+#     fout = "data/"+str(MT)+"/"+str(step+50)
+#     if (os.path.exists(fout)):
+#         os.remove(fout)
+#     value = step*0.5
+#     x_test = Transform (xTest, yTest, MT, value)
+#     with open(fout, 'wb') as f:
+#         pickle.dump([x_test, yTest], f)
+# for step in range(-50,50):
+#     print("MR: Rotate, Step: "+str(step+50))
+#     fout = "variables/Transformations/Rotate/"+str(step+50)
+#     if (os.path.exists(fout)):
+#         os.remove(fout)
+#     x_test = Transform (xTest, yTest, Rotate, step)
+#     with open(fout, 'wb') as f:
+#         pickle.dump([x_test, yTest], f)
+
+
+# for step in range(-50,50):
+#     print("MR: Shear, Step: "+str(step+50))
+#     fout = "variables/Transformations/Shear/"+str(step+50)
+#     if (os.path.exists(fout)):
+#         os.remove(fout)
+#     x_test = Transform (xTest, yTest, Shear, step)
+#     with open(fout, 'wb') as f:
+#         pickle.dump([x_test, yTest], f)
+        
+for step in range(-50,50):
+    print("MR: ShiftX, Step: "+str(step+50))
+    fout = "data/ShiftX/"+str(step+50)
+    if (os.path.exists(fout)):
+        os.remove(fout)
+    x_test = Transform (xTest, yTest, ShiftX, step)
+    with open(fout, 'wb') as f:
[…]

### 2020-04-21 EMNIST-Letter/base.py

@@ -1,0 +1,589 @@
+from include import *
+
+xTestBackup = []
+yTestBackup = []
+xTrainBackup = []
+yTrainBackup = []
+
+def conv_net(x_dict, n_classes, dropout, reuse, is_training):
+    
+    # Define a scope for reusing the variables
+    with tf.variable_scope('ConvNet', reuse=reuse):
+        # TF Estimator input is a dict, in case of multiple inputs
+        x = x_dict['images']
+
+        # MNIST data input is a 1-D vector of 784 features (28*28 pixels)
+        # Reshape to match picture format [Height x Width x Channel]
+        # Tensor input become 4-D: [Batch Size, Height, Width, Channel]
+        x = tf.reshape(x, shape=[-1, 28, 28, 1])
+
+        # Convolution Layer with 32 filters 
+        conv1 = tf.layers.conv2d(x, 32, 5, activation=tf.nn.relu)
+
+        # Convolution Layer with 64 filters 
+        conv2 = tf.layers.conv2d(conv1, 64, 3, activation=tf.nn.relu)
+
+        # Flatten the data to a 1-D vector for the fully connected layer
+        fc1 = tf.contrib.layers.flatten(conv2)
+
+        # Fully connected layer (in tf contrib folder for now)
+        fc1 = tf.layers.dense(fc1, 1024)
+        # Apply Dropout (if is_training is False, dropout is not applied)
+        fc1 = tf.layers.dropout(fc1, rate=dropout, training=is_training)
+
+        # Output layer, class prediction
+        out = tf.layers.dense(fc1, n_classes)
+
+    return out
+
+# Define the model function (following TF Estimator Template)
+def model_fn(features, labels, mode):
+    
+    # Build the neural network
+    # Because Dropout have different behavior at training and prediction time, we
+    # need to create 2 distinct computation graphs that still share the same weights.
+    logits_train = conv_net(features, num_classes, dropout, reuse=False, is_training=True)
+    logits_test = conv_net(features, num_classes, dropout, reuse=True, is_training=False)
+    
+    # Predictions
+    pred_classes = tf.argmax(logits_test, axis=1)
+    pred_probas = tf.nn.softmax(logits_test)
+    
+    # If prediction mode, early return
+    if mode == tf.estimator.ModeKeys.PREDICT:
[…]

### 2020-04-21 EMNIST-Letter/implementKnn.py

@@ -1,0 +1,67 @@
+from base import *
+
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+xTrain = mnist.train.images
+yTrain = mnist.train.labels-1
+
+xTrain = xTrain.reshape(xTrain.shape[0], 1, 28, 28)
+xTrain = Transform (xTrain, yTrain, Rotate, 0)
+xTrain = xTrain.reshape(xTrain.shape[0],  784)
+ 
+
+def processResults2 (predMatrix, yMatrix):
+    totalData = [0]*num_classes
+    for y in yMatrix:
+        totalData[y] = totalData[y]+1
+    aMatrix = []
+    accMatrix = [[0]*num_classes for x in range(num_classes)]
+    for j in range(len(predMatrix)):
+        accMatrix[yMatrix[j]][predMatrix[j]] += 1
+            
+    for x in range(len(accMatrix)):
+        for y in range(len(accMatrix[x])):
+            accMatrix[x][y] = round(accMatrix[x][y]/totalData[x], 3)
+                
+    aMatrix.append(accMatrix)
+    return aMatrix
+
+start = datetime.datetime.now()
+neigh = KNeighborsClassifier(n_neighbors=3)
+neigh.fit(xTrain, yTrain)
+end = datetime.datetime.now()
+print(end-start)
+
+accuracyMatrix = []
+yMatrix = []
+pMatrix = []
+accMatrix = []
+
+Algo = sys.argv[1]
+MT = sys.argv[2]
+
+for step in range(-50,50):
+    accuracy = 0
+    with open("data/"+str(MT)+"/"+str(step+50), 'rb') as f:
+        [xTest, yTest] = pickle.load(f)
+
+    xTest = xTest.reshape(xTest.shape[0],  784)
+    
+    start = datetime.datetime.now()
+    pTemp = neigh.predict( xTest )
+    end = datetime.datetime.now()
+    print(end-start)
+    accuracy = accuracy_score(yTest, pTemp)
+    
+    accMatrixTemp = processResults2(pTemp, yTest)
+    accuracyMatrix.append(accuracy)
+    yMatrix.append(yTest)
+    pMatrix.append(pTemp)
+    accMatrix.append(accMatrixTemp)
+    print("Done!")
+    print("Accuracy:", accuracy)       
+fname = "data/Output/"+Algo+"_"+str(MT)
+if (os.path.exists(fname)):
[…]

### 2020-04-21 EMNIST-Letter/implementNeuralNetwork.py

@@ -1,0 +1,47 @@
+# Network Parameters
+from base import *
+
+yMatrix = []
+predMatrix = []
+accuracyMatrix = []
+accMatrix = []
+
+Algo = sys.argv[1]
+MT = sys.argv[2]
+
+model_dir = "models/"+Algo
+#model_dir = "models/Test"+str(i)
+if Algo == "CNN":
+    model = tf.estimator.Estimator(model_fn, model_dir=model_dir)
+elif Algo == "NN":
+    model = tf.estimator.Estimator(nn_model_fn, model_dir=model_dir)
+yMatrixTemp = []
+predMatrixTemp = []
+accuracyMatrixTemp = []
+
+for step in range(-50,50):
+    with open("data/"+str(MT)+"/"+str(step+50), 'rb') as f:
+        [xTest, yTest] = pickle.load(f)
+    yTest = np.array(yTest)
+    if Algo == NN:
+        xTest = xTest.reshape(xTest.shape[0],  784)
+    p,a = TestModel (model, xTest, yTest, False)
+    yMatrixTemp.append(yTest)
+    predMatrixTemp.append(p)
+    accuracyMatrixTemp.append(a)
+    print ("Step: "+str(step)+" Accuracy: "+str(a))
+accMatrixTemp = processResults(predMatrixTemp, yMatrixTemp)
+yMatrix.append(yMatrixTemp)
+predMatrix.append(predMatrixTemp)
+accuracyMatrix.append(accuracyMatrixTemp)
+accMatrix.append(accMatrixTemp)
+ 
+fname = "data/Output/"+Algo+"_"+str(MT)
+
+if (os.path.exists(fname)):
+        os.remove(fname)
+with open(fname, 'wb') as f:
+    pickle.dump([yMatrix, predMatrix, accuracyMatrix, accMatrix], f)
+
+
+

### 2020-04-21 EMNIST-Letter/implementSVM.py

@@ -1,0 +1,67 @@
+from base import *
+from include import *
+
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+xTrain = mnist.train.images
+yTrain = mnist.train.labels-1
+
+xTrain = xTrain.reshape(xTrain.shape[0], 1, 28, 28)
+xTrain = Transform (xTrain, yTrain, Rotate, 0)
+xTrain = xTrain.reshape(xTrain.shape[0],  784)
+
+def processResults2 (predMatrix, yMatrix):
+    totalData = [0]*num_classes
+    for y in yMatrix:
+        totalData[y] = totalData[y]+1
+    aMatrix = []
+    accMatrix = [[0]*num_classes for x in range(num_classes)]
+    for j in range(len(predMatrix)):
+        accMatrix[yMatrix[j]][predMatrix[j]] += 1
+            
+    for x in range(len(accMatrix)):
+        for y in range(len(accMatrix[x])):
+            accMatrix[x][y] = round(accMatrix[x][y]/totalData[x], 3)
+                
+    aMatrix.append(accMatrix)
+    return aMatrix
+
+start = datetime.datetime.now()
+clf = svm.SVC()
+clf.fit(xTrain, yTrain)
+end = datetime.datetime.now()
+print(end-start)
+
+accuracyMatrix = []
+yMatrix = []
+pMatrix = []
+accMatrix = []
+
+Algo = sys.argv[1]
+MT = sys.argv[2]
+startIndex = int(sys.argv[3])
+endIndex = sys.argv[4]
+outVal = sys.argv[5]
+
+for step in range(int(startIndex), int(endIndex)):
+    accuracy = 0
+    with open("data/"+str(MT)+"/"+str(step+50), 'rb') as f:
+        [xTest, yTest] = pickle.load(f)
+
+    xTest = xTest.reshape(xTest.shape[0],  784)
+    
+    pTemp = clf.predict(xTest)
+    accuracy = accuracy_score(yTest, pTemp)
+    
+    accMatrixTemp = processResults2(pTemp, yTest)
+    accuracyMatrix.append(accuracy)
+    yMatrix.append(yTest)
+    pMatrix.append(pTemp)
+    accMatrix.append(accMatrixTemp)
+    print("Done!")
+    print("Accuracy:", accuracy)       
+fname = "data/Output/SVM/"+Algo+"_"+str(MT)+"_"+str(outVal)
[…]

### 2020-04-21 EMNIST-Letter/include.py

@@ -1,0 +1,74 @@
+
+# coding: utf-8
+
+# In[ ]:
+
+
+from __future__ import division, print_function, absolute_import
+
+# Import MNIST data
+import os
+import enum
+import pickle
+import logging
+import datetime
+import shutil, sys                                                                                                                                                    
+import numpy as np
+import tensorflow as tf
+from matplotlib import pyplot
+from keras import backend as K
+from itertools import groupby
+from operator import itemgetter
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import figure
+#from keras.datasets import mnist
+#from keras.datasets import fashion_mnist
+from sklearn.metrics import accuracy_score
+from sklearn.preprocessing import StandardScaler
+from sklearn.svm import SVC
+from sklearn import svm
+from sklearn.pipeline import Pipeline
+from sklearn.model_selection import GridSearchCV
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.metrics import confusion_matrix
+from sklearn.metrics import classification_report
+#from sklearn.metrics import multilabel_confusion_matrix
+from keras.preprocessing.image import ImageDataGenerator
+from tensorflow.examples.tutorials.mnist import input_data
+
+K.set_image_dim_ordering('th')
+logging.getLogger("tensorflow").setLevel(logging.INFO)
+
+# In[ ]:
+Shade = "Shade"
+Rotate = "Rotate"
+Shear = "Shear"
+ShiftX = "ShiftX"
+ShiftY = "ShiftY"
+ZoomX = "ZoomX"
+ZoomY = "ZoomY"
+
+Test = "Test"
+Train = "Train"
+
+# Training Parameters
+learning_rate = 0.01
+num_steps = 500
+batch_size = 128
+
+# Network Parameters
+n_hidden_1 = 256 # 1st layer number of neurons
+n_hidden_2 = 256 # 2nd layer number of neurons
+num_input = 784 # MNIST data input (img shape: 28*28)
+dropout = 0.25 # Dropout, probability to drop a unit
+
+num_classes = 26
+num_images = 1000
+
+NN = "NN"
+CNN = "CNN"
+KNN = "KNN"
+NB = "NB"
+SVM = "SVM"
+
+Algo = CNN

### 2020-04-21 EMNIST-Letter/trainNeuralNetworks.py

@@ -1,0 +1,51 @@
+# Training Parameters
+from base import *
+
+# Training Parameters
+mnist = input_data.read_data_sets("data/Original", one_hot=False)
+
+# Load the Mnist test data
+xTmp = mnist.test.images
+yTmp = list(mnist.test.labels-1)
+xTmp = xTmp.reshape(xTmp.shape[0], 1, 28, 28)
+# # convert from int to float
+xTmp = xTmp.astype('float32')
+xTest = []
+for x in xTmp:
+    xTest.append(np.transpose(x))
+xTest = np.array(xTest)
+xTest = xTest.reshape(xTest.shape[0],  784)
+yTest = yTmp
+xTestBackup = xTest.copy()
+yTestBackup = yTmp.copy()
+
+# Load the Mnist test data
+xTmp = mnist.train.images
+yTmp = list(mnist.train.labels-1)
+xTmp = xTmp.reshape(xTmp.shape[0], 1, 28, 28)
+# # convert from int to float
+xTmp = xTmp.astype('float32')
+xTrain = []
+for x in xTmp:
+    xTrain.append(np.transpose(x))
+xTrain = np.array(xTrain)
+xTrain = xTrain.reshape(xTrain.shape[0],  784)
+yTrain = yTmp
+xTrainBackup = xTrain.copy()
+yTrainBackup = yTmp.copy()
+
+Algo = CNN
+
+   
+model_dir = "models/"+Algo
+#model_dir = "models/Test"+str(i)
+if (os.path.exists(model_dir)):
+    shutil.rmtree(model_dir)
+if Algo == "CNN":
+    model = tf.estimator.Estimator(model_fn, model_dir=model_dir)
+elif Algo == "NN":
+    model = tf.estimator.Estimator(nn_model_fn, model_dir=model_dir)
+
+TrainModel (model, xTrain, yTrain, False)
+p,a = TestModel (model, xTest, yTest, False)
+print ("Step: "+" Accuracy: "+str(a))    

### 2020-04-22 chapters/litReview/finalLit.tex
Final final

@@
 Software testing is a very common practice in the software industry and is used to ensure the quality of the product.
-Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc.\cite{Bertolino2007} A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost.
+Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc \cite{Bertolino2007}.
+A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost.
 Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.\\
@@
 
- A third and more effective method of addressing some of the concerns about the oracle problem is the use of differential testing.
-McKeeman \cite{McKeeman98differentialtesting} first introduced the idea of differential testing, which works by testing a dataset on two or more comparable systems.
+ A third and more effective method of addressing some of the concerns about the oracle problem is by the use of differential testing.
+Differential testing focuses on two main objectives; one is that the behaviors that are supposed to remain unchanged do so, and the second is that all the discrepancies in the output are explained.
+McKeeman \cite{McKeeman98differentialtesting} first introduced the idea of differential testing, which works by testing a dataset on multiple comparable systems.
+In differential testing, two versions of a software system are selected.
+One bug-free version of the program is chosen while the other is a test version, which is a modified version of the program and, thus, needs testing.
 The systems are run with mechanically generated test cases, and their output is observed.
@@
 It has successfully uncovered bugs in various domains like C compilers, JVM, SSL/TLS implementations, etc.
+Gulzar, Zhu, and Han \cite{gulzar2019} conducted a log analysis of 2104 diff tests from an organization-wide diff testing framework at Google and found that the main reason behind the popularity of diff tests is their ability to simulate real production systems and their low maintenance overhead.
 However, since it requires two or more similar systems, it inherits some of the same problems of pseudo-oracle testing.
+They also identified some other limitations of differential testing, where they are found to be more time-intensive to run and often generate noisy and flaky outcomes \cite{gulzar2019}.
+
  Developing sophisticated oracles is another way of encountering the oracle problem.

### 2020-04-22 chapters/methodology/dataset.tex
Final final

@@
 The EMNIST-Digit and EMNIST-MNIST datasets are directly compatible with the original MNIST dataset.
-For this study, we choose "EMNIST Letters" split, which has $145,600$ characters in 26 balanced classes where each class has the same number of samples.
+For this study, we choose "EMNIST Letters" split, which has $119,800$ characters in 26 balanced classes where each class has the same number of samples.
 The characters are in uppercase and lowercase, which have have been merged into one 26-class set.
@@
 \subsection{Fashion MNIST Dataset}
-Zalando's article images consist of a set of $55,000$ training examples and $10,000$ test examples.
+A dataset of Zalando's article images which consist of a set of $55,000$ training examples and $10,000$ test examples.
 The dataset is commonly referred to as the Fashion-MNIST dataset.

### 2020-04-22 chapters/methodology/properties.tex
Final final

@@
-\section{Identifying Metamorphic Relations} \label{identifyingMR}
+\section{Identifying Metamorphic Transformations} \label{identifyingMR}
+Some common problems with images are that they can have some small random rotations, or they could be located a bit off from the center, or the exposure of the picture could be high.
+These problems with images prompted us to look into affine transformations as a possible set of transformations to use for this project.
 To answer our first research question, we implemented some affine transformations on the datasets as possible candidates for metamorphic properties.
@@
 Thus we selected these five transformations as metamorphic properties for each dataset: rotate, shear, shade, shift the image along $x$-axis, and shift the image along $y$-axis.
+It should be noted that there more affine transformations than the five we identified, and they can be used as metamorphic transformation as well.
+However, these transformations appear to be the most common ways one can manipulate image datasets.
 Each image in the testing dataset (MNIST, Fashion-MNIST, and EMNIST-Letter) was transformed using these five metamorphic properties.
 We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
+
+After some primary investigation using the transformed datasets and some standard machine learning algorithms, we saw that the machine learning algorithms produced very similar accuracies on datasets, which were very similar to the original dataset.
+Thus, we defined our metamorphic relation as "a small change in the input from a known test case should lead to a similarly small change (or no change) in the output." We use this metamorphic relation for all the transformations.
 
@@
             \includegraphics[width=\linewidth]{images/shade1.png}
-            \caption{Value: 0}
+            \caption{Shading Value: 0}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\textwidth]{images/shade2.png}
-            \caption{Value: 80}
+            \caption{Shading Value: 0.80}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\linewidth]{images/shade3.png}
-            \caption{Value: 99}
+            \caption{Shading Value: 0. 99}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\linewidth]{images/shiftx1.png}
-            \caption{Value: 10}
+            \caption{Pixel shift: 10}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\textwidth]{images/shiftx2.png}
-            \caption{Value: 0}
+            \caption{Pixel shift: 0}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\linewidth]{images/shiftx3.png}
-            \caption{Value: -10}
+            \caption{Pixel shift: -10}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\linewidth]{images/shifty1.png}
-            \caption{Value: -10}
+            \caption{Pixel shift: -10}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\textwidth]{images/shifty2.png}
-            \caption{Value: 0}
+            \caption{Pixel shift: 0}
             \label{fig:Rotate-misclass0}
@@
             \includegraphics[width=\linewidth]{images/shifty3.png}
-            \caption{Value: 10}
+            \caption{Pixel shift: 10}
             \label{fig:Rotate-misclass0}

### 2020-04-22 chapters/results/BackupOfRobustnessData.tex
Final final

--- 2020-04-20 chapters/results/results.tex
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ylabel={Degree of transfromation},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth,]%ytick=\empty]
+\nextgroupplot[ylabel={Degree of transfromation},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnistx};
@@
 
-\nextgroupplot[ybar, width=0.85\textwidth,height=.5\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms}]
+\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms}]
 \addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnisty};
@@
 The figure \ref{fig:RobGraphforFashion} shows the same graph for the Fahion-MNIST dataset.
-Here the Naive Bayes algorithm shows the most robustness for all the five transformations since the dataset can be transformed for larger values before the accuracy is dissimilar to the original dataset.
+Here the Naive Bayes algorithm shows the most robustness for all the five transformations since the dataset can be transformed for larger values before the accuracy drops significantly lower than the original dataset.
 
@@
 Similarly, for the MNIST-Letter dataset, we find that the $k$NN algorithm is the most robust for all the transformation except shading.
-For the shading algorithm, the Naive Bayes algorithm shows the most robustness.
+For the shading algorithm, the Naive Bayes algorithm once again shows the most robustness.

### 2020-04-22 chapters/results/discussion.tex
Final final

@@
 These recommendations can be used as a test case generation strategy to generate additional transformed test data for MNIST, Fashion-MNIST, and EMNIST-Letter dataset.
-Future researches should consider using our metamorphic transformations and recommendations to generate new test cases for machine learning algorithms.
+Future researches should consider using our metamorphic transformations and recommendations to generate new test cases for their machine learning algorithms.

### 2020-04-22 chapters/results/figures.tex
Final final

@@
 
-  To further compare the accuracy of the different classes, we calculated the area under each curve for each plot.
+  To answer the second research question and compare the accuracy of the different classes, we calculated the area under each curve for each plot.
 The following tables show the area under the curve for each class $[0,9]$ in the above graphs.
@@
         \end{tabular}
-        \caption{Area under curve for each class for MR: Rotation.}
+        \caption{Area under curve for each class for MR: Rotate.}
         \label{tbl:test-file-formatRotate}
@@
     \end{tabular}
-    \caption{Area under curve for each class for MR: Shading.}
+    \caption{Area under curve for each class for MR: Shade.}
     \label{tbl:test-file-formatShade}
@@
 
-A similar analysis was also done for the Fashion-MNIST, and, EMNIST dataset but due to space limitation they are not reported here, instead, they are reported on the project's github page \cite{abhishek2020}.
+From the analysis above we conclude that metamorphic transformations affect the classes differently and their effect on the individual classes should be considered while creating follow-up test cases.
+A similar analysis was also done for the Fashion-MNIST, and, EMNIST dataset but due to space limitations they are not reported here, instead, they are reported on the project's github page \cite{abhishek2020}.
 
@@
 In tables \ref{tbl:test-file-formatRotate} to \ref{tbl:test-file-formatShiftY}, we have seen that the different classes are affected differently depending upon the algorithm, and the metamorphic transformation applied to them.
-In this section, we want to make recommendations to pick the best values for transforming metamorphic properties such that the accuracy of the transformed dataset will be close to the original dataset.
-For this framework, we define accuracy being close as it is within $90\%$ of the original dataset.
+In this section, we answer the third research question by making recommendations to pick the best values for transforming metamorphic properties such that the accuracy of the transformed dataset will be close to the original dataset.
+For this framework, if the accuracy of the follow-up test cases is above $90\%$ of the original dataset, it is considered close to the original dataset.
 A tester will be able to use these recommendations to generate new data that are similar to the original dataset.

### 2020-04-22 chapters/results/robustnessGraphs.tex
Final final

--- 2020-04-20 chapters/results/robustness.tex
@@
-\section{Testing for Robustness by transformation}
-When the rotation metamorphic transformation is applied to the MNIST dataset, the convolutional neural-network algorithm has the largest bar.
-This means that that a larger angle of rotation can be applied to the MNIST dataset before it's accuracy drops below $90\%$ of the original MNIST dataset.
-Similarly, Naive Bayes is the most robust for Fashion-MNIST datset and KNN is the most robust for EMNIST dataset.
-
 \pgfplotstableread[row sep=\\,col sep=&]{
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=40,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.35\textwidth,]%ytick=\empty]
+\nextgroupplot[ylabel={Range of transformations},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.35\textwidth, y label style={at={(axis description cs:-0.01,0.001)}},]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnistx};
@@
 
-\nextgroupplot[ybar, width=0.85\textwidth,height=.35\textwidth, bar width=.2cm,yshift=1cm,ymin=-40,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
+\nextgroupplot[ybar, width=0.85\textwidth,height=.35\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms},x label style={at={(axis description cs:0.5,-0.1)},anchor=north}]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\mnisty};
@@
 \end{figure}
-
-% \subsection{Shade}
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-% \hline
-%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-% \hline
-% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-% \hline
-% 0  &   0.0&0.6 & 0.0&0.74 & 0.0&0.96 & 0.0&0.5 & 0.0&0.51 \\
-% \hline
-% 1  &   0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 & 0.0&0.99 \\
-% \hline
-% 2  &   0.0&0.64 & 0.0&0.78 & 0.0&0.93 & 0.0&0.5 & 0.0&0.49 \\
-% \hline
-% 3  &   0.0&0.62 & 0.0&0.76 & 0.0&0.97 & 0.0&0.49 & 0.0&0.5  \\
-% \hline
-% 4  &   0.0&0.63 & 0.0&0.87 & 0.0&0.99 & 0.0&0.51 & 0.0&0.5 \\
-% \hline
-% 5  &   0.0&0.62 & 0.0&0.91 & 0.0&0.92 & 0.0&0.53 & 0.0&0.5  \\
-% \hline
-% 6  &   0.0&0.62 & 0.0&0.81 & 0.0&0.97 & 0.0&0.5 & 0.0&0.5 \\
-% \hline
-% 7  &   0.0&0.6 & 0.0&0.89 & 0.0&0.98 & 0.0&0.51 & 0.0&0.52\\
-% \hline
-% 8  &   0.0&0.57 & 0.0&0.61 & 0.0&0.9 & 0.0&0.49 & 0.0&0.49\\
-% \hline
-% 9  &   0.0&0.57 & 0.0&0.7 & 0.0&0.94 & 0.0&0.5 & 0.0&0.5\\ 
-% \hline
-% \end{tabular}
-% \caption{Shade.}
-% \label{tbl:test-file-format}
-% \end{table}
-
-% \subsubsection{MT: Shade}
-% \pgfplotstableread[row sep=\\,col sep=&]{
-%     interval & Digit & Fashion & Letter \\
-%     CNN   & 64.6  & 55.6  & 36.76  \\
-%     NN    & 80.6 & 56.1  & 74.69  \\
-%     NB    & 95.5 & 68.63 & 62.30 \\
-%     SVM   & 55.2 & 55.8 & 40.81 \\
-%     KNN   & 55.0  & 51.9 & 56.29 \\
-%     }\shade
-
-% \begin{tikzpicture}
-%     \begin{axis}[
-%             ybar,
-%             bar width=.75cm,
-%             width=\textwidth,
-%             height=.5\textwidth,
-%             legend style={at={(0.5,1)},
-%                 anchor=north,legend columns=-1},
-%             symbolic x coords={CNN,NN,NB,SVM,KNN},
-%             xtick=data,
-%             nodes near coords,
-%             nodes near coords align={vertical},
-%             ymin=0,ymax=120,
-%             ylabel={Value},
-%         ]
-%         \addplot table[x=interval,y=Digit]{\shade};
-%         \addplot table[x=interval,y=Fashion]{\shade};
-%         \addplot table[x=interval,y=Letter]{\shade};
-%         \legend{Digit, Fashion, Letter}
-%     \end{axis}
-% \end{tikzpicture}
 
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth,]%ytick=\empty]
+\nextgroupplot[ylabel={Range of transformations},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth, y label style={at={(axis description cs:-.009,.5)}},]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shadex};
@@
 
-\nextgroupplot[ybar, width=0.85\textwidth,height=0, bar width=.2cm,yshift=1cm,ymin=0,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shadey}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},ytick=\empty,]
+\nextgroupplot[ybar, width=0.85\textwidth,height=0, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shadey}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms},x label style={at={(axis description cs:0.5,-0.1)},anchor=north}]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shadey};
@@
 \end{figure}
-For the shading metamorphic property we find that Naive Bayes is the most robust algorithm for all the three datasets.
 
-% \subsection{Shear}
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-% \hline
-%  & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-% \hline
-% Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-% \hline
-% 0  &   -24&28 & -19&16 & -17&10 & -36&25 & -50&39 \\
-% \hline
-% 1  &   -50&18 & -24&14 & -14&10 & -50&24 & -50&49 \\
-% \hline
-% 2  &   -22&33 & -25&25 & -17&49 & -25&26 & -32&29 \\
-% \hline
-% 3  &   -25&23 & -31&21 & -12&33 & -32&22 & -35&35  \\
-% \hline
-% 4  &   -25&20 & -17&17 & -25&13 & -21&31 & -24&18 \\
-% \hline
-% 5  &   -32&26 & -24&18 & -45&4 & -25&23 & -31&27  \\
-% \hline
-% 6  &   -39&29 & -23&30 & -9&21 & -31&30 & -40&34 \\
-% \hline
-% 7  &   -21&20 & -23&18 & -26&40 & -24&23 & -26&16 \\
-% \hline
-% 8  &   -26&25 & -22&23 & -16&17 & -36&27 & -36&22 \\
-% \hline
-% 9  &   -17&21 & -13&15 & -6&15 & -20&16 & -23&15\\ 
-% \hline
-% \end{tabular}
-% \caption{Shear.}
-% \label{tbl:test-file-format}
-% \end{table}
-\newline
-
-% \subsubsection{MT: Shear}
-% \pgfplotstableread[row sep=\\,col sep=&]{
-%     interval & Digit & Fashion & Letter \\
-%     CNN & 52.4 & 38.81 & 28.84 \\
-%     NN  & 41.8 & 41.18 & 28.11 \\
-%     NB  & 39.9 & 53.6 & 31.5 \\
-%     SVM & 54.7 & 53.8 & 34.84 \\
-%     KNN & 63.1 & 45.1 & 38.23 \\
-%     }\shear
-
-% \begin{tikzpicture}
-%     \begin{axis}[
-%             ybar,
-%             bar width=.75cm,
-%             width=\textwidth,
-%             height=.5\textwidth,
-%             legend style={at={(0.5,1)},
-%                 anchor=north,legend columns=-1},
-%             symbolic x coords={CNN,NN,NB,SVM,KNN},
-%             xtick=data,
-%             nodes near coords,
-%             nodes near coords align={vertical},
-%             ymin=0,ymax=120,
-%             ylabel={Angle},
-%         ]
-%         \addplot table[x=interval,y=Digit]{\shear};
-%         \addplot table[x=interval,y=Fashion]{\shear};
-%         \addplot table[x=interval,y=Letter]{\shear};
-%         \legend{Digit, Fashion, Letter}
-%     \end{axis}
-% \end{tikzpicture}
 \pgfplotstableread[row sep=\\,col sep=&]{
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=60,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
+\nextgroupplot[ylabel={Range of transformations},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.35\textwidth, y label style={at={(axis description cs:-0.01,0.001)}},]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearx};
@@
 
-\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-60,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\sheary}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
+\nextgroupplot[ybar, width=0.85\textwidth,height=.35\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\sheary}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms},x label style={at={(axis description cs:0.5,-0.1)},anchor=north}]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\sheary};
@@
 \end{figure}
-For the Shearing property, the convolutional neural-network is the most robust. The Fashion-MNIST and EMNIST datasets have Naive Bayes and KNN as the most robust algorithm respectively.
-% \subsection{ShiftX}
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
-%     \hline
-%      & \multicolumn{2}{c}{\textbf{CNN}} &  \multicolumn{2}{|c|}{\textbf{NN}} &\multicolumn{2}{c}{\textbf{NB}} & \multicolumn{2}{|c|}{\textbf{SVM}} & \multicolumn{2}{c|}{\textbf{kNN}} \\
-%     \hline
-%     Digit  &   Start & End & Start & End & Start & End & Start & End & Start & End \\
-%     \hline
-%     0  &   -5&4 & -3&3 & -4&3 & -4&3 & -4&4 \\
-%     \hline
-%         \multirow{3}{*}{1}
-%             &-50&-29 & -50&-38 &  \multirow{3}{*}{-2}&\multirow{3}{*}{2} & -50&-28 & -50&-25\\
-%             &-5&5 & -2&1 & & & -6&4 & -9&11\\
-%             &32&49 & 40&49  & & & 28&49 & 27&49\\
-%     \hline
-%     \multirow{2}{*}{2}  
-%         &   \multirow{2}{*}{-7}&\multirow{2}{*}{7}  &  \multirow{2}{*}{-5}&\multirow{2}{*}{6}  &  -41&-25   &  \multirow{2}{*}{-5}&\multirow{2}{*}{8} & \multirow{2}{*}{-5}&\multirow{2}{*}{11}\\
-%         & & &   & & -12&6   & & & &\\          
-%     \hline
-%     3  &   -6&3 & -7&1 & -7&0 & -7&2 & -8&4  \\
-%     \hline
-%     4  &   -7&6 & -4&4 & -5&5 & -4&5 & -5&4 \\
-%     \hline
-%     5  &   -5&8 & -2&7 & -2&21 & -3&9 & -5&13 \\
-%     \hline
-%     6  &   -5&8 & -4&4 & -3&3 & -5&5 & -5&5 \\
-%     \hline
-%     7  &   -5&6 & -6&2 & -4&2 & -7&4 & -11&4 \\
-%     \hline
-%     8  &   -4&5 & -2&4 & -1&5 & -3&4 & -3&6 \\
-%     \hline
-%     9  &   -5&5 & -4&2 & -2&2 & -4&3 & -3&3 \\ 
-%     \hline
-% \end{tabular}
-% \caption{ShiftX.}
-% \label{tbl:test-file-format}
-% \end{table}
-\newline
 
-% \subsubsection{MT: ShiftX}
-% \pgfplotstableread[row sep=\\,col sep=&]{
-%     interval & Digit & Fashion & Letter \\
-%     CNN & 11.2 & 5.166666666666667 & 2.892857142857143 \\ 
-%     NN & 6.9 & 8.615384615384615 & 2.3214285714285716 \\
-%     NB & 8.727272727272727 & 18.0 & 2.5454545454545454 \\
-%     SVM & 8.545454545454545 & 7.3076923076923075 & 3.0 \\
-%     KNN & 10.416666666666666 & 6.6 & 3.75 \\
-%     }\shiftX
-
-% \begin{tikzpicture}
-%     \begin{axis}[
-%             ybar,
-%             bar width=.75cm,
-%             width=\textwidth,
-%             height=.5\textwidth,
-%             legend style={at={(0.5,1)},
-%                 anchor=north,legend columns=-1},
-%             symbolic x coords={CNN,NN,NB,SVM,KNN},
-%             xtick=data,
-%             nodes near coords,
-%             nodes near coords align={vertical},
-%             ymin=0,ymax=50,
-%             ylabel={Pixels},
-%         ]
-%         \addplot table[x=interval,y=Digit]{\shiftX};
-%         \addplot table[x=interval,y=Fashion]{\shiftX};
-%         \addplot table[x=interval,y=Letter]{\shiftX};
-%         \legend{Digit, Fashion, Letter}
-%     \end{axis}
-% \end{tikzpicture}
 \pgfplotstableread[row sep=\\,col sep=&]{
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=10,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.3\textwidth,]%ytick=\empty]
+\nextgroupplot[ylabel={Range of transformations},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=10,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.35\textwidth, y label style={at={(axis description cs:-0.01,0.001)}},]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearxX};
@@
 
-\nextgroupplot[ybar, width=0.85\textwidth,height=.3\textwidth, bar width=.2cm,yshift=1cm,ymin=-10,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shearxY}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west}]
+\nextgroupplot[ybar, width=0.85\textwidth,height=.35\textwidth, bar width=.2cm,yshift=1cm,ymin=-10,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shearxY}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms},x label style={at={(axis description cs:0.5,-0.1)},anchor=north}]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearxY};
@@
 
-On average the length of the bars for ShiftX metamorphic property is much lower than rotation, shearing, or, shading.
-This means that the algorithms are much less robust when the images are shifted in the direction of X axis.
-Among the algorithms we implemented, CNN is the most robust on MNIST-digit dataset, Naive Bayes on MNIST-Fashion, and, all the algorithms perform equally on the EMNIST dataset.
-
-% \subsubsection{MT: ShiftY}
-% \pgfplotstableread[row sep=\\,col sep=&]{
-%     interval & Digit & Fashion & Letter \\
-%     CNN & 6.6 & 1.4 & 2.0714285714285716 \\
-%     NN & 4.7272727272727275 & 4.076923076923077 & 2.357142857142857 \\
-%     NB & 6.0 & 8.285714285714286 & 2.5161290322580645 \\
-%     SVM & 6.8 & 4.428571428571429 & 2.357142857142857 \\
-%     KNN & 11.3 & 5.333333333333333 & 3.1379310344827585 \\
-%     }\shiftY
-
-% \newline
-% \begin{tikzpicture}
-%     \begin{axis}[
-%             ybar,
-%             bar width=.75cm,
-%             width=\textwidth,
-%             height=.5\textwidth,
-%             legend style={at={(0.5,1)},
-%                 anchor=north,legend columns=-1},
-%             symbolic x coords={CNN,NN,NB,SVM,KNN},
-%             xtick=data,
-%             nodes near coords,
-%             nodes near coords align={vertical},
-%             ymin=0,ymax=50,
-%             ylabel={Pixels},
-%         ]
-%         \addplot table[x=interval,y=Digit]{\shiftY};
-%         \addplot table[x=interval,y=Fashion]{\shiftY};
-%         \addplot table[x=interval,y=Letter]{\shiftY};
-%         \legend{Digit, Fashion, Letter}
-%     \end{axis}
-% \end{tikzpicture}
 \pgfplotstableread[row sep=\\,col sep=&]{
@@
 \begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
-\nextgroupplot[ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=10,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.3\textwidth,]%ytick=\empty]
+\nextgroupplot[ylabel={Range of transformations},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=10,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.83\textwidth,height=.35\textwidth, y label style={at={(axis description cs:-0.01,0.001)}},]%ytick=\empty]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearyX};
@@
 
-\nextgroupplot[ybar, width=0.85\textwidth,height=.3\textwidth, bar width=.2cm,yshift=1cm,ymin=-10,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shearyY}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},]
+\nextgroupplot[ybar, width=0.83\textwidth,height=.35\textwidth, bar width=.2cm,yshift=1cm,ymin=-10,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\shearyY}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms},x label style={at={(axis description cs:0.5,-0.1)},anchor=north}]
 \addplot[fill=blue,draw=black] table[x=Mx,y=My]{\shearyY};
@@
 \end{figure}
-Just like the ShiftX property, the length of bars here are much smaller than others.
-Thus al here we find that k-NN is also more robust than the rest of the algorithms we tested when applied to MNIST-digit and EMNIST-letter dataset.
-While, Naive Bayes is more robust when applied to MNIST-Fashion dataset.
